### 2018-08-01 analysis/01_analysis.Rmd

---
title: "Discon analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data preprocessing}
# Data pre-processing
```

# Do proportion of choices match the frequency in the distribution

```{r plot1}

```

# Does the framing influence the match between choice and distribution

```{r plot 2}

```

### 2018-08-02 experiments/discon.js
added code for new novel items

@@ -101,11 +101,11 @@ function getKeys(obj){
 
 showSlide("instructions");
 
-var slides = [1, 2, "choice"]
+var slides = [1, 2, 3, 4, 5, 6, "choice"]
 
 var trials = [0, 1, 2, 3, 4, 5]
 
-var trialType = shuffle([0, 1])
+var trialType = shuffle(["preference", "statistical"])
 
 var currTrialType = trialType[0];
 
@@ -151,6 +151,20 @@ var novelItems = shuffleProperties(allNovel);
 
 var categoryNames = getKeys(familiarItems);
 
+var trackRepeats = new Map();
+
+for (i=0; i < categoryNames.length; i++) {
+    trackRepeats.set(categoryNames[i], 3); 
+}
+
+function checkCategory (category) {
+    if (trackRepeats.get(category) > 0) {
+        return true;
+    } else {
+        return false;
+    }
+}
+
 //names of all possible targets, also orderedTargetNames1
 var posTargetNames = shuffle(categoryNames);
 
@@ -169,13 +183,15 @@ var posTargetNames2 = posTargetNames.slice();
 var orderedTargetNames2 = new Array();
 
 for (nTarget = 0; nTarget < posTargetNames.length; nTarget++) {
-    if(posTargetNames2[0] != posTargetNames[nTarget]) {
+    if(posTargetNames2[0] != posTargetNames[nTarget] 
+       && checkCategory(posTargetNames2[0])) {
         targetsF2.push(familiarItems[posTargetNames2[0]].slice());
         shuffle(targetsF2[nTarget]);
         orderedTargetNames2.push(posTargetNames2[0]);
         //remove first category
         posTargetNames2.splice(0, 1);
         posTargetNames2 = shuffle(posTargetNames2);
+        trackRepeats[posTargetNames2[0]]--;
     } else {
         nTarget--;
         posTargetNames2 = shuffle(posTargetNames2);
@@ -190,13 +206,15 @@ var orderedTargetNames3 = new Array();
 
 for (nTarget = 0; nTarget < posTargetNames.length; nTarget++) {
     if(posTargetNames3[0] != posTargetNames[nTarget] 
-       && posTargetNames3[0] != orderedTargetNames2[nTarget]){
+       && posTargetNames3[0] != orderedTargetNames2[nTarget]
+       && checkCategory(posTargetNames3[0])){
         targetsF3.push(familiarItems[posTargetNames3[0]].slice());
[…]

### 2018-08-02 experiments/discon.js
preload background

@@ -6,6 +6,22 @@ for (i = 0; i < preloadItems.length; i++) {
     images[i].src = "images/" + preloadItems[i] + ".png";
 }
 
+var backgroundImages = new Array();
+for (i = 1; i <= 10; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back" + i + ".jpg";
+}
+
+$("#button").click(function() {
+    //disable accept button if in turk preview mode
+    if (turk.previewMode) {
+      showSlide("instructions");
+      alert("Please accept HIT to view");
+    } else {
+      showSlide('introAll')
+    }
+});
+
 function showSlide(id) {
     // Hide all slides
     $(".slide").hide();
@@ -412,11 +428,11 @@ var experiment = {
 
             data = {
                 experiment: "distribution",
-                phase: "training",
-                agent: trainingAgents[trials[0]],
-                slide: experiment.slides[0],
                 trial: trials[0] + 1,
                 trialType: currTrialType,
+                agent: trainingAgents[trials[0]],
+                phase: "training",
+                slide: experiment.slides[0],
 
                 distribution: posDist[trials[0]],
                 target1: trialTargets[trials[0]][0],
@@ -543,12 +559,12 @@ var experiment = {
 
             data = {
                 experiment: "distribution",
-                phase: "test",
-                agent: trainingAgents[trials[0]],
-                slide: experiment.slides[0],
                 trial: trials[0] + 1,
                 trialType: currTrialType,
-
+                agent: trainingAgents[trials[0]],
+                phase: "test",
+                slide: experiment.slides[0],
+                
                 distribution: posDist[trials[0]],
                 target1: trialTargets[trials[0]][0],
                 target2: trialTargets[trials[0]][1],
@@ -605,82 +621,4 @@ var experiment = {
 
         $(".agent_transition").click(experiment.intro); 
     },
-
-    trainingDot : function () {
-        function createDot(dotx, doty, i) {
-            var dots = [1, 2, 3, 4, 5];
-
-            var dot = document.createElement("img");
-            dot.setAttribute("class", "dot");
-            dot.id = "dot_" + dots[i];
-            dot.src = "dots/dot_" + dots[i] + ".jpg";
-
-            var x = Math.floor(Math.random() * 850);
-            var y = Math.floor(Math.random() * 550);
-
-            var invalid = "true";
-            //make sure dots do not overlap
-            while (true) {  
-                invalid = "true";
[…]

### 2018-08-02 experiments/discon.js
fix unending loop error

@@ -1,4 +1,4 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "grapes", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bottle", "cup", "bowl", "box", "plate", "glass", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoes", "socks", "pants","shirt", "jacket", "dress", "N1_vehicles", "N1_fruits", "N1_mammals", "N1_containers", "N1_furniture", "N1_clothes", "N2_vehicles", "N2_fruits", "N2_mammals", "N2_containers", "N2_furniture", "N2_clothes", "N3_vehicles", "N3_fruits", "N3_mammals", "N3_containers", "N3_furniture", "N3_clothes"];
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "grapes", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bottle", "cup", "bowl", "box", "plate", "glass", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoes", "socks", "pants","shirt", "jacket", "dress", "N1_vehicles", "N1_fruits", "N1_mammals", "N1_containers", "N1_furniture", "N1_clothes", "N2_vehicles", "N2_fruits", "N2_mammals", "N2_containers", "N2_furniture", "N2_clothes", "N3_vehicles", "N3_fruits", "N3_mammals", "N3_containers", "N3_furniture", "N3_clothes", "bread", "tv", "pencil"];
 
 var images = new Array();
 for (i = 0; i < preloadItems.length; i++) {
@@ -198,20 +198,43 @@ var posTargetNames2 = posTargetNames.slice();
 
 var orderedTargetNames2 = new Array();
 
-for (nTarget = 0; nTarget < posTargetNames.length; nTarget++) {
-    if(posTargetNames2[0] != posTargetNames[nTarget] 
-       && checkCategory(posTargetNames2[0])) {
-        targetsF2.push(familiarItems[posTargetNames2[0]].slice());
-        shuffle(targetsF2[nTarget]);
-        orderedTargetNames2.push(posTargetNames2[0]);
-        //remove first category
-        posTargetNames2.splice(0, 1);
-        posTargetNames2 = shuffle(posTargetNames2);
[…]

### 2018-08-02 experiments/discon.js
add debrief on last slide

@@ -654,7 +654,7 @@ var experiment = {
         experiment.trials.shift();
 
         if (experiment.trials.length == 0) {
-            setTimeout(function() { turk.submit(experiment) }, 0);
+            setTimeout(function() { turk.submit(experiment) }, 5000);
             showSlide("finished");
             return;
         }

### 2018-08-02 analysis/01_analysis.Rmd
adding code for data preprocessing

@@
 knitr::opts_chunk$set(echo = TRUE)
+
+library(jsonlite)
+library(tidyr)
+library(stringr)
+library(dplyr)
 ```
@@
 # Data pre-processing
+
+files <- dir("sandbox-results")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("sandbox-results/",f,sep="")
+  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  id <- as_data_frame(jd$answers$data$data) %>%
+    mutate(workerid = jd$WorkerId)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+raw_data
 ```

### 2018-08-03 analysis/01_analysis.Rmd
analysis file, code changes: pick recorded correctly, keep track of category of picked item in input slides, keep track of the category of the final input slide

--- 2018-08-01 analysis/01_analysis.Rmd
@@
 knitr::opts_chunk$set(echo = TRUE)
+
+library(tidyverse)
+library(ggplot2)
+library(jsonlite)
+library(tidyr)
+library(stringr)
+library(dplyr)
+library(ggthemes)
+library(langcog)
 ```
@@
 # Data pre-processing
+
+files <- dir("../../pilot_1_raw_data/production-results")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("../../pilot_1_raw_data/production-results/",f,sep="")
+  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  id <- as_data_frame(jd$answers$data$data) %>%
+    mutate(workerid = jd$WorkerId)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+data <- raw_data %>%
+  mutate(correct_target3 = ifelse(correct_target1 == 0 & correct_target2 == 0, 1, 0)) %>%
+  mutate(distribution = as.character(distribution),
+         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
+         pick = ifelse(pickPos == "item_l", item_l, ifelse(pickPos == "item_r", item_r, ifelse(pickPos=="item_m", item_m, NA))),
+         correct_item = ifelse(pick == correctItem, 1, 0),
+         pickTest = substr(pick, 4, length(pick)),
+         correct_target1 = ifelse(pickTest == target1, 1, 0),
+         correct_target2 = ifelse(pickTest == target2, 1, 0),
+         correct_target3 = ifelse(pickTest == target3, 1, 0))
+
+write.csv(data, file="../data/pilot.data.csv")
+
+# data <- read_csv(file="../data/pilot.data.csv")
 ```
 
+```{r sanity checks}
+data %>%
+  filter(phase == 'training') %>%
+  group_by(workerid) %>%
+  summarise(correct = mean(correct_item))
+
+drop <- data %>%
+  filter(phase == 'training') %>%
+  group_by(workerid) %>%
+  summarise(correct = mean(correct_item)) %>%
+  filter(correct < 0.83) %>%
+  pull(workerid)
+
+data <- data %>%
+  filter(!workerid %in% drop)
+```
+
+```{r}
+data %>%
+  filter(phase == "test", distribution == "c(4, 2, 0)") %>%
+  group_by(pickTest) %>%
+  summarise(mean = mean(correct_target1))
+```
 # Do proportion of choices match the frequency in the distribution
@@
 ```{r plot1}
+plot1 <- data %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, workerid) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -workerid) %>%
+  group_by(distribution, item) %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot(plot1,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  facet_grid(~distribution) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few()
 
@@
 ```{r plot 2}
+plot2 <- data %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, workerid, trialType) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
+  group_by(distribution, trialType, item) %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot(plot2,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  facet_grid(trialType~distribution) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few()
 
 ```
+
+# Comparing the last input with the picked object by distribution
+
+```{r plot 2}
+a <- data %>%
+  filter(slide == 6) %>%
+  select(workerid, pick)
+
+b <- data %>%
+  filter(slide == "choice") %>%
+  select(workerid, distribution, pickTest, correct_target1)
+
+b$pickSlide6 = a$pick
+
+b <- b %>%
+  filter(distribution != "c(6, 0, 0)", correct_target1 == 1) %>%
+  arrange(distribution) %>%
+  group_by(distribution) %>%
+  summarise(n = length(distribution))
+
+# 30/59 trials picking the same category as the last input slide.
+# 24/33 for 4, 2, 0
+# 7/26 for 2, 2, 2
+
+```

### 2018-08-03 experiments/discon.js

@@ -15,10 +15,10 @@ for (i = 1; i <= 10; i++) {
 $("#button").click(function() {
     //disable accept button if in turk preview mode
     if (turk.previewMode) {
-      showSlide("instructions");
-      alert("Please accept HIT to view");
+        showSlide("instructions");
+        alert("Please accept HIT to view");
     } else {
-      showSlide('introAll')
+        showSlide('introAll')
     }
 });
 
@@ -332,6 +332,15 @@ for (var m=0; m < trials.length; m++) {
     trainingAgents.push(posAgents[m]);
 }
 
+function findCategory (pick) {
+    for (var i = 0; i < categoryNames.length; i++) {
+        var categoryArray = categoryNames[i]+"F";
+        if (eval(categoryArray).includes(pick))  {
+            return categoryNames[i];
+        }
+    }
+}
+
 var experiment = {
     slides: slides.slice(),
     trials: trials,
@@ -344,7 +353,7 @@ var experiment = {
     trialTargets: trialTargets,
     trialFamiliarItems: trialFamiliarItems,
     novelItems: novelItems,
-    
+
     novelWords: novelWords, 
 
     posDist: posDist,
@@ -354,6 +363,8 @@ var experiment = {
     backgrounds: backgrounds,
 
     position: [], 
+
+    lastInputCat: "",
 
     data: [], 
 
@@ -453,16 +464,17 @@ var experiment = {
         //        sourceSound("sounds/" + correctItem + ".mp3");
         //        playSound();
 
+
         $(".item").click(function() {
             var clickedItem = event.target;
 
             var pickId = event.target.id;
 
-            if(pickId == "item_r") {
+            if(pickId == "item_l") {
                 var pick = experiment.position[0];
             } else if(pickId == "item_m") {
                 var pick = experiment.position[1];
-            } else if (pickId == "item_l") {
+            } else if (pickId == "item_r") {
                 var pick = experiment.position[2];
             }
 
@@ -471,6 +483,11 @@ var experiment = {
                 var correct_item = 1;
             } else {
                 var correct_item = 0;
+            }
+            
+            // stores category of the final input slide
+            if (experiment.slides[0] == 6) {
+                experiment.lastInputCat = findCategory(pick);
             }
 
             $(".item").unbind("click");
@@ -496,6 +513,7 @@ var experiment = {
                 correctItem: correctItem,
                 pick: pick,
                 pickPos: pickId,
+                pickCat: findCategory(pick),
[…]

### 2018-08-07 experiments/discon.js
new categories: instruments, buildings. New novel items

@@ -1,4 +1,4 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "grapes", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bottle", "cup", "bowl", "box", "plate", "glass", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoes", "socks", "pants","shirt", "jacket", "dress", "N1_vehicles", "N1_fruits", "N1_mammals", "N1_containers", "N1_furniture", "N1_clothes", "N2_vehicles", "N2_fruits", "N2_mammals", "N2_containers", "N2_furniture", "N2_clothes", "N3_vehicles", "N3_fruits", "N3_mammals", "N3_containers", "N3_furniture", "N3_clothes", "bread", "tv", "pencil"];
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "grapes", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bottle", "cup", "bowl", "box", "plate", "glass", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoes", "socks", "pants","shirt", "jacket", "dress", "drum", "flute", "guitar", "piano", "trumpet", "violin", "castle", "church", "factory", "house", "igloo", "tent", "N1_vehicles", "N1_fruits", "N1_mammals", "N1_containers", "N1_furniture", "N1_clothes", "N2_vehicles", "N2_fruits", "N2_mammals", "N2_containers", "N2_furniture", "N2_clothes", "N3_vehicles", "N3_fruits", "N3_mammals", "N3_containers", "N3_furniture", "N3_clothes", "bread", "tv", "pencil"];
 
 var images = new Array();
 for (i = 0; i < preloadItems.length; i++) {
@@ -130,33 +130,37 @@ var backgrounds = shuffle([1, 2, 3, 4, 5, 6, 7, 8, 9, 10])
 var vehiclesF = shuffle(["car", "truck", "train", "bus", "airplane", "boat"])
 var fruitsF = shuffle(["strawberry", "apple", "banana", "grapes", "orange", "melon"])
 var mammalsF = shuffle(["dog", "cat", "horse", "bear", "cow", "monkey"])
-var containersF = shuffle(["bottle", "cup", "bowl", "box", "plate", "glass"])
[…]

### 2018-08-08 analysis/01_analysis.Rmd
new categories: instruments, buildings. New novel items
shuffle trial sets

@@
   filter(phase == 'test') %>%
-  group_by(distribution, workerid) %>%
+  group_by(distribution, target1, workerid) %>%
   summarise(correct = mean(correct_target1),
@@
             correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid) %>%
-  group_by(distribution, item) %>%
+  gather(item, prop_correct, -distribution, -workerid, -target1) %>%
+  group_by(distribution, target1, item) %>%
   multi_boot_standard(col = "prop_correct")
@@
   geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  facet_grid(~distribution) +
+#  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  facet_grid(target1~distribution) +
   geom_hline(yintercept = 1/3, lty=2) +
@@
 ```{r plot 2}
+plot2 <- data %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, workerid, trialType) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
+  arrange(workerid)
+
+ # group_by(distribution, trialType, item) %>%
+ # multi_boot_standard(col = "prop_correct")
+
+ggplot() + 
+  geom_jitter(data = plot2, 
+              aes(x = item, y=prop_correct, fill=item, col=trialType),
+              height = 0.1,
+              width = 0.1) +
+  facet_grid(trialType~distribution) +
+  theme(legend.position="none")
+
 plot2 <- data %>%
@@
 ```
+
+```{r}
+data %>%
+  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
+  group_by(pick) %>%
+  summarise(n = length(correct_target1),
+            mean = mean(correct_target1)) %>%
+  arrange(mean)
+```

### 2018-08-08 experiments/discon.js

@@ -1,4 +1,4 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "grapes", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bottle", "cup", "bowl", "box", "plate", "glass", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoes", "socks", "pants","shirt", "jacket", "dress", "drum", "flute", "guitar", "piano", "trumpet", "violin", "castle", "church", "factory", "house", "igloo", "tent", "N1_vehicles", "N1_fruits", "N1_mammals", "N1_containers", "N1_furniture", "N1_clothes", "N2_vehicles", "N2_fruits", "N2_mammals", "N2_containers", "N2_furniture", "N2_clothes", "N3_vehicles", "N3_fruits", "N3_mammals", "N3_containers", "N3_furniture", "N3_clothes", "bread", "tv", "pencil"];
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "grapes", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoes", "socks", "pants","shirt", "jacket", "dress", "drum", "flute", "guitar", "piano", "trumpet", "violin", "castle", "church", "factory", "house", "igloo", "tent", "N1_vehicles", "N1_fruits", "N1_mammals", "N1_containers", "N1_furniture", "N1_clothes", "N2_vehicles", "N2_fruits", "N2_mammals", "N2_containers", "N2_furniture", "N2_clothes", "N3_vehicles", "N3_fruits", "N3_mammals", "N3_containers", "N3_furniture", "N3_clothes", "bread", "tv", "pencil"];
 
 var images = new Array();
 for (i = 0; i < preloadItems.length; i++) {
@@ -198,12 +198,13 @@ for (var nTarget = 0; nTarget < trials.length; nTarget++) {
 
 var targetsF2 = new Array();
 
-var posTargetNames2 = shuffle(posTargetNames.slice());
+var posTargetNames2 = posTargetNames.slice();
 
 var orderedTargetNames2 = new Array();
 
 function orderTargetsF2 (posTargetNames2, posTargetNames) {
     var tempPosTargetNames2 = posTargetNames2.slice();
[…]

### 2018-08-10 analysis/01_analysis.Rmd
new experiment: remove framing, use anaphora and familiar items for test slides

@@
   filter(phase == 'test') %>%
-  group_by(distribution, target1, workerid) %>%
+  group_by(distribution, workerid) %>%
   summarise(correct = mean(correct_target1),
@@
             correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -target1) %>%
-  group_by(distribution, target1, item) %>%
+  gather(item, prop_correct, -distribution, -workerid) %>%
+  group_by(distribution, item) %>%
   multi_boot_standard(col = "prop_correct")
@@
   geom_bar(stat='identity') +
-#  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  facet_grid(target1~distribution) +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("correct", "correct2", "correct3"),
+                       labels = c("most frequent", "second most frequent", "least frequent"))+
+  facet_grid(~distribution, 
+             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
   geom_hline(yintercept = 1/3, lty=2) +
   ylim(0, 1) +
-  theme_few()
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
 
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  facet_grid(trialType~distribution) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("correct", "correct2", "correct3"),
+                       labels = c("most frequent", "second most frequent", "least frequent"))+
+  facet_grid(trialType~distribution, 
+             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
   geom_hline(yintercept = 1/3, lty=2) +
   ylim(0, 1) +
-  theme_few()
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
 

### 2018-08-10 experiments/discon_framing.js

@@ -1,4 +1,4 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "grapes", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoes", "socks", "pants","shirt", "jacket", "dress", "drum", "flute", "guitar", "piano", "trumpet", "violin", "F1_vehicles", "F1_fruits", "F1_mammals", "F1_instruments", "F1_furniture", "F1_clothes", "F2_vehicles", "F2_fruits", "F2_mammals", "F2_instruments", "F2_furniture", "F2_clothes", "F3_vehicles", "F3_fruits", "F3_mammals", "F3_instruments", "F3_furniture", "F3_clothes", "bread", "tv", "pencil"];
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "grapes", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoes", "socks", "pants","shirt", "jacket", "dress", "drum", "flute", "guitar", "piano", "trumpet", "violin", "castle", "church", "factory", "house", "igloo", "tent", "N1_vehicles", "N1_fruits", "N1_mammals", "N1_containers", "N1_furniture", "N1_clothes", "N2_vehicles", "N2_fruits", "N2_mammals", "N2_containers", "N2_furniture", "N2_clothes", "N3_vehicles", "N3_fruits", "N3_mammals", "N3_containers", "N3_furniture", "N3_clothes", "bread", "tv", "pencil"];
 
 var images = new Array();
 for (i = 0; i < preloadItems.length; i++) {
@@ -7,9 +7,9 @@ for (i = 0; i < preloadItems.length; i++) {
 }
 
 var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
+for (i = 1; i <= 10; i++) {
     backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+    backgroundImages[i].src = "images/backgrounds/back" + i + ".jpg";
 }
 
 $("#button").click(function() {
[…]

### 2018-08-10 experiments/discon.js
fix trial shuffle problem

@@ -249,10 +249,10 @@ function orderTargetsF3 (posTargetNames3, orderedTargetNames2, posTargetNames) {
 
 function orderTargetsF3Helper (tempPosTargetNames3, tempPosTargetNames2, tempPosTargetNames, posTargetNames3, orderedTargetNames2, posTargetNames) {
     if(tempPosTargetNames3.length == 1) {
-        if (tempPosTargetNames2[0] != tempPosTargetNames[0]
+        if (tempPosTargetNames3[0] != tempPosTargetNames[0]
             && tempPosTargetNames3[0] != tempPosTargetNames2[0]
             && checkCategory(tempPosTargetNames3[0])) {
-            targetsF2.push(shuffle(familiarItems[tempPosTargetNames3[0]].slice()));
+            targetsF3.push(shuffle(familiarItems[tempPosTargetNames3[0]].slice()));
             orderedTargetNames3.push(tempPosTargetNames3[0]);
             trackRepeats[tempPosTargetNames3[0]]--;
         } else {
@@ -303,6 +303,18 @@ for (nTrial = 0; nTrial < trials.length; nTrial++) {
     familiarItemsMap.set(trialTargets[nTrial][2], targetsF3[nTrial]);
     trialFamiliarItems.push(familiarItemsMap);
 }
+
+// array contains 6 items
+function shuffleByIndex(array) {
+    for (var i = 0; i < shuffle(trials.slice()); i++) {
+        var temp = array[i];
+        array[i] = array[shuffleIndex[i]];
+        array[shuffleIndex[i]] = temp;
+    }
+}
+
+shuffleByIndex(trialTargets);
+shuffleByIndex(trialFamiliarItems);
 
 var posDist = shuffle([[4, 2, 0], [6, 0, 0], [2, 2, 2], [4, 2, 0], [6, 0, 0], [2, 2, 2]]);
 

### 2018-08-10 experiments/discon.js
no longer separating between items for input and novel slides

@@ -1,4 +1,4 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "grapes", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoes", "socks", "pants","shirt", "jacket", "dress", "drum", "flute", "guitar", "piano", "trumpet", "violin", "F1_vehicles", "F1_fruits", "F1_mammals", "F1_instruments", "F1_furniture", "F1_clothes", "F2_vehicles", "F2_fruits", "F2_mammals", "F2_instruments", "F2_furniture", "F2_clothes", "F3_vehicles", "F3_fruits", "F3_mammals", "F3_instruments", "F3_furniture", "F3_clothes", "bread", "tv", "pencil"];
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "grapes", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoes", "socks", "pants", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
 
 var images = new Array();
 for (i = 0; i < preloadItems.length; i++) {
@@ -123,21 +123,12 @@ var trials = [0, 1, 2, 3, 4, 5]
 
 var backgrounds = shuffle([1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]);
 
-//familiar arrays
-var vehiclesF = shuffle(["car", "truck", "train", "bus", "airplane", "boat"])
-var fruitsF = shuffle(["strawberry", "apple", "banana", "grapes", "orange", "melon"])
-var mammalsF = shuffle(["dog", "cat", "horse", "bear", "cow", "monkey"])
-var furnitureF = shuffle(["bed", "chair", "table", "closet", "drawer", "sofa", "lamp"])
-var clothesF = shuffle(["shoes", "socks", "pants","shirt", "jacket", "dress"])
-var instrumentsF = shuffle(["drum", "flute", "guitar", "piano", "trumpet", "violin"])
-
-//training arrays
[…]

### 2018-08-10 experiments/discon.js
change background between slides

@@ -341,7 +341,7 @@ var experiment = {
     trainingDist: trainingDist,
 
     trainingAgents: trainingAgents,
-    backgrounds: backgrounds,
+    backgrounds: backgrounds.slice(),
 
     position: [], 
 
@@ -351,12 +351,12 @@ var experiment = {
 
     introAll: function() {
         showSlide("introAll");
-        document.getElementById("text_introAll").innerHTML = "You're visiting the house of these little animals. They will introduce you to the things they have at home. Your task is to click on the things they have at home.";
+        document.getElementById("text_introAll").innerHTML = "You're visiting the house of these little animals. They will introduce you to the kinds of things they have at home. Your task is to click on the things they talk about.";
         document.getElementById("text_introAll_2").innerHTML = "To move forward within the experiment, press the \"Next\" button. Press below to start.";
     },
 
     intro: function () {
-        background2("images/backgrounds/back_int" + backgrounds[0] + ".jpg");
+        background2("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
 
         showSlide("transition");
 
@@ -383,7 +383,7 @@ var experiment = {
 
         experiment.position = shuffle([experiment.targetsF[0][0], experiment.targetsF2[0][0], experiment.targetsF3[0][0]]);
 
-        background("images/backgrounds/back_int" + backgrounds[0] + ".jpg");
+        background("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
 
         showSlide("input");
 
@@ -405,12 +405,12 @@ var experiment = {
             showLeftItem();
             showMiddleItem();
             showRightItem();
-        }, 500);
+        }, 1000);
 
         // pause for 1.5s before "next" button appears.
         setTimeout(function() {
             document.getElementById("next-input").style.visibility = "visible";
-        }, 1000);
+        }, 1500);
     },
 
     train2 : function() {
@@ -492,11 +492,12 @@ var experiment = {
             experiment.trainingDist[trials[0]].shift();
 
             experiment.slides.shift();
+            experiment.backgrounds.shift();
 
             setTimeout(function() {
                 clickedItem.style.border = '0px';
                 experiment.train();
-            }, 1000);
+            }, 1500);
         });
     },
 
@@ -506,7 +507,7 @@ var experiment = {
         document.getElementById("next-input").style.visibility = 'hidden';
[…]

### 2018-08-14 analysis/01_analysis.Rmd
recency experiment with 5,1,0

@@
 data <- raw_data %>%
-  mutate(correct_target3 = ifelse(correct_target1 == 0 & correct_target2 == 0, 1, 0)) %>%
   mutate(distribution = as.character(distribution),
-         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
-         pick = ifelse(pickPos == "item_l", item_l, ifelse(pickPos == "item_r", item_r, ifelse(pickPos=="item_m", item_m, NA))),
-         correct_item = ifelse(pick == correctItem, 1, 0),
-         pickTest = substr(pick, 4, length(pick)),
-         correct_target1 = ifelse(pickTest == target1, 1, 0),
-         correct_target2 = ifelse(pickTest == target2, 1, 0),
-         correct_target3 = ifelse(pickTest == target3, 1, 0))
+         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))
 
-write.csv(data, file="../data/pilot.data.csv")
+ # data <- raw_data %>%
+ #  mutate(correct_target3 = ifelse(correct_target1 == 0 & correct_target2 == 0, 1, 0)) %>%
+ #  mutate(distribution = as.character(distribution),
+ #         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
+ #         pick = ifelse(pickPos == "item_l", item_l, ifelse(pickPos == "item_r", item_r, ifelse(pickPos=="item_m", item_m, NA))),
+ #         correct_item = ifelse(pick == correctItem, 1, 0),
+ #         pickTest = substr(pick, 4, length(pick)),
+ #         correct_target1 = ifelse(pickTest == target1, 1, 0),
+ #         correct_target2 = ifelse(pickTest == target2, 1, 0),
+ #         correct_target3 = ifelse(pickTest == target3, 1, 0))
+
+# write.csv(data, file="../data/pilot.data.csv")
 
@@
   filter(!workerid %in% drop)
+
 ```
 
+# Some preliminary tests
 ```{r}
-data %>%
-  filter(phase == "test", distribution == "c(4, 2, 0)") %>%
-  group_by(pickTest) %>%
-  summarise(mean = mean(correct_target1))
+data_test <- data %>% 
+  filter (phase == "test", distribution == "c(4, 2, 0)") %>%
+  summarise (lastInput = mean(same_lastInput),
+             n = length(distribution))
+#23/38 trials
+
+data_test <- data %>%
+  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
+  summarise (correct1 = mean(correct_target1))
+
+data_test <- data %>%
+  filter(phase == "test", distribution == "c(2, 2, 2)") %>%
+  summarise (lastInput = mean(same_lastInput),
+             n = length(distribution))
+# 23/38
+
+```
+
+# Salience of each category
+```{r}
+plot1 <- data %>%
+  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
+  group_by(distribution, target1) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3))
+
+plot1 <- data %>%
+  filter(phase == "test", distribution == "c(6, 0, 0)", target1 == "vehicles")
+
+# clothes: 2
+# fruits: 5
+# furniture: 10
+# instruments: 4
+# mammals: 8
+# vehicles: 9
+
+plot1 <- data %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, workerid, target1) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -workerid, -target1) %>%
+  group_by(distribution, item, target1) %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot(plot1,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("correct", "correct2", "correct3"),
+                       labels = c("most frequent", "second most frequent", "least frequent"))+
+  facet_grid(target1~distribution) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
 ```
@@
 
+```
+# How does the last item seen affect the object chosen in the anaphora case? 
+```{r}
+plot2 <- data %>%
+  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
+  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
+  group_by (distribution, workerid) %>%
+  summarise (lastInput = mean(same_lastInput),
+             n = n()) %>% 
+  multi_boot_standard(col = "lastInput")
+
+plot2 <- data %>%
+  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
+  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
+  group_by (distribution, workerid) %>%
+  summarise (lastInput = mean(same_lastInput),
+             n = n()) %>% 
+  multi_boot_standard(col = "lastInput")
+
+ggplot(plot2,
+       aes(x = distribution, y = mean, fill = distribution)) +
+  geom_bar(stat='identity', width = 0.3) +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few()
+```
+# Does the graded distribution come through in cases where the last input does not affect the object choice?
+```{r}
+plot3 <- data %>%
+  filter(phase == "test", distribution == "c(4, 2, 0)", same_lastInput == 0) %>%
+  group_by(distribution, workerid) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -workerid) %>%
+  group_by(distribution, item) %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot(plot3,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("correct", "correct2", "correct3"),
+                       labels = c("most frequent", "second most frequent", "least frequent"))+
+  facet_grid(~distribution, 
+             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
 ```
@@
 
-```{r plot 2}
+```{r}
 a <- data %>%
@@
   filter(slide == "choice") %>%
-  select(workerid, distribution, pickTest, correct_target1)
+  select(workerid, distribution, pickCat, correct_target1)
 
@@
 ```
-
-```{r}
-data %>%
-  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
-  group_by(pick) %>%
-  summarise(n = length(correct_target1),
-            mean = mean(correct_target1)) %>%
-  arrange(mean)
-```

### 2018-08-14 experiments/discon_recency.js

@@ -1,0 +1,665 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "grapes", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoes", "socks", "pants", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+$("#button").click(function() {
+    //disable accept button if in turk preview mode
+    if (turk.previewMode) {
+        showSlide("instructions");
+        alert("Please accept HIT to view");
+    } else {
+        showSlide('introAll')
+    }
+});
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
+    $("#"+id+"_"+orient).show();
+}
+
+function sourceRightItem(a) {
+    document.getElementById("item_r").src=a;
+}
+
+function showRightItem() {
+    document.getElementById('item_r').style.visibility='visible';
+}
+
+function hideRightItem() {
+    document.getElementById('item_r').style.visibility='hidden';
+}
+
+function sourceMiddleItem(a) {
+    document.getElementById("item_m").src=a;
+}
+
+function showMiddleItem() {
+    document.getElementById('item_m').style.visibility='visible';
[…]

### 2018-08-14 experiments/discon_recency.js
track worker ip and geo

@@ -334,6 +334,11 @@ function findCategory (pick) {
     }
 }
 
+// get client’s ip information and store in app object
+$.getJSON('https://ipapi.co/json/', function(data) {
+ ip = JSON.stringify(data, null, 2);
+});
+
 var experiment = {
     slides: slides.slice(),
     trials: trials,
@@ -468,7 +473,7 @@ var experiment = {
             clickedItem.style.border = '5px solid blue';
 
             data = {
-                experiment: "distribution",
+                experiment: "recency",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],
@@ -488,7 +493,9 @@ var experiment = {
                 pick: pick,
                 pickPos: pickId,
                 pickCat: findCategory(pick),
-                correct_item: correct_item
+                correct_item: correct_item,
+                
+                workerIp: ip
             }
 
             experiment.data.push(data);
@@ -596,7 +603,7 @@ var experiment = {
             clickedItem.style.border = '5px solid blue';
 
             data = {
-                experiment: "distribution",
+                experiment: "recency",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],
@@ -621,7 +628,9 @@ var experiment = {
                 correct_target3: correct_target3,
 
                 lastInputCat: experiment.lastInputCat,
-                same_lastInput: same_lastInput
+                same_lastInput: same_lastInput,
+                
+                workerIp: ip
             }
             experiment.data.push(data);
 

### 2018-08-14 experiments/discon_recency.js
record and submit worker IP

@@ -472,6 +472,8 @@ var experiment = {
             $(".item").unbind("click");
             clickedItem.style.border = '5px solid blue';
 
+            workerIp = JSON.parse(ip);
+            
             data = {
                 experiment: "recency",
                 trial: trials[0] + 1,
@@ -495,7 +497,7 @@ var experiment = {
                 pickCat: findCategory(pick),
                 correct_item: correct_item,
                 
-                workerIp: ip
+                workerIp: workerIp.ip
             }
 
             experiment.data.push(data);
@@ -602,6 +604,8 @@ var experiment = {
             $(".item").unbind("click");
             clickedItem.style.border = '5px solid blue';
 
+            workerIp = JSON.parse(ip);
+            
             data = {
                 experiment: "recency",
                 trial: trials[0] + 1,
@@ -630,7 +634,7 @@ var experiment = {
                 lastInputCat: experiment.lastInputCat,
                 same_lastInput: same_lastInput,
                 
-                workerIp: ip
+                workerIp: workerIp.ip
             }
             experiment.data.push(data);
 

### 2018-08-15 analysis/01_analysis.Rmd
new recency experiments

@@
 
+#Recency data
+```{r}
+files <- dir("../../recency_raw_data/production-results")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("../../recency_raw_data/production-results/",f,sep="")
+  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  id <- as_data_frame(jd$answers$data$data) %>%
+    mutate(workerid = jd$WorkerId)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+data <- raw_data %>%
+  mutate(distribution = as.character(distribution),
+         distribution = factor(distribution, levels = c("c(5, 1, 0)", "c(2, 2, 2)")))
+data$workerIp
+
+```
+
+#Pilot 1 data
 ```{r data preprocessing}
@@
   facet_grid(~distribution, 
-             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
+             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
   geom_hline(yintercept = 1/3, lty=2) +

### 2018-08-15 experiments/discon_framing.js

@@ -1,4 +1,4 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "grapes", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoes", "socks", "pants","shirt", "jacket", "dress", "drum", "flute", "guitar", "piano", "trumpet", "violin", "castle", "church", "factory", "house", "igloo", "tent", "N1_vehicles", "N1_fruits", "N1_mammals", "N1_containers", "N1_furniture", "N1_clothes", "N2_vehicles", "N2_fruits", "N2_mammals", "N2_containers", "N2_furniture", "N2_clothes", "N3_vehicles", "N3_fruits", "N3_mammals", "N3_containers", "N3_furniture", "N3_clothes", "bread", "tv", "pencil"];
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "cherry", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoe", "sock", "hat","shirt", "jacket", "dress", "drum", "flute", "guitar", "piano", "trumpet", "violin", "castle", "church", "factory", "house", "igloo", "tent", "N1_vehicles", "N1_fruits", "N1_mammals", "N1_containers", "N1_furniture", "N1_clothes", "N2_vehicles", "N2_fruits", "N2_mammals", "N2_containers", "N2_furniture", "N2_clothes", "N3_vehicles", "N3_fruits", "N3_mammals", "N3_containers", "N3_furniture", "N3_clothes", "bread", "tv", "pencil"];
 
 var images = new Array();
 for (i = 0; i < preloadItems.length; i++) {
@@ -128,10 +128,10 @@ var currTrialType = trialType[0];
 var backgrounds = shuffle([1, 2, 3, 4, 5, 6, 7, 8, 9, 10])
 
 var vehiclesF = shuffle(["car", "truck", "train", "bus", "airplane", "boat"])
-var fruitsF = shuffle(["strawberry", "apple", "banana", "grapes", "orange", "melon"])
+var fruitsF = shuffle(["strawberry", "apple", "banana", "cherry", "orange", "melon"])
[…]

### 2018-08-15 experiments/discon_recency_last.js

@@ -473,7 +473,7 @@ var experiment = {
             workerIp = JSON.parse(ip);
             
             data = {
-                experiment: "recency",
+                experiment: "recency_last ",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],
@@ -556,7 +556,7 @@ var experiment = {
     choice2 : function() {
         document.getElementById("next-novel").style.visibility = "hidden";    
 
-        document.getElementById("text_correctItem").innerHTML = "Here's another one. Can you click on it?"
+        document.getElementById("text_correctItem").innerHTML = "Here's the last one. Can you click on it?"
 
         $(".item").click(function() {
             var clickedItem = event.target;
@@ -605,7 +605,7 @@ var experiment = {
             workerIp = JSON.parse(ip);
             
             data = {
-                experiment: "recency",
+                experiment: "recency_last",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],

### 2018-08-15 experiments/discon_recency_look.js

@@ -336,7 +336,7 @@ function findCategory (pick) {
 
 // get client’s ip information and store in app object
 $.getJSON('https://ipapi.co/json/', function(data) {
- ip = JSON.stringify(data, null, 2);
+    ip = JSON.stringify(data, null, 2);
 });
 
 var experiment = {
@@ -433,11 +433,7 @@ var experiment = {
         var correctCategory = trialFamiliarItems[trials[0]].get(trainingDist[trials[0]][0]);
         var correctItem = correctCategory[0];
 
-        if(correctItem == "apple" || correctItem == "airplane" || correctItem == "elephant" || correctItem == "orange") {
-            document.getElementById("text_correctItem").innerHTML = "Here's an " + correctItem + ". Can you click on the " + correctItem + "?";
-        } else {
-            document.getElementById("text_correctItem").innerHTML = "Here's a " + correctItem + ". Can you click on the " + correctItem + "?";
-        }
+        document.getElementById("text_correctItem").innerHTML = "Look at that. Can you click on the " + correctItem + "?";
 
         //        sourceSound("sounds/" + correctItem + ".mp3");
         //        playSound();
@@ -471,9 +467,9 @@ var experiment = {
             clickedItem.style.border = '5px solid blue';
 
             workerIp = JSON.parse(ip);
-            
+
             data = {
-                experiment: "recency",
+                experiment: "recency_look",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],
@@ -494,7 +490,7 @@ var experiment = {
                 pickPos: pickId,
                 pickCat: findCategory(pick),
                 correct_item: correct_item,
-                
+
                 workerIp: workerIp.ip
             }
 
@@ -556,7 +552,7 @@ var experiment = {
     choice2 : function() {
         document.getElementById("next-novel").style.visibility = "hidden";    
 
-        document.getElementById("text_correctItem").innerHTML = "Here's another one. Can you click on it?"
+        document.getElementById("text_correctItem").innerHTML = "Look at that. Can you click on it?"
 
         $(".item").click(function() {
             var clickedItem = event.target;
@@ -603,9 +599,9 @@ var experiment = {
             clickedItem.style.border = '5px solid blue';
 
             workerIp = JSON.parse(ip);
-            
+
             data = {
-                experiment: "recency",
+                experiment: "recency_look",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],
[…]

### 2018-08-16 analysis/01_analysis.Rmd
kid experiment, summary markdown file

--- 2018-08-14 analysis/01_analysis.Rmd
@@
 
+#Pilot 1 data
 ```{r data preprocessing}
@@
   labs(x="", y= "proportion chosen")
-
 ```
@@
 ```
+
+# Are there 2 strategies in determining what "another one" means?
+```{r}
+plot3 <- data %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, workerid) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -workerid) %>%
+  group_by(distribution, item)
+
+plot3a <- plot3 %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot() +
+  geom_jitter(data = plot3, aes(x = item, y = prop_correct, col = distribution, alpha = .2), width = .3,height = .025)+
+  geom_pointrange(data = plot3a, aes(x = item, y = mean, col = distribution, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  facet_grid(~distribution)+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="Item Chosen", y="Proportion Chosen")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+ # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+
+#No - if 2 strategies: there should be fewer dots in the middle
+```
+# Does where (5,1,0) occurs determine the strategy of chosing the last item?
+```{r}
+plot3 <- data %>%
+  filter(phase == 'test', distribution == "c(5, 1, 0)") %>%
+  mutate(distType = ifelse(trial < 4, "early", "late")) %>%
+  group_by(distribution, workerid, distType) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -workerid, -distType) %>%
+  group_by(distribution, item, distType)
+
+plot3a <- plot3 %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot() +
+  geom_jitter(data = plot3, aes(x = item, y = prop_correct, col = distribution, alpha = .2), width = .3,height = .025)+
+  geom_pointrange(data = plot3a, aes(x = item, y = mean, col = distribution, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  facet_grid(~distType)+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="Item Chosen", y="Proportion Chosen")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+ # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
 # Does the graded distribution come through in cases where the last input does not affect the object choice?
@@
 # 7/26 for 2, 2, 2
-
 ```

### 2018-08-16 analysis/01_pilot_summary.Rmd
kid experiment, summary markdown file

---
title: "DisCon Pilot Summary"
output: html_document
---

```{r setup, include=FALSE}
#Libraries
knitr::opts_chunk$set(echo = FALSE, warning = FALSE) #no code, no warning printed
library(knitr)
library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
```

```{r data loading, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

#Pilot data preprocessing
files <- dir("../../pilot_1_raw_data/production-results")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../pilot_1_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_pilot_another <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))

#Recency "Here's another one" data preprocessing
files <- dir("../../recency_raw_data/production-results")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../recency_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_recency_another <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(5, 1, 0)", "c(2, 2, 2)")))

data_ip <- data_recency_another %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))

data_recency_another <- data_recency_another %>% 
  distinct(workerIp, trial, slide, .keep_all = TRUE)

#Recency "Here's the last one." data preprocessing
files <- dir("../../recency_last_raw_data/production-results")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../recency_last_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_recency_last <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(5, 1, 0)", "c(2, 2, 2)")))

data_ip <- data_recency_last %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))

data_recency_last <- data_recency_last %>% 
  distinct(workerIp, trial, slide, .keep_all = TRUE)

#Recency look data preprocessing
files <- dir("../../recency_look_raw_data/production-results")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../recency_look_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_recency_look <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(5, 1, 0)", "c(2, 2, 2)")))

data_ip <- data_recency_look %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))

data_recency_look <- data_recency_look %>% 
  distinct(workerIp, trial, slide, .keep_all = TRUE)

#Combine recency data
data_recency <- bind_rows(data_recency_another, data_recency_last, data_recency_look)
```

```{r sanity checks, include=FALSE} 
#remove duplicated ips and workers who do not pass the training threshold
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

# Training threshold check for data_pilot_another
data_pilot_another %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item))

drop <- data_pilot_another %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

data_pilot_another <- data_pilot_another %>%
  filter(!workerid %in% drop)

# IP check for data_recency
data_recency <- data_recency %>% 
  distinct(workerIp, trial, slide, .keep_all = TRUE)

# Training threshold check for data_recency
data_recency %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item))

drop <- data_recency %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

data_recency <- data_recency %>%
  filter(!workerid %in% drop)
```

# Pilot experiment

## Descriptives

### Task description
Each experiment contains 6 trials. Each trial contains 6 training slides (non-ambiguous utterance) and 1 test slide (ambiguous utterance), as shown below.

![Training slide](../pictures/pilot_training.png){width=250px} ![Test slide](../pictures/pilot_test.png){width=250px}

The items appearing in a trial belong to a set of 3 categories of items (for e.g. musical instruments, fruits, vehicles) that is unique across 6 trials. We run the experiment with distributions (6-0-0), (4-2-0), and (2-2-2), with each number corresponding to how many times a category has items appear in the trial.

### Sample size
We remove responses that get less than 5/6 correct in training slides. If there are duplicated IPs, we only take the first response.
```{r sample size data_pilot_another, echo=FALSE}
# summarise all unique ips across 3 experiments (do this after general description of task)

sample_size <- data_pilot_another %>%
  distinct(workerid, .keep_all = TRUE)

sample_size %>%
 summarise(n = n()) %>%
 kable()
```

### Finding
```{r plot1, fig.width = 8, echo=FALSE}
plot1 <- data_pilot_another %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid) %>%
  group_by(distribution, item) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```

There is a graded response in distribution (4-2-0) corresponding to the frequency of appearance of each category. This fits with our hypothesis that people use common ground to resolve anaphora.

However, this result could also be driven by a recency effect where people simply choose according to the category of the last seen item.

```{r plot2, echo=FALSE}
plot2 <- data_pilot_another %>%
  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
  group_by (distribution, workerid) %>%
  summarise (lastInput = mean(same_lastInput),
             n = n()) %>% 
  multi_boot_standard(col = "lastInput")

ggplot(plot2,
       aes(x = distribution, y = mean, fill = distribution)) +
  geom_bar(stat='identity', width = 0.3) +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Distribution",
                       breaks = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)"),
                       labels = c("(6-0-0)", "(4-2-0)", "(2-2-2)"))+
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen same as last item")
```

In order to look at the recency, we manipulate the experiment 
2 new types of expression for the test slide

### 2018-08-16 experiments/discon.js

@@ -1,657 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "grapes", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoes", "socks", "pants", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
-}
-
[…]

### 2018-08-16 experiments/discon_framing.js

@@ -1,732 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "strawberry", "apple", "banana", "cherry", "orange", "melon", "dog", "cat", "horse", "bear", "cow", "monkey", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "shoe", "sock", "hat","shirt", "jacket", "dress", "drum", "flute", "guitar", "piano", "trumpet", "violin", "castle", "church", "factory", "house", "igloo", "tent", "N1_vehicles", "N1_fruits", "N1_mammals", "N1_containers", "N1_furniture", "N1_clothes", "N2_vehicles", "N2_fruits", "N2_mammals", "N2_containers", "N2_furniture", "N2_clothes", "N3_vehicles", "N3_fruits", "N3_mammals", "N3_containers", "N3_furniture", "N3_clothes", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 10; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
[…]

### 2018-08-16 experiments/discon_look_kid.js

@@ -1,0 +1,651 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+$("#button").click(function() {
+    //disable accept button if in turk preview mode
+    if (turk.previewMode) {
+        showSlide("instructions");
+        alert("Please accept HIT to view");
+    } else {
+        showSlide('introAll')
+    }
+});
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
+    $("#"+id+"_"+orient).show();
+}
+
+function sourceRightItem(a) {
+    document.getElementById("item_r").src=a;
+}
+
+function showRightItem() {
+    document.getElementById('item_r').style.visibility='visible';
+}
+
+function hideRightItem() {
+    document.getElementById('item_r').style.visibility='hidden';
+}
+
+function sourceMiddleItem(a) {
+    document.getElementById("item_m").src=a;
+}
+
+function showMiddleItem() {
+    document.getElementById('item_m').style.visibility='visible';
+}
+
[…]

### 2018-08-16 experiments/discon_look_relative.js

@@ -1,0 +1,651 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+$("#button").click(function() {
+    //disable accept button if in turk preview mode
+    if (turk.previewMode) {
+        showSlide("instructions");
+        alert("Please accept HIT to view");
+    } else {
+        showSlide('introAll')
+    }
+});
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
+    $("#"+id+"_"+orient).show();
+}
+
+function sourceRightItem(a) {
+    document.getElementById("item_r").src=a;
+}
+
+function showRightItem() {
+    document.getElementById('item_r').style.visibility='visible';
+}
+
+function hideRightItem() {
+    document.getElementById('item_r').style.visibility='hidden';
+}
+
+function sourceMiddleItem(a) {
+    document.getElementById("item_m").src=a;
+}
+
+function showMiddleItem() {
+    document.getElementById('item_m').style.visibility='visible';
+}
+
[…]

### 2018-08-16 experiments/discon_old.js

@@ -1,677 +1,0 @@
-// preload
-var preFruits = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","empty.png"];
-
-//for critical trials and fillers
-var images = new Array();
-for (i = 0; i < preFruits.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preFruits[i];
-}
-
-
-var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3"];
-//for critical trials and fillers
-var sound = new Array();
-for (i = 0; i < preSounds.length; i++) {
-    sound[i] = new Audio();
-    sound[i].src = "sound/" + preSounds[i];
-}
-
-// ## Helper functions
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function showText(id) {
-    $(".text").hide();
-    $("#"+id).show();
-}
-
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".point_agent_l").hide();
-    $(".point_agent_r").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function hideAgent() {
-    $(".agent").hide();
-}
-
-
-function choiceAgent(id) {
-    $(".agent").hide();
-    $("#"+id+"_choice").show();
-}
-
-function sourceRightFruit(a) {
[…]

### 2018-08-16 experiments/discon_recency.js

@@ -1,676 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
-}
[…]

### 2018-08-16 experiments/discon_recency_last.js

@@ -1,676 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
-}
[…]

### 2018-08-16 experiments/mmturkey.js

@@ -214,12 +214,12 @@ turk = turk || {};
 // htmlify(rawData)
 
 
-      $.post("https://langcog.stanford.edu/cgi-bin/MCC/novel/mcc.php",{expHTML: JSON.stringify(rawData)}, "json");
+      $.post("https://langcog.stanford.edu/cgi-bin/DisCon/discon.php",{expHTML: JSON.stringify(rawData)}, "json");
 
       return;
     }
 
-    $.post("https://langcog.stanford.edu/cgi-bin/MCC/novel/mcc.php",{expHTML: JSON.stringify(rawData)}, "json");
+    $.post("https://langcog.stanford.edu/cgi-bin/DisCon/discon.php",{expHTML: JSON.stringify(rawData)}, "json");
     // // Otherwise, submit the form
     // form.action = "https://langcog.stanford.edu/cgi-bin/SC_noisy/parenting_proj.php";
     // form.method = "POST";

### 2018-08-16 analysis/01_kids.Rmd
summary markdown file

---
title: "DisCon Kids Pilot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)

```

```{r}
# Data pre-processing

files <- dir("../data/kids_pilot/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../data/kids_pilot/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
   # mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))
```

### 2018-08-16 analysis/01_pilot_summary.Rmd
summary markdown file

@@
 
-# Pilot experiment
+# Pilot Experiment
 
@@
 ### Task description
+
 Each experiment contains 6 trials. Each trial contains 6 training slides (non-ambiguous utterance) and 1 test slide (ambiguous utterance), as shown below.
 
-![Training slide](../pictures/pilot_training.png){width=250px} ![Test slide](../pictures/pilot_test.png){width=250px}
+![Training slide](../pictures/pilot_training.png){width=350px} ![Test slide](../pictures/pilot_test.png){width=350px}
+
+Left: training slide, Right: test slide
 
@@
 
-### Finding
-```{r plot1, fig.width = 8, echo=FALSE}
-plot1 <- data_pilot_another %>%
+## Finding
+```{r pilot_plot1, fig.width = 8, echo=FALSE}
+pilot_plot1 <- data_pilot_another %>%
   filter(phase == 'test') %>%
@@
 
-ggplot(plot1,
+ggplot(pilot_plot1,
        aes(x = item, y=mean, fill=item)) +
@@
 
-There is a graded response in distribution (4-2-0) corresponding to the frequency of appearance of each category. This fits with our hypothesis that people use common ground to resolve anaphora.
+There is a graded response in distribution (4-2-0) corresponding to the frequency of appearance of each category.
+This fits with our hypothesis that people use common ground to identify the reference of an ambiguous utterance.
 
@@
 
-```{r plot2, echo=FALSE}
-plot2 <- data_pilot_another %>%
+```{r pilot_plot2, fig.width = 8, echo=FALSE}
+pilot_plot2 <- data_pilot_another %>%
   filter(phase == "test", distribution != "c(6, 0, 0)") %>%
@@
 
-ggplot(plot2,
+ggplot(pilot_plot2,
        aes(x = distribution, y = mean, fill = distribution)) +
@@
 
-In order to look at the recency, we manipulate the experiment 
-2 new types of expression for the test slide
+We see that people are choosing the item in the test slide in the same category as the last training item above chance, suggesting a possbily strong recency effect.
+
+# Recency Effect Experiment
+
+## Descriptives
+
+### Task description
+
+In order to look at the recency effect more closely, we manipulate the experiment to look at distribution (5-1-0) where the last item preceding the test slide is never in the most frequent category.
+We also use 2 new phrasing for the test slide, "Here's the last one" and "Look at that" Distribution (2-2-2), with all category appearances randomized, is used as the control.
+
+![Training slide](../pictures/last_training.png){width=350px} ![Test slide](../pictures/last_test.png){width=350px}
+
+![Training slide](../pictures/look_training.png){width=350px} ![Test slide](../pictures/look_test.png){width=350px}
+
+Left: training slide, Right: test slide
+
+### Sample size
+We remove responses that get less than 5/6 correct in training slides. If there are duplicated IPs, we only take the first response.
+```{r sample size data_recency, echo=FALSE}
+# summarise all unique ips across 3 experiments (do this after general description of task)
+
+sample_size <- data_recency %>%
+  distinct(workerid, .keep_all = TRUE)
+
+sample_size %>%
+ summarise(n = n()) %>%
+ kable()
+```
+
+## Finding
+```{r recency_plot1, fig.width = 8, echo = FALSE}
+recency_plot1 <- data_recency %>%
+  filter(phase == 'test', distribution == "c(5, 1, 0)") %>%
+  group_by(distribution, workerid, experiment) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -workerid, -experiment) %>%
+  group_by(distribution, item, experiment) %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot(recency_plot1,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("correct", "correct2", "correct3"),
+                       labels = c("most frequent", "second most frequent", "least frequent"))+
+  facet_grid(~experiment, 
+             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", recency = "Here's another one.", recency_last = "Here's the last one.", recency_look = "Look at that."))) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
+```
+
+Distribution (5, 1, 0)
+
+We see that the recency effect is reduced when "Here's the last one" and "Look at that" are used.
+We observe a higher increase in proportion of people choosing the item from the least frequent category in the condition "Here's the last one", perhaps because it is possible to interpret "the last one" as the item from the category that has not appeared.
+"Look at that" looks closest to the graded response that corresponds to people using common ground to identify reference.
+```{r recency_plot3, fig.height = 5, fig.width = 10, echo = FALSE}
+recency_plot3 <- data_recency %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, workerid, experiment) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -workerid, -experiment) %>%
+  group_by(distribution, item, experiment)
+
+recency_plot3a <- recency_plot3 %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot() +
+  geom_jitter(data = recency_plot3, aes(x = item, y = prop_correct, col = item, alpha = .2), width = .3,height = .025)+
+  geom_pointrange(data = recency_plot3a, aes(x = item, y = mean, col = item, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  scale_colour_solarized(name = "Chosen item",
+                       breaks = c("correct", "correct2", "correct3"),
+                       labels = c("most frequent", "second most frequent", "least frequent"))+
+  facet_grid(experiment~distribution,
+             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", recency = "Here's another one.", recency_last = "Here's the last one.", recency_look = "Look at that.")))+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="item chosen", y="proportion chosen")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
+```
+
+```{r recency_plot2, fig.width = 8, echo = FALSE}
+recency_plot2 <- data_recency %>%
+  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
+  group_by (distribution, workerid, experiment) %>%
+  summarise (lastInput = mean(same_lastInput),
+             n = n()) %>%
+  group_by(distribution, experiment) %>%
+  multi_boot_standard(col = "lastInput")
+
+ggplot(recency_plot2,
+       aes(x = distribution, y = mean, fill = distribution)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Distribution",
+                       breaks = c("c(5, 1, 0)", "c(2, 2, 2)"),
+                       labels = c("(5-1-0)", "(2-2-2)"))+
+  facet_grid(~experiment, 
+             labeller = as_labeller(c(recency = "Here's another one.", recency_last = "Here's the last one.", recency_look = "Look at that.")))+ 
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen same as last item")
+```
+
+# Moving forward
+We stay with "Look at that." as the phrasing for the test slide.
+
+We run 2 experiments with adults, with the same setup:
+
+1. (6-0-0) vs (4-2-0) vs (2-2-2)
+2. (3-0-0) vs (2-1-0) vs (1-1-1)
+
+to test the effect of relative and absolute strength.
+
+We run the 3rd experiment with other distributions that are interesting, such as (1-0-0) and (3-2-1).
+
+We start pilotting on kids, with the distributions (6-0-0) vs (4-2-0) vs (2-2-2).

### 2018-08-16 experiments/discon_look_kid.js

@@ -12,16 +12,6 @@ for (i = 1; i <= 12; i++) {
     backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
 }
 
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
 function showSlide(id) {
     // Hide all slides
     $(".slide").hide();
@@ -349,6 +339,21 @@ var experiment = {
 
     data: [], 
 
+    checkInput: function() {
+        //subject ID
+        if (document.getElementById("subjectID").value.length < 1) {
+            $("#checkMessage").html('<font color="red">You must input a subject ID</font>');
+            return;
+        }
+        if (document.getElementById("subjectAge").value.length < 1) {
+            $("#checkMessage").html('<font color="red">You must input a subject age</font>');
+            return;
+        }
+        experiment.subid = document.getElementById("subjectID").value
+        experiment.subage = document.getElementById("subjectAge").value
+        experiment.introAll()
+    },  
+
     introAll: function() {
         showSlide("introAll");
         document.getElementById("text_introAll").innerHTML = "You're visiting the house of these little animals. They will introduce you to the kinds of things they have at home. Your task is to click on the things they talk about.";
@@ -419,7 +424,7 @@ var experiment = {
 
         var correctCategory = trialFamiliarItems[trials[0]].get(trainingDist[trials[0]][0]);
         var correctItem = correctCategory[0];
-        
+
         document.getElementById("text_correctItem").innerHTML = "Look at that. Can you click on the " + correctItem + "?";
 
         //        sourceSound("sounds/" + correctItem + ".mp3");
@@ -453,8 +458,13 @@ var experiment = {
             $(".item").unbind("click");
             clickedItem.style.border = '5px solid blue';
 
+            var subid = experiment.subid;
+            var subage = experiment.subage;    
+            
             data = {
-                experiment: "distribution",
+                subid: subid,
+                subage: subage,
+                experiment: "distribution_kids",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],
@@ -502,7 +512,7 @@ var experiment = {
         document.getElementById("next-novel").style.visibility = 'hidden';
 
         background("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
-        
+
[…]

### 2018-08-16 experiments/discon_recency_look.js

@@ -1,672 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
-}
[…]

### 2018-08-16 experiments/discon_look_kid.js
fix relative adult experiment to the right number of slides

@@ -451,7 +451,7 @@ var experiment = {
             }
 
             // stores category of the final input slide
-            if (experiment.slides[0] == 6) {
+            if (experiment.slides[0] == slides.length - 1) {
                 experiment.lastInputCat = findCategory(pick);
             }
 

### 2018-08-16 experiments/discon_look_relative.js

@@ -446,7 +446,7 @@ var experiment = {
             }
 
             // stores category of the final input slide
-            if (experiment.slides[0] == 6) {
+            if (experiment.slides[0] == slides.length - 1) {
                 experiment.lastInputCat = findCategory(pick);
             }
 

### 2018-08-22 analysis/01_pilot_summary.Rmd
remove data folder

@@
 ---
+
+Successful communication requires coordination between speakers and listeners in a variety of ways.
+The accrual of shared knowledge between interlocutors (e.g.
+"common ground") during discourse is of particular interest.
+To date, most theories characterize common ground in a categorical fashion - either you have it or you don't.
+We explore the degree to which interlocutors display graded sensitivity to common ground, maintaining uncertainty over shared knowledge during a conversation.
 
@@
 
-## Descriptives
+## Task description
 
-### Task description
-
-Each experiment contains 6 trials. Each trial contains 6 training slides (non-ambiguous utterance) and 1 test slide (ambiguous utterance), as shown below.
+Each experiment contains 6 trials.
+Each trial contains 6 training slides (non-ambiguous utterance) and 1 test slide (ambiguous utterance), as shown below.
+For the first experiment, the ambiguous utterance consists of saying "Here's another one."
 
@@
 
-### Sample size
+## Sample size
 We remove responses that get less than 5/6 correct in training slides. If there are duplicated IPs, we only take the first response.
@@
 
+The dotted line represents performance expected by chance (1/3), and the error bar are 95% CIs.
+
+In distribution (6-0-0), most participants choose the most frequent category.
+
 There is a graded response in distribution (4-2-0) corresponding to the frequency of appearance of each category.
@@
 
-However, this result could also be driven by a recency effect where people simply choose according to the category of the last seen item.
+However, this result could also be driven by a recency effect where participants simply choose according to the category of the last seen item.
 
@@
 
-We see that people are choosing the item in the test slide in the same category as the last training item above chance, suggesting a possbily strong recency effect.
+We see that participants are choosing the item in the test slide in the same category as the last training item above chance, suggesting a possibly strong recency effect.
+
+The reason we're seeing this recency effect may be the semantics of "another" as it makes strong reference to the last category seen.
 
@@
 
-## Descriptives
+In order to look at the recency effect more closely, we manipulate the experiment to look at distribution (5-1-0) where the last item preceding the test slide is never in the most frequent category.
+We vary the wording in the ambiguous utterance.
 
-### Task description
+## Task description
 
-In order to look at the recency effect more closely, we manipulate the experiment to look at distribution (5-1-0) where the last item preceding the test slide is never in the most frequent category.
-We also use 2 new phrasing for the test slide, "Here's the last one" and "Look at that" Distribution (2-2-2), with all category appearances randomized, is used as the control.
+We use 2 new phrasings for the test slide, "Here's the last one" and "Look at that." Distribution (2-2-2), with all category appearances randomized, is used as the control.
 
@@
 sample_size %>%
+ mutate(wording = ifelse(experiment == "recency", "another one", ifelse(experiment == "recency_last ", "last one", "look at that"))) %>%
+ group_by(wording) %>%
  summarise(n = n()) %>%
@@
 
-Distribution (5, 1, 0)
+Distribution (5, 1, 0) where the last item preceding the test slide is never in the most frequent category
 
 We see that the recency effect is reduced when "Here's the last one" and "Look at that" are used.
-We observe a higher increase in proportion of people choosing the item from the least frequent category in the condition "Here's the last one", perhaps because it is possible to interpret "the last one" as the item from the category that has not appeared.
+We observe a higher increase in proportion of participants choosing the item from the least frequent category in the condition "Here's the last one", perhaps because it is possible to interpret "the last one" as the item from the category that has not appeared.
 "Look at that" looks closest to the graded response that corresponds to people using common ground to identify reference.
-```{r recency_plot3, fig.height = 5, fig.width = 10, echo = FALSE}
-recency_plot3 <- data_recency %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, experiment) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -experiment) %>%
-  group_by(distribution, item, experiment)
-
-recency_plot3a <- recency_plot3 %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot() +
-  geom_jitter(data = recency_plot3, aes(x = item, y = prop_correct, col = item, alpha = .2), width = .3,height = .025)+
-  geom_pointrange(data = recency_plot3a, aes(x = item, y = mean, col = item, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  scale_colour_solarized(name = "Chosen item",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))+
-  facet_grid(experiment~distribution,
-             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", recency = "Here's another one.", recency_last = "Here's the last one.", recency_look = "Look at that.")))+
-  geom_hline(yintercept = 1/3, lty=2)+
-  labs(x="item chosen", y="proportion chosen")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
-```
 
@@
 
+Proportion of participants choosing the item at test slide in the same category that appears on the last training slide.
+
 # Moving forward
-We stay with "Look at that." as the phrasing for the test slide.
+We stay with "Look at that." as the phrasing for the test slide because it produces an inference that is closest to a common ground inference.
+Furthermore, it's also compatible with a potential speaker change condition.
 
@@
 
-to test the effect of relative and absolute strength.
+to test the effect of relative and absolute input.
 

### 2018-08-29 analysis/01_analysis.Rmd
sound recordings

@@
 
-```{r plot1}
+```{r proportion of choices}
 plot1 <- data %>%
@@
 # How does the last item seen affect the object chosen in the anaphora case? 
-```{r}
-plot2 <- data %>%
-  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
-  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
-  group_by (distribution, workerid) %>%
-  summarise (lastInput = mean(same_lastInput),
-             n = n()) %>% 
-  multi_boot_standard(col = "lastInput")
-
+```{r last item}
 plot2 <- data %>%
@@
 ```
+
+# Are participants choosing the middle item more? 
+```{r middle item}
+plot3 <- data %>%
+  filter(phase == 'test') %>%
+  mutate(pick_l = ifelse(pickPos == "item_l", 1, 0), 
+         pick_m = ifelse(pickPos == "item_m", 1, 0),
+         pick_r = ifelse(pickPos == "item_r", 1, 0)) %>%
+  group_by(distribution, workerid) %>%
+  summarise(choose_l = mean(pick_l),
+            choose_m = mean(pick_m),
+            choose_r = mean(pick_r)) %>%
+  gather(item, prop_choose, -distribution, -workerid) %>%
+  group_by(distribution, item) %>%
+  multi_boot_standard(col = "prop_choose")
+
+ggplot(plot3,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("choose_l", "choose_m", "choose_r"),
+                       labels = c("left", "middle", "right"))+
+  facet_grid(~distribution, 
+             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)"))) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
+```
+
+# Are participants choosing the middle item even when the middle item is wrong? 
+```{r middle item, chose incorrectly}
+plot4 <- data %>%
+  filter(phase == 'test', correct_target1 == 0) %>%
+  mutate(pick_l = ifelse(pickPos == "item_l", 1, 0), 
+         pick_m = ifelse(pickPos == "item_m", 1, 0),
+         pick_r = ifelse(pickPos == "item_r", 1, 0)) %>%
+  group_by(distribution, workerid) %>%
+  summarise(choose_l = mean(pick_l),
+            choose_m = mean(pick_m),
+            choose_r = mean(pick_r)) %>%
+  gather(item, prop_choose, -distribution, -workerid) %>%
+  group_by(distribution, item) %>%
+  multi_boot_standard(col = "prop_choose")
+
+ggplot(plot4,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("choose_l", "choose_m", "choose_r"),
+                       labels = c("left", "middle", "right"))+
+  facet_grid(~distribution, 
+             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)"))) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
+```

### 2018-08-29 analysis/01_kids.Rmd
sound recordings

@@
 
-```{r}
-# Data pre-processing
+```{r data pre-processing}
 
-files <- dir("../data/kids_pilot/")
+files <- dir("../../data/kids_pilot/")
 
@@
 for (f in files) {
-  jf <- paste("../data/kids_pilot/",f,sep="")
+  jf <- paste("../../data/kids_pilot/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- as_data_frame(jd$data$data)
-   # mutate(workerid = jd$WorkerId)
   raw_data <- bind_rows(raw_data, id)
@@
 ```
+
+```{r sanity checks}
+data <- data %>% 
+  filter(subid != "", subid != "test", subid != "Test")
+
+data %>%
+  filter(phase == 'training') %>%
+  group_by(subid) %>%
+  summarise(correct = mean(correct_item))
+
+drop <- data %>%
+  filter(phase == 'training') %>%
+  group_by(subid) %>%
+  summarise(correct = mean(correct_item)) %>%
+  filter(correct < 0.83) %>%
+  pull(subid)
+
+data <- data %>%
+  filter(!subid %in% drop)
+
+```
+
+# Do proportion of choices match the frequency in the distribution
+
+```{r proportion of choices}
+plot1 <- data %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, subid) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -subid) %>%
+  group_by(distribution, item) %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot(plot1,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("correct", "correct2", "correct3"),
+                       labels = c("most frequent", "second most frequent", "least frequent"))+
+  facet_grid(~distribution, 
+             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
+```
+
+# How does the last item seen affect the object chosen in the anaphora case? 
+```{r last item}
+plot2 <- data %>%
+  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
+  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
+  group_by (distribution, subid) %>%
+  summarise (lastInput = mean(same_lastInput),
+             n = n()) %>% 
+  multi_boot_standard(col = "lastInput")
+
+ggplot(plot2,
+       aes(x = distribution, y = mean, fill = distribution)) +
+  geom_bar(stat='identity', width = 0.3) +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few()
+```
+
+# Are participants choosing the middle item more? 
+```{r middle item}
+plot3 <- data %>%
+  filter(phase == 'test') %>%
+  mutate(pick_l = ifelse(pickPos == "item_l", 1, 0), 
+         pick_m = ifelse(pickPos == "item_m", 1, 0),
+         pick_r = ifelse(pickPos == "item_r", 1, 0)) %>%
+  group_by(distribution, subid) %>%
+  summarise(choose_l = mean(pick_l),
+            choose_m = mean(pick_m),
+            choose_r = mean(pick_r)) %>%
+  gather(item, prop_choose, -distribution, -subid) %>%
+  group_by(distribution, item) %>%
+  multi_boot_standard(col = "prop_choose")
+
+ggplot(plot3,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("choose_l", "choose_m", "choose_r"),
+                       labels = c("left", "middle", "right"))+
+  facet_grid(~distribution, 
+             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)"))) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
+```
+
+# Are participants choosing the middle item even when the middle item is wrong? 
+```{r middle item, chose incorrectly}
+plot4 <- data %>%
+  filter(phase == 'test', correct_target1 == 0) %>%
+  mutate(pick_l = ifelse(pickPos == "item_l", 1, 0), 
+         pick_m = ifelse(pickPos == "item_m", 1, 0),
+         pick_r = ifelse(pickPos == "item_r", 1, 0)) %>%
+  group_by(distribution, subid) %>%
+  summarise(choose_l = mean(pick_l),
+            choose_m = mean(pick_m),
+            choose_r = mean(pick_r)) %>%
+  gather(item, prop_choose, -distribution, -subid) %>%
+  group_by(distribution, item) %>%
+  multi_boot_standard(col = "prop_choose")
+
+ggplot(plot4,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("choose_l", "choose_m", "choose_r"),
+                       labels = c("left", "middle", "right"))+
+  facet_grid(~distribution, 
+             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)"))) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
+```

### 2018-08-29 experiments/discon_look_kid.js

@@ -300,7 +300,9 @@ for (var i=0; i < trials.length; i++) {
     shuffle(trainingDist[i]);
 }
 
-var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
+var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Pig", "Sheep", "Tiger"])
+
+//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
 
 var trainingAgents = new Array();
 for (var m=0; m < trials.length; m++) {
@@ -338,6 +340,8 @@ var experiment = {
     lastInputCat: "",
 
     data: [], 
+    
+    sound: new Audio(),
 
     checkInput: function() {
         //subject ID
@@ -356,7 +360,7 @@ var experiment = {
 
     introAll: function() {
         showSlide("introAll");
-        document.getElementById("text_introAll").innerHTML = "You're visiting the house of these little animals. They will introduce you to the kinds of things they have at home. Your task is to click on the things they talk about.";
+        document.getElementById("text_introAll").innerHTML = "You're visiting the house of these little animals. They will introduce you to the kinds of things they have at home. Your task is to touch the things they talk about.";
         document.getElementById("text_introAll_2").innerHTML = "To move forward within the experiment, press the \"Next\" button. Press below to start.";
     },
 
@@ -369,8 +373,20 @@ var experiment = {
         document.getElementById("text_intro").innerHTML = "Hi, I'm " + trainingAgents[trials[0]] + ". These are the things I have at home.";
 
         document.getElementById("text_transition").innerHTML = "";
-
-        $(".agent_transition").click(experiment.train);      
+        
+        sourceSound("sounds/" + "hi_" + trainingAgents[trials[0]] + ".mp3");
+        playSound();
+        
+        sound = document.getElementById("sound");
+        
+        sound.onended = function() {
+            sourceSound("sounds/" + "intro_" + trainingAgents[trials[0]] + ".mp3");
+            playSound();
+            sound = document.getElementById("sound");
+            sound.onended = function() {
+                $(".agent_transition").click(experiment.train);
+            };
+        };
     },
 
     train : function () {
@@ -407,15 +423,20 @@ var experiment = {
         setTimeout(function() {
[…]

### 2018-08-29 experiments/discon_look_kid.js
more sound recordings, moved positions of objects, remove text

@@ -300,7 +300,7 @@ for (var i=0; i < trials.length; i++) {
     shuffle(trainingDist[i]);
 }
 
-var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Pig", "Sheep", "Tiger"])
+var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger"])
 
 //var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
 
@@ -365,15 +365,15 @@ var experiment = {
     },
 
     intro: function () {
+        
+        $(".agent_transition").unbind("click");
+        
         background2("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
 
         showSlide("transition");
 
         showAgent(trainingAgents[trials[0]], "transition");
-        document.getElementById("text_intro").innerHTML = "Hi, I'm " + trainingAgents[trials[0]] + ". These are the things I have at home.";
-
-        document.getElementById("text_transition").innerHTML = "";
-        
+     
         sourceSound("sounds/" + "hi_" + trainingAgents[trials[0]] + ".mp3");
         playSound();
         
@@ -389,8 +389,10 @@ var experiment = {
         };
     },
 
-    train : function () {
-        document.getElementById("text_correctItem").style.visibility = "hidden";
+    train : function () { 
+        background("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
+
+        showSlide("input");
 
         document.getElementById("next-input").style.visibility = "hidden";        
         document.getElementById("next-novel").style.visibility = "hidden";
@@ -403,10 +405,6 @@ var experiment = {
         }
 
         experiment.position = shuffle([experiment.targetsF[0][0], experiment.targetsF2[0][0], experiment.targetsF3[0][0]]);
-
-        background("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
-
-        showSlide("input");
 
         showAgent(trainingAgents[trials[0]], "straight");
 
@@ -421,32 +419,21 @@ var experiment = {
 
         // pause for 1s before images appear
         setTimeout(function() {
-            document.getElementById("text_correctItem").style.visibility = "visible";
-            document.getElementById("text_correctItem").innerHTML = "Let's see...";
             
             showLeftItem();
[…]

### 2018-08-29 experiments/discon_look_kid_simple.js
new experiment for kids, 4 trials 6-0-0

@@ -12,16 +12,6 @@ for (i = 1; i <= 12; i++) {
     backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
 }
 
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
 function showSlide(id) {
     // Hide all slides
     $(".slide").hide();
@@ -119,7 +109,7 @@ showSlide("instructions");
 
 var slides = [1, 2, 3, 4, 5, 6, "choice"]
 
-var trials = [0, 1, 2, 3, 4, 5]
+var trials = [0, 1, 2, 3]
 
 var backgrounds = shuffle([1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]);
 
@@ -295,7 +285,7 @@ function shuffleByIndex(array) {
 shuffleByIndex(trialTargets);
 shuffleByIndex(trialFamiliarItems);
 
-var posDist = shuffle([[4, 2, 0], [6, 0, 0], [2, 2, 2], [4, 2, 0], [6, 0, 0], [2, 2, 2]]);
+var posDist = shuffle([[6, 0, 0], [6, 0, 0], [6, 0, 0], [6, 0, 0]]);
 
 //distribution for each trial
 var trainingDist = new Array();
@@ -310,7 +300,9 @@ for (var i=0; i < trials.length; i++) {
     shuffle(trainingDist[i]);
 }
 
-var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
+var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger"])
+
+//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
 
 var trainingAgents = new Array();
 for (var m=0; m < trials.length; m++) {
@@ -349,27 +341,58 @@ var experiment = {
 
     data: [], 
 
+    sound: new Audio(),
+
+    checkInput: function() {
+        //subject ID
+        if (document.getElementById("subjectID").value.length < 1) {
[…]

### 2018-08-29 experiments/discon_look_relative.js

@@ -454,7 +454,7 @@ var experiment = {
             clickedItem.style.border = '5px solid blue';
 
             data = {
-                experiment: "distribution",
+                experiment: "distribution_adults_relative",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],
@@ -582,7 +582,7 @@ var experiment = {
             clickedItem.style.border = '5px solid blue';
 
             data = {
-                experiment: "distribution",
+                experiment: "distribution_adults_relative",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],

### 2018-08-29 analysis/01_kids.Rmd
preload audios

@@
 
-files <- dir("../../data/kids_pilot/")
+files <- dir("../../kids_simple/")
 
@@
 for (f in files) {
-  jf <- paste("../../data/kids_pilot/",f,sep="")
+  jf <- paste("../../kids_simple/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))

### 2018-08-29 experiments/discon_look_kid_simple.js

@@ -6,6 +6,27 @@ for (i = 0; i < preloadItems.length; i++) {
     images[i].src = "images/" + preloadItems[i] + ".png";
 }
 
+//only preload relevant audios (no speaker change)
+var preloadAudios = ["hi", "lets", "intro", "thank", "it"];
+
+var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger"])
+
+//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
+
+var audios = new Array();
+for (i = 0; i < posAgents.length; i++) {
+    for (j = 0; j < preloadAudios.length; j++) {
+        var audio = new Audio();
+        audio.src = "sounds/" + preloadAudios[j] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+    for (k = 0; k < preloadItems.length - 3; k++) {
+        var audio = new Audio();
+        audio.src = "sounds/" + preloadItems[k] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+}
+
 var backgroundImages = new Array();
 for (i = 1; i <= 12; i++) {
     backgroundImages[i] = new Image();
@@ -299,10 +320,6 @@ for (var i=0; i < trials.length; i++) {
     }
     shuffle(trainingDist[i]);
 }
-
-var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger"])
-
-//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
 
 var trainingAgents = new Array();
 for (var m=0; m < trials.length; m++) {

### 2018-08-30 analysis/01_analysis.Rmd
collect ip

@@
 
-files <- dir("../../pilot_1_raw_data/production-results")
+files <- dir("../../adult_relative_raw_data/production-results/")
 
@@
 for (f in files) {
-  jf <- paste("../../pilot_1_raw_data/production-results/",f,sep="")
+  jf <- paste("../../adult_relative_raw_data/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
@@
   mutate(distribution = as.character(distribution),
-         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))
+         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
+         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
 

### 2018-08-30 experiments/discon_look.js

@@ -326,6 +326,11 @@ function findCategory (pick) {
     }
 }
 
+// get client’s ip information and store in app object
+$.getJSON('https://ipapi.co/json/', function(data) {
+ ip = JSON.stringify(data, null, 2);
+});
+
 var experiment = {
     slides: slides.slice(),
     trials: trials,
@@ -453,6 +458,8 @@ var experiment = {
             $(".item").unbind("click");
             clickedItem.style.border = '5px solid blue';
 
+            workerIp = JSON.parse(ip);
+            
             data = {
                 experiment: "distribution_adults",
                 trial: trials[0] + 1,
@@ -474,7 +481,9 @@ var experiment = {
                 pick: pick,
                 pickPos: pickId,
                 pickCat: findCategory(pick),
-                correct_item: correct_item
+                correct_item: correct_item,
+                
+                workerIp: workerIp.ip
             }
 
             experiment.data.push(data);
@@ -581,6 +590,8 @@ var experiment = {
             $(".item").unbind("click");
             clickedItem.style.border = '5px solid blue';
 
+            workerIp = JSON.parse(ip);
+            
             data = {
                 experiment: "distribution_adults",
                 trial: trials[0] + 1,
@@ -607,7 +618,9 @@ var experiment = {
                 correct_target3: correct_target3,
 
                 lastInputCat: experiment.lastInputCat,
-                same_lastInput: same_lastInput
+                same_lastInput: same_lastInput,
+                
+                workerIp: workerIp.ip
             }
             experiment.data.push(data);
 

### 2018-08-30 experiments/discon_look_relative.js

@@ -326,6 +326,11 @@ function findCategory (pick) {
     }
 }
 
+// get client’s ip information and store in app object
+$.getJSON('https://ipapi.co/json/', function(data) {
+ ip = JSON.stringify(data, null, 2);
+});
+
 var experiment = {
     slides: slides.slice(),
     trials: trials,
@@ -453,6 +458,8 @@ var experiment = {
             $(".item").unbind("click");
             clickedItem.style.border = '5px solid blue';
 
+            workerIp = JSON.parse(ip);
+            
             data = {
                 experiment: "distribution_adults_relative",
                 trial: trials[0] + 1,
@@ -474,7 +481,9 @@ var experiment = {
                 pick: pick,
                 pickPos: pickId,
                 pickCat: findCategory(pick),
-                correct_item: correct_item
+                correct_item: correct_item,
+                
+                workerIp: workerIp.ip
             }
 
             experiment.data.push(data);
@@ -581,6 +590,8 @@ var experiment = {
             $(".item").unbind("click");
             clickedItem.style.border = '5px solid blue';
 
+            workerIp = JSON.parse(ip);
+            
             data = {
                 experiment: "distribution_adults_relative",
                 trial: trials[0] + 1,
@@ -607,7 +618,9 @@ var experiment = {
                 correct_target3: correct_target3,
 
                 lastInputCat: experiment.lastInputCat,
-                same_lastInput: same_lastInput
+                same_lastInput: same_lastInput,
+                
+                workerIp: workerIp.ip
             }
             experiment.data.push(data);
 

### 2018-09-08 analysis/01_adult.Rmd
add adult experiment with all trials 6-0-0, add sound recordings for Pig, add analysis files for kids' pilot results and adults results

--- 2018-08-16 analysis/01_analysis.Rmd
@@
 ---
-title: "Discon analysis"
+title: "Discon Adult Analysis"
 output: html_document
@@
 
-#Pilot 1 data
 ```{r data preprocessing}
@@
   mutate(distribution = as.character(distribution),
-         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))
-
- # data <- raw_data %>%
- #  mutate(correct_target3 = ifelse(correct_target1 == 0 & correct_target2 == 0, 1, 0)) %>%
- #  mutate(distribution = as.character(distribution),
- #         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
- #         pick = ifelse(pickPos == "item_l", item_l, ifelse(pickPos == "item_r", item_r, ifelse(pickPos=="item_m", item_m, NA))),
- #         correct_item = ifelse(pick == correctItem, 1, 0),
- #         pickTest = substr(pick, 4, length(pick)),
- #         correct_target1 = ifelse(pickTest == target1, 1, 0),
- #         correct_target2 = ifelse(pickTest == target2, 1, 0),
- #         correct_target3 = ifelse(pickTest == target3, 1, 0))
-
-# write.csv(data, file="../data/pilot.data.csv")
-
-# data <- read_csv(file="../data/pilot.data.csv")
+         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
+         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
 ```
-
-```{r sanity checks}
-data %>%
-  filter(phase == 'training') %>%
-  group_by(workerid) %>%
-  summarise(correct = mean(correct_item))
-
-drop <- data %>%
-  filter(phase == 'training') %>%
-  group_by(workerid) %>%
-  summarise(correct = mean(correct_item)) %>%
-  filter(correct < 0.83) %>%
-  pull(workerid)
-
-data <- data %>%
-  filter(!workerid %in% drop)
-
-```
-
-# Some preliminary tests
-```{r}
-data_test <- data %>% 
-  filter (phase == "test", distribution == "c(4, 2, 0)") %>%
-  summarise (lastInput = mean(same_lastInput),
-             n = length(distribution))
-#23/38 trials
-
-data_test <- data %>%
-  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
-  summarise (correct1 = mean(correct_target1))
-
-data_test <- data %>%
-  filter(phase == "test", distribution == "c(2, 2, 2)") %>%
-  summarise (lastInput = mean(same_lastInput),
-             n = length(distribution))
-# 23/38
-
-```
-
-# Salience of each category
-```{r}
-plot1 <- data %>%
-  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
-  group_by(distribution, target1) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3))
-
-plot1 <- data %>%
-  filter(phase == "test", distribution == "c(6, 0, 0)", target1 == "vehicles")
-
-# clothes: 2
-# fruits: 5
-# furniture: 10
-# instruments: 4
-# mammals: 8
-# vehicles: 9
-
-plot1 <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, target1) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -target1) %>%
-  group_by(distribution, item, target1) %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot(plot1,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))+
-  facet_grid(target1~distribution) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
-```
-# Do proportion of choices match the frequency in the distribution
-
-```{r plot1}
-plot1 <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid) %>%
-  group_by(distribution, item) %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot(plot1,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))+
-  facet_grid(~distribution, 
-             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
-```
-# How does the last item seen affect the object chosen in the anaphora case? 
-```{r}
-plot2 <- data %>%
-  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
-  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
-  group_by (distribution, workerid) %>%
-  summarise (lastInput = mean(same_lastInput),
-             n = n()) %>% 
-  multi_boot_standard(col = "lastInput")
-
-plot2 <- data %>%
-  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
-  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
-  group_by (distribution, workerid) %>%
-  summarise (lastInput = mean(same_lastInput),
-             n = n()) %>% 
-  multi_boot_standard(col = "lastInput")
-
-ggplot(plot2,
-       aes(x = distribution, y = mean, fill = distribution)) +
-  geom_bar(stat='identity', width = 0.3) +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few()
-```
-
-# Are there 2 strategies in determining what "another one" means?
-```{r}
-plot3 <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid) %>%
-  group_by(distribution, item)
-
-plot3a <- plot3 %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot() +
-  geom_jitter(data = plot3, aes(x = item, y = prop_correct, col = distribution, alpha = .2), width = .3,height = .025)+
-  geom_pointrange(data = plot3a, aes(x = item, y = mean, col = distribution, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  facet_grid(~distribution)+
-  geom_hline(yintercept = 1/3, lty=2)+
-  labs(x="Item Chosen", y="Proportion Chosen")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
- # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
-
-#No - if 2 strategies: there should be fewer dots in the middle
-```
-# Does where (5,1,0) occurs determine the strategy of chosing the last item?
-```{r}
-plot3 <- data %>%
-  filter(phase == 'test', distribution == "c(5, 1, 0)") %>%
-  mutate(distType = ifelse(trial < 4, "early", "late")) %>%
-  group_by(distribution, workerid, distType) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -distType) %>%
-  group_by(distribution, item, distType)
-
-plot3a <- plot3 %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot() +
-  geom_jitter(data = plot3, aes(x = item, y = prop_correct, col = distribution, alpha = .2), width = .3,height = .025)+
-  geom_pointrange(data = plot3a, aes(x = item, y = mean, col = distribution, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  facet_grid(~distType)+
-  geom_hline(yintercept = 1/3, lty=2)+
-  labs(x="Item Chosen", y="Proportion Chosen")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
- # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
-```
-
-# Does the graded distribution come through in cases where the last input does not affect the object choice?
-```{r}
-plot3 <- data %>%
-  filter(phase == "test", distribution == "c(4, 2, 0)", same_lastInput == 0) %>%
-  group_by(distribution, workerid) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid) %>%
-  group_by(distribution, item) %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot(plot3,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))+
-  facet_grid(~distribution, 
-             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
-```
-
-# Does the framing influence the match between choice and distribution
-
-```{r plot 2}
-plot2 <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, trialType) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
-  arrange(workerid)
-
- # group_by(distribution, trialType, item) %>%
- # multi_boot_standard(col = "prop_correct")
-
-ggplot() + 
-  geom_jitter(data = plot2, 
-              aes(x = item, y=prop_correct, fill=item, col=trialType),
-              height = 0.1,
-              width = 0.1) +
-  facet_grid(trialType~distribution) +
-  theme(legend.position="none")
-
-plot2 <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, trialType) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
-  group_by(distribution, trialType, item) %>% 
-  multi_boot_standard(col = "prop_correct")
-
-ggplot(plot2,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))+
-  facet_grid(trialType~distribution, 
-             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
-
-```
-
-# Comparing the last input with the picked object by distribution
-
-```{r}
-a <- data %>%
-  filter(slide == 6) %>%
-  select(workerid, pick)
-
-b <- data %>%
-  filter(slide == "choice") %>%
-  select(workerid, distribution, pickCat, correct_target1)
-
-b$pickSlide6 = a$pick
-
-b <- b %>%
-  filter(distribution != "c(6, 0, 0)", correct_target1 == 1) %>%
-  arrange(distribution) %>%
-  group_by(distribution) %>%
-  summarise(n = length(distribution))
-
-# 30/59 trials picking the same category as the last input slide.
-# 24/33 for 4, 2, 0
-# 7/26 for 2, 2, 2
-```

### 2018-09-08 analysis/01_kids_summary.Rmd
add adult experiment with all trials 6-0-0, add sound recordings for Pig, add analysis files for kids' pilot results and adults results

---
title: "DisCon Kids Pilot Summary"
output: html_document
---

```{r setup, include=FALSE}
#Libraries
knitr::opts_chunk$set(echo = FALSE, warning = FALSE) #no code, no warning printed
library(knitr)
library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
```

```{r data loading, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

#Data preprocessing
files <- dir("../../kids_simple/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../kids_simple/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
         subage = ifelse(subid == '180831_5', 2, subage)) # child 180831_5 is 2 but recorded as 3
```

```{r sanity checks, include=FALSE} 
#remove participants who do not pass the training threshold
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

data <- data %>% 
  filter(subid != "", subid != "test", subid != "Test")

data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item))

drop <- data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(subid)

data <- data %>%
  filter(!subid %in% drop)
```

# Kids' Experiment

## Task description

Each experiment contains 4 trials, because a previous pilot run with 4 children showed that 6 trials is too long for their attention span. Each trial contains 6 training slides (non-ambiguous utterance) and 1 test slide (ambiguous utterance), as shown below. Instead of showing the words on the screen like in the adult pilot, sound recordings of the animals are played.

![Training slide](../pictures/kids_training.png){width=350px} ![Test slide](../pictures/kids_test.png){width=350px}

Left: training slide, Right: test slide

The items appearing in a trial belong to a set of 3 categories of items (from the 6 categories: musical instruments, fruits, vehicles, furniture, mammals, clothes) that is unique across 4 trials. We run the experiment with distribution (6-0-0) across all 4 trials, with each number corresponding to how many times a category has items appear in the trial. This is to see if children are able to make category inference from the most informative set of input.

In contrast to the adult version, we moved the items first because during the first pilot run, children had a strong bias to pick the item in the middle, presumably because they were trying to interpret the agent's gaze.

## Sample size
We remove responses that get less than 5/6 correct in training slides.

```{r sample size, echo=FALSE}
sample_size <- data %>%
  distinct(subid, .keep_all = TRUE)

sample_size %>%
 group_by(subage) %>%
 summarise(n = n()) %>%
 kable(col.names = c(`subage` = "age", `n` = "n"))
```

## Finding

### Overall
```{r plot1 jitter, echo=FALSE, warning = FALSE}
#Jitter version
plot1 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, subid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -subid) %>%
  group_by(distribution, item)

plot1a <- plot1 %>%
  multi_boot_standard(col = "prop_correct")

ggplot() +
  geom_jitter(data = plot1, aes(x = item, y = prop_correct, col = item, alpha = .2), width = .3,height = .025)+
  geom_pointrange(data = plot1a, aes(x = item, y = mean, col = item, ymin = ci_lower, ymax = ci_upper),size = .8)+
  scale_colour_solarized(name = "Chosen item", 
                         breaks = c("correct", "correct2", "correct3"),
                         labels = c("most frequent", "second most frequent", "least frequent")) +
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="", y="proportion chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F) +
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank()) 
```

The dotted line represents performance expected by chance (1/3), and the error bar are 95% CIs.

More participants are able to choose the item from the most frequent category compared to the other two categories, however, performance is not much above chance level.

### By age group

We then want to further look at the result by age group.

```{r plot2, fig.width = 8, echo=FALSE, warning = FALSE}
plot2 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, subid, subage) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -subid, -subage) %>%
  group_by(distribution, item, subage) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot2,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(distribution~subage, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", `2` = "2", `3` = "3", `4` = "4"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```

From the data, 2-year-olds appear to be best at choosing the item from the most frequent category, followed by 3 and 4-year-olds respectively. However, this may be because of the small number of participants for each age group, and also the distribution of most frequent categories.

### Choosing the middle item

When only cases where the participants did not choose the correct item are included, we observe a higher proportion of participants choosing the middle item than the left and right items.

```{r plot4, echo=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

plot4 <- data %>%
  filter(phase == 'test', correct_target1 == 0) %>%
  mutate(pick_l = ifelse(pickPos == "item_l", 1, 0), 
         pick_m = ifelse(pickPos == "item_m", 1, 0),
         pick_r = ifelse(pickPos == "item_r", 1, 0)) %>%
  group_by(distribution, subid) %>%
  summarise(choose_l = mean(pick_l),
            choose_m = mean(pick_m),
            choose_r = mean(pick_r)) %>%
  gather(item, prop_choose, -distribution, -subid) %>%
  group_by(distribution, item) %>%
  multi_boot_standard(col = "prop_choose")

ggplot(plot4,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("choose_l", "choose_m", "choose_r"),
                       labels = c("left", "middle", "right"))+
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```

### Result by category

During the pilot, it also seemed that participants are able to pick up on some categories more than others.

For reference, the number of appearances as the most frequent category for each category is as such:

```{r category size, echo=FALSE}
category_size <- data %>%
  filter(phase == "test") %>%
  group_by(target1) %>%
  summarise(n = n()) %>%
  kable(col.names = c(`target1` = "category", `n` = "n"))

category_size
```

Here we're plotting only the most frequent category. Participants picked up on mammals the most, followed by vehicles, fruits, clothes, instruments, furniture.

```{r plot5, echo=FALSE, warning = FALSE, cache = TRUE}

plot5 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, subid, target1) %>%
  summarise(correct = mean(correct_target1)) %>%
  gather(item, prop_correct, -distribution, -subid, -target1) %>%
  group_by(distribution, item, target1) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot5,
       aes(x = target1, y=mean, fill=item)) +
  geom_bar(stat='identity') +
 # geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized()+
  guides(fill = F) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  labs(x="category", y= "proportion chosen")
```

### Result by trial

We also want to look at whether participants change their choosing strategy across trials, for example, because they have picked up that the task is to choose the item from the most frequent category and thus perform better over time.

```{r plot6, echo=FALSE, warning = FALSE}
plot6 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, trial, subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  gather(item, prop_correct, -distribution, -trial, -subid) %>%
  group_by(distribution, item, trial) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot6, 
       aes(x = trial, y = mean, col = item)) +
  geom_line(aes(group = item)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  scale_colour_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+ 
  geom_hline(yintercept = 1/3, lty=2)+
  theme_few() +
  labs(x="trial", y= "proportion chosen")
```

We see that while the 4th trial has the best performance (most participants choosing the item from the most frequent category), there is a decline in performance in the 3rd trial.

# Moving forward
## Design decisions
* Four trials looks like a suitable length for the attention span of participants in the age group we are looking at.
* From the analysis of item category salience, we will remove the category of furniture and instruments, which do not seem to perform as well as the other 4 categories (mammals, vehicles, fruits, clothes).

## Data collection
* We pilot 10 more children with 4 categories and 4 trials with distribution (6-0-0). If the results go in the same direction as the previous results, we run a full sample of 2-, 3-, and 4-year-olds (20 children per age group). 
* If the results from the pilot suggest that children will not be able to do this, we change the procedure so that the agent is explicitly naming the target category (for example, asks for "car" 6 times instead of for different vehicles).

### 2018-09-08 analysis/01_study1_adult.Rmd
add adult experiment with all trials 6-0-0, add sound recordings for Pig, add analysis files for kids' pilot results and adults results

---
title: "DisCon Adult Study 1"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
```

```{r data preprocessing}
# Data pre-processing
files <- dir("../../adult_raw_data/production-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_high <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))

files <- dir("../../adult_relative_raw_data/production-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_relative_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_low <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
```

```{r sanity checks, include=FALSE} 
#remove duplicated ips and workers who do not pass the training threshold
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

data_low_ip <- data_low %>% 
  filter(!is.na(workerIp)) %>%
  distinct(workerIp, trial, slide, .keep_all = TRUE)

data_low_no_ip <- data_low %>%
  filter(is.na(workerIp))

data_low <- bind_rows(data_low_ip, data_low_no_ip)

data_high_ip <- data_high %>% 
  filter(!is.na(workerIp)) %>%
  distinct(workerIp, trial, slide, .keep_all = TRUE)

data_high_no_ip <- data_high %>%
  filter(is.na(workerIp))

data_high <- bind_rows(data_high_ip, data_high_no_ip)

data <- bind_rows(data_high, data_low)

data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item))

drop <- data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

data <- data %>%
  filter(!workerid %in% drop) %>%
  mutate(distribution_prop = ifelse(distribution == "c(6, 0, 0)" | distribution == "c(3, 0, 0)", "1.00-0.00-0.00", ifelse(distribution == "c(4, 2, 0)" | distribution == "c(2, 1, 0)", "0.66-0.33-0.00", "0.33-0.33-0.33")),
         distribution_prop = factor(distribution_prop, levels = c("1.00-0.00-0.00", "0.66-0.33-0.00", "0.33-0.33-0.33")))

sample_size <- data %>%
  distinct(workerid, .keep_all = TRUE)

sample_size %>%
 summarise(n = n()) %>%
 kable()
```

```{r plot1, echo=FALSE}
plot1 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution_prop, workerid, experiment) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution_prop, -workerid, -experiment) %>%
  group_by (distribution_prop, item, experiment) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(experiment~distribution_prop,
             labeller = as_labeller(c("distribution_adults" = "high", "distribution_adults_relative" = "low", "1.00-0.00-0.00" = "1.00-0.00-0.00", "0.66-0.33-0.00" = "0.66-0.33-0.00", "0.33-0.33-0.33" = "0.33-0.33-0.33"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```

```{r plot2, echo=FALSE}
plot2 <- data %>%
  filter(phase == "test", distribution != "c(6, 0, 0)", distribution != "c(3, 0, 0)") %>%
  group_by (distribution, workerid) %>%
  summarise (lastInput = mean(same_lastInput),
             n = n()) %>% 
  multi_boot_standard(col = "lastInput")

ggplot(plot2,
       aes(x = distribution, y = mean, fill = distribution)) +
  geom_bar(stat='identity', width = 0.3) +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Distribution",
                       breaks = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(2, 1, 0)", "c(1, 1, 1)"),
                       labels = c("(6-0-0)", "(4-2-0)", "(2-2-2)", "(3-0-0)", "(2-1-0)", "(1-1-1)"))+
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen same as last item")
```

```{r wilcoxon test}
## Wilcoxon tests against chance
library(exactRankTests)

data %>%
  filter(phase == "test") %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(distribution) %>%
  mutate(mean= mean(unlist(correct)),
         stat = wilcox.exact(unlist(correct), mu = 0.5)$statistic,
         p = wilcox.exact(unlist(correct), mu = 0.5)$p.value) %>%
  select(distribution,mean,stat,p) %>%
  knitr::kable(digits = 3)
```

```{r Bayesian}
library(brms)

data_inf <- data%>%
  filter(phase == "test")

prior1 <- get_prior(correct_target1 ~ distribution_prop * experiment +
                      (distribution_prop | workerid) + (distribution_prop | agent),
                    data = data_inf, family = bernoulli())

# registered  model
bm1 <- brm(correct_target1 ~ distribution_prop * experiment +
                      (distribution_prop | workerid) + (distribution_prop | agent),
                    data = data_inf, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          prior = prior1,
          iter = 100000)
summary(bm1)

prior2 <- get_prior(correct_target1 ~ distribution_prop +
                      (distribution_prop | workerid) + (distribution_prop | agent),
                    data = data_inf, family = bernoulli())

bm2 <- brm(correct_target1 ~ distribution_prop  +
                      (distribution_prop | workerid) + (distribution_prop | agent),
                    data = data_inf, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          prior = prior2,
          iter = 100000)
summary(bm2)

bf_full_null <- bayes_factor(bm1, bm2, log = FALSE, maxiter = 5000)

bf_full_null
```

### 2018-09-08 experiments/discon_look_600.js

@@ -1,0 +1,664 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+$("#button").click(function() {
+    //disable accept button if in turk preview mode
+    if (turk.previewMode) {
+        showSlide("instructions");
+        alert("Please accept HIT to view");
+    } else {
+        showSlide('introAll')
+    }
+});
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
+    $("#"+id+"_"+orient).show();
+}
+
+function sourceRightItem(a) {
+    document.getElementById("item_r").src=a;
+}
+
+function showRightItem() {
+    document.getElementById('item_r').style.visibility='visible';
+}
+
+function hideRightItem() {
+    document.getElementById('item_r').style.visibility='hidden';
+}
+
+function sourceMiddleItem(a) {
+    document.getElementById("item_m").src=a;
+}
+
+function showMiddleItem() {
+    document.getElementById('item_m').style.visibility='visible';
+}
+
[…]

### 2018-09-08 experiments/discon_look_kid_simple_4cat.js

@@ -9,7 +9,7 @@ for (i = 0; i < preloadItems.length; i++) {
 //only preload relevant audios (no speaker change)
 var preloadAudios = ["hi", "lets", "intro", "thank", "it"];
 
-var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger"])
+var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger", "Pig"])
 
 //var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
 

### 2018-09-12 analysis/01_analysis.Rmd
analysis files for adults and kids

@@
 
-files <- dir("../../adult_relative_raw_data/production-results/")
+files <- dir("../../adult_600_raw_data/sandbox-results/")
 
@@
 for (f in files) {
-  jf <- paste("../../adult_relative_raw_data/production-results/",f,sep="")
+  jf <- paste("../../adult_600_raw_data/sandbox-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))

### 2018-09-12 analysis/01_study2_adult.Rmd
analysis files for adults and kids

---
title: "DisCon Adult Study 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
```

```{r data preprocessing}
# Data pre-processing

files <- dir("../../adult_600_raw_data/production-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
```

```{r sanity checks, include=FALSE} 
#remove duplicated ips and workers who do not pass the training threshold
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

data <- data %>% 
  distinct(workerIp, trial, slide, .keep_all = TRUE)

data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item))

drop <- data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

data <- data %>%
  filter(!workerid %in% drop)

sample_size <- data %>%
  distinct(workerid, .keep_all = TRUE)

sample_size %>%
 summarise(n = n()) %>%
 kable()
```

```{r plot1, echo=FALSE}
plot1 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid) %>%
  group_by(distribution, item) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~distribution,
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```

#Results across trials
```{r plot2, echo=FALSE}
plot2 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, trial, workerid) %>%
  summarise(correct = mean(correct_target1)) %>%
  gather(item, prop_correct, -distribution, -trial, -workerid) %>%
  group_by(distribution, item, trial) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot2, 
       aes(x = trial, y = mean, col = item)) +
  geom_line(aes(group = item)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  scale_colour_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+ 
  geom_hline(yintercept = 1/3, lty=2)+
  theme_few() +
  labs(x="trial", y= "proportion chosen")
```

### 2018-09-12 experiments/discon_look_kid.js

@@ -1,698 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-//only preload relevant audios (no speaker change)
-var preloadAudios = ["hi", "lets", "intro", "thank", "it"];
-
-var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger"])
-
-//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
-
-var audios = new Array();
-for (i = 0; i < posAgents.length; i++) {
-    for (j = 0; j < preloadAudios.length; j++) {
-        var audio = new Audio();
-        audio.src = "sounds/" + preloadAudios[j] + "_" + posAgents[i] + ".mp3"
-        audios.push(audio);
-    }
-    for (k = 0; k < preloadItems.length - 3; k++) {
-        var audio = new Audio();
-        audio.src = "sounds/" + preloadItems[k] + "_" + posAgents[i] + ".mp3"
-        audios.push(audio);
-    }
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
[…]

### 2018-09-12 experiments/discon_look_kid_simple.js

@@ -1,775 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-//only preload relevant audios (no speaker change)
-var preloadAudios = ["hi", "lets", "intro", "thank", "it"];
-
-var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger", "Pig"])
-
-//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
-
-var audios = new Array();
-for (i = 0; i < posAgents.length; i++) {
-    for (j = 0; j < preloadAudios.length; j++) {
-        var audio = new Audio();
-        audio.src = "sounds/" + preloadAudios[j] + "_" + posAgents[i] + ".mp3"
-        audios.push(audio);
-    }
-    for (k = 0; k < preloadItems.length - 3; k++) {
-        var audio = new Audio();
-        audio.src = "sounds/" + preloadItems[k] + "_" + posAgents[i] + ".mp3"
-        audios.push(audio);
-    }
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
[…]

### 2018-09-12 analysis/01_kids_summary.Rmd
datasets

@@
          subage = ifelse(subid == '180831_5', 2, subage)) # child 180831_5 is 2 but recorded as 3
+
+write.csv(data, file="../data/01_kids_summary.data.csv")
+
+data <- read_csv(file="../data/pilot.data.csv")
 ```

### 2018-09-12 analysis/01_pilot_summary.Rmd
datasets

@@
          distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))
+
+write.csv(data_pilot_another, file="../data/01_piot_summary_pilot_another.data.csv")
+data_pilot_another <- read_csv(file="../data/01_piot_summary_pilot_another.data.csv")
 
@@
 data_recency <- bind_rows(data_recency_another, data_recency_last, data_recency_look)
+
+write.csv(data_recency, file="../data/01_piot_summary_recency.data.csv")
+data_recency <- read_csv(file="../data/01_piot_summary_recency.data.csv")
 ```

### 2018-09-12 analysis/01_study1_adult.Rmd
analysis files for adults and kids
datasets

@@
 
+write.csv(data_high, file="../data/01_study1_adult_high.data.csv")
+data_high <- read_csv(file="../data/01_study1_adult_high.data.csv")
+
 files <- dir("../../adult_relative_raw_data/production-results/")
@@
          distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
+
+write.csv(data_high, file="../data/01_study1_adult_low.data.csv")
+data_low <- read_csv(file="../data/01_study1_adult_low.data.csv")
+
 ```
@@
 
+saveRDS(bm1, "01_study1_adult_models/bm1.rds")
+saveRDS(bm2, "01_study1_adult_models/bm2.rds")
+
 bf_full_null <- bayes_factor(bm1, bm2, log = FALSE, maxiter = 5000)

### 2018-09-12 analysis/01_study2_adult.Rmd
datasets

@@
          distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
+
+write.csv(data, file="../data/01_study2_adult.data.csv")
+data <- read_csv(file="../data/01_study2_adult.data.csv")
 ```

### 2018-10-28 experiments/discon_look_600_cat_name.js
adult experiment, visual and name

@@ -365,8 +365,10 @@ var experiment = {
         document.getElementById("text_introCat").innerHTML = "Here are the kinds of things they will talk about:";
         document.getElementById("text_introCat_1").innerHTML = "clothes";
         document.getElementById("text_introCat_2").innerHTML = "vehicles";
-        document.getElementById("text_introCat_3").innerHTML = "fruits";
+        document.getElementById("text_introCat_3").innerHTML = "furniture";
         document.getElementById("text_introCat_4").innerHTML = "animals";
+        document.getElementById("text_introCat_5").innerHTML = "instruments";
+        document.getElementById("text_introCat_6").innerHTML = "fruits";
     },
 
     intro: function () {

### 2018-10-29 experiments/discon_look_600_cat_name.js
change layout of adult experiment

@@ -362,16 +362,27 @@ var experiment = {
     
     introCat: function() {
         showSlide("introCat");
-        document.getElementById("text_introCat").innerHTML = "Here are the kinds of things they will talk about:";
-        document.getElementById("text_introCat_1").innerHTML = "clothes";
-        document.getElementById("text_introCat_2").innerHTML = "vehicles";
-        document.getElementById("text_introCat_3").innerHTML = "furniture";
-        document.getElementById("text_introCat_4").innerHTML = "animals";
-        document.getElementById("text_introCat_5").innerHTML = "instruments";
-        document.getElementById("text_introCat_6").innerHTML = "fruits";
+        document.getElementById("next-intro").style.visibility = "hidden";
+        document.getElementById("text_introCat").innerHTML = "Here are the kinds of things they will talk about. Take a good look and try to remember them."; 
+        
+        document.getElementById("text_introCat_2").innerHTML = "Wait for the Next button to appear to start the game.";
+        
+        document.getElementById("text_cat1").innerHTML = "clothes";
+        document.getElementById("text_cat2").innerHTML = "vehicles";
+        document.getElementById("text_cat3").innerHTML = "furniture";
+        document.getElementById("text_cat4").innerHTML = "animals";
+        document.getElementById("text_cat5").innerHTML = "instruments";
+        document.getElementById("text_cat6").innerHTML = "fruits";
+         setTimeout(function() {
+            document.getElementById("next-intro").style.visibility = "visible";
+        }, 15000);
     },
-
+    
     intro: function () {
+        document.getElementById("next-intro").style.visibility = "hidden"; 
+        
+        document.getElementById("next-trial").style.visibility = "hidden";
+        
         background2("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
 
         showSlide("transition");
@@ -381,11 +392,15 @@ var experiment = {
 
         document.getElementById("text_transition").innerHTML = "";
 
-        $(".agent_transition").click(experiment.train);      
+        setTimeout(function() {
+            document.getElementById("next-trial").style.visibility = "visible";
+        }, 1500);       
     },
 
     train : function () {
         document.getElementById("text_correctItem").style.visibility = "hidden";
+        
+        document.getElementById("next-trial").style.visibility = "hidden";
 
         document.getElementById("next-input").style.visibility = "hidden";        
         document.getElementById("next-novel").style.visibility = "hidden";
@@ -472,7 +487,7 @@ var experiment = {
[…]

### 2018-10-29 experiments/discon_look_600_cat_vis.js

@@ -362,10 +362,22 @@ var experiment = {
     
     introCat: function() {
         showSlide("introCat");
-        document.getElementById("text_introCat").innerHTML = "Here are the kinds of things they will talk about:"; 
+        
+        document.getElementById("next-intro").style.visibility = "hidden";
+        document.getElementById("text_introCat").innerHTML = "Here are the kinds of things they will talk about. Take a good look and try to remember them."; 
+        
+        document.getElementById("text_introCat_2").innerHTML = "Wait for the Next button to appear to start the game.";
+        
+        setTimeout(function() {
+            document.getElementById("next-intro").style.visibility = "visible";
+        }, 15000);
     },
 
     intro: function () {
+        document.getElementById("next-intro").style.visibility = "hidden"; 
+        
+        document.getElementById("next-trial").style.visibility = "hidden";
+        
         background2("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
 
         showSlide("transition");
@@ -375,11 +387,15 @@ var experiment = {
 
         document.getElementById("text_transition").innerHTML = "";
 
-        $(".agent_transition").click(experiment.train);      
+        setTimeout(function() {
+            document.getElementById("next-trial").style.visibility = "visible";
+        }, 1500);   
     },
 
     train : function () {
         document.getElementById("text_correctItem").style.visibility = "hidden";
+        
+        document.getElementById("next-trial").style.visibility = "hidden";
 
         document.getElementById("next-input").style.visibility = "hidden";        
         document.getElementById("next-novel").style.visibility = "hidden";
@@ -466,7 +482,7 @@ var experiment = {
             workerIp = JSON.parse(ip);
             
             data = {
-                experiment: "distribution_adults",
+                experiment: "distribution_adults_visual",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],
@@ -598,7 +614,7 @@ var experiment = {
             workerIp = JSON.parse(ip);
             
             data = {
-                experiment: "distribution_adults",
+                experiment: "distribution_adults_visual",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],

### 2018-10-29 analysis/01_pilot_summary.Rmd
updated data files

@@
 
-write.csv(data_recency, file="../data/01_piot_summary_recency.data.csv")
-data_recency <- read_csv(file="../data/01_piot_summary_recency.data.csv")
+write.csv(data_recency, file="../data/01_pilot_summary_recency.data.csv")
+data_recency <- read_csv(file="../data/01_pilot_summary_recency.data.csv")
 ```

### 2018-10-30 analysis/02_kids_power_analysis_600.Rmd
add power analysis for kids 600 4 cat

---
title: "DisCon Kids Pilot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)

library(lsr)
library(pwr)

```

```{r data}
# data from pilot
data <- read_csv(file="../data/kids_4cat_pilot.data.csv")
```
# Data processing
```{r sanity checks}
data <- data %>% 
  filter(subid != "", subid != "test", subid != "Test")

# check training performance
data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item))

# filter out children that don't get known words right
drop <- data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(subid)

data %>%
  filter(!subid %in% drop) %>%
  group_by(subage) %>%
  summarise(n = length(unique(subid)))

```

# Visualizing the data

```{r}
p1 <- data %>%
      filter(phase == "test")%>% # only test trials
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_target1))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion Correct Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Age")
```

# Power analysis
``` {r power analysis}
power <- data %>%
  filter(phase == 'test') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_target1))

t.test(power$correct, mu = 1/3)

d <- cohensD(power$correct, mu = 1/3)

pwr.t.test(d = d, sig.level = 0.05, power = .8, type = c("one.sample"))
```

### 2018-11-05 experiments/discon_look_600_cat_name.js
slight fix of name and visual experiments

@@ -661,6 +661,8 @@ var experiment = {
 
     transition: function() {
         background2("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
+        
+        document.getElementById("next-trial").style.visibility = "hidden";
 
         showSlide("transition");
         showAgent(trainingAgents[trials[0]], "transition");
@@ -685,6 +687,8 @@ var experiment = {
 
         experiment.slides = slides.slice();
 
-        $(".agent_transition").click(experiment.intro); 
+        setTimeout(function() {
+            document.getElementById("next-trial").style.visibility = "visible";
+        }, 1500);       
     },
 }

### 2018-11-05 experiments/discon_look_600_cat_vis.js

@@ -656,6 +656,8 @@ var experiment = {
 
     transition: function() {
         background2("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
+        
+        document.getElementById("next-trial").style.visibility = "hidden";
 
         showSlide("transition");
         showAgent(trainingAgents[trials[0]], "transition");
@@ -680,6 +682,8 @@ var experiment = {
 
         experiment.slides = slides.slice();
 
-        $(".agent_transition").click(experiment.intro); 
+        setTimeout(function() {
+            document.getElementById("next-trial").style.visibility = "visible";
+        }, 1500);       
     },
 }

### 2018-11-07 analysis/01_adult_600_intro.Rmd
mumble mumble experiment

---
title: "Discon Naming and Visual Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE) #no code, no warning printed
library(knitr)
library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
```

#Pilot 1 data
```{r data preprocessing}
# Data pre-processing

files <- dir("../../adult_600_raw_data/production-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_control <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)")))

data_ip <- data_control %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))

data_control <- data_control %>% 
  distinct(workerIp, trial, slide, .keep_all = TRUE)

files <- dir("../../adult_600_visual/production-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_visual/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_visual <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)")))

data_ip <- data_visual %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))

data_visual <- data_visual %>% 
  distinct(workerIp, trial, slide, .keep_all = TRUE)

files <- dir("../../adult_600_name/production-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_name/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_name <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)")))

data_ip <- data_name %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))

data_name <- data_name %>% 
  distinct(workerIp, trial, slide, .keep_all = TRUE)

data <- bind_rows(data_control, data_name, data_visual)
```

```{r}
data_ip <- data %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))
```

```{r sanity checks}
data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item))

drop <- data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

data <- data %>%
  filter(!workerid %in% drop)
```
```{r}

sample_size <- data %>%
  distinct(workerid, .keep_all = TRUE)

sample_size %>%
 group_by(experiment) %>%
 summarise(n = n())
```

```{r plot1}
plot1 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, experiment) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -experiment) %>%
  group_by(distribution, item, experiment) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~experiment, 
             labeller = as_labeller(c(distribution_adults = "Control", distribution_adults_name = "Names", distribution_adults_visual = "Visual"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")

```

### 2018-11-07 analysis/01_analysis.Rmd
mumble mumble experiment

@@
 
-files <- dir("../../adult_600_raw_data/sandbox-results/")
+files <- dir("../../adult_600_visual/sandbox-results/")
 
@@
 for (f in files) {
-  jf <- paste("../../adult_600_raw_data/sandbox-results/",f,sep="")
+  jf <- paste("../../adult_600_visual/sandbox-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))

### 2018-11-07 experiments/discon_look_600_cat_name.js

@@ -379,9 +379,9 @@ var experiment = {
     },
     
     intro: function () {
-        document.getElementById("next-intro").style.visibility = "hidden"; 
         
         document.getElementById("next-trial").style.visibility = "hidden";
+        document.getElementById("next-train").style.visibility = "hidden";
         
         background2("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
 
@@ -393,7 +393,7 @@ var experiment = {
         document.getElementById("text_transition").innerHTML = "";
 
         setTimeout(function() {
-            document.getElementById("next-trial").style.visibility = "visible";
+            document.getElementById("next-train").style.visibility = "visible";
         }, 1500);       
     },
 
@@ -662,7 +662,8 @@ var experiment = {
     transition: function() {
         background2("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
         
-        document.getElementById("next-trial").style.visibility = "hidden";
+       document.getElementById("next-trial").style.visibility = "hidden";
+        document.getElementById("next-train").style.visibility = "hidden";
 
         showSlide("transition");
         showAgent(trainingAgents[trials[0]], "transition");

### 2018-11-07 experiments/discon_look_600_mumble.js

@@ -356,21 +356,25 @@ var experiment = {
 
     introAll: function() {
         showSlide("introAll");
+        
+        document.getElementById("next-watchout").style.visibility = "visible";
+       
+        document.getElementById("next-intro").style.visibility = "hidden"; 
         document.getElementById("text_introAll").innerHTML = "You're visiting the house of these little animals. They will introduce you to the kinds of things they have at home. Your task is to click on the things they talk about.";
-        document.getElementById("text_introAll_2").innerHTML = "To move forward within the experiment, press the \"Next\" button. Press below to start.";
+         document.getElementById("text_introAll_2").innerHTML = "To move forward within the experiment, press the \"Next\" button.";
+        
     },
     
-    introCat: function() {
-        showSlide("introCat");
-        
-        document.getElementById("next-intro").style.visibility = "hidden";
-        document.getElementById("text_introCat").innerHTML = "Here are the kinds of things they will talk about. Take a good look and try to remember them."; 
-        
-        document.getElementById("text_introCat_2").innerHTML = "Wait for the Next button to appear to start the game.";
-        
-        setTimeout(function() {
-            document.getElementById("next-intro").style.visibility = "visible";
-        }, 15000);
+    introAll2: function() {
+       showSlide("introAll"); 
+        document.getElementById("next-watchout").style.visibility = "hidden";
+       
+        document.getElementById("next-intro").style.visibility = "visible"; 
+        document.getElementById("text_introAll").innerHTML = "";
+        document.getElementById("text_watchout").innerHTML = "Watch out!"
+        document.getElementById("text_watchout_2").innerHTML = "Sometimes the animals mumble and you will not be able to hear the word they say. In such cases, choose the object you think they were talking about.";
+        document.getElementById("text_introAll_2").innerHTML = "To move forward within the experiment, press the \"Next\" button. Press below to start.";
+       
     },
 
     intro: function () {
@@ -388,13 +392,11 @@ var experiment = {
 
         setTimeout(function() {
             document.getElementById("next-train").style.visibility = "visible";
-        }, 1500); 
+        }, 1500);      
     },
 
     train : function () {
         document.getElementById("text_correctItem").style.visibility = "hidden";
-        
-        document.getElementById("next-trial").style.visibility = "hidden";
 
         document.getElementById("next-input").style.visibility = "hidden";        
[…]

### 2018-11-11 experiments/discon_look_600_mumble.js
change distribution label

@@ -483,7 +483,7 @@ var experiment = {
             workerIp = JSON.parse(ip);
             
             data = {
-                experiment: "distribution_adults",
+                experiment: "distribution_adults_mumble",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],
@@ -616,7 +616,7 @@ var experiment = {
             workerIp = JSON.parse(ip);
             
             data = {
-                experiment: "distribution_adults",
+                experiment: "distribution_adults_mumble",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],

### 2018-11-11 analysis/01_adult_mumble.Rmd
mumble data

--- 2018-11-07 analysis/01_analysis.Rmd
@@
 ---
-title: "Discon analysis"
+title: "Mumble Experiment Analysis"
 output: html_document
@@
 
-files <- dir("../../adult_600_visual/sandbox-results/")
+files <- dir("../../adult_600_mumble/production-results/")
 
@@
 for (f in files) {
-  jf <- paste("../../adult_600_visual/sandbox-results/",f,sep="")
+  jf <- paste("../../adult_600_mumble/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
@@
 
- # data <- raw_data %>%
- #  mutate(correct_target3 = ifelse(correct_target1 == 0 & correct_target2 == 0, 1, 0)) %>%
- #  mutate(distribution = as.character(distribution),
- #         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
- #         pick = ifelse(pickPos == "item_l", item_l, ifelse(pickPos == "item_r", item_r, ifelse(pickPos=="item_m", item_m, NA))),
- #         correct_item = ifelse(pick == correctItem, 1, 0),
- #         pickTest = substr(pick, 4, length(pick)),
- #         correct_target1 = ifelse(pickTest == target1, 1, 0),
- #         correct_target2 = ifelse(pickTest == target2, 1, 0),
- #         correct_target3 = ifelse(pickTest == target3, 1, 0))
+ write.csv(data, file="../data/01_adult_mumble_data.csv")
 
-# write.csv(data, file="../data/pilot.data.csv")
-
-# data <- read_csv(file="../data/pilot.data.csv")
+ data <- read_csv(file="../data/01_adult_mumble_data.csv")
 ```
@@
 
-# Some preliminary tests
-```{r}
-data_test <- data %>% 
-  filter (phase == "test", distribution == "c(4, 2, 0)") %>%
-  summarise (lastInput = mean(same_lastInput),
-             n = length(distribution))
-#23/38 trials
-
-data_test <- data %>%
-  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
-  summarise (correct1 = mean(correct_target1))
-
-data_test <- data %>%
-  filter(phase == "test", distribution == "c(2, 2, 2)") %>%
-  summarise (lastInput = mean(same_lastInput),
-             n = length(distribution))
-# 23/38
-
-```
-
-# Salience of each category
-```{r}
-plot1 <- data %>%
-  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
-  group_by(distribution, target1) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3))
-
-plot1 <- data %>%
-  filter(phase == "test", distribution == "c(6, 0, 0)", target1 == "vehicles")
-
-# clothes: 2
-# fruits: 5
-# furniture: 10
-# instruments: 4
-# mammals: 8
-# vehicles: 9
-
-plot1 <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, target1) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -target1) %>%
-  group_by(distribution, item, target1) %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot(plot1,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))+
-  facet_grid(target1~distribution) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
-```
-# Do proportion of choices match the frequency in the distribution
-
 ```{r proportion of choices}
@@
   facet_grid(~distribution, 
-             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
-```
-# How does the last item seen affect the object chosen in the anaphora case? 
-```{r last item}
-plot2 <- data %>%
-  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
-  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
-  group_by (distribution, workerid) %>%
-  summarise (lastInput = mean(same_lastInput),
-             n = n()) %>% 
-  multi_boot_standard(col = "lastInput")
-
-ggplot(plot2,
-       aes(x = distribution, y = mean, fill = distribution)) +
-  geom_bar(stat='identity', width = 0.3) +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few()
-```
-
-# Are there 2 strategies in determining what "another one" means?
-```{r}
-plot3 <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid) %>%
-  group_by(distribution, item)
-
-plot3a <- plot3 %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot() +
-  geom_jitter(data = plot3, aes(x = item, y = prop_correct, col = distribution, alpha = .2), width = .3,height = .025)+
-  geom_pointrange(data = plot3a, aes(x = item, y = mean, col = distribution, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  facet_grid(~distribution)+
-  geom_hline(yintercept = 1/3, lty=2)+
-  labs(x="Item Chosen", y="Proportion Chosen")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
- # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
-
-#No - if 2 strategies: there should be fewer dots in the middle
-```
-# Does where (5,1,0) occurs determine the strategy of chosing the last item?
-```{r}
-plot3 <- data %>%
-  filter(phase == 'test', distribution == "c(5, 1, 0)") %>%
-  mutate(distType = ifelse(trial < 4, "early", "late")) %>%
-  group_by(distribution, workerid, distType) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -distType) %>%
-  group_by(distribution, item, distType)
-
-plot3a <- plot3 %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot() +
-  geom_jitter(data = plot3, aes(x = item, y = prop_correct, col = distribution, alpha = .2), width = .3,height = .025)+
-  geom_pointrange(data = plot3a, aes(x = item, y = mean, col = distribution, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  facet_grid(~distType)+
-  geom_hline(yintercept = 1/3, lty=2)+
-  labs(x="Item Chosen", y="Proportion Chosen")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
- # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
-```
-
-# Does the graded distribution come through in cases where the last input does not affect the object choice?
-```{r}
-plot3 <- data %>%
-  filter(phase == "test", distribution == "c(4, 2, 0)", same_lastInput == 0) %>%
-  group_by(distribution, workerid) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid) %>%
-  group_by(distribution, item) %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot(plot3,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))+
-  facet_grid(~distribution, 
-             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
-```
-
-# Does the framing influence the match between choice and distribution
-
-```{r plot 2}
-plot2 <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, trialType) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
-  arrange(workerid)
-
- # group_by(distribution, trialType, item) %>%
- # multi_boot_standard(col = "prop_correct")
-
-ggplot() + 
-  geom_jitter(data = plot2, 
-              aes(x = item, y=prop_correct, fill=item, col=trialType),
-              height = 0.1,
-              width = 0.1) +
-  facet_grid(trialType~distribution) +
-  theme(legend.position="none")
-
-plot2 <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, trialType) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
-  group_by(distribution, trialType, item) %>% 
-  multi_boot_standard(col = "prop_correct")
-
-ggplot(plot2,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))+
-  facet_grid(trialType~distribution, 
-             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
-
-```
-
-# Comparing the last input with the picked object by distribution
-
-```{r}
-a <- data %>%
-  filter(slide == 6) %>%
-  select(workerid, pick)
-
-b <- data %>%
-  filter(slide == "choice") %>%
-  select(workerid, distribution, pickCat, correct_target1)
-
-b$pickSlide6 = a$pick
-
-b <- b %>%
-  filter(distribution != "c(6, 0, 0)", correct_target1 == 1) %>%
-  arrange(distribution) %>%
-  group_by(distribution) %>%
-  summarise(n = length(distribution))
-
-# 30/59 trials picking the same category as the last input slide.
-# 24/33 for 4, 2, 0
-# 7/26 for 2, 2, 2
-```
-
-# Are participants choosing the middle item more? 
-```{r middle item}
-plot3 <- data %>%
-  filter(phase == 'test') %>%
-  mutate(pick_l = ifelse(pickPos == "item_l", 1, 0), 
-         pick_m = ifelse(pickPos == "item_m", 1, 0),
-         pick_r = ifelse(pickPos == "item_r", 1, 0)) %>%
-  group_by(distribution, workerid) %>%
-  summarise(choose_l = mean(pick_l),
-            choose_m = mean(pick_m),
-            choose_r = mean(pick_r)) %>%
-  gather(item, prop_choose, -distribution, -workerid) %>%
-  group_by(distribution, item) %>%
-  multi_boot_standard(col = "prop_choose")
-
-ggplot(plot3,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("choose_l", "choose_m", "choose_r"),
-                       labels = c("left", "middle", "right"))+
-  facet_grid(~distribution, 
              labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)"))) +
@@
 ```
-
-# Are participants choosing the middle item even when the middle item is wrong? 
-```{r middle item, chose incorrectly}
-plot4 <- data %>%
-  filter(phase == 'test', correct_target1 == 0) %>%
-  mutate(pick_l = ifelse(pickPos == "item_l", 1, 0), 
-         pick_m = ifelse(pickPos == "item_m", 1, 0),
-         pick_r = ifelse(pickPos == "item_r", 1, 0)) %>%
-  group_by(distribution, workerid) %>%
-  summarise(choose_l = mean(pick_l),
-            choose_m = mean(pick_m),
-            choose_r = mean(pick_r)) %>%
-  gather(item, prop_choose, -distribution, -workerid) %>%
-  group_by(distribution, item) %>%
-  multi_boot_standard(col = "prop_choose")
-
-ggplot(plot4,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("choose_l", "choose_m", "choose_r"),
-                       labels = c("left", "middle", "right"))+
-  facet_grid(~distribution, 
-             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)"))) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
-```

### 2018-11-14 analysis/01_adult_510_recency.Rmd
clean up analysis folder and add overview file

---
title: "Discon recency analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
```

#Recency data ("another one")
```{r}
files <- dir("../../recency_raw_data/production-results")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../recency_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_recency_another <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(5, 1, 0)", "c(2, 2, 2)")))

data_ip <- data_recency_another %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))

data_recency_another <- data_recency_another %>% 
  distinct(workerIp, trial, slide, .keep_all = TRUE)
```

#Recency data ("Here's the last one.")
```{r}
files <- dir("../../recency_last_raw_data/production-results")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../recency_last_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_recency_last <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(5, 1, 0)", "c(2, 2, 2)")))

data_ip <- data_recency_last %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))

data_recency_last <- data_recency_last %>% 
  distinct(workerIp, trial, slide, .keep_all = TRUE)
```

#Recency data ("Look at that.")
```{r}
files <- dir("../../recency_look_raw_data/production-results")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../recency_look_raw_data/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data_recency_look <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(5, 1, 0)", "c(2, 2, 2)")))

data_ip <- data_recency_look %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))

data_recency_look <- data_recency_look %>% 
  distinct(workerIp, trial, slide, .keep_all = TRUE)
```

```{r}
data <- bind_rows(data_recency_another, data_recency_last, data_recency_look)

#check if workerIp is repeating
data_ip <- data %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))
```

```{r sanity checks}
data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item))

drop <- data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

data <- data %>%
  filter(!workerid %in% drop)
```

# Do proportion of choices match the frequency in the distribution?
```{r plot1}
plot1 <- data %>%
  filter(phase == 'test', distribution == "c(5, 1, 0)") %>%
  group_by(distribution, workerid, experiment) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -experiment) %>%
  group_by(distribution, item, experiment) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~experiment, 
             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", recency = "Here's another one.", recency_last = "Here's the last one.", recency_look = "Look at that."))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```

# How does the last item seen affect the object chosen in the anaphora case? 
```{r}
plot2 <- data %>%
  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
#  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
  group_by (distribution, workerid, experiment) %>%
  summarise (lastInput = mean(same_lastInput),
             n = n()) %>%
  group_by(distribution, experiment) %>%
  multi_boot_standard(col = "lastInput")

ggplot(plot2,
       aes(x = distribution, y = mean, fill = distribution)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  facet_grid(~experiment, 
             labeller = as_labeller(c(recency = "Here's another one.", recency_last = "Here's the last one.", recency_look = "Look at that.")))+ 
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  labs(x="", y= "proportion chosen same as last item")
```

# Are there 2 strategies in determining what "another one" means?
```{r}
plot3 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, experiment) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -experiment) %>%
  group_by(distribution, item, experiment)

plot3a <- plot3 %>%
  multi_boot_standard(col = "prop_correct")

ggplot() +
  geom_jitter(data = plot3, aes(x = item, y = prop_correct, col = item, alpha = .2), width = .3,height = .025)+
  geom_pointrange(data = plot3a, aes(x = item, y = mean, col = item, ymin = ci_lower, ymax = ci_upper),size = .8)+
  facet_grid(experiment~distribution, 
             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", recency = "Here's another one.", recency_last = "Here's the last one.", recency_look = "Look at that.")))+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Item Chosen", y="Proportion Chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
 # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))

#No - if 2 strategies: there should be fewer dots in the middle
```

### 2018-11-14 analysis/01_adult_it_overview.Rmd
clean up analysis folder and add overview file

---
title: "Adults 6-0-0/5-1-0 overview"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
library(lsr)
```

Here we compare data from the 6-0-0 distribution in four different conditions. 
*"it" - At test, animal asks: "Can you click on it?".
*"it - name categories" - same as "it" but participants read the names of the categories that will feature in the game as part of the introduction.
*"it - show categories" - same as "it" but participants see all pictures that will feature in the game grouped by category as part of the introduction.
*"mumble" - At test, animal asks: "Can you click on the [mumble mumble]?". Participants are told that animals sometimes mumble during the introdcution.

```{r importing data, include=F}

# data for differetn intros

intros <- read_csv(file="../data/adult_intros.data.csv")

drop_intros <- intros %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

intros <- intros  %>%
  filter(!workerid %in% drop_intros)%>%
  mutate(experiment = recode(experiment,
                             "distribution_adults_name" = "it - name categories",
                             "distribution_adults_visual" = "it - show categories",
                             "distribution_adults" = "it"))
# mumble data

 mumble <- read_csv(file="../data/01_adult_mumble_data.csv")%>%
   mutate(experiment = "mumble")

# filter out children that don't get known words right
drop_mumble <- mumble %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

mumble <- mumble  %>%
  filter(!workerid %in% drop_mumble)

# data for 510

d510 <- read_csv(file="../data/01_pilot_summary_recency.data.csv") %>%
  filter(distribution == "c(5, 1, 0)")

### combining datasets

data <- bind_rows(
  mumble,
  intros
)

```

# Correct choice by experiment
```{r, echo = F}
plot1 <- data %>%
  filter(phase != "training")%>%
  group_by(experiment,workerid)%>%
  summarise(correct = mean(correct_target1))

plot2 <-plot1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = plot1, aes(x = experiment, y = correct, col = experiment, alpha = .2), width = .3,height = .01)+
  geom_pointrange(data = plot2, aes(x = experiment, y = mean, col = experiment, ymin = ci_lower, ymax = ci_upper),size = .8)+
  #facet_grid(~distribution)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Experiment", y="Proportion Correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F, col = F) 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

# Bayesian t-tests for each condition
```{r}

library(BayesianFirstAid)

data %>%
  filter(phase != "training") %>%
  group_by(experiment, workerid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(experiment) %>%
  mutate(mu = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,1],
         HDIlo = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,5],
         HDIup = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,6],
         eff.size = bayes.t.test(unlist(correct), mu = 1/3)$stats[4,1]) %>%
  select(mu,HDIlo,HDIup,eff.size)

```

# Correct choice by experiment and category
```{r}
plot3 <- data %>%
  filter(phase != "training")%>%
  group_by(experiment,target1, workerid)%>%
  summarise(correct = mean(correct_target1))%>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_pointrange(data = plot3, aes(x = target1, y = mean, col = experiment, ymin = ci_lower, ymax = ci_upper),size = .8)+
  facet_grid(experiment~.)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Target Category", y="Proportion Correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F, col = F) 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

# Correct chioce by experiment and trial
```{r}
plot4 <- data %>%
  filter(phase != "training")%>%
  group_by(experiment,trial, workerid)%>%
  summarise(correct = mean(correct_target1))%>%
  multi_boot_standard(col = "correct")

ggplot(data = plot4,aes(x = trial, y = mean, col = experiment)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper))+
  #facet_grid(experiment~.)+
  geom_line(aes(group = experiment)) + 
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Trial", y="Proportion Correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F) 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

# Test to see if the most recent is picked: 510 distribution

Here the last item was always from a different category
```{r}
plot5 <- d510 %>%
  filter(phase != "training", 
         experiment == "recency_look")%>%
  group_by(experiment,workerid)%>%
  summarise(correct = mean(correct_target1))

plot6 <-plot5 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = plot5, aes(x = experiment, y = correct, col = experiment, alpha = .2), width = .3,height = .01)+
  geom_pointrange(data = plot6, aes(x = experiment, y = mean, col = experiment, ymin = ci_lower, ymax = ci_upper),size = .8)+
  #facet_grid(~distribution)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Experiment", y="Proportion Correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F, col = F) 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

```

```{r}
d510 %>%
  filter(phase != "training") %>%
  group_by(experiment, workerid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(experiment) %>%
  mutate(mu = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,1],
         HDIlo = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,5],
         HDIup = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,6],
         eff.size = bayes.t.test(unlist(correct), mu = 1/3)$stats[4,1]) %>%
  select(mu,HDIlo,HDIup,eff.size)
```

### 2018-11-14 analysis/02_kids.Rmd
clean up analysis folder and add overview file

--- 2018-08-29 analysis/01_kids.Rmd
@@
 
+library(lsr)
+library(pwr)
+
 ```
@@
 ```{r data pre-processing}
+
+files <- dir("../../kids_simple_4cat/")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("../../kids_simple_4cat/",f,sep="")
+  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  id <- as_data_frame(jd$data$data)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+data_4cat <- raw_data %>%
+  mutate(distribution = as.character(distribution),
+         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))
 
@@
 
-data <- raw_data %>%
+data_6cat <- raw_data %>%
   mutate(distribution = as.character(distribution),
-         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))
+         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)"))) %>%
+  filter(target1 != "furniture", target1 != "instruments")
+
+data <- bind_rows(data_4cat, data_6cat)
+
+write.csv(data, file="../data/kids_4cat_pilot.data.csv")
+
+data <- read_csv(file="../data/kids_4cat_pilot.data.csv")
 ```
@@
 
-data <- data %>%
-  filter(!subid %in% drop)
+data %>%
+  filter(!subid %in% drop) %>%
+  group_by(subage) %>%
+  summarise(n = length(unique(subid)))
 
@@
 ```
+
+```{r plot2, fig.width = 8, echo=FALSE, warning = FALSE}
+plot2 <- data %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, subid, subage) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -subid, -subage) %>%
+  group_by(distribution, item, subage) %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot(plot2,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("correct", "correct2", "correct3"),
+                       labels = c("most frequent", "second most frequent", "least frequent"))+
+  facet_grid(distribution~subage, 
+             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", `2` = "2", `3` = "3", `4` = "4"))) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
+```
+
+```{r plot5, echo=FALSE, warning = FALSE, cache = TRUE}
+
+plot5 <- data %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, subid, target1) %>%
+  summarise(correct = mean(correct_target1)) %>%
+  gather(item, prop_correct, -distribution, -subid, -target1) %>%
+  group_by(distribution, item, target1) %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot(plot5,
+       aes(x = target1, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+ # geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized()+
+  guides(fill = F) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  labs(x="category", y= "proportion chosen")
+```
+
+``` {r power analysis}
+power <- data %>%
+  filter(phase == 'test') %>%
+  group_by(subid) %>%
+  summarise(correct = mean(correct_target1))
+
+t.test(power$correct, mu = 1/3)
+
+cohensD(power$correct, mu = 1/3)
+
+pwr.t.test(d = 0.5127475, sig.level = 0.05, power = .8, type = c("one.sample"))
+```

### 2018-11-25 analysis/01_analysis.Rmd
speaker change experiment

@@
   facet_grid(~distribution, 
-             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
+             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
   geom_hline(yintercept = 1/3, lty=2) +

### 2018-11-25 experiments/discon_look_600_speakerchange.js

@@ -1,0 +1,753 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+$("#button").click(function() {
+    //disable accept button if in turk preview mode
+    if (turk.previewMode) {
+        showSlide("instructions");
+        alert("Please accept HIT to view");
+    } else {
+        showSlide('introAll')
+    }
+});
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
+    $("#"+id+"_"+orient).show();
+}
+
+function sourceRightItem(a) {
+    document.getElementById("item_r").src=a;
+}
+
+function showRightItem() {
+    document.getElementById('item_r').style.visibility='visible';
+}
+
+function hideRightItem() {
+    document.getElementById('item_r').style.visibility='hidden';
+}
+
+function sourceMiddleItem(a) {
+    document.getElementById("item_m").src=a;
+}
+
+function showMiddleItem() {
+    document.getElementById('item_m').style.visibility='visible';
[…]

### 2018-12-17 experiments/discon_look_600_speakerchange.js
make objects disappear and appear with speakers

@@ -538,6 +538,9 @@ var experiment = {
 
             setTimeout(function() {
                 document.getElementById("text_correctItem").style.visibility = "hidden";
+                hideLeftItem();
+                hideMiddleItem();
+                hideRightItem();
             }, 2000);
 
         }, 2000);
@@ -551,8 +554,8 @@ var experiment = {
                 $("#"+alternativeAgents[0]+"_look_l").animate({opacity: 1, queue: true},1000);
                 $("#"+alternativeAgents[0]+"_look_l").animate({left: 300, queue: true},2000);
                 setTimeout(function() {
-                document.getElementById("text_correctItem").style.visibility = "visible";
-                document.getElementById("text_correctItem").innerHTML = "Oh hi, I'm " + alternativeAgents[0] +"!";
+                    document.getElementById("text_correctItem").style.visibility = "visible";
+                    document.getElementById("text_correctItem").innerHTML = "Oh hi, I'm " + alternativeAgents[0] +"!";
                 }, 1000);
                
             }, 5000)
@@ -568,8 +571,8 @@ var experiment = {
                 $("#"+trainingAgents[trials[0]]+"_look_l").animate({opacity: 1, queue: true},1000);
                 $("#"+trainingAgents[trials[0]]+"_look_l").animate({left: 300, queue: true},2000);
                 setTimeout(function() {
-                document.getElementById("text_correctItem").style.visibility = "visible";
-                document.getElementById("text_correctItem").innerHTML = "I'm back."
+                    document.getElementById("text_correctItem").style.visibility = "visible";
+                    document.getElementById("text_correctItem").innerHTML = "I'm back."
                 }, 1000);
                 
             }, 5000)
@@ -596,14 +599,11 @@ var experiment = {
         }
 
         sourceLeftItem("images/" + experiment.position[0] + ".png");
-        hideLeftItem();
 
         sourceMiddleItem("images/" + experiment.position[1] + ".png");
-        hideMiddleItem();
-
+      
         sourceRightItem("images/" + experiment.position[2] + ".png");
-        hideRightItem();
-
+       
         // pause for 1s before items appear.
         setTimeout(function() {
             document.getElementById("text_correctItem").style.visibility = "visible";
@@ -718,8 +718,12 @@ var experiment = {
         document.getElementById("next-train").style.visibility = "hidden";
 
         showSlide("transition");
-        showAgent(trainingAgents[trials[0]], "transition");
-
[…]

### 2018-12-18 analysis/01_adult_it_overview.Rmd
update adult overview analysis file

@@
 d510 %>%
-  filter(phase != "training") %>%
+  filter(phase != "training",
+         experiment == "recency_look") %>%
   group_by(experiment, workerid) %>%

### 2018-12-19 experiments/discon_look_600_speakerchange.js
changes to speaker change experiment

@@ -117,7 +117,7 @@ function getKeys(obj){
 
 showSlide("instructions");
 
-var slides = [1, 2, 3, 4, 5, 6, "speaker", "choice"]
+var slides = [1, 2, 3, 4, 5, 6, "choice"]
 
 var trials = [0, 1, 2, 3, 4, 5]
 
@@ -400,11 +400,6 @@ var experiment = {
             return;
         }
 
-        if (experiment.slides[0] == "speaker") {
-            experiment.speaker();
-            return;
-        }
-
         experiment.position = shuffle([experiment.targetsF[0][0], experiment.targetsF2[0][0], experiment.targetsF3[0][0]]);
 
         background("images/backgrounds/back_int" + experiment.backgrounds[0] + ".jpg");
@@ -526,9 +521,8 @@ var experiment = {
 
     speaker : function () {
        
-        showSlide("input");
-        showAgent(trainingAgents[trials[0]], "straight");
-        document.getElementById("text_correctItem").style.visibility = "visible";
+        //showAgent(trainingAgents[trials[0]], "straight");
+        //document.getElementById("text_correctItem").style.visibility = "visible";
         document.getElementById("text_correctItem").innerHTML = "I need to go.";
 
         setTimeout(function() {
@@ -538,9 +532,9 @@ var experiment = {
 
             setTimeout(function() {
                 document.getElementById("text_correctItem").style.visibility = "hidden";
-                hideLeftItem();
+/*                hideLeftItem();
                 hideMiddleItem();
-                hideRightItem();
+                hideRightItem();*/
             }, 2000);
 
         }, 2000);
@@ -556,7 +550,8 @@ var experiment = {
                 setTimeout(function() {
                     document.getElementById("text_correctItem").style.visibility = "visible";
                     document.getElementById("text_correctItem").innerHTML = "Oh hi, I'm " + alternativeAgents[0] +"!";
-                }, 1000);
+                    showAgent(alternativeAgents[0], "straight");
+                }, 3000);
                
             }, 5000)
             
@@ -573,12 +568,13 @@ var experiment = {
                 setTimeout(function() {
                     document.getElementById("text_correctItem").style.visibility = "visible";
                     document.getElementById("text_correctItem").innerHTML = "I'm back."
-                }, 1000);
+                    showAgent(trainingAgents[trials[0]], "straight");
+                }, 3000);
                 
             }, 5000)
         };
 
-        setTimeout(experiment.choice, 9000);
[…]

### 2018-12-19 experiments/discon_look_600_speakerchange.js
changes to speaker change experiment

@@ -520,9 +520,6 @@ var experiment = {
     },
 
     speaker : function () {
-       
-        //showAgent(trainingAgents[trials[0]], "straight");
-        //document.getElementById("text_correctItem").style.visibility = "visible";
         document.getElementById("text_correctItem").innerHTML = "I need to go.";
 
         setTimeout(function() {
@@ -532,12 +529,9 @@ var experiment = {
 
             setTimeout(function() {
                 document.getElementById("text_correctItem").style.visibility = "hidden";
-/*                hideLeftItem();
-                hideMiddleItem();
-                hideRightItem();*/
             }, 2000);
 
-        }, 2000);
+        }, 500);
 
         if (experiment.speakerChange[0] == "change"){
 
@@ -573,8 +567,6 @@ var experiment = {
                 
             }, 5000)
         };
-
-       // setTimeout(experiment.choice, 9000);
     },
 
     choice : function () {
@@ -603,10 +595,10 @@ var experiment = {
             showLeftItem();
             showMiddleItem();
             showRightItem();
-            setTimeout(experiment.speaker(), 1000);
-        }, 2000);
+            experiment.speaker();
+        }, 1000);
 
-        // pause for 1.5s before "next" button appears.
+        // pause for 10s before "next" button appears.
         setTimeout(function() {
             document.getElementById("next-novel").style.visibility = 'visible';
         }, 10000);

### 2018-12-19 experiments/discon_look_600_speakerchange.js
record speaker change

@@ -667,7 +667,8 @@ var experiment = {
                 agent: trainingAgents[trials[0]],
                 phase: "test",
                 slide: experiment.slides[0], speakerChange:experiment.speakerChange[0],
-
+                alternativeAgent: alternativeAgents[0],
+                    
                 distribution: posDist[trials[0]],
                 target1: trialTargets[trials[0]][0],
                 target2: trialTargets[trials[0]][1],

### 2018-12-20 analysis/01_adult_speakerchange.Rmd
change label for speaker change experiment

---
title: "DisCon Speaker Change Adult Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2018-12-20 experiments/discon_look_600_speakerchange.js

@@ -476,7 +476,7 @@ var experiment = {
             workerIp = JSON.parse(ip);
 
             data = {
-                experiment: "distribution_adults",
+                experiment: "distribution_adults_speakerchange",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],
@@ -661,7 +661,7 @@ var experiment = {
             workerIp = JSON.parse(ip);
 
             data = {
-                experiment: "distribution_adults",
+                experiment: "distribution_adults_speakerchange",
                 trial: trials[0] + 1,
 
                 agent: trainingAgents[trials[0]],

### 2018-12-21 analysis/01_adult_speakerchange.Rmd
change introduction of speaker change experiment

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE) #no code, no warning printed
+library(knitr)
+library(tidyverse)
+library(ggplot2)
+library(jsonlite)
+library(tidyr)
+library(stringr)
+library(dplyr)
+library(ggthemes)
+library(langcog)
 ```
 
-## R Markdown
+#Pilot 1 data
+```{r data preprocessing}
+# Data pre-processing
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+files <- dir("../../adult_600_speakerchange/sandbox-results/")
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("../../adult_600_speakerchange/sandbox-results/",f,sep="")
+  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  id <- as_data_frame(jd$answers$data$data) %>%
+    mutate(workerid = jd$WorkerId)
+  raw_data <- bind_rows(raw_data, id)
+}
 
-```{r cars}
-summary(cars)
+data <- raw_data %>%
+  mutate(distribution = as.character(distribution),
+         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
+         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
 ```
 
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
+```{r}
+data_ip <- data %>%
+  filter(phase == 'training') %>%
+  group_by(workerIp) %>%
+  summarise(correct = mean(correct_item))
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r sanity checks}
+data %>%
+  filter(phase == 'training') %>%
+  group_by(workerid) %>%
+  summarise(correct = mean(correct_item))
+
+drop <- data %>%
+  filter(phase == 'training') %>%
+  group_by(workerid) %>%
+  summarise(correct = mean(correct_item)) %>%
+  filter(correct < 0.83) %>%
+  pull(workerid)
+
+data <- data %>%
+  filter(!workerid %in% drop)
+```
+```{r}
+
+sample_size <- data %>%
+  distinct(workerid, .keep_all = TRUE)
+
+sample_size %>%
+ group_by(experiment) %>%
+ summarise(n = n())
+```
+
+```{r plot1}
+plot1 <- data %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, workerid, speakerChange) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -workerid, -speakerChange) %>%
+  group_by(distribution, item, speakerChange) %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot(plot1,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("correct", "correct2", "correct3"),
+                       labels = c("most frequent", "second most frequent", "least frequent"))+
+  facet_grid(~speakerChange, 
+             labeller = as_labeller(c(change = "speaker change", same = "no change"))) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
+
+```

### 2018-12-21 experiments/discon_look_600_speakerchange.js

@@ -365,7 +365,7 @@ var experiment = {
 
     introAll: function() {
         showSlide("introAll");
-        document.getElementById("text_introAll").innerHTML = "You're visiting the house of these little animals. They will introduce you to the kinds of things they have at home. Your task is to click on the things they talk about.";
+        document.getElementById("text_introAll").innerHTML = "You're visiting the house of these little animals. They will introduce you to the kinds of things they have at home. Your task is to click on the things they talk about. Pay close attention to the animals. Sometimes one animal goes away and a different animal returns.";
         document.getElementById("text_introAll_2").innerHTML = "To move forward within the experiment, press the \"Next\" button. Press below to start.";
     },
 

### 2018-12-23 experiments/discon_look_600_speakerchange_oppositeside.js
make speaker change more clear

@@ -1,0 +1,768 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+$("#button").click(function() {
+    //disable accept button if in turk preview mode
+    if (turk.previewMode) {
+        showSlide("instructions");
+        alert("Please accept HIT to view");
+    } else {
+        showSlide('introAll')
+    }
+});
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
+    $("#"+id+"_"+orient).show();
+}
+
+function sourceRightItem(a) {
+    document.getElementById("item_r").src=a;
+}
+
+function showRightItem() {
+    document.getElementById('item_r').style.visibility='visible';
+}
+
+function hideRightItem() {
+    document.getElementById('item_r').style.visibility='hidden';
+}
+
+function sourceMiddleItem(a) {
+    document.getElementById("item_m").src=a;
+}
+
+function showMiddleItem() {
+    document.getElementById('item_m').style.visibility='visible';
[…]

### 2018-12-24 experiments/discon_look_600_speakerchange_oppositeside.js
change speaker change experiment

@@ -543,24 +543,13 @@ var experiment = {
                 $("#"+alternativeAgents[0]+"_look_r").animate({left: 300, queue: true},2000);
 
                 setTimeout(function() {
-
-                    showAgent(alternativeAgents[0], "look_l");
-                    document.getElementById(alternativeAgents[0]+"_look_l").style.left="300px";
-                    setTimeout(function() {
-
-                        showAgent(alternativeAgents[0], "look_r");
-                        document.getElementById(alternativeAgents[0]+"_look_l").style.left="300px";
-                    }, 1000);
-                }, 3000);
-
-                setTimeout(function() {
                     showAgent(alternativeAgents[0], "straight");
                     document.getElementById("text_correctItem").style.visibility = "visible";
                     document.getElementById("text_correctItem").innerHTML = "Hi, I'm " + alternativeAgents[0] + "!";
                     setTimeout(function() {
                         document.getElementById("text_correctItem").innerHTML = "What's going on here?";
                     }, 1500);
-                }, 5000);
+                }, 3000);
 
             }, 5000)
 
@@ -621,7 +610,7 @@ var experiment = {
         if (experiment.speakerChange[0] == "change"){
             setTimeout(function() {
                 document.getElementById("next-novel").style.visibility = 'visible';
-            }, 15000);
+            }, 12000);
         };
     },
 

### 2019-01-09 analysis/01_adult_speakerchange.Rmd
prepare kids' experiment

@@
 
-files <- dir("../../adult_600_speakerchange/sandbox-results/")
+files <- dir("../../adult_600_speakerchange/production-results/")
 
@@
 for (f in files) {
-  jf <- paste("../../adult_600_speakerchange/sandbox-results/",f,sep="")
+  jf <- paste("../../adult_600_speakerchange/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
@@
 
+plot3 <- data %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, workerid, speakerChange) %>%
+  summarise(correct = mean(correct_target1)) %>%
+  gather(item, prop_correct, -distribution, -workerid, -speakerChange) %>%
+  group_by(distribution, item, speakerChange)
+
+plot3a <- plot3 %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot() +
+  geom_jitter(data = plot3, aes(x = speakerChange, y = prop_correct, col = speakerChange, alpha = .2), width = .3,height = .025)+
+  geom_pointrange(data = plot3a, aes(x = speakerChange, y = mean, col = speakerChange, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="Speaker Change", y="Correct Item Chosen")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F) +
+scale_colour_solarized(name = "Speaker Change",
+                       breaks = c("correct", "correct2", "correct3"),
+                       labels = c("most frequent", "second most frequent", "least frequent"))
+
 ```
+#Check how many of the participants choosing correct in the no change condition is affected in the speaker change condition
+```{r plot2}
+pull <- data %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, workerid, speakerChange) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  filter(speakerChange == "same" & correct > 1/3) %>%
+  pull(workerid)
+
+plot2 <- data%>%
+  filter(workerid %in% pull) %>%
+  filter(phase == 'test') %>%
+  group_by(distribution, workerid, speakerChange) %>%
+  summarise(correct = mean(correct_target1),
+            correct2 = mean(correct_target2),
+            correct3 = mean(correct_target3)) %>%
+  gather(item, prop_correct, -distribution, -workerid, -speakerChange) %>%
+  group_by(distribution, item, speakerChange) %>%
+  multi_boot_standard(col = "prop_correct")
+
+ggplot(plot2,
+       aes(x = item, y=mean, fill=item)) +
+  geom_bar(stat='identity') +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  scale_fill_solarized(name = "Chosen item",
+                       breaks = c("correct", "correct2", "correct3"),
+                       labels = c("most frequent", "second most frequent", "least frequent"))+
+  facet_grid(~speakerChange, 
+             labeller = as_labeller(c(change = "speaker change", same = "no change"))) +
+  geom_hline(yintercept = 1/3, lty=2) +
+  ylim(0, 1) +
+  theme_few() +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
+  labs(x="", y= "proportion chosen")
+```

### 2019-01-09 experiments/discon_look_kid_simple_4cat.js

@@ -366,13 +366,8 @@ var experiment = {
             $("#checkMessage").html('<font color="red">You must input a subject age</font>');
             return;
         }
-        if (document.getElementById("subjectOrder").value.length < 1) {
-			$("#checkMessage").html('<font color="red">You must input an order number</font>');
-			return;
-		}
         experiment.subid = document.getElementById("subjectID").value;
         experiment.subage = document.getElementById("subjectAge").value;
-        experiment.suborder = document.getElementById("subjectOrder").value
         experiment.trainingDot()
         
     },  
@@ -445,7 +440,7 @@ var experiment = {
 
             document.getElementById("next-input").style.visibility = "visible";
 
-        }, 1000);
+        }, 900);
     },
 
     train2 : function() {
@@ -490,12 +485,10 @@ var experiment = {
 
                 var subid = experiment.subid;
                 var subage = experiment.subage; 
-                var suborder =  experiment.suborder;
 
                 data = {
                     subid: subid,
                     subage: subage,
-                    suborder: suborder,
                     experiment: "distribution_kids_simple",
                     trial: trials[0] + 1,
 
@@ -533,7 +526,7 @@ var experiment = {
                 setTimeout(function() {
                     clickedItem.style.border = '0px';
                     experiment.train();
-                }, 1500);
+                }, 900);
             }); 
         };
     },
@@ -568,7 +561,7 @@ var experiment = {
 
             document.getElementById("next-novel").style.visibility = 'visible';
 
-        }, 1000);
+        }, 900);
     },
 
     choice2 : function() {
@@ -626,12 +619,10 @@ var experiment = {
 
                 var subid = experiment.subid;
                 var subage = experiment.subage;  
-                var suborder =  experiment.suborder;
 
                 data = {
                     subid: subid,
                     subage: subage,
-                    suborder: suborder,
                     experiment: "distribution_kids_simple",
                     trial: trials[0] + 1,
 
@@ -666,7 +657,7 @@ var experiment = {
                 setTimeout(function() {
                     clickedItem.style.border = '0px';
                     experiment.transition();
-                }, 1500);
+                }, 900);
             });
         };       
     },

### 2019-01-12 analysis/01_analysis.Rmd
Added preference experiment

@@
 
-files <- dir("../../adult_600_mumble/production-results/")
+files <- dir("../../pilot_1_raw_data/production-results_framing/")
 
@@
 for (f in files) {
-  jf <- paste("../../adult_600_mumble/production-results/",f,sep="")
+  jf <- paste("../../pilot_1_raw_data/production-results_framing/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
@@
   filter(phase == 'test') %>%
-  group_by(distribution, workerid, trialType) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
+  group_by(distribution, trialType) %>%
+  summarise(correct = mean(correct_target1)
+            ) %>%
+  gather(item, prop_correct, -distribution, -trialType) %>%
   arrange(workerid)
 
- # group_by(distribution, trialType, item) %>%
- # multi_boot_standard(col = "prop_correct")
+  group_by(distribution, trialType, item) %>%
+  multi_boot_standard(col = "prop_correct")
 

### 2019-01-12 experiments/discon_look_600_speakerchange_oppositeside_preference.js

@@ -1,0 +1,749 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+$("#button").click(function() {
+    //disable accept button if in turk preview mode
+    if (turk.previewMode) {
+        showSlide("instructions");
+        alert("Please accept HIT to view");
+    } else {
+        showSlide('introAll')
+    }
+});
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
+    $("#"+id+"_"+orient).show();
+}
+
+function sourceRightItem(a) {
+    document.getElementById("item_r").src=a;
+}
+
+function showRightItem() {
+    document.getElementById('item_r').style.visibility='visible';
+}
+
+function hideRightItem() {
+    document.getElementById('item_r').style.visibility='hidden';
+}
+
+function sourceMiddleItem(a) {
+    document.getElementById("item_m").src=a;
+}
+
+function showMiddleItem() {
+    document.getElementById('item_m').style.visibility='visible';
[…]

### 2019-01-13 experiments/discon_look_600_speakerchange_oppositeside_preference.js
changed intro of speakers to 'favorite things'

@@ -365,7 +365,7 @@ var experiment = {
 
     introAll: function() {
         showSlide("introAll");
-        document.getElementById("text_introAll").innerHTML = "You're visiting the house of these little animals. They will introduce you to their favroite things. Your task is to click on the things they talk about.";
+        document.getElementById("text_introAll").innerHTML = "You're visiting the house of these little animals. They will introduce you to their favorite things. Your task is to click on the things they talk about.";
         document.getElementById("text_introAll_3").innerHTML = "Pay close attention to the animals. Sometimes one animal goes away and a different animal returns.";
         document.getElementById("text_introAll_2").innerHTML = "To move forward within the experiment, press the \"Next\" button. Press below to start.";
     },
@@ -379,7 +379,7 @@ var experiment = {
         showSlide("transition");
 
         showAgent(trainingAgents[trials[0]], "transition");
-        document.getElementById("text_intro").innerHTML = "Hi, I'm " + trainingAgents[trials[0]] + ". These are the things I like.";
+        document.getElementById("text_intro").innerHTML = "Hi, I'm " + trainingAgents[trials[0]] + ". Let me tell you about my favorite things.";
 
         document.getElementById("text_transition").innerHTML = "";
 
@@ -546,7 +546,7 @@ var experiment = {
                 setTimeout(function() {
                     showAgent(alternativeAgents[0], "straight");
                     document.getElementById("text_correctItem").style.visibility = "visible";
-                    document.getElementById("text_correctItem").innerHTML = "Hi, I'm " + alternativeAgents[0] + "!";
+                    document.getElementById("text_correctItem").innerHTML = "Hi, I'm " + alternativeAgents[0] + ". Let me tell you about my favorite things.";
                 }, 3000);
 
             }, 5000)

### 2019-01-16 analysis/02_kids.Rmd
update analysis file

@@
 files <- dir("../../kids_simple_4cat/")
+#files <- dir("../../kids_raw_data/600/")
 
@@
   jf <- paste("../../kids_simple_4cat/",f,sep="")
+#  jf <- paste("../../kids_raw_data/600/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))

### 2019-01-16 analysis/02_kids_600.Rmd
new analysis file for kids data

---
title: "DisCon Kids Pilot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
library(readxl)

library(lsr)
library(pwr)

```

```{r data pre-processing}

#files <- dir("../../kids_simple_4cat/")
files <- dir("../../kids_raw_data/600/")

raw_data <- data_frame()
for (f in files) {
#  jf <- paste("../../kids_simple_4cat/",f,sep="")
  jf <- paste("../../kids_raw_data/600/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,36,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  filter(Condition == "d600")%>%
  mutate(dob = as.Date(dob))%>%
  select(subid,experimenter,keep_drop,sex,dob)

#unique(log$subid)
#sum(log$keep_drop == "drop")

data <- left_join(raw_data,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

unique(data$subid)

#write.csv(data, file="../data/kids_600.data.csv")

#data <- read_csv(file="../data/kids_600.data.csv")
```

```{r sanity checks}
data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item))

drop <- data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(subid)

data %>%
  filter(!subid %in% drop) %>%
  group_by(subage) %>%
  summarise(n = length(unique(subid)))

```
# Proportion correct choice in training trials

```{r}
pt1 <- data %>%
  filter(phase == 'training')%>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_item))

pt2 <- pt1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = pt1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .025)+
  geom_pointrange(data = pt2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

# Proportion correct choice in test trials by age bin

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_target1))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .025)+
  geom_pointrange(data = p2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

Proportion correct choice by age continous

```{r}
p3 <- data %>%
  filter(phase == 'test')%>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct_target1))

ggplot(data = p3, aes(x = age_num, y = correct)) +
  geom_jitter(width = .0,height = .0, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = .6, span = 2)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)
```

### 2019-01-16 analysis/02_kids_600.Rmd
new analysis file for kids data

@@
 
+#unique(raw_data$subid)
+
+# linking the data to the demographics spreadsheet
+# always check if subjects get "lost" due do differetn subids
 log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
@@
 #unique(log$subid)
-#sum(log$keep_drop == "drop")
 
@@
 
-unique(data$subid)
+#unique(data$subid)
 
@@
 ```{r sanity checks}
+# filtering out subjects that perform poorly on training trials
 data %>%
@@
 
+data <- data %>%
+  filter(!subid %in% drop)
+```
+
+# Participants
+
+```{r}
 data %>%
-  filter(!subid %in% drop) %>%
-  group_by(subage) %>%
-  summarise(n = length(unique(subid)))
+  group_by(subage)%>%
+  summarise(n = length(unique(subid)))%>%
+  knitr::kable(digits = 2)
+```
 
-```
 # Proportion correct choice in training trials

### 2019-01-18 analysis/01_adult_speakerchange_preference.Rmd
analysis code and data for speaker change experiment

--- 2019-01-09 analysis/01_adult_speakerchange.Rmd
@@
 ---
-title: "DisCon Speaker Change Adult Analysis"
+title: "DisCon Speaker Change Adult with Preference Analysis"
 output: html_document
@@
 
-files <- dir("../../adult_600_speakerchange/production-results/")
+files <- dir("../../adult_600_speakerchange_preference/production-results/")
 
@@
 for (f in files) {
-  jf <- paste("../../adult_600_speakerchange/production-results/",f,sep="")
+  jf <- paste("../../adult_600_speakerchange_preference/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))

### 2019-01-18 analysis/01_study1_adult.Rmd
data for different intros
analysis code and data for speaker change experiment

@@
 ---
-title: "DisCon Adult Study 1"
+title: "DisCon Adult Study 1 (Absolute and Relative Strength of Inputs)"
 output: html_document
@@
 
-write.csv(data_high, file="../data/01_study1_adult_low.data.csv")
+write.csv(data_low, file="../data/01_study1_adult_low.data.csv")
 data_low <- read_csv(file="../data/01_study1_adult_low.data.csv")

### 2019-01-18 analysis/01_adult_speakerchange.Rmd
data file for speaker change preference experiment

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE) #no code, no warning printed
 library(knitr)
@@
          distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
+
 ```
@@
 ```
-#Check how many of the participants choosing correct in the no change condition is affected in the speaker change condition
-```{r plot2}
-pull <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, speakerChange) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  filter(speakerChange == "same" & correct > 1/3) %>%
-  pull(workerid)
+```{r wilcoxon test}
+## Wilcoxon tests against chance
+library(exactRankTests)
 
-plot2 <- data%>%
-  filter(workerid %in% pull) %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, speakerChange) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -speakerChange) %>%
-  group_by(distribution, item, speakerChange) %>%
-  multi_boot_standard(col = "prop_correct")
+data %>%
+  filter(phase == "test") %>%
+  group_by(distribution, workerid) %>%
+  summarise(correct = mean(correct_target1)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(distribution) %>%
+  mutate(mean= mean(unlist(correct)),
+         stat = wilcox.exact(unlist(correct), mu = 0.5)$statistic,
+         p = wilcox.exact(unlist(correct), mu = 0.5)$p.value) %>%
+  select(distribution,mean,stat,p) %>%
+  knitr::kable(digits = 3)
+```
 
-ggplot(plot2,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))+
-  facet_grid(~speakerChange, 
-             labeller = as_labeller(c(change = "speaker change", same = "no change"))) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
+```{r Bayesian}
+library(brms)
+
+data_inf <- data%>%
+  filter(phase == "test")
+
+prior1 <- get_prior(correct_target1 ~ speakerChange * experiment +
+                      (speakerChange | workerid) + (speakerChange | agent),
+                    data = data_inf, family = bernoulli())
+
+# registered  model
+bm1 <- brm(correct_target1 ~ speakerChange * experiment +
+                      (speakerChange | workerid) + (speakerChange | agent),
+                    data = data_inf, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          prior = prior1,
+          iter = 20000)
+summary(bm1)
+
+prior2 <- get_prior(correct_target1 ~ speakerChange +
+                      (speakerChange | workerid) + (speakerChange | agent),
+                    data = data_inf, family = bernoulli())
+
+bm2 <- brm(correct_target1 ~ speakerChange  +
+                      (speakerChange | workerid) + (speakerChange | agent),
+                    data = data_inf, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          prior = prior2,
+          iter = 20000)
+summary(bm2)
+
+saveRDS(bm1, "01_adult_speakerchange_preference_models/bm1.rds")
+saveRDS(bm2, "01_adult_speakerchange_preference_models/bm2.rds")
+
+bf_full_null <- bayes_factor(bm1, bm2, log = FALSE, maxiter = 5000)
+
+bf_full_null
 ```

### 2019-01-18 analysis/01_adult_speakerchange_preference.Rmd
data file for speaker change preference experiment

@@
          distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
+
+write.csv(data, file="../data/01_adult_speakerchange_preference.data.csv")
+data <- read_csv(file="../data/01_adult_speakerchange_preference.data.csv")
 ```
@@
 ```
-#Check how many of the participants choosing correct in the no change condition is affected in the speaker change condition
-```{r plot2}
-pull <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, speakerChange) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  filter(speakerChange == "same" & correct > 1/3) %>%
-  pull(workerid)
+```{r wilcoxon test}
+## Wilcoxon tests against chance
+library(exactRankTests)
 
-plot2 <- data%>%
-  filter(workerid %in% pull) %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, speakerChange) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -speakerChange) %>%
-  group_by(distribution, item, speakerChange) %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot(plot2,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))+
-  facet_grid(~speakerChange, 
-             labeller = as_labeller(c(change = "speaker change", same = "no change"))) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
+data %>%
+  filter(phase == "test") %>%
+  group_by(distribution, workerid) %>%
+  summarise(correct = mean(correct_target1)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(distribution) %>%
+  mutate(mean= mean(unlist(correct)),
+         stat = wilcox.exact(unlist(correct), mu = 0.5)$statistic,
+         p = wilcox.exact(unlist(correct), mu = 0.5)$p.value) %>%
+  select(distribution,mean,stat,p) %>%
+  knitr::kable(digits = 3)
 ```

### 2019-01-18 analysis/01_adult_speakerchange_preference.Rmd
add model to adult speaker change experiment

@@
 
-#Pilot 1 data
+# Data for speaker change with preference framing
 ```{r data preprocessing}
@@
 
-write.csv(data, file="../data/01_adult_speakerchange_preference.data.csv")
+#write.csv(data, file="../data/01_adult_speakerchange_preference.data.csv")
+
 data <- read_csv(file="../data/01_adult_speakerchange_preference.data.csv")
@@
 
-```{r}
-data_ip <- data %>%
-  filter(phase == 'training') %>%
-  group_by(workerIp) %>%
-  summarise(correct = mean(correct_item))
-```
+## Cleaning data
+
+Remove participants who perform below cut-off in training and who participated
 
 ```{r sanity checks}
-data %>%
-  filter(phase == 'training') %>%
-  group_by(workerid) %>%
-  summarise(correct = mean(correct_item))
-
-drop <- data %>%
+drop_train <- data %>%
   filter(phase == 'training') %>%
@@
 data <- data %>%
-  filter(!workerid %in% drop)
+  distinct(workerid, trial, slide, .keep_all = TRUE)%>%
+  filter(!workerid %in% drop_train)
 ```
+## Sample size
+
 ```{r}
+data %>%
+  filter(phase=="test")%>%
+  group_by(speakerChange)%>%
+  summarise(N = length(unique(workerid)),
+            datapoints = n())
 
-sample_size <- data %>%
-  distinct(workerid, .keep_all = TRUE)
-
-sample_size %>%
- group_by(experiment) %>%
- summarise(n = n())
 ```
 
+# Plotting performance by condition
+
 ```{r plot1}
-plot1 <- data %>%
-  filter(phase == 'test') %>%
-  group_by(distribution, workerid, speakerChange) %>%
-  summarise(correct = mean(correct_target1),
-            correct2 = mean(correct_target2),
-            correct3 = mean(correct_target3)) %>%
-  gather(item, prop_correct, -distribution, -workerid, -speakerChange) %>%
-  group_by(distribution, item, speakerChange) %>%
-  multi_boot_standard(col = "prop_correct")
-
-ggplot(plot1,
-       aes(x = item, y=mean, fill=item)) +
-  geom_bar(stat='identity') +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  scale_fill_solarized(name = "Chosen item",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))+
-  facet_grid(~speakerChange, 
-             labeller = as_labeller(c(change = "speaker change", same = "no change"))) +
-  geom_hline(yintercept = 1/3, lty=2) +
-  ylim(0, 1) +
-  theme_few() +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
-  labs(x="", y= "proportion chosen")
-
 plot3 <- data %>%
@@
 ```
+
+# Comparison to chance in each condition
+
 ```{r wilcoxon test}
@@
   filter(phase == "test") %>%
-  group_by(distribution, workerid) %>%
+  group_by(speakerChange, workerid) %>%
   summarise(correct = mean(correct_target1)) %>%
   summarise(correct = list(correct)) %>%
-  group_by(distribution) %>%
+  group_by(speakerChange) %>%
   mutate(mean= mean(unlist(correct)),
-         stat = wilcox.exact(unlist(correct), mu = 0.5)$statistic,
-         p = wilcox.exact(unlist(correct), mu = 0.5)$p.value) %>%
-  select(distribution,mean,stat,p) %>%
+         stat = wilcox.exact(unlist(correct), mu = 1/3)$statistic,
+         p = wilcox.exact(unlist(correct), mu = 1/3)$p.value) %>%
+  select(speakerChange,mean,stat,p) %>%
   knitr::kable(digits = 3)
 ```
+
+# Model
+
+```{r Bayesian}
+library(brms)
+
+model_data <- data%>%
+  filter(phase == "test")
+
+#   model
+
+bm1 <- readRDS("../saves/01_adult_speakerchange_model_bm1.rds")
+
+brm(correct_target1 ~ speakerChange +
+                      (speakerChange | workerid) + (speakerChange | target1),
+                    data = model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
+
+saveRDS(bm1, "../saves/01_adult_speakerchange_model_bm1.rds")
+
+```
+
+## Plot model predictors
+
+```{r}
+bayesplot::mcmc_areas(as.array(bm1), pars = c("b_Intercept", "b_speakerChangesame"), prob = 0.95)+
+  geom_vline(xintercept = 0, lty = 2, col = "black")+
+  theme_few()
+```
+
+## Model comparison
+
+```{r}
+# model comparison
+# reduced model
+
+bm2 <- readRDS("../saves/01_adult_speakerchange_model_bm2.rds")
+
+bm2 <- brm(correct_target1 ~ 1 +
+                      (speakerChange | workerid) + (speakerChange | target1),
+                    data = model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
+
+saveRDS(bm2, "../saves/01_adult_speakerchange_model_bm2.rds")
+
+# WAIC scores
+
+child_waic <- brms::WAIC(bm1, bm2, compare = F)
+
+child_weights <- model_weights(bm1, bm2)
+
+# Bayes Factors (slightly variable)
+bf_full_null <- bayes_factor(bm1, bm2, log = FALSE, maxiter = 5000)
+
+```
+## Model comparison using WAIC and Bayes Factor
+```{r}
+data_frame(
+  model = c("bm1_w_condition","bm2"),
+  WAIC = c(child_waic$bm1$estimates[3,1],child_waic$bm2$estimates[3,1]),
+  SE = c(child_waic$bm1$estimates[3,2],child_waic$bm2$estimates[3,2]),
+  weight = c(child_weights[1],child_weights[2]),
+  BF_bm1_bm2 = c(round(bf_full_null$bf,2),"-"))%>%
+  kable(digits = 2)
+```

### 2019-02-20 analysis/01_adult_speakerchange_preference.Rmd
update kids analysis

@@
   scale_colour_solarized(name = "Speaker Change",
-                       breaks = c("correct", "correct2", "correct3"),
-                       labels = c("most frequent", "second most frequent", "least frequent"))
+                       breaks = c("change", "same"),
+                       labels = c("Different Speaker", "Same Speaker"))
 

### 2019-02-20 analysis/02_kids_600.Rmd
update kids analysis

@@
   filter(Condition == "d600")%>%
-  mutate(dob = as.Date(dob))%>%
+  mutate(dob = as.numeric(dob),
+         dob = as.Date(dob,origin = "1899-12-30"))%>%
   select(subid,experimenter,keep_drop,sex,dob)
@@
 
-# Proportion correct choice in test trials by age bin
+# Proportion correct choice in test trials across age bins
 
@@
   filter(phase == 'test')%>%
+  group_by(experiment,subid) %>%
+  summarise(correct = mean(correct_target1))
+
+p2 <- p1 %>%
+  group_by(experiment) %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p1, aes(x = experiment, y = correct,  alpha = .2),width = .2,height = .01)+
+  geom_pointrange(data = p2, aes(x = experiment, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="",y="Proportion correct in training")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+
+  scale_color_solarized()
+```
+
+# Proportion correct choice in test trials by age bin
+
+```{r proportion of choices}
+p3 <- data %>%
+  filter(phase == 'test')%>%
   group_by(subage, subid) %>%
@@
 
-p2 <- p1 %>%
+p4 <- p1 %>%
   multi_boot_standard(col = "correct")
@@
 ggplot() +
-  geom_jitter(data = p1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .025)+
-  geom_pointrange(data = p2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_jitter(data = p3, aes(x = subage, y = correct, col = subage, alpha = .2),width = .2,height = .01)+
+  geom_pointrange(data = p4, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 1/3, lty=2)+
@@
 ```{r}
-p3 <- data %>%
+p5 <- data %>%
   filter(phase == 'test')%>%
@@
 
-ggplot(data = p3, aes(x = age_num, y = correct)) +
+ggplot(data = p5, aes(x = age_num, y = correct)) +
   geom_jitter(width = .0,height = .0, alpha = .5)+

### 2019-02-23 analysis/01_adult_speakerchange_preference.Rmd
update kids 600 analysis

@@
 
-child_waic <- brms::WAIC(bm1, bm2, compare = F)
+waic <- brms::WAIC(bm1, bm2, compare = F)
 
-child_weights <- model_weights(bm1, bm2)
+weights <- model_weights(bm1, bm2)
 
@@
   model = c("bm1_w_condition","bm2"),
-  WAIC = c(child_waic$bm1$estimates[3,1],child_waic$bm2$estimates[3,1]),
-  SE = c(child_waic$bm1$estimates[3,2],child_waic$bm2$estimates[3,2]),
-  weight = c(child_weights[1],child_weights[2]),
+  WAIC = c(waic$bm1$estimates[3,1],waic$bm2$estimates[3,1]),
+  SE = c(waic$bm1$estimates[3,2],waic$bm2$estimates[3,2]),
+  weight = c(weights[1],weights[2]),
   BF_bm1_bm2 = c(round(bf_full_null$bf,2),"-"))%>%

### 2019-02-23 analysis/02_kids_600.Rmd
update kids analysis file
update kids 600 analysis

@@
 library(readxl)
+library(knitr)
 
@@
 
-p4 <- p1 %>%
+p4 <- p3 %>%
+  group_by(subage) %>%
   multi_boot_standard(col = "correct")
@@
 ggplot(data = p5, aes(x = age_num, y = correct)) +
-  geom_jitter(width = .0,height = .0, alpha = .5)+
+  geom_jitter(width = .01,height = .01, alpha = .5)+
   geom_smooth(method = "lm",  se = T,  alpha = .5, size = .6, span = 2)+
@@
 ```
+
+# Bayesian t-test against chance across age groups
+
+```{r}
+## one sample bayesian t-tests
+library(BayesFactor)
+
+data %>%
+  filter(phase != "training") %>%
+  group_by(subage, subid) %>%
+  summarise(correct = mean(correct_target1)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(subage) %>%
+  mutate(mean= mean(unlist(correct)),
+         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
+  select(subage,mean,bf) %>%
+  knitr::kable(digits = 3)
+
+samples = ttestBF(x$correct, mu = 1/3, posterior = T, iterations = 1000)
+
+```
+
+# Model 
+```{r}
+library(brms)
+
+model_data <- data%>%
+  filter(phase == "test")%>%
+  mutate(age_num = scale(age_num))
+
+mean(model_data$age_num)
+
+#   model
+
+kbm1 <- brm(correct_target1 ~ age_num +
+                      (1| subid) + (1 | target1),
+                    data = model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
+
+summary(kbm1)
+```
+
+```{r}
+bayesplot::mcmc_areas(as.array(kbm1), pars = c("b_Intercept", "b_age_num"), prob = 0.95)+
+  geom_vline(xintercept = 0, lty = 2, col = "black")+
+  theme_few()
+```
+
+```{r}
+kbm2 <- brm(correct_target1 ~ 1 +
+                      (1| subid) + (1 | target1),
+                    data = model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
+
+summary(kbm2)
+```
+
+## Model comparison
+
+```{r}
+child_waic <- brms::WAIC(kbm1, kbm2, compare = F)
+
+child_weights <- model_weights(kbm1, kbm2)
+
+# Bayes Factors (slightly variable)
+bf_full_null <- bayes_factor(kbm1, kbm2, log = FALSE, maxiter = 5000)
+```
+
+```{r}
+data_frame(
+  model = c("kbm1_w_age","kbm2"),
+  WAIC = c(child_waic$kbm1$estimates[3,1],child_waic$kbm2$estimates[3,1]),
+  SE = c(child_waic$kbm1$estimates[3,2],child_waic$kbm2$estimates[3,2]),
+  weight = c(child_weights[1],child_weights[2]),
+  BF_bm1_bm2 = c(round(bf_full_null$bf,2),"-"))%>%
+  kable(digits = 2)
+```

### 2019-02-27 experiments/discon_look_kid_simple_4cat_within.js
added kids' experiment for within subject

@@ -1,0 +1,786 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+//only preload relevant audios (no speaker change)
+var preloadAudios = ["hi", "lets", "intro", "thank", "it"];
+
+var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger", "Pig"])
+
+//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
+
+var audios = new Array();
+for (i = 0; i < posAgents.length; i++) {
+    for (j = 0; j < preloadAudios.length; j++) {
+        var audio = new Audio();
+        audio.src = "sounds/" + preloadAudios[j] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+    for (k = 0; k < preloadItems.length - 3; k++) {
+        var audio = new Audio();
+        audio.src = "sounds/" + preloadItems[k] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
[…]

### 2019-03-01 analysis/02_kids_600.Rmd
update kids analysis file

@@
 library(pwr)
+
+library(coda)
+library(reshape2)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
 
@@
   filter(phase != "training") %>%
-  group_by(subage, subid) %>%
+  group_by(subid) %>%
+  summarise(correct = mean(correct_target1)) %>%
+  summarise(correct = list(correct)) %>%
+  mutate(mean= mean(unlist(correct)),
+         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
+  select(mean,bf) %>%
+  knitr::kable(digits = 3)
+
+```
+
+# BAyesian t-test by age group
+
+```{r}
+## one sample bayesian t-tests
+library(BayesFactor)
+
+data %>%
+  filter(phase != "training") %>%
+  group_by(subage,subid) %>%
   summarise(correct = mean(correct_target1)) %>%
@@
 
-samples = ttestBF(x$correct, mu = 1/3, posterior = T, iterations = 1000)
+```
+Plotting posterior based on t-test
+
+```{r}
+plot_post <- data %>%
+  filter(phase != "training") %>%
+  group_by(subage,subid) %>%
+  summarise(correct = mean(correct_target1))%>%
+  summarise(correct = list(correct)) %>%
+  group_by(subage) %>%
+  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 10000)[,"mu"])))%>%
+  select(-correct)
+
+plot_dens_ci <- plot_post %>%
+  summarise(mode = estimate_mode(unlist(posterior)),
+            lci = hdi_lower(unlist(posterior)),
+            uci = hdi_upper(unlist(posterior)))
+
+#### make density plot ?
+
+plot_dens <- data_frame(
+  age = rep(c(3,4), each = 10000),
+  posterior = c(unlist(plot_post%>%filter(subage == "3") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "4") %>% pull(posterior)))
+)
+
+densities <- plot_dens %>%
+  group_by(age) %>%
+  do(., dens = density(.$posterior))
+
+densities_df <-
+  data.frame(
+    age = c(rep('3', 512),
+              rep('4', 512)),
+    x = c(densities$dens[[1]]$x, 
+          densities$dens[[2]]$x),
+    y = c(densities$dens[[1]]$y,
+          densities$dens[[2]]$y)
+  ) %>%
+  group_by(age)%>%
+  mutate (
+    ci_shade = ifelse( age == "3",
+      ifelse( x <= plot_dens_ci%>%filter(subage == "3")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "3")%>%pull(uci), "OFF", "ON"), ifelse( x <= plot_dens_ci%>%filter(subage == "4")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "4")%>%pull(uci), "OFF", "ON")))
+
+ggplot(plot_dens, aes(posterior, group = factor(age))) +
+  geom_density(alpha = .5)+
+  geom_vline(xintercept = 1/3, lty=2)+
+  geom_area(data = densities_df %>% filter(ci_shade == "ON"), aes(x = x, y = y, fill = age), alpha = .5) + 
+  labs(x="Proportion Correct")+
+  theme_few() +
+  xlim(-0.05,1.05)+
+  guides(alpha = F)+
+  scale_fill_solarized(name = "Age")+
+  theme(axis.title.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        axis.text.y = element_blank())
 
@@
   mutate(age_num = scale(age_num))
-
-mean(model_data$age_num)
 

### 2019-03-01 analysis/02_kids_power_analysis_600.Rmd
update kids analysis file

@@
 ```
+
+# Bayesian Power analysis
+
+```{r}
+N           <- 1000  # Number of MC reps
+n           <- 20  # Sample size
+sigma       <- 0.3    # Error standard devation
+
+true_mu     <- (0.5785714-1/3)	  # True value of mu
+
+pri.mn.anal <- 0    # Prior for mu
+pri.sd.anal <- Inf
+
+ L <- rep(0,N)
+ U <- rep(0,N)
+
+ set.seed(0820)
+
+ for(rep in 1:N){
+
+  #Generate data:
+    Y  <- rnorm(n,true_mu,sigma)
+
+   #Compute posterior 95% interval:
+    post.var <- 1/(n/sigma^2+1/pri.sd.anal^2)
+    post.mn  <- post.var*(pri.mn.anal/pri.sd.anal^2+sum(Y)/sigma^2)
+    L[rep]   <- post.mn-1.96*sqrt(post.var)
+    U[rep]   <- post.mn+1.96*sqrt(post.var)
+ }
+
+plot(NA,xlim=c(-1,1),ylim=c(1,N),xlab="95% interval",ylab="Replication")
+abline(v=0)
+
+for(rep in 1:N){
+    reject <- L[rep]>0 | U[rep]<0
+    lines(c(L[rep],U[rep]),c(rep,rep),col=ifelse(reject>0,2,1))
+}
+
+ mean(L>0 | U<0)
+```

### 2019-03-01 analysis/02_kids_600.Rmd
add kids data

@@
 
-#data <- read_csv(file="../data/kids_600.data.csv")
+data <- read_csv(file="../data/kids_600.data.csv")
 ```
@@
   geom_hline(yintercept = 1/3, lty=2)+
-  labs(x="",y="Proportion correct in training")+
+  labs(x="",y="Proportion correct")+
   theme_few() +
@@
   guides(alpha = F)+
-  scale_color_solarized()
+  scale_color_solarized(name = "Age")
 ```
@@
 ggplot(data = p5, aes(x = age_num, y = correct)) +
-  geom_jitter(width = .01,height = .01, alpha = .5)+
-  geom_smooth(method = "lm",  se = T,  alpha = .5, size = .6, span = 2)+
+  geom_jitter(width = .01, height = .0, alpha = .5)+
+  geom_smooth(method = "lm",  se = T,  alpha = .5, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
   geom_hline(yintercept = 1/3, lty=2)+
-  labs(x="Age",y="Proportion correct choice")+
+  labs(x="Age",y="Proportion correct")+
   theme_few() +
@@
   group_by(subage) %>%
-  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 10000)[,"mu"])))%>%
+  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 1000)[,"mu"])))%>%
   select(-correct)
@@
 plot_dens <- data_frame(
-  age = rep(c(3,4), each = 10000),
+  age = rep(c(3,4), each = 1000),
   posterior = c(unlist(plot_post%>%filter(subage == "3") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "4") %>% pull(posterior)))

### 2019-03-02 analysis/02_kids_600.Rmd
update data file kids

@@
 output: html_document
+  code_folding: hide
 ---
@@
 
-```{r data pre-processing}
+```{r data pre-processing, include = F}
 
@@
          age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
+  select(-dob, -check_age,-keep_drop,-experimenter,-test_date,-numberOfTrials,-nunberOfTrials)
 
@@
 
-data <- read_csv(file="../data/kids_600.data.csv")
+##data <- read_csv(file="../data/kids_600.data.csv")
 ```
@@
 data %>%
-  group_by(subage)%>%
+  group_by(subage
+           #,sex
+           )%>%
   summarise(n = length(unique(subid)))%>%
@@
 ggplot() +
-  geom_jitter(data = pt1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .025)+
+  geom_jitter(data = pt1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .0)+
   geom_pointrange(data = pt2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  geom_hline(yintercept = 1/3, lty=2)+
+  geom_hline(yintercept = 5/6, lty=2)+
   labs(x="",y="Proportion correct in training")+
@@
   group_by(experiment,subid) %>%
-  summarise(correct = mean(correct_target1))
+  summarise(correct = mean(correct_target1),
+            sd = sd(correct_target1))
 
@@
 # Model 
-```{r}
+```{r, include = F}
 library(brms)
@@
 
-```{r}
+```{r, include = F}
 kbm2 <- brm(correct_target1 ~ 1 +

### 2019-03-02 experiments/discon_look_kid_simple_4cat_within.js
changed within experiment so that distribution is correctly reflected

@@ -305,7 +305,7 @@ function shuffleByIndex(array) {
 shuffleByIndex(trialTargets);
 shuffleByIndex(trialFamiliarItems);
 
-var posDist = shuffle([[6, 0, 0], [6, 0, 0], [6, 0, 0], [6, 0, 0]]);
+var posDist = shuffle([[6, 0, 0], [6, 0, 0], [1, 0, 0], [1, 0, 0]]);
 
 //distribution for each trial
 var trainingDist = new Array();

### 2019-03-03 analysis/02_kids_600.Rmd
add plots to kids analysis file

@@
 
-# BAyesian t-test by age group
+# Bayesian t-test by age group
 
@@
 
+# Comparison to chance based on model
+
+```{r}
+chance_data <- data %>%
+  filter(phase != "training") %>%
+  group_by(subage,subid) %>%
+  summarise(correct = mean(correct_target1)) %>%
+  mutate(comp_chance= ifelse(correct<1/3,0,1))
+
+library(brms)
+
+chance_model <- brm(comp_chance ~ 1,
+                    data = chance_data, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
+
+summary(chance_model)
+
+```
+
+```{r}
+bayesplot::mcmc_areas(as.array(chance_model), pars = c("b_Intercept"), prob = 0.95)+
+  geom_vline(xintercept = 0, lty = 2, col = "black")+
+  theme_few()
+```
+
 # Model 
@@
 model_data <- data%>%
-  filter(phase == "test")%>%
+  filter(phase != "training")%>%
   mutate(age_num = scale(age_num))
@@
 ```
+
+# Check category, position and trial
+
+## category effects
+```{r proportion of choices}
+cat_plot <- data %>%
+  filter(phase == 'test')%>%
+  group_by(target1,subid) %>%
+  summarise(correct = mean(correct_target1))
+
+cat_plot_mean <- cat_plot %>%
+  group_by(target1) %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = cat_plot, aes(x = target1, y = correct,  alpha = .2, col = target1),width = .2,height = .01)+
+  geom_pointrange(data = cat_plot_mean, aes(x = target1, y = mean,  ymin = ci_lower, ymax = ci_upper, col = target1),size = .8)+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+
+  scale_color_solarized()
+```
+
+## position effects
+```{r proportion of choices}
+pos_plot <- data %>%
+  filter(phase == 'test')%>%
+  group_by(pickPos,subid) %>%
+  summarise(correct = mean(correct_target1))
+
+pos_plot_mean <- pos_plot %>%
+  group_by(pickPos) %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = pos_plot, aes(x = pickPos, y = correct,  alpha = .2, col = pickPos),width = .2,height = .01)+
+  geom_pointrange(data = pos_plot_mean, aes(x = pickPos, y = mean,  ymin = ci_lower, ymax = ci_upper, col = pickPos),size = .8)+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+
+  scale_color_solarized()
+```
+
+## trial effects
+```{r proportion of choices}
+trial_plot <- data %>%
+  filter(phase == 'test')
+
+ggplot(data = trial_plot, aes(x = trial, y = correct_target1)) +
+  geom_jitter(alpha = .2,width = .2,height = .01)+
+  geom_smooth(method = "loess",  se = T, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+
+  scale_color_solarized()
+```

### 2019-03-13 experiments/discon_look_kid_simple_4cat_within.js
fix nTrials and distribution not corresponding

@@ -132,9 +132,6 @@ var slides = [1, 2, 3, 4, 5, 6, "choice"]
 
 var trials = [0, 1, 2, 3]
 
-// 2 times with 6 trial slides, 2 times with 1 trial slides
-var nTrials = shuffle([6, 6, 1, 1])
-
 var backgrounds = shuffle([1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]);
 
 var vehiclesF = shuffle(["car", "truck", "train", "bus", "airplane", "boat", "motorbike"])
@@ -306,6 +303,12 @@ shuffleByIndex(trialTargets);
 shuffleByIndex(trialFamiliarItems);
 
 var posDist = shuffle([[6, 0, 0], [6, 0, 0], [1, 0, 0], [1, 0, 0]]);
+
+// 2 times with 6 trial slides, 2 times with 1 trial slides
+var nTrials = new Array();
+for (var i = 0; i < posDist.length; i++) {
+    nTrials.push(posDist[i][0]);
+}
 
 //distribution for each trial
 var trainingDist = new Array();

### 2019-03-14 analysis/02_kids_6v1.Rmd
analysis pipeline 6v1

--- 2019-03-02 analysis/02_kids_600.Rmd
@@
 ---
-title: "DisCon Kids Pilot"
+title: "DisCon Children 6 vs. 1 exposure trials"
 output: html_document
@@
 #files <- dir("../../kids_simple_4cat/")
-files <- dir("../../kids_raw_data/600/")
+files <- dir("../../kids_raw_data/6v1/")
 
@@
 #  jf <- paste("../../kids_simple_4cat/",f,sep="")
-  jf <- paste("../../kids_raw_data/600/",f,sep="")
+  jf <- paste("../../kids_raw_data/6v1/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
@@
 log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
-  filter(Condition == "d600")%>%
+  filter(Condition == "d6v1")%>%
   mutate(dob = as.numeric(dob),
@@
   mutate(distribution = as.character(distribution),
-         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
          age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F), 
+         distribution = ifelse(distribution == "c(6, 0, 0)", "6-0-0","1-0-0"))%>%
   select(-dob, -check_age,-keep_drop,-experimenter,-test_date,-numberOfTrials,-nunberOfTrials)
@@
   filter(phase == 'test')%>%
-  group_by(experiment,subid) %>%
+  group_by(distribution,subid) %>%
   summarise(correct = mean(correct_target1),
@@
 p2 <- p1 %>%
-  group_by(experiment) %>%
+  group_by(distribution) %>%
   multi_boot_standard(col = "correct")
@@
 ggplot() +
-  geom_jitter(data = p1, aes(x = experiment, y = correct,  alpha = .2),width = .2,height = .01)+
-  geom_pointrange(data = p2, aes(x = experiment, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
-  geom_hline(yintercept = 1/3, lty=2)+
-  labs(x="",y="Proportion correct in training")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+
-  scale_color_solarized()
-```
-
-# Proportion correct choice in test trials by age bin
-
-```{r proportion of choices}
-p3 <- data %>%
-  filter(phase == 'test')%>%
-  group_by(subage, subid) %>%
-  summarise(correct = mean(correct_target1))
-
-p4 <- p3 %>%
-  group_by(subage) %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = p3, aes(x = subage, y = correct, col = subage, alpha = .2),width = .2,height = .01)+
-  geom_pointrange(data = p4, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_jitter(data = p1, aes(x = distribution, y = correct, col = distribution), alpha = .2 ,width = .2,height = .01)+
+  geom_pointrange(data = p2, aes(x = distribution, y = mean,  ymin = ci_lower, ymax = ci_upper, col = distribution),size = .8)+
   geom_hline(yintercept = 1/3, lty=2)+
@@
   guides(alpha = F)+
-  scale_color_solarized(name = "Age")
-```
-
-Proportion correct choice by age continous
-
-```{r}
-p5 <- data %>%
-  filter(phase == 'test')%>%
-  group_by(age_num, subid) %>%
-  summarise(correct = mean(correct_target1))
-
-ggplot(data = p5, aes(x = age_num, y = correct)) +
-  geom_jitter(width = .01, height = .0, alpha = .5)+
-  geom_smooth(method = "lm",  se = T,  alpha = .5, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
-  geom_hline(yintercept = 1/3, lty=2)+
-  labs(x="Age",y="Proportion correct")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(3,5)+
-  guides(alpha = F)
-```
-
-# Bayesian t-test against chance across age groups
-
-```{r}
-## one sample bayesian t-tests
-library(BayesFactor)
-
-data %>%
-  filter(phase != "training") %>%
-  group_by(subid) %>%
-  summarise(correct = mean(correct_target1)) %>%
-  summarise(correct = list(correct)) %>%
-  mutate(mean= mean(unlist(correct)),
-         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
-  select(mean,bf) %>%
-  knitr::kable(digits = 3)
-
-```
-
-# BAyesian t-test by age group
-
-```{r}
-## one sample bayesian t-tests
-library(BayesFactor)
-
-data %>%
-  filter(phase != "training") %>%
-  group_by(subage,subid) %>%
-  summarise(correct = mean(correct_target1)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(subage) %>%
-  mutate(mean= mean(unlist(correct)),
-         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
-  select(subage,mean,bf) %>%
-  knitr::kable(digits = 3)
-
-```
-Plotting posterior based on t-test
-
-```{r}
-plot_post <- data %>%
-  filter(phase != "training") %>%
-  group_by(subage,subid) %>%
-  summarise(correct = mean(correct_target1))%>%
-  summarise(correct = list(correct)) %>%
-  group_by(subage) %>%
-  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 1000)[,"mu"])))%>%
-  select(-correct)
-
-plot_dens_ci <- plot_post %>%
-  summarise(mode = estimate_mode(unlist(posterior)),
-            lci = hdi_lower(unlist(posterior)),
-            uci = hdi_upper(unlist(posterior)))
-
-#### make density plot ?
-
-plot_dens <- data_frame(
-  age = rep(c(3,4), each = 1000),
-  posterior = c(unlist(plot_post%>%filter(subage == "3") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "4") %>% pull(posterior)))
-)
-
-densities <- plot_dens %>%
-  group_by(age) %>%
-  do(., dens = density(.$posterior))
-
-densities_df <-
-  data.frame(
-    age = c(rep('3', 512),
-              rep('4', 512)),
-    x = c(densities$dens[[1]]$x, 
-          densities$dens[[2]]$x),
-    y = c(densities$dens[[1]]$y,
-          densities$dens[[2]]$y)
-  ) %>%
-  group_by(age)%>%
-  mutate (
-    ci_shade = ifelse( age == "3",
-      ifelse( x <= plot_dens_ci%>%filter(subage == "3")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "3")%>%pull(uci), "OFF", "ON"), ifelse( x <= plot_dens_ci%>%filter(subage == "4")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "4")%>%pull(uci), "OFF", "ON")))
-
-ggplot(plot_dens, aes(posterior, group = factor(age))) +
-  geom_density(alpha = .5)+
-  geom_vline(xintercept = 1/3, lty=2)+
-  geom_area(data = densities_df %>% filter(ci_shade == "ON"), aes(x = x, y = y, fill = age), alpha = .5) + 
-  labs(x="Proportion Correct")+
-  theme_few() +
-  xlim(-0.05,1.05)+
-  guides(alpha = F)+
-  scale_fill_solarized(name = "Age")+
-  theme(axis.title.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        axis.text.y = element_blank())
-
+  scale_color_solarized()
 ```
@@
 
-kbm1 <- brm(correct_target1 ~ age_num +
-                      (1| subid) + (1 | target1),
+kbm1 <- brm(correct_target1 ~ age_num * distribution
+                      (condition| subid) + (condition | target1),
                     data = model_data, family = bernoulli(),
@@
 ```{r, include = F}
-kbm2 <- brm(correct_target1 ~ 1 +
-                      (1| subid) + (1 | target1),
+kbm2 <- brm(correct_target1 ~ age_num +
+                      (condition| subid) + (condition | target1),
                     data = model_data, family = bernoulli(),
@@
 ```
+
+# Check category, position and trial
+
+## category effects
+```{r proportion of choices}
+cat_plot <- data %>%
+  filter(phase == 'test')%>%
+  group_by(target1,subid) %>%
+  summarise(correct = mean(correct_target1))
+
+cat_plot_mean <- cat_plot %>%
+  group_by(target1) %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = cat_plot, aes(x = target1, y = correct,  alpha = .2, col = target1),width = .2,height = .01)+
+  geom_pointrange(data = cat_plot_mean, aes(x = target1, y = mean,  ymin = ci_lower, ymax = ci_upper, col = target1),size = .8)+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F, col = F)+
+  scale_color_solarized()
+```
+
+## position effects
+```{r }
+pos_plot <- data %>%
+  filter(phase == 'test')%>%
+  group_by(pickPos,subid) %>%
+  summarise(n = n())%>%
+  group_by(pickPos)%>%
+  multi_boot_standard(col = "n")
+
+ggplot() +
+  geom_pointrange(data = pos_plot, aes(x = pickPos, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
+   labs(x="Item position",y="Mean item in this position chosen at test")+
+  theme_few() +
+  ylim(0,4)+
+  guides(alpha = F)+
+  scale_color_solarized()
+```
+
+## trial effects
+```{r proportion of choices}
+trial_plot <- data %>%
+  filter(phase == 'test')
+
+ggplot(data = trial_plot, aes(x = trial, y = correct_target1)) +
+  geom_jitter(alpha = .2,width = .2,height = .01)+
+  geom_smooth(method = "loess",  se = T, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+
+  scale_color_solarized()
+```
+
+# one sample wilcoxon
+```{r}
+
+# Based on: http://ipg.idsia.ch/preprints/benavoli2014a.pdf
+source("../scripts/isignrank.test.R")
+
+rank_data <- data %>%
+  filter(phase == 'test')%>%
+  group_by(experiment,subid) %>%
+  summarise(correct = mean(correct_target1)) %>%
+  mutate(chance = rep(1/3,length(correct)))
+
+isignrank.test(rank_data$chance,rank_data$correct,"two.sided")
+
+# Based on : https://arxiv.org/pdf/1712.06941.pdf
+source("../scripts/signRankSampler.R")
+
+rank_test <- signRankGibbsSampler(rank_data$correct,rank_data$chance)
+
+rank_test_plot <- data.frame(rank_test)
+
+ggplot(rank_test_plot, aes(plogis(deltaSamples))) +
+  geom_density(alpha = .5)+
+  xlim(0,1)
+```

### 2019-03-14 analysis/02_kids_pilot.Rmd
analysis pipeline 6v1

--- 2019-01-16 analysis/02_kids.Rmd
@@
 ```
+
+# 2yo in 600
+
+```{r data pre-processing, include = F}
+
+#files <- dir("../../kids_simple_4cat/")
+files <- dir("../../kids_raw_data/pilot/600/")
+
+raw_data <- data_frame()
+for (f in files) {
+#  jf <- paste("../../kids_simple_4cat/",f,sep="")
+  jf <- paste("../../kids_raw_data/pilot/600/",f,sep="")
+  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,36,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+```
+
+```{r proportion of choices}
+pos_plot <- raw_data %>%
+  filter(phase == 'test')%>%
+  group_by(pickPos,subid) %>%
+  summarise(n = n())
+
+pos_plot2 <- pos_plot%>%
+  group_by(pickPos)%>%
+  multi_boot_standard(col = "n")
+
+ggplot() +
+  geom_jitter(data = pos_plot, aes(x = pickPos, y = n, col = subid),size = 2, height = 0, alpha = 1)+
+  geom_hline(yintercept = 4/3, lty=2)+
+  geom_pointrange(data = pos_plot2, aes(x = pickPos, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
+  labs(x="Item position",y="Mean number of times item was chosen")+
+  theme_few() +
+  ylim(0,4)+
+  guides(alpha = F)+
+  scale_color_ptol()
+```
+
+```{r}
+p1 <- raw_data %>%
+  filter(phase == 'test')%>%
+  group_by(experiment,subid) %>%
+  summarise(correct = mean(correct_target1))
+
+p2 <- p1 %>%
+  group_by(experiment) %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p1, aes(x = experiment, y = correct,  alpha = .2),width = .2,height = .01)+
+  geom_pointrange(data = p2, aes(x = experiment, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+
+  scale_color_solarized()
+```

### 2019-03-14 scripts/isignrank.test.R

@@ -1,0 +1,420 @@
+#isignrank.test Bayesian Wilcoxon signed rank test based on the Imprecise Dirichlet Process.
+#      This is the Bayesian improved version of iwilcox.test
+#
+#
+#   isignrank.test(x,y,"greater") performs a hypothesis test for P(Z>=-Z)>1/2 
+#   with Z=Y-X and posterior probability 0.95. It returns the result of the deicison.
+#   H=1 indicates that the hypothesis P(Z>=-Z)>1/2 is true with posterior
+#   probability greater than 0.95, i.e., Lower_Prob>0.95. H=0 indicates
+#   P(Z>=-Z)>1/2 is not true with posterior greater than 0.95, i.e.,
+#   Upper_Prob<0.95. Finally, H=2 indicates an indeterminate instance, i.e.,
+#   we cannot decide if  P(Z>=-Z)>1/2 is true with posterior probability
+#   greater than 0.95. This means that the posterior inferences are prior
+#   dependent, i.e., Lower_Prob<0.95 and  Upper_Prob>0.95.
+#
+#   isignrank.test(x,y,"greater") -- evaluates the hypothesis  P(Z>=-Z)>1/2. This is the
+#                Bayesian improved version of wilcox.test(x,y,"greater", paired=TRUE)  (default value).
+#   isignrank.test(x,y,"less") -- evaluates the hypothesis  P(Z <= -Z)>1/2. This is the
+#                Bayesian improved version of wilcox.test(x,y,"less", paired=TRUE) .
+#   isignrank.test(x,y,"two.sided") -- performs a two-sided Bayesian test, i.e., H=1 if 1/2 is
+#                not included in the 1-ALPHA lower and upper HPD credible
+#                intervals. H=0 if 1/2 is included in the 1-ALPHA lower and
+#                upper HPD credible. H=2 otherwise, indeterminate case.
+#                This is the Bayesian improved version of wilcox.test(x,y,'two.sided', paired=TRUE).
+#
+#   isignrank.test(...,alpha=value) returns the result of the hypothesis
+#   test with posterior probability gretaer than 1-value.
+#
+#   isignrank.test(...,s=value) sets the value of the prior strength of 
[…]

### 2019-03-14 scripts/signRankSampler.R

@@ -1,0 +1,117 @@
+
+signRankGibbsSampler <- function(xVals, yVals = NULL, testValue = 0, nSamples = 10000, progBar = FALSE, cauchyPriorParameter = 1/sqrt(2),
+                            nGibbsIterations = 5, varyTies = TRUE) {
+  
+  if (progBar) {
+    myBar <- txtProgressBar(min = 1, max = nSamples, initial = 1, char = "*",style=3,width=50)
+  }
+  
+  n <- length(xVals)
+  nDF <- n-1
+
+  if (!is.null(yVals)) { 
+    differenceScores <- xVals - yVals
+  } else {
+      differenceScores <- xVals - testValue
+  }
+  
+  differenceSigns <- (sign(differenceScores))
+  absDifferenceRanked <- rank(abs(differenceScores))
+  prodSignAbsRank <- differenceSigns * absDifferenceRanked
+  
+  initDiffSamples <- sort(abs(rnorm(n)))[absDifferenceRanked]
+  sampledDiffsAbs <- abs(initDiffSamples)
+  diffSamples <- numeric(n)
+  
+  deltaSamples <- gSamples <- numeric(nSamples)
+  diffSamplesMatrix <- matrix(nrow=nSamples,ncol=n)
+  
+  oldDeltaProp <- 0
+  
+  for (j in 1:nSamples) {
+    for (i in sample(n)) {
+      
+      currentRank <- absDifferenceRanked[i]
+      
+      currentBounds <- upperLowerTruncation(ranks=absDifferenceRanked, values=sampledDiffsAbs, currentRank=currentRank)
+      if (is.infinite(currentBounds[["under"]])) {currentBounds[["under"]] <- 0}
+      
+      sampledDiffsAbs[i] <- myTruncNormSim(currentBounds[["under"]], currentBounds[["upper"]], 
+                                           mu = abs(oldDeltaProp), sd=1)
+    }
+    
+    diffSamples <- sampledDiffsAbs * differenceSigns
+    
+    if (any(differenceSigns == 0) && varyTies) {
+      nullSamples <- sampledDiffsAbs[differenceSigns == 0] * sample(c(-1,1), size = sum(differenceSigns == 0), replace = T)
+      diffSamples[which(differenceSigns == 0)] <- nullSamples
+    }
+    
[…]

### 2019-03-21 analysis/02_kids_600.Rmd
update kids analysis

@@
 ---
-title: "DisCon Kids Pilot"
+title: "DisCon Children 6 exposure trials"
 output: html_document
@@
 kbm1 <- brm(correct_target1 ~ age_num +
-                      (1| subid) + (1 | target1),
+                      (1| subid) + (age_num | target1),
                     data = model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.95),
+          control = list(adapt_delta = 0.99),
           sample_prior = F,
           save_all_pars = TRUE,
-          iter = 2000)
+          iter = 5000)
 
@@
 kbm2 <- brm(correct_target1 ~ 1 +
-                      (1| subid) + (1 | target1),
+                      (1| subid) + (age_num | target1),
                     data = model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.95),
+          control = list(adapt_delta = 0.99),
           sample_prior = F,
           save_all_pars = TRUE,
-          iter = 2000)
+          iter = 5000)
 
@@
   ylim(-0.05,1.05)+
-  guides(alpha = F)+
+  guides(alpha = F, col = F)+
   scale_color_solarized()
@@
 ## position effects
-```{r proportion of choices}
+```{r }
 pos_plot <- data %>%
@@
   group_by(pickPos,subid) %>%
-  summarise(correct = mean(correct_target1))
-
-pos_plot_mean <- pos_plot %>%
-  group_by(pickPos) %>%
-  multi_boot_standard(col = "correct")
+  summarise(n = n())%>%
+  group_by(pickPos)%>%
+  multi_boot_standard(col = "n")
 
 ggplot() +
-  geom_jitter(data = pos_plot, aes(x = pickPos, y = correct,  alpha = .2, col = pickPos),width = .2,height = .01)+
-  geom_pointrange(data = pos_plot_mean, aes(x = pickPos, y = mean,  ymin = ci_lower, ymax = ci_upper, col = pickPos),size = .8)+
-  geom_hline(yintercept = 1/3, lty=2)+
-  labs(x="",y="Proportion correct")+
+  geom_pointrange(data = pos_plot, aes(x = pickPos, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
+  labs(x="Item position",y="Mean item in this position chosen at test")+
   theme_few() +
-  ylim(-0.05,1.05)+
+  ylim(0,4)+
   guides(alpha = F)+
@@
 ```
+
+# one sample wilcoxon
+```{r}
+
+# Based on: http://ipg.idsia.ch/preprints/benavoli2014a.pdf
+source("../scripts/isignrank.test.R")
+
+rank_data <- data %>%
+  filter(phase == 'test')%>%
+  group_by(experiment,subid) %>%
+  summarise(correct = mean(correct_target1)) %>%
+  mutate(chance = rep(1/3,length(correct)))
+
+isignrank.test(rank_data$chance,rank_data$correct,"two.sided")
+
+# Based on : https://arxiv.org/pdf/1712.06941.pdf
+source("../scripts/signRankSampler.R")
+
+rank_test <- signRankGibbsSampler(rank_data$correct,rank_data$chance)
+
+rank_test_plot <- data.frame(rank_test)
+
+ggplot(rank_test_plot, aes(plogis(deltaSamples))) +
+  geom_density(alpha = .5)+
+  xlim(0,1)
+```

### 2019-05-29 analysis/02_kids_600.Rmd
add analysis for 6v1 and 600 2yo

@@
 #files <- dir("../../kids_simple_4cat/")
-files <- dir("../../kids_raw_data/600/")
+files <- dir("../../kids_raw_data/test/")
 
@@
 #  jf <- paste("../../kids_simple_4cat/",f,sep="")
-  jf <- paste("../../kids_raw_data/600/",f,sep="")
+  jf <- paste("../../kids_raw_data/test/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,36,str_length(jf)-11)
+  date <- str_sub(jf,37,str_length(jf)-11)
   id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
@@
 }
+
+raw_data <- raw_data %>%
+  filter(subid != "190402_3_d600")
 
@@
 log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
+  mutate(subid = ifelse(subid == "190416_4_d6v1","190416_4_d600",subid))%>%
   filter(Condition == "d600")%>%
@@
 #unique(log$subid)
+
+raw_data%>%
+  filter(experiment !="distribution_kids_simple_within")%>%
+  group_by(subid)%>%
+  summarise(n())%>%
+  filter(!(subid %in% unique(log$subid)))
 
@@
 
-#unique(data$subid)
+unique(data$subid)
 
@@
 ##data <- read_csv(file="../data/kids_600.data.csv")
+
 ```
@@
   ylim(-0.05,1.05)+
-  xlim(3,5)+
+  xlim(2,5)+
   guides(alpha = F)
@@
 plot_dens <- data_frame(
-  age = rep(c(3,4), each = 1000),
-  posterior = c(unlist(plot_post%>%filter(subage == "3") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "4") %>% pull(posterior)))
+  age = rep(c(2,3,4), each = 1000),
+  posterior = c(unlist(plot_post%>%filter(subage == "2") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "3") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "4") %>% pull(posterior)))
 )
@@
   data.frame(
-    age = c(rep('3', 512),
+    age = c(rep('2', 512),
+            rep('3', 512),
               rep('4', 512)),
     x = c(densities$dens[[1]]$x, 
-          densities$dens[[2]]$x),
+          densities$dens[[2]]$x,
+          densities$dens[[3]]$x),
     y = c(densities$dens[[1]]$y,
-          densities$dens[[2]]$y)
+          densities$dens[[2]]$y,
+          densities$dens[[3]]$y)
   ) %>%
@@
     ci_shade = ifelse( age == "3",
-      ifelse( x <= plot_dens_ci%>%filter(subage == "3")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "3")%>%pull(uci), "OFF", "ON"), ifelse( x <= plot_dens_ci%>%filter(subage == "4")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "4")%>%pull(uci), "OFF", "ON")))
+                       ifelse( x <= plot_dens_ci%>%filter(subage == "3")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "3")%>%pull(uci), "OFF", "ON"),
+                       ifelse(age == "2", ifelse( x <= plot_dens_ci%>%filter(subage == "2")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "2")%>%pull(uci), "OFF", "ON"),
+      ifelse( x <= plot_dens_ci%>%filter(subage == "4")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "4")%>%pull(uci), "OFF", "ON"))))
 

### 2019-05-29 analysis/02_kids_6v1.Rmd
add analysis for 6v1 and 600 2yo

@@
 #files <- dir("../../kids_simple_4cat/")
-files <- dir("../../kids_raw_data/6v1/")
+files <- dir("../../kids_raw_data/test/")
 
@@
 #  jf <- paste("../../kids_simple_4cat/",f,sep="")
-  jf <- paste("../../kids_raw_data/6v1/",f,sep="")
+  jf <- paste("../../kids_raw_data/test/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,36,str_length(jf)-11)
+  date <- str_sub(jf,37,str_length(jf)-11)
   id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
@@
 
-#unique(raw_data$subid)
+unique(raw_data$subid)
+
+raw_data <- raw_data %>%
+  mutate(subage = ifelse(subid == "190313_2_d6v1","4",subage))
 
@@
 
+raw_data%>%
+  filter(experiment =="distribution_kids_simple_within")%>%
+  group_by(subid)%>%
+  summarise(n())%>%
+  filter(!(subid %in% unique(log$subid)))
+
 #unique(log$subid)
@@
          distribution = ifelse(distribution == "c(6, 0, 0)", "6-0-0","1-0-0"))%>%
-  select(-dob, -check_age,-keep_drop,-experimenter,-test_date,-numberOfTrials,-nunberOfTrials)
+  select(-dob, check_age,-keep_drop,-experimenter,-test_date,-numberOfTrials,-nunberOfTrials)
 
@@
   group_by(subage
-           #,sex
            )%>%
@@
   geom_pointrange(data = pt2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  geom_hline(yintercept = 5/6, lty=2)+
+  geom_hline(yintercept = 1/3, lty=2)+
   labs(x="",y="Proportion correct in training")+
@@
   filter(phase == 'test')%>%
-  group_by(distribution,subid) %>%
+  group_by(subage, distribution,subid) %>%
   summarise(correct = mean(correct_target1),
@@
 p2 <- p1 %>%
-  group_by(distribution) %>%
+  group_by(subage,distribution) %>%
   multi_boot_standard(col = "correct")
@@
 ggplot() +
-  geom_jitter(data = p1, aes(x = distribution, y = correct, col = distribution), alpha = .2 ,width = .2,height = .01)+
-  geom_pointrange(data = p2, aes(x = distribution, y = mean,  ymin = ci_lower, ymax = ci_upper, col = distribution),size = .8)+
+  geom_jitter(data = p1, aes(x = distribution, y = correct, col = subage), alpha = .2 ,width = .2,height = .01)+
+  geom_pointrange(data = p2, aes(x = distribution, y = mean,  ymin = ci_lower, ymax = ci_upper, col = subage),size = .8, position = position_dodge(width = .5))+
   geom_hline(yintercept = 1/3, lty=2)+
@@
   scale_color_solarized()
+```
+
+# Proportion correct choice by age continous
+
+```{r}
+p5 <- data %>%
+  filter(phase == 'test')%>%
+  group_by(distribution,age_num, subid) %>%
+  summarise(correct = mean(correct_target1))
+
+ggplot(data = p5, aes(x = age_num, y = correct, col = distribution,fill = distribution)) +
+  geom_jitter(width = .01, height = .0, alpha = .5)+
+  geom_smooth(method = "lm",  se = T,  alpha = .5, size = 1, alpha = .5 )+
+  geom_hline(yintercept = 1/3, lty=2)+
+  labs(x="Age",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(3,5)+
+  guides(alpha = F)+
+  scale_color_ptol()+
+  scale_fill_ptol()
 ```
@@
 
-kbm1 <- brm(correct_target1 ~ age_num * distribution
-                      (condition| subid) + (condition | target1),
+kbm1 <- brm(correct_target1 ~ age_num * distribution +
+                      (distribution| subid) + (distribution | target1),
                     data = model_data, family = bernoulli(),
@@
 ```{r}
-bayesplot::mcmc_areas(as.array(kbm1), pars = c("b_Intercept", "b_age_num"), prob = 0.95)+
+bayesplot::mcmc_areas(as.array(kbm1), pars = c("b_Intercept", "b_age_num", "b_distribution6M0M0", "b_age_num:distribution6M0M0"), prob = 0.95)+
   geom_vline(xintercept = 0, lty = 2, col = "black")+
@@
 kbm2 <- brm(correct_target1 ~ age_num +
-                      (condition| subid) + (condition | target1),
+                      (distribution| subid) + (distribution | target1),
                     data = model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.95),
+          control = list(adapt_delta = 0.99),
           sample_prior = F,
@@
 ```{r}
-child_waic <- brms::WAIC(kbm1, kbm2, compare = F)
+child_waic <- brms::waic(kbm1, kbm2, compare = F)
 
-child_weights <- model_weights(kbm1, kbm2)
+child_weights <- model_weights(kbm1, kbm2, weights = "waic")
 
@@
 data_frame(
-  model = c("kbm1_w_age","kbm2"),
-  WAIC = c(child_waic$kbm1$estimates[3,1],child_waic$kbm2$estimates[3,1]),
-  SE = c(child_waic$kbm1$estimates[3,2],child_waic$kbm2$estimates[3,2]),
+  model = c("kbm1_w_condition","kbm2"),
+  WAIC = c(child_waic$loo$kbm1$estimates[3,1],child_waic$loo$kbm2$estimates[3,1]),
+  SE = c(child_waic$loo$kbm1$estimates[3,2],child_waic$loo$kbm2$estimates[3,2]),
   weight = c(child_weights[1],child_weights[2]),

### 2019-07-31 analysis/02_kids_600.Rmd
speaker change experiment for kids

@@
 ```{r}
-chance_data <- data %>%
-  filter(phase != "training") %>%
-  group_by(subage,subid) %>%
-  summarise(correct = mean(correct_target1)) %>%
-  mutate(comp_chance= ifelse(correct<1/3,0,1))
+model_data <- data%>%
+  filter(phase != "training")%>%
+  mutate(age_num = scale(age_num))
 
@@
 
-chance_model <- brm(comp_chance ~ 1,
-                    data = chance_data, family = bernoulli(),
-          control = list(adapt_delta = 0.95),
+chance_model <- brm(correct_target1 ~ 1 + 
+                      (1| subid) + (age_num | target1),
+                    data = model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
           sample_prior = F,

### 2019-07-31 experiments/discon_look_kid_simple_4cat_speakerchange.js

@@ -1,0 +1,920 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+//only preload relevant audios (no speaker change)
+var preloadAudios = ["hi", "lets", "intro", "thank", "it", "needtogo", "imback"];
+
+var posAgents = shuffle(["Bear", "Cat", "Elephant", "Frog", "Sheep", "Tiger", "Mouse"])
+
+//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
+
+var audios = new Array();
+for (i = 0; i < posAgents.length; i++) {
+    for (j = 0; j < preloadAudios.length; j++) {
+        var audio = new Audio();
+        audio.src = "sounds/speakerchange/" + preloadAudios[j] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+    for (k = 0; k < preloadItems.length - 3; k++) {
+        var audio = new Audio();
+        audio.src = "sounds/speakerchange/" + preloadItems[k] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
[…]

### 2019-08-01 experiments/discon_look_kid_simple_4cat_speakerchange.js
change location for the data to be sent to and intro

@@ -383,8 +383,8 @@ var experiment = {
 
     introAll: function() {
         showSlide("introAll");
-        document.getElementById("text_introAll").innerHTML = "In this game, you're going to meet the little animals. They each live in a house and they have many different kinds of things at home. Each animal will tell you about some of things they have in their house.";
-        document.getElementById("text_introAll_2").innerHTML = "Your job is to touch the thing the animal is talking about. So, listen carefully and find out which one you have to touch.";
+        document.getElementById("text_introAll").innerHTML = "In this game, you're going to meet the little animals. They each live in a house and they have many different kinds of things at home. Each animal will tell you about their favorite things.";
+        document.getElementById("text_introAll_2").innerHTML = "Your job is to touch the thing the animal is talking about. So, listen carefully and find out which one you have to touch. Pay close attention to the animals when they leave the room. Sometimes a different animal returns.";
     },
 
     intro: function () {

### 2019-08-01 experiments/mmturkey_kids_speaker_change.js

@@ -1,0 +1,263 @@
+// Bundle in Crockford's JSON2.js
+var JSON;JSON||(JSON={});
+(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
+e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
+"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2019-11-25 analysis/02_kids_600.Rmd
update repo to check analysis

@@
 output: html_document
-  code_folding: hide
+
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
 
@@
 library(knitr)
-
+library(brms)
 library(lsr)
@@
 raw_data <- raw_data %>%
-  filter(subid != "190402_3_d600")
+  filter(subid != "190402_3_d600")%>%
+  mutate(subage = str_replace(subage," ",""))
 
@@
 log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
-  mutate(subid = ifelse(subid == "190416_4_d6v1","190416_4_d600",subid))%>%
+  mutate(subid = ifelse(subid == "190416_4_d6v1","190416_4_d600",subid),
+         subid = ifelse(subid == "190828_3_d500","190828_3_d600",subid))%>%
   filter(Condition == "d600")%>%
@@
 
-```{r sanity checks}
+```{r sanity checks, include = F}
 # filtering out subjects that perform poorly on training trials
@@
 
+```{r}
+#clean data file for repo
+data_ex1 <- data %>%
+  filter(phase == "test")%>%
+  mutate(correct = ifelse(correct_target1 == "1", 1, 0),
+         target_category = target1, 
+         picked_category = pickCat,
+         experiment = "simple_inference", 
+         id = paste0("part_",as.numeric(as.factor(subid))),
+         id = paste(id, experiment, sep = "_"),
+         speaker = agent,
+         age_group = subage)%>%
+  select(id, age_group,age_num,sex,experiment,trial,speaker,target_category, picked_category,correct)
+
+write_csv(data_ex1, path="../data/data_ex1.csv")
+```
+
 # Participants
@@
   knitr::kable(digits = 2)
+
 ```
@@
 
-```{r proportion of choices}
+```{r}
 p1 <- data %>%
@@
 
-```{r proportion of choices}
+```{r}
 p3 <- data %>%
@@
 
-Proportion correct choice by age continous
+# Proportion correct choice by age continous
 
@@
   geom_jitter(width = .01, height = .0, alpha = .5)+
-  geom_smooth(method = "lm",  se = T,  alpha = .5, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
+  geom_smooth(method = "glm",  se = T,  alpha = .5, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
   geom_hline(yintercept = 1/3, lty=2)+
@@
 ```
-Plotting posterior based on t-test
 
-```{r}
+# Plotting posterior based on t-test
+
+```{r, echo = F}
 plot_post <- data %>%
@@
 
-ggplot(plot_dens, aes(posterior, group = factor(age))) +
+post_plot <- ggplot(plot_dens, aes(posterior, group = factor(age))) +
   geom_density(alpha = .5)+
@@
   guides(alpha = F)+
-  scale_fill_solarized(name = "Age")+
+  scale_fill_ptol(name = "Age")+
   theme(axis.title.y = element_blank(),
@@
 
+post_plot
 ```
 
-# Comparison to chance based on model
-
-```{r}
+```{r, include = F, cache = T}
 model_data <- data%>%
@@
 chance_model <- brm(correct_target1 ~ 1 + 
-                      (1| subid) + (age_num | target1),
+                      (1| subid),
                     data = model_data, family = bernoulli(),
@@
           sample_prior = F,
+          chains = 4, 
+          cores = 4,
+          silent = T, 
+          refresh = 0, 
           save_all_pars = TRUE,
@@
 
-```{r}
+```{r, include = F}
 bayesplot::mcmc_areas(as.array(chance_model), pars = c("b_Intercept"), prob = 0.95)+
@@
 # Model
-```{r, include = F}
-library(brms)
 
+## Model with age
+```{r, cache = T}
 model_data <- data%>%
@@
 kbm1 <- brm(correct_target1 ~ age_num +
-                      (1| subid) + (age_num | target1),
+                      (1| subid),
                     data = model_data, family = bernoulli(),
@@
           sample_prior = F,
+          chains = 4, 
+          cores = 4,
           save_all_pars = TRUE,
@@
 summary(kbm1)
+
+waic1 <- waic(kbm1)
 ```
+### Plotting model fixed effects
 
@@
 
-```{r, include = F}
+## Model without age
+
+```{r, cache = T}
 kbm2 <- brm(correct_target1 ~ 1 +
-                      (1| subid) + (age_num | target1),
+                      (1| subid),
                     data = model_data, family = bernoulli(),
@@
           sample_prior = F, 
+          chains = 4, 
+          cores = 4,
           save_all_pars = TRUE,
@@
 summary(kbm2)
+
+waic2 <- waic(kbm2)
 ```
@@
 ```{r}
-child_waic <- brms::WAIC(kbm1, kbm2, compare = F)
-
 child_weights <- model_weights(kbm1, kbm2)
@@
   model = c("kbm1_w_age","kbm2"),
-  WAIC = c(child_waic$kbm1$estimates[3,1],child_waic$kbm2$estimates[3,1]),
-  SE = c(child_waic$kbm1$estimates[3,2],child_waic$kbm2$estimates[3,2]),
+  WAIC = c(child_waic$loos$kbm1$waic,child_waic$loos$kbm2$waic),
+  SE = c(child_waic$loos$kbm1$se_waic,child_waic$loos$kbm2$se_waic),
   weight = c(child_weights[1],child_weights[2]),
@@
   kable(digits = 2)
+
 ```
 
-# Check category, position and trial
-
-## category effects
-```{r proportion of choices}
+```{r , include = F}
 cat_plot <- data %>%
@@
 
-## position effects
-```{r }
+```{r , include = F}
 pos_plot <- data %>%
@@
 
-## trial effects
-```{r proportion of choices}
+```{r , include = F}
 trial_plot <- data %>%
@@
 
-# one sample wilcoxon
-```{r}
+```{r, include = F}
 

### 2019-11-25 analysis/02_kids_6v1.Rmd
update repo to check analysis

@@
 
+```{r}
+#clean data file for repo
+data_ex2 <- data %>%
+  filter(phase == "test")%>%
+  mutate(correct = ifelse(correct_target1 == "1", 1, 0),
+         condition = ifelse(distribution == "6-0-0", "high_input", "low_input"),
+         target_category = target1, 
+         picked_category = pickCat,
+         experiment = "variable_input", 
+         speaker = agent,
+         id = paste0("part_",as.numeric(as.factor(subid))),
+         id = paste(id, experiment, sep = "_"),
+         age_group = subage)%>%
+  select(id, age_group,age_num,sex,experiment,trial,condition, speaker, target_category, picked_category,correct)
+
+write_csv(data_ex2, path="../data/data_ex2.csv")
+```
+
 # Participants
@@
   filter(phase == 'test')%>%
-  group_by(subage, distribution,subid) %>%
-  summarise(correct = mean(correct_target1),
-            sd = sd(correct_target1))
+  group_by(experiment,subid) %>%
+  summarise(correct = mean(correct_target1))
 
 p2 <- p1 %>%
-  group_by(subage,distribution) %>%
+  group_by(experiment) %>%
   multi_boot_standard(col = "correct")
@@
 ggplot() +
-  geom_jitter(data = p1, aes(x = distribution, y = correct, col = subage), alpha = .2 ,width = .2,height = .01)+
-  geom_pointrange(data = p2, aes(x = distribution, y = mean,  ymin = ci_lower, ymax = ci_upper, col = subage),size = .8, position = position_dodge(width = .5))+
+  geom_jitter(data = p1, aes(x = experiment, y = correct, col = experiment), alpha = .2 ,width = .2,height = .01)+
+  geom_pointrange(data = p2, aes(x = experiment, y = mean,  ymin = ci_lower, ymax = ci_upper, col = experiment),size = .8, position = position_dodge(width = .5))+
   geom_hline(yintercept = 1/3, lty=2)+
@@
 kbm1 <- brm(correct_target1 ~ age_num * distribution +
-                      (distribution| subid) + (distribution | target1),
+                      (distribution| subid),
                     data = model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.95),
+          control = list(adapt_delta = 0.99),
           sample_prior = F,
+          chains = 4, 
+          cores = 4, 
           save_all_pars = TRUE,
@@
 ```
+```{r, include = F}
+#   model
 
-```{r, include = F}
-kbm2 <- brm(correct_target1 ~ age_num +
-                      (distribution| subid) + (distribution | target1),
+kbm2 <- brm(correct_target1 ~ age_num + distribution +
+                      (distribution| subid),
                     data = model_data, family = bernoulli(),
@@
           sample_prior = F,
+          chains = 4, 
+          cores = 4, 
           save_all_pars = TRUE,
@@
 summary(kbm2)
+```
+
+```{r, include = F}
+kbm3 <- brm(correct_target1 ~ age_num +
+                      (distribution| subid),
+                    data = model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4, 
+          cores = 4, 
+          save_all_pars = TRUE,
+          iter = 2000)
+
+summary(kbm3)
 ```
@@
 trial_plot <- data %>%
-  filter(phase == 'test')
+  filter(phase == 'test')5
 
-ggplot(data = trial_plot, aes(x = trial, y = correct_target1)) +
+ggplot(data = trial_plot, aes(x = trial, col = distribution,  y = correct_target1)) +
   geom_jitter(alpha = .2,width = .2,height = .01)+
-  geom_smooth(method = "loess",  se = T, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
+  geom_smooth(method = "loess",  se = T, size = 1, alpha = .5 )+
   geom_hline(yintercept = 1/3, lty=2)+
@@
   theme_few() +
+  #facet_grid(~subage)+
   ylim(-0.05,1.05)+

### 2019-11-25 analysis/02_kids_speaker_change.Rmd
update repo to check analysis

---
title: "DisCon Children Speaker Change"
output: html_document
  code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
library(readxl)
library(knitr)

library(lsr)
library(pwr)

library(coda)
library(reshape2)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

```

```{r data pre-processing, include = F}

#files <- dir("../../kids_simple_4cat/")
files <- dir("../../kids_raw_data/speaker_change/")

raw_data <- data_frame()
for (f in files) {
#  jf <- paste("../../kids_simple_4cat/",f,sep="")
  jf <- paste("../../kids_raw_data/speaker_change/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,58,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

raw_data <- raw_data %>%
   mutate(subid = str_replace(subid, "_d600","_dsc"),
          subid = ifelse(subid == "190915_1_dsc", "190918_1_dsc", subid),
          subid = ifelse(subid == "190929_2_dsc", "190920_2_dsc", subid))

unique(raw_data$subid)

# linking the data to the demographics spreadsheet
# always check if subjects get "lost" due do differetn subids
log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  filter(Condition == "dsc")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"))%>%
  select(subid,experimenter,keep_drop,sex,dob)

raw_data%>%
  filter(experiment =="distribution_kids_simple_speakerchange")%>%
  group_by(subid)%>%
  summarise(n())%>%
  filter(!(subid %in% unique(log$subid)))

#unique(log$subid)

data <- left_join(raw_data,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(distribution = as.character(distribution),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F), 
         distribution = ifelse(distribution == "c(6, 0, 0)", "6-0-0","1-0-0"))%>%
  select(-dob, check_age,-keep_drop,-experimenter,-test_date)

#unique(data$subid)

#write.csv(data, file="../data/kids_speaker_change_data.csv")

##data <- read_csv(file="../data/kids_speaker_change_data.csv")
```

```{r sanity checks}
# filtering out subjects that perform poorly on training trials
data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item))

drop <- data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(subid)

data <- data %>%
  filter(!subid %in% drop,
         subage != "2")
```

```{r}
#clean data file for repo
data_ex3 <- data %>%
  filter(subage != "2",
         phase == "test")%>%
  mutate(correct = ifelse(correct_target1 == "1", 1, 0),
         condition = ifelse(speakerChange == "same", "same_speaker", "different_speaker"),
         target_category = target1, 
         picked_category = pickCat,
         experiment = "speaker_change", 
         id = paste0("part_",as.numeric(as.factor(subid))),
         id = paste(id, experiment, sep = "_"),
         speaker = ifelse(speakerChange == "change", alternativeAgent, agent),
         age_group = subage)%>%
  select(id, age_group,age_num,sex,experiment,trial,condition, speaker, target_category, picked_category,correct)

write_csv(data_ex3, path="../data/data_ex3.csv")
```

# Participants

```{r}
data %>%
  group_by(subage)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)
```

# Proportion correct choice in training trials

```{r}
pt1 <- data %>%
  filter(phase == 'training')%>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_item))

pt2 <- pt1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = pt1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .0)+
  geom_pointrange(data = pt2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()

```

# Proportion correct choice in test trials across age bins

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(age_num,speakerChange,subid) %>%
  summarise(correct = mean(correct_target1))

p2 <- p1 %>%
  group_by(speakerChange) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_point(data = p1, aes(x = speakerChange, y = correct, col = speakerChange), alpha = .2 , position = position_jitterdodge(dodge.width = .5, jitter.width = .1))+
  geom_pointrange(data = p2, aes(x = speakerChange, y = mean,  ymin = ci_lower, ymax = ci_upper, col = speakerChange),size = .8, position = position_dodge(width = .5))+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_ptol()
```

```{r proportion of choices}
p3 <- data %>%
  filter(phase == 'test')%>%
  group_by(subage, speakerChange,subid) %>%
  summarise(correct = mean(correct_target1))

p4 <- p3 %>%
  group_by(subage,speakerChange) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_point(data = p3, aes(x = subage, y = correct, col = speakerChange), alpha = .2 , position = position_jitterdodge(dodge.width = .5, jitter.width = .1))+
  geom_pointrange(data = p4, aes(x = subage, y = mean,  ymin = ci_lower, ymax = ci_upper, col = speakerChange),size = .8, position = position_dodge(width = .5))+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_ptol()
```

```{r}
library(BayesFactor)

data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage)%>%
  mutate(mean= mean(unlist(correct)),
         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
  select(subage,mean,bf)

plot_post <- data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1))%>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 1000)[,"mu"])))%>%
  select(-correct)

plot_dens_ci <- plot_post %>%
  summarise(mode = estimate_mode(unlist(posterior)),
            lci = hdi_lower(unlist(posterior)),
            uci = hdi_upper(unlist(posterior)))
```

# Proportion correct choice by age continous

```{r}
p5 <- data %>%
  filter(phase == 'test')%>%
  group_by(speakerChange,age_num, subid) %>%
  summarise(correct = mean(correct_target1))

ggplot(data = p5, aes(x = age_num, y = correct, col = speakerChange,fill = speakerChange)) +
  geom_jitter(width = .01, height = .0, alpha = .5)+
  geom_smooth(method = "glm",  span = 1, se = T,  alpha = .5, size = 1, alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)+
  scale_color_ptol()+
  scale_fill_ptol()
```

# Model 
```{r, include = F}
library(brms)

model_data <- data%>%
  filter(phase != "training")%>%
  mutate(age_num = scale(age_num),
         item = ifelse(speakerChange == "change", alternativeAgent, agent))

#   model

kbm1 <- brm(correct_target1 ~ age_num * speakerChange +
                      (speakerChange| subid) + (age_num * speakerChange | item),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 5000)

summary(kbm1)

kbm1_1 <- brm(correct_target1 ~ age_num * speakerChange +
                      (speakerChange| subid),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 5000)

summary(kbm1_1)

model_weights(kbm1, kbm1_1, weights = "waic")

```

```{r}
bayesplot::mcmc_areas(as.array(kbm1), pars = c("b_Intercept", "b_age_num", "b_speakerChangesame", "b_age_num:speakerChangesame"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

```{r, include = F}
kbm2 <- brm(correct_target1 ~ age_num + speakerChange +
                      (speakerChange| subid) + (age_num * speakerChange | item),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 5000)

summary(kbm2)

kbm2_2 <- brm(correct_target1 ~ age_num + speakerChange +
                      (speakerChange| subid),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 20000)

summary(kbm2_2)
```

```{r}
bayesplot::mcmc_areas(as.array(kbm2), pars = c("b_Intercept", "b_age_num", "b_speakerChangesame"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

```{r, include = F}
kbm3 <- brm(correct_target1 ~ age_num +
                      (speakerChange| subid) + (age_num * speakerChange | item),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 5000)

summary(kbm3)

kbm3_3 <- brm(correct_target1 ~ age_num +
                      (speakerChange| subid),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 20000)

summary(kbm3_3)
```

## Model comparison

```{r}
child_waic <- brms::waic(kbm1, kbm2, kbm3, compare = F)

child_weights <- model_weights(kbm1, kbm2,kbm3, weights = "waic")

# Bayes Factors (slightly variable)
bf_full_null_1 <- bayes_factor(kbm1, kbm3, log = FALSE, maxiter = 5000)

bf_full_null_2 <- bayes_factor(kbm1, kbm2, log = FALSE, maxiter = 5000)

bf_full_null_3 <- bayes_factor(kbm2, kbm3, log = FALSE, maxiter = 5000)
```

```{r}
data_frame(
  model = c("model_w_int","model_w_condition","null_model"),
  WAIC = c(child_waic$loo$kbm1$estimates[3,1],child_waic$loo$kbm2$estimates[3,1],child_waic$loo$kbm3$estimates[3,1]),
  SE = c(child_waic$loo$kbm1$estimates[3,2],child_waic$loo$kbm2$estimates[3,2],child_waic$loo$kbm3$estimates[3,2]),
  weight = c(child_weights[1],child_weights[2],child_weights[3]),
  BF_vs_null = c(round(bf_full_null_1$bf,2),round(bf_full_null_3$bf,2),"-"))%>%
  kable(digits = 2)
```

# Check category, position and trial

## category effects
```{r proportion of choices}
cat_plot <- data %>%
  filter(phase == 'test')%>%
  group_by(target1,subid) %>%
  summarise(correct = mean(correct_target1))

cat_plot_mean <- cat_plot %>%
  group_by(target1) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = cat_plot, aes(x = target1, y = correct,  alpha = .2, col = target1),width = .2,height = .01)+
  geom_pointrange(data = cat_plot_mean, aes(x = target1, y = mean,  ymin = ci_lower, ymax = ci_upper, col = target1),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F, col = F)+
  scale_color_solarized()
```

## position effects
```{r }
pos_plot <- data %>%
  filter(phase == 'test')%>%
  group_by(pickPos,subid) %>%
  summarise(n = n())%>%
  group_by(pickPos)%>%
  multi_boot_standard(col = "n")

ggplot() +
  geom_pointrange(data = pos_plot, aes(x = pickPos, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
   labs(x="Item position",y="Mean item in this position chosen at test")+
  theme_few() +
  ylim(0,4)+
  guides(alpha = F)+
  scale_color_solarized()
```

## trial effects
```{r proportion of choices}
trial_plot <- data %>%
  filter(phase == 'test')

ggplot(data = trial_plot, aes(x = trial, y = correct_target1)) +
  geom_jitter(alpha = .2,width = .2,height = .01)+
  geom_smooth(method = "loess",  se = T, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

# one sample wilcoxon
```{r}

# Based on: http://ipg.idsia.ch/preprints/benavoli2014a.pdf
source("../scripts/isignrank.test.R")

rank_data <- data %>%
  filter(phase == 'test')%>%
  group_by(speakerChange,subage,subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  mutate(chance = rep(1/3,length(correct)))

isignrank.test(rank_data$chance,rank_data$correct,"two.sided")

# Based on : https://arxiv.org/pdf/1712.06941.pdf
source("../scripts/signRankSampler.R")

rank_test <- signRankGibbsSampler(rank_data$correct,rank_data$chance)

rank_test_plot <- data.frame(rank_test)

ggplot(rank_test_plot, aes(plogis(deltaSamples))) +
  geom_density(alpha = .5)+
  xlim(0,1)
```

### 2019-11-25 analysis/discon_summary.Rmd
update repo to check analysis

---
title: "DisCon Summary"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(langcog)
library(readxl)
library(knitr)
library(brms)
library(BayesFactor)
library(coda)
library(ggpubr)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r data files, include = F}

data_ex1 <- read_csv(file="../data/data_ex1.csv")

data_ex2 <- read_csv(file="../data/data_ex2.csv")

data_ex3 <- read_csv(file="../data/data_ex3.csv")

```

# Basic procedure

Each trial has an input phase (left) and a test phase (right). During the input phase the speaker directly names objects from a particular category. In the test phase, new objects from the same category are shown but the speaker ambiguously asks for "it". Main question: Do children pick the object from the same category.

```{r, fig.cap="Setup for child experiment. Input trial on the left and test trial on the right. Children heard pre-recorded utterances."}
include_graphics("../stimuli_pictures/kids_setup.png")
```

# General note on inference

I ran Bayesian GLMMs fit via brms. We include random effects for subject and item (speaker) and random slopes for condition whenever applicable. I used model comparisons as the main way of doing inference about age and condition effects. I used the following indicators (following Richard McElreath's book).

* WAIC score: WAIC is an information criterion which guards against overfitting the data by penalizing by the number of parameters in the model. It is taken to be an indicator of how good a model's out of sample predictions are. The lower, the better.

* WAIC weights: A model’s weight is an estimate of the probability that the model will make the best predictions on new data, conditional on the set of models considered. These sum up to 1.

After finding the "winning model", I use Bayes Factors to compare the winning model to alternative models without the predictors in question and also look at the predictors directly within the model to check the direction (positive vs. negative) and whether the CI overlaps with 0.

# General note on adult data

We have adult data (MTurk) for Experiment 1 and 3. For Experiment 2, we have data that tests the effect of amount of input but with different conditions. Adult experiments were not pre-registered, mainly because we used them to find the best procedure. If we were to include adults in the paper, we might want to consider running them again with a pre-registration. Here, they are only included in the plots.

# Experiment 1: Simple inference

Children received 6 input trials before the test trials. Main question was whether they pick the object from the same category.

## Participants

We tested 2,3 and 4yo. We added 2yo later and also increased the sample size for them because we expected a smaller effect. Children received 4 trials in a single condition.

```{r}
data_ex1 %>%
  group_by(age_group)%>%
  summarise(n = length(unique(id)))%>%
  knitr::kable(digits = 2)
```

## Results

```{r, fig.width=10, fig.height=5}
p1_ex1_child <- data_ex1 %>%
  mutate(age_group = as.character(age_group))%>%
  group_by(age_group, age_num,id) %>%
  summarise(correct = mean(correct))

p1_ex1_adult <- read_csv(file="../data/01_study2_adult.data.csv")%>%
  filter(phase=="test")%>%
  group_by(workerid)%>%
  summarise(correct = mean(correct_target1))%>%
  mutate(age_group = "adult")

p1_ex1 <- bind_rows(
  p1_ex1_child,
  p1_ex1_adult
)

p2_ex1 <- p1_ex1 %>%
  group_by(age_group) %>%
  multi_boot_standard(col = "correct")

ex1_age_bin <- ggplot() +
  geom_jitter(data = p1_ex1, aes(x = age_group, y = correct),alpha = .2, width = .1,height = .0)+
  geom_pointrange(data = p2_ex1, aes(x = age_group, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = .5))+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age group",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_ptol()

ex1_age_cont <- ggplot(p1_ex1, aes(x = age_num, y = correct)) +
  geom_jitter(alpha = .2, width = .1,height = .0)+
  geom_smooth(method = "glm",  se = T,  alpha = .5, size = 1)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_ptol()

ggarrange(ex1_age_bin, ex1_age_cont)

```

### Comparison to chance

We bin data by age and use a one-sample Bayesian t-test to compare performance to chance. The table below shows Bayes Factors (BF) for each age group.

```{r}
data_ex1 %>%
  group_by(age_group,id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(age_group) %>%
  mutate(mean= mean(unlist(correct)),
         BF = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
  select(age_group,mean,BF) %>%
  knitr::kable(digits = 3)
```

3 and 4yo seem to make the basic inference while the evidence is not that strong for 2yo. Because of that, we did not run 2yo in subsequent experiments.

### Effect of age

Here we use a Bayesian GLMM to look at the effect of age. For inference we compare it to a model without age as a predictor.

```{r, cache = T, include = F}
model_data_ex1 <- data_ex1 %>%
  mutate(z_age_num = age_num - mean(age_num))

#   model

ex1_m1 <- brm(correct ~ z_age_num +
                      (1| id) + (1| item),
                    data = model_data_ex1, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4,
          #refresh = 0,
          save_all_pars = TRUE,
          iter = 5000)

ex1_m1_waic <- as_tibble(waic(ex1_m1)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(Estimate)
ex1_m1_waic_se <- as_tibble(waic(ex1_m1)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(SE)

ex1_m2 <- brm(correct ~ 1 +
                      (1| id) + (1| item),
                    data = model_data_ex1, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4,
          #refresh = 0,
          save_all_pars = TRUE,
          iter = 5000)

ex1_m2_waic <- as_tibble(waic(ex1_m2)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(Estimate)
ex1_m2_waic_se <- as_tibble(waic(ex1_m2)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(SE)

ex1_waic_weights <- model_weights(ex1_m1, ex1_m2, weights = "waic")

ex1_bf <- bayes_factor(ex1_m1, ex1_m2, log = FALSE, maxiter = 5000)

```

The table below shows WAIC scores and weights for each model (RE = random effects, same for each model). The column BF_age_model shows the Bayes Factor for the model comparison between the full model (with age in that case) and each reduced model (here: without age)

```{r}
tibble(
  model = c("model_w_age: age_num + RE","null_model: 1 + RE"),
  WAIC = c(ex1_m1_waic,ex1_m2_waic),
  SE = c(ex1_m1_waic_se,ex1_m2_waic_se),
  weight = c(ex1_waic_weights[1],ex1_waic_weights[2]),
  BF_age_model = c("-",round(ex1_bf$bf,2)))%>%
  kable(digits = 2)
```

The model comparison favors the model with age as predictor. This is broadly in line with the analysis binned by age. However, the effect of age is not too strong: The BF in favor of the model with age is not that high and the predictor for age in the model overlaps with 0 (see plot below).

```{r, fig.cap="Posterior distribution for model fixed effects. Point indicates posterior mean, thick line shows 50%CI and thin line shows 95% CI.", fig.height=2, fig.align="center"}
bayesplot::mcmc_intervals(as.array(ex1_m1), pars = c("b_Intercept","b_z_age_num"), prob = 0.50, prob_outer = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

# Experiment 2: Variable input

Here we varied the number of input children received before each test trial. They either heard the speaker name six objects from the same category (high input) or just one (low input). Main question was whether their performance drops with lower input.

## Participants

The sample size in this study was rather small because age effects were not our major focus. We were mainly interested in the effect of condition. Children received again 4 trials, 2 in each condition.

```{r}
data_ex2 %>%
  group_by(age_group)%>%
  summarise(n = length(unique(id)))%>%
  knitr::kable(digits = 2)
```

## Results

```{r, fig.width=10, fig.height=5.5}
p1_ex2 <- data_ex2 %>%
  group_by(condition, age_group, age_num,id) %>%
  summarise(correct = mean(correct))

p2_ex2 <- p1_ex2 %>%
  group_by(condition,age_group) %>%
  multi_boot_standard(col = "correct")

ex2_age_bin <- ggplot() +
 geom_point(data = p1_ex2, aes(x = age_group, y = correct, col = condition), alpha = .2 , position = position_jitterdodge(dodge.width = .5, jitter.width = .1))+
  geom_pointrange(data = p2_ex2, aes(x = age_group, y = mean,  ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .5))+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_ptol()

ex2_age_cont <- ggplot(p1_ex2, aes(x = age_num, y = correct, col = condition, fill = condition)) +
  geom_jitter(alpha = .2, width = .1,height = .0)+
  geom_smooth(method = "glm",  se = T,  alpha = .5, size = 1)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_ptol()+
  scale_fill_ptol()

ggarrange(ex2_age_bin, ex2_age_cont, common.legend = T)

```

### Effect of condition

```{r, cache = T, include = F}
model_data_ex2 <- data_ex2 %>%
  mutate(z_age_num = age_num - mean(age_num))

#   model

ex2_m1 <- brm(correct ~ condition * z_age_num +
                      (condition| id) + (condition| item),
                    data = model_data_ex2, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4,
          #refresh = 0,
          save_all_pars = TRUE,
          iter = 5000)

ex2_m1_waic <- as_tibble(waic(ex2_m1)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(Estimate)

ex2_m1_waic_se <- as_tibble(waic(ex2_m1)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(SE)

ex2_m2 <- brm(correct ~ condition + z_age_num +
                      (condition| id) + (condition| item),
                    data = model_data_ex2, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4,
          #refresh = 0,
          save_all_pars = TRUE,
          iter = 5000)

ex2_m2_waic <- as_tibble(waic(ex2_m2)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(Estimate)

ex2_m2_waic_se <- as_tibble(waic(ex2_m2)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(SE)

ex2_m3 <- brm(correct ~ z_age_num +
                      (condition| id) + (condition| item),
                    data = model_data_ex2, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4,
          #refresh = 0,
          save_all_pars = TRUE,
          iter = 5000)

ex2_m3_waic <- as_tibble(waic(ex2_m3)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(Estimate)
ex2_m3_waic_se <- as_tibble(waic(ex2_m3)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(SE)

ex2_waic_weights <- model_weights(ex2_m1, ex2_m2, ex2_m3, weights = "waic")

ex2_bf_1 <- bayes_factor(ex2_m1, ex2_m3, log = FALSE, maxiter = 5000)

ex2_bf_2 <- bayes_factor(ex2_m1, ex2_m2, log = FALSE, maxiter = 5000)
```

The table below shows WAIC scores and weights for each model. The column BF_int_model shows the Bayes Factor for the model comparison between the full model (interaction model) and each reduced model (here: with main effect of condition or null model without condition).

```{r}
tibble(
  model = c("model_w_interaction: condition * age_num + RE", "model_w_condition: condition + age_num + RE","null_model: age_num + RE"),
  WAIC = c(ex2_m1_waic,ex2_m2_waic,ex2_m3_waic),
  SE = c(ex2_m1_waic_se,ex2_m2_waic_se,ex2_m3_waic_se),
  weight = c(ex2_waic_weights[1],ex2_waic_weights[2],ex2_waic_weights[3]),
  BF_int_model = c("-",round(ex2_bf_2$bf,2),round(ex2_bf_1$bf,2)))%>%
  kable(digits = 2)
```

The model comparison favors the null model with only age as predictor. (Note, however, that the Bayes Factor favors the interaction model). Condition seems not to affect children's performance. Overall, adding a second condition seems to have made the general task harder for younger children. This is also reflected in the reliably positive effect of age in the null model (plotted below).

```{r, fig.cap ="Posterior distribution for model fixed effects. Point indicates posterior mean, thick line shows 50%CI and thin line shows 95% CI.", fig.height=2, fig.align="center"}

bayesplot::mcmc_intervals(as.array(ex2_m3), pars = c("b_Intercept","b_z_age_num"), prob = 0.50, prob_outer = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

# Experiment 3: Speaker change

Here we tested whether children make speaker specific inferences. That is, whether they see the topic of a conversation as specific to a particular speaker. Children received 6 input trials with one speaker, then the speaker left the scene and either the same or a different speaker returned. At test, the speaker always asked for "it".

## Participants

Here we again tested a larger sample to also look at age effects. Children received 4 trials, 2 in each condition.

```{r}
data_ex3 %>%
  group_by(age_group)%>%
  summarise(n = length(unique(id)))%>%
  knitr::kable(digits = 2)
```

## Results

```{r, fig.width=10, fig.height=5.5}
p1_ex3_child<- data_ex3 %>%
  mutate(age_group = as.character(age_group))%>%
  group_by(condition, age_group, age_num,id) %>%
  summarise(correct = mean(correct))

p1_ex3_adult <- read_csv(file="../data/01_adult_speakerchange_preference.data.csv")%>%
  filter(phase=="test")%>%
  mutate(condition = ifelse(speakerChange == "same", "same_speaker", "different_speaker"))%>%
  group_by(workerid,condition)%>%
  summarise(correct = mean(correct_target1))%>%
  mutate(age_group = "adult")

p1_ex3 <- bind_rows(
  p1_ex3_child,
  p1_ex3_adult
)

p2_ex3 <- p1_ex3 %>%
  group_by(condition,age_group) %>%
  multi_boot_standard(col = "correct")

ex3_age_bin <- ggplot() +
 geom_point(data = p1_ex3, aes(x = age_group, y = correct, col = condition), alpha = .2 , position = position_jitterdodge(dodge.width = .5, jitter.width = .1))+
  geom_pointrange(data = p2_ex3, aes(x = age_group, y = mean,  ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .5))+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age Group",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_ptol()

ex3_age_cont <- ggplot(p1_ex3_child, aes(x = age_num, y = correct, col = condition, fill = condition)) +
  geom_jitter(alpha = .2, width = .1,height = .0)+
  geom_smooth(method = "glm",  se = T,  alpha = .5, size = 1)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_ptol()+
  scale_fill_ptol()

ggarrange(ex3_age_bin, ex3_age_cont, common.legend = T)

```

### Effect of condition

```{r, cache = T, include = F}
model_data_ex3 <- data_ex3 %>%
  mutate(z_age_num = age_num - mean(age_num))

#   model

ex3_m1 <- brm(correct ~ condition * z_age_num +
                      (condition| id) + ( condition| item),
                    data = model_data_ex3, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4,
          #refresh = 0,
          save_all_pars = TRUE,
          iter = 5000)

ex3_m1_waic <- as_tibble(waic(ex3_m1)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(Estimate)

ex3_m1_waic_se <- as_tibble(waic(ex3_m1)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(SE)

ex3_m2 <- brm(correct ~ condition + z_age_num +
                      (condition| id) + ( condition| item),
                    data = model_data_ex3, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4,
          #refresh = 0,
          save_all_pars = TRUE,
          iter = 5000)

ex3_m2_waic <- as_tibble(waic(ex3_m2)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(Estimate)

ex3_m2_waic_se <- as_tibble(waic(ex3_m2)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(SE)

ex3_m3 <- brm(correct ~ z_age_num +
                      (condition| id) + ( condition| item),
                    data = model_data_ex3, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4,
          #refresh = 0,
          save_all_pars = TRUE,
          iter = 5000)

ex3_m3_waic <- as_tibble(waic(ex3_m3)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(Estimate)
ex3_m3_waic_se <- as_tibble(waic(ex3_m3)$estimates, rownames = "criterion")%>%filter(criterion == "waic")%>%pull(SE)

ex3_waic_weights <- model_weights(ex3_m1, ex3_m2,ex3_m3, weights = "waic")

ex3_bf_1 <- bayes_factor(ex3_m1, ex3_m2, log = FALSE, maxiter = 5000)

ex3_bf_2 <- bayes_factor(ex3_m1, ex3_m3, log = FALSE, maxiter = 5000)
```

The table below shows WAIC scores and weights for each model. The column BF_int_model shows the Bayes Factor for the model comparison between the full model (interaction model) and each reduced model (here: with main effect of condition or null model without condition).

```{r}
tibble(
  model = c("model_w_interaction: condition * age_num + RE", "model_w_condition: condition + age_num + RE","null_model: age_num + RE"),
  WAIC = c(ex3_m1_waic,ex3_m2_waic,ex3_m3_waic),
  SE = c(ex3_m1_waic_se,ex3_m2_waic_se,ex3_m3_waic_se),
  weight = c(ex3_waic_weights[1],ex3_waic_weights[2],ex3_waic_weights[3]),
  BF_int_model = c("-",round(ex3_bf_1$bf,2),round(ex3_bf_2$bf,2)))%>%
  kable(digits = 2)
```

The model comparison favors the interaction model. Bayes Factors also suggest that this model fits the data better compared to the other models. When looking at the model predictors, we see a positive interaction effect, mirroring what we see in the graphs above, namely that younger children do not distinguish between the two conditions, but older children do.

```{r, fig.cap="Posterior distribution for model fixed effects. Point indicates posterior mean, thick line shows 50%CI and thin line shows 95% CI.", fig.height=4, fig.align="center"}
bayesplot::mcmc_intervals(as.array(ex3_m1), pars = c("b_Intercept","b_z_age_num", "b_conditionsame_speaker", "b_conditionsame_speaker:z_age_num"), prob = 0.50, prob_outer = .95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

# Conclusion

Children make inferences about what the general "topic" of a discourse is and use this to identify the referent of an ambiguous utterance. The amount of input they receive seems to have no direct effect on this inference. Older children treat the discourse topic as something that is specific to a particular speaker.

### 2019-11-25 paper/manuscript.Rmd
update repo to check analysis

---
title             : "What’s she talking about? Category based discourse inferences in early childhood"
shorttitle        : "Discourse inferences in early childhood"

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Jahnallee 59, 04109 Leipzig, Germany"
    email         : "manuel.bohn@uni-leipzig.de"
  - name          : "Khuyen Nha Le"
    affiliation   : "1"
  - name          : "Benjamin Peloquin"
    affiliation   : "1"
  - name          : "Bahar Köymen"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Stanford University"
  - id            : "2"
    institution   : "Leipzig University"
  - id            : "3"
    institution   : "University of Manchester"

authornote: |
  We thank Megan Merrick and Sabina Zacco for their help with the data collection. MB received funding from the European Union’s Horizon   2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no. 749229.

abstract: |
  tbd...

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["library.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(tidyverse)
library(ggplot2)
library(brms)
library(ggthemes)
library(langcog)
library(ggpubr)
library(BayesFactor)
library(broom)
library(coda)
library(reshape2)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r load data}
ex1_data <- read_csv(file="../data/data_ex1.csv")
ex2_data <- read_csv(file="../data/data_ex2.csv")
ex3_data <- read_csv(file="../data/data_ex3.csv")
```

# Experiment 1

All experimental procedures, sample sizes and statistical analysis were pre-registered (see https://osf.io/9ypxn and https://osf.io/fyaxq). The experimental procedure can be found in the assoicated online repository at https://github.com/manuelbohn/disCon.

## Participants
```{r participants-ex1, include = F}
desc_ex1 <- ex1_data%>%
  group_by(age_group)%>%
  summarise(n = length(unique(id)), 
            age = mean(age_num), 
            min_age = min(age_num),
            max_age = max(age_num))
```

We obtained valid data from 71 children, including `r desc_ex1%>%filter(age_group == "2")%>%pull(n)` 2-year-olds (mean = `r desc_ex1%>%filter(age_group == "2")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "2")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "2")%>%pull(max_age)`), `r desc_ex1%>%filter(age_group == "3")%>%pull(n)` 3-year-olds (mean = `r desc_ex1%>%filter(age_group == "3")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "3")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "3")%>%pull(max_age)`) and `r desc_ex1%>%filter(age_group == "4")%>%pull(n)` 4-year-olds (mean = `r desc_ex1%>%filter(age_group == "4")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "4")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "4")%>%pull(max_age)`). We tested a larger sample of 2-year-olds because we expected a weaker effect in this age group. In addition, 12 children were recruited but not tested becasue their parents reported less than 75% of English exposure at home. Ten children started the experiment but did not finish it because they became impatient (7) or the equipment broke (3). Three children were tested but excluded becasue they were correct in less than 5/6 training trials (see below). All children were recruited from the floor of a Children's museum in San José, California, USA. The population from which this sample is drawn is characterised by diverse ethnic background and high socioeconimic status. Parents gave informed consent and provided demographic information. All experiments reported in this paper were approved by the Stanford Institutional Review Board (protocol no. 357 19960).

```{r fig1, include = T, fig.align = "center", fig.cap = "Left: Screenshot from the experimental setup. Right: Stimuli pictures for the four categories: fruits, vehicles, clothes and mammals.", out.width="450px"}
knitr::include_graphics("../figures/setup.png")
```

## Method

Study materials were presented as a picture book on a tablet computer [@frank2016using]. Children reponded by touching objects on the screen. Responses were automatically saved. The experimenter guided children through the procedure and read out general instructions. The study was framed as visit to the house of the little animals which would show the child the things they have at home. Utterances made by the different animals were pre-recorded from native English speakers, with one speaker per animal. On each trial, children saw one animal in the middle of the screen with three objects above them (Figure \ref{fig:fig1}, left). Each objects was from different category (mammals, vehicles, clothes and fruits). For each category, we had pictures of seven different category memebers (e.g. for vehicles: car, truck, train, bus, airplane, boat and motorbike, see Figure \ref{fig:fig1}, right). The trial started with six training rounds, in which the animal named one of the objects above them, asking the child to touch it (e.g. "Look at that, can you touch the horse"). From one round to the next, the pictures changed but the categories remained the same. For example, children saw a skirt, a horse and a motorcylce on the first training round and a jacket, a dog and a bus on the second. During training, the speaker consitently named objects from the same target category. After six training rounds, children received a test round in which the speaker used a pronoun to refer to one of the objects ("Look at that, can you touch *it*"). Categories were ranomdly selected at the beginning of each trial and so was the order of pictures within each category. The position of each picture (left, right mddle) was also randomly determined on each round. Children received four trials, one with each category as the target.

## Results 
```{r experiment1, cache = T, include = F}

bf_t_overall <- ex1_data %>%
  group_by(id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  mutate(mean= mean(unlist(correct)),
         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf)

bf_t_age <- ex1_data %>%
  group_by(age_group, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(age_group)%>%
  mutate(mean= mean(unlist(correct)),
         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf)

ex1_model_data <- ex1_data%>%
  mutate(age_num = age_num - mean(age_num))

prior_ex1_m1 <- c(set_prior("normal(0,10)", class = "b", coef = "age_num"))

ex1_m1 <- brm(correct ~ age_num + (1|id) + (1|speaker),
                    data = ex1_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          prior = prior_ex1_m1, 
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 50000)%>%
  saveRDS(., "../saves/ex1_model1.rds")

ex1_m1 <-readRDS("../saves/ex1_model1.rds")

ex1_m2 <- brm(correct ~ 1 + (1|id) + (1|speaker),
                    data = ex1_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 50000)%>%
  saveRDS(., "../saves/ex1_model2.rds")

ex1_m2 <-readRDS("../saves/ex1_model2.rds")

ex1_waic <- brms::waic(ex1_m1, ex1_m2, compare = F)

ex1_weights <- model_weights(ex1_m1, ex1_m2, weights = "waic")

bf_ex1 <- bayes_factor(ex1_m1, ex1_m2, log = FALSE, maxiter = 5000)

t1 <- tibble(
  Model = c("correct ~ age + RE","correct ~ 1 + RE"),
  WAIC = c(ex1_waic$loo$ex1_m1$estimates[3,1],ex1_waic$loo$ex1_m2$estimates[3,1]),
  SE = c(ex1_waic$loo$ex1_m1$estimates[3,2],ex1_waic$loo$ex1_m2$estimates[3,2]),
  weight = c(ex1_weights["ex1_m1"],ex1_weights["ex1_m2"]),
  BF = c("-",round(bf_ex1$bf,2)))
```

```{r plots1, include = F}
pex1_1 <- ex1_data %>%
  group_by(experiment,age_group,age_num, id) %>%
  summarise(correct = mean(correct))

pex1_2 <- pex1_1 %>%
  group_by(experiment,age_group) %>%
  multi_boot_standard(col = "correct")

samples1 <- posterior_samples(ex1_m1, "^b")%>%
  mutate(sample = 1:length(b_age_num))

samples <- expand_grid(samples1,ex1_model_data$age_num)%>%
  mutate(y = plogis(b_Intercept + b_age_num * `ex1_model_data$age_num`),
         age = `ex1_model_data$age_num` + mean(ex1_data$age_num),
         experiment = "simple_inference")%>%
  filter(sample < 1000)

map_model <- tibble(
  age = ex1_model_data$age_num,
  int = fixef(ex1_m1)[1,1],
  slope = fixef(ex1_m1)[2,1]
)%>%
  mutate(y = plogis(int + slope * age),
         age = age + mean(ex1_data$age_num))

p1 <- ggplot() +
  geom_hline(yintercept = 1/3, lty=2, size = 1)+
  geom_jitter(data = pex1_1,aes(x = age_num, y= correct, col = experiment), width = .00, height = .01, alpha = .5)+
  geom_line(data = samples, aes(x = age, y = y, group = sample), col = "#CC6677", size = .025)+
  geom_line(data = map_model, aes(x = age, y = y), col = "#CC6677", size = 1)+
  #geom_smooth(data = ex1_data,aes(x = age_num, y= correct, col = experiment), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, col = F)+
  scale_color_manual(values = "#CC6677")

# density plot

plot_post <- ex1_data %>%
  group_by(age_group,id) %>%
  summarise(correct = mean(correct))%>%
  summarise(correct = list(correct)) %>%
  group_by(age_group) %>%
  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 1000)[,"mu"])))%>%
  select(-correct)

plot_dens_ci <- plot_post %>%
  summarise(mode = estimate_mode(unlist(posterior)),
            lci = hdi_lower(unlist(posterior)),
            uci = hdi_upper(unlist(posterior)))

plot_dens <- tibble(
  age = rep(c(2,3,4), each = 1000),
  posterior = c(unlist(plot_post%>%filter(age_group == "2") %>% pull(posterior)),unlist(plot_post%>%filter(age_group == "3") %>% pull(posterior)),unlist(plot_post%>%filter(age_group == "4") %>% pull(posterior)))
)

densities <- plot_dens %>%
  group_by(age) %>%
  do(., dens = density(.$posterior))

densities_df <-
  tibble(
    age = c(rep('2', 512),
            rep('3', 512),
              rep('4', 512)),
    x = c(densities$dens[[1]]$x, 
          densities$dens[[2]]$x,
          densities$dens[[3]]$x),
    y = c(densities$dens[[1]]$y,
          densities$dens[[2]]$y,
          densities$dens[[3]]$y)
  ) %>%
  group_by(age)%>%
  mutate (
    ci_shade = ifelse( age == "3",
                       ifelse( x <= plot_dens_ci%>%filter(age_group == "3")%>%pull(lci) | x >= plot_dens_ci%>%filter(age_group == "3")%>%pull(uci), "OFF", "ON"),
                       ifelse(age == "2", ifelse( x <= plot_dens_ci%>%filter(age_group == "2")%>%pull(lci) | x >= plot_dens_ci%>%filter(age_group == "2")%>%pull(uci), "OFF", "ON"),
      ifelse( x <= plot_dens_ci%>%filter(age_group == "4")%>%pull(lci) | x >= plot_dens_ci%>%filter(age_group == "4")%>%pull(uci), "OFF", "ON"))))

post_plot <- ggplot(plot_dens, aes(posterior, group = age)) +
  geom_vline(xintercept = 1/3, lty=2, size = 1)+
  geom_area(data = densities_df %>% filter(ci_shade == "ON"), aes(x = x, y = y, fill = age), alpha = .5) + 
  geom_density(alpha = .5, size = 1)+
  labs(y="Probability density", x="Proportion correct")+
  theme_few() +
  xlim(-0.05,1.05)+
  guides(alpha = F)+
  scale_fill_ordinal(name = "Age")
```

```{r fig2, include = T, fig.align = "center", fig.cap = "A: Posterior probability distribution for the mean for each age bin. Shaded regions indicate 95\\% CIs. B: Correct  responses for age continously. Transparent dots show aggregated data from individual participants. Red line with grey shows the smoothed conditional mean of the data in each condition..", fig.width=10, fig.height=4}

ggarrange(post_plot,p1, nrow = 1, labels = c("A","B"))
```

The dependent variable in all analysis was whether the touched object at test was from the same category as the objects named throughout the training rounds. All following analysis were computed in R [@R-base]. As a first step, we aggregated respones across trials for each child and compared the proportion of correct responses to a level expected by chance (33% correct) within each age bin. We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes factor (BF) in favor of the hypothesis that performance is above chance (see Figure \ref{fig:fig2}A). We found little evidence that 2-year olds performed above chance (mean proportion correct = `r bf_t_age%>%filter(age_group == "2")%>%pull(mean)`, BF = `r bf_t_age%>%filter(age_group == "2")%>%pull(bf)`) but found subtantial evidence for 3-year-olds (mean proportion correct = `r bf_t_age%>%filter(age_group == "3")%>%pull(mean)`, BF = `r bf_t_age%>%filter(age_group == "3")%>%pull(bf)`) and 4-year-olds (mean proportion correct = `r bf_t_age%>%filter(age_group == "4")%>%pull(mean)`, BF = `r bf_t_age%>%filter(age_group == "4")%>%pull(bf)`).

To analyse responses continously across age we used generalized linear mixed models (GLMM) fit via the function `brm` from the R-package `brms` [@R-brms_a]. All models had default priors and included random effects for participant id and speaker. Inference was based on comparing models that differed in whether they included the key predictor of interest, in this case age. Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights. WAIC is an indicator of the model's predictive accuracy for out of sample data and model's with lower scores are preferred. WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data. We quantified the evidence in favor of the model with the lowest WAIC score (highest WAIC weight) compared to alternative models by computing Bayes factors via the funtion `bayes_factor` from the R-package `brms` [@R-brms_a].

The model comparison favored the model including age as a predictor (Table \ref{tab:table1}). The model estiamte for age was positive ($\beta$ = `r fixef(ex1_m1)[2,1]`, 95% confidence interval (CI) = `r fixef(ex1_m1)[2,3]` - `r fixef(ex1_m1)[2,4]`), suggesting an increase in performance with age (see also Figure \ref{fig:fig2}B). However, the evidence in support of this model was modest, speaking against subtantial developmental gains across the age range considered.

## Discussion

```{r table1,results = "asis"}
apa_table(
  t1
  , caption = "Model comparison for Experiment 1"
  , note = "All models had the same random effects (RE) structure. BF denotes the Bayes Factor in favor to the model with the highest WAIC weight."
  , escape = T
)
```

# Experiment 2

Registration: https://osf.io/x2k4p

## Participants

## Material and Procedure

## Results and Discussion

```{r experiment2, cache = T, include = F}

ex2_model_data <- ex2_data%>%
  mutate(age_num = age_num - mean(age_num))

prior_ex2_m1 <- c(set_prior("normal(0,10)", class = "b", coef = "age_num"),
                  set_prior("normal(0,10)", class = "b", coef = "conditionlow_input"),
                  set_prior("normal(0,10)", class = "b", coef = "age_num:conditionlow_input"))

ex2_m1 <- brm(correct ~ age_num * condition + (condition|id) + (condition|speaker),
                    data = ex2_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          prior = prior_ex2_m1,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 50000)%>%
  saveRDS(., "../saves/ex2_model1.rds")

ex2_m1 <-readRDS("../saves/ex2_model1.rds")

prior_ex2_m2 <- c(set_prior("normal(0,10)", class = "b", coef = "age_num"),
                  set_prior("normal(0,10)", class = "b", coef = "conditionlow_input"))

ex2_m2 <- brm(correct ~ age_num + condition + (condition|id) + (condition|speaker),
                    data = ex2_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          prior = prior_ex2_m2,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 50000)%>%
  saveRDS(., "../saves/ex2_model2.rds")

ex2_m2 <-readRDS("../saves/ex2_model2.rds")

prior_ex2_m3 <- c(set_prior("normal(0,10)", class = "b", coef = "age_num"))

ex2_m3 <- brm(correct ~ age_num + (condition|id) + (condition|speaker),
                    data = ex2_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          prior = prior_ex2_m3,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 50000)%>%
  saveRDS(., "../saves/ex2_model3.rds")

ex2_m3 <-readRDS("../saves/ex2_model3.rds")

ex2_waic <- brms::waic(ex2_m1, ex2_m2,ex2_m3, compare = F)

ex2_weights <- model_weights(ex2_m1, ex2_m2,ex2_m3, weights = "waic")

bf_ex2_1 <- bayes_factor(ex2_m3, ex2_m1, log = FALSE)

bf_ex2_2 <- bayes_factor(ex2_m3, ex2_m2, log = FALSE)

t2 <- tibble(
  Model = c("correct ~ age + RE","correct ~ age * condition + RE","correct ~ age + condition + RE"),
  WAIC = c(ex2_waic$loo$ex2_m3$estimates[3,1],ex2_waic$loo$ex2_m1$estimates[3,1],ex2_waic$loo$ex2_m2$estimates[3,1]),
  SE = c(ex2_waic$loo$ex2_m3$estimates[3,2],ex2_waic$loo$ex2_m1$estimates[3,2],ex2_waic$loo$ex2_m2$estimates[3,2]),
  weight = c(ex2_weights[3],ex2_weights[1],ex2_weights[2]),
  BF = c("-",round(bf_ex2_1$bf,2),round(bf_ex2_2$bf,2)))
```

```{r table2,results = "asis"}
apa_table(
  t2
  , caption = "Model comparison for Experiment 2"
  , note = "All models had the same random effects (RE) structure. BF denotes the Bayes Factor in favor to the model with the highest WAIC weight."
  , escape = T
)
```

# Experiment 3

Registration: https://osf.io/5e9pk

## Participants

## Material and Procedure

## Results and Discussion

```{r experiment3, cache = T, include = F}

ex3_model_data <- ex3_data%>%
  mutate(age_num = age_num - mean(age_num))

prior_ex3_m1 <- c(set_prior("normal(0,5)", class = "b", coef = "intercept"),
                  set_prior("normal(0,5)", class = "b", coef = "age_num"),
                  set_prior("normal(0,5)", class = "b", coef = "conditionsame_speaker"),
                  set_prior("normal(0,5)", class = "b", coef = "age_num:conditionsame_speaker"))

ex3_m1 <- brm(correct ~ age_num * condition + (condition|id) + (condition|speaker),
                    data = ex3_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
   add_criterion("waic")%>%
  saveRDS(., "../saves/ex3_model1.rds")

hypothesis(ex3_m1, hypothesis = 'age_num:conditionsame_speaker = 0')

ex3_m1 <-readRDS("../saves/ex3_model1.rds")

ex3_m2 <- update(ex3_m1, 
                 formula = ~ . -age_num:conditionsame_speaker, 
                 newdata = ex3_model_data,
                 chains = 4,
                 cores = 4,
                 save_all_pars = TRUE)%>%
   add_criterion("waic")%>%
  saveRDS(., "../saves/ex3_model2.rds")

ex3_m2 <-readRDS("../saves/ex3_model2.rds")

ex3_m3 <- update(ex3_m1, 
                 formula = ~ . - age_num:conditionsame_speaker - conditionsame_speaker, 
                 newdata = ex3_model_data,
                 chains = 4,
                 cores = 4,
                 save_all_pars = TRUE)%>%
   add_criterion("waic")%>%
  saveRDS(., "../saves/ex3_model3.rds")

ex3_m3 <-readRDS("../saves/ex3_model3.rds")

bf_ex3_1 <- bayes_factor(ex3_m1, ex3_m2, log = FALSE)

bf_ex3_2 <- bayes_factor(ex3_m1, ex3_m2, log = FALSE)

t3 <- loo_compare(ex3_m1, ex3_m2, ex3_m3, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Model")%>%
  mutate(
    Model = recode(Model, ex3_m1 = "correct ~ age * condition + RE", 
                   ex3_m2 = "correct ~ age + condition + RE",
                   ex3_m3 = "correct ~ age + RE"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 3),
    WAIC = round(waic, 2),
    SE = round(se_waic,2),
    BF = c("-",round(bf_ex3_1$bf,2),round(bf_ex3_2$bf,2)))%>%
  select(Model, WAIC, SE, BF)

```

```{r table3,results = "asis"}
apa_table(
  t3
  , caption = "Model comparison for Experiment 3"
  , note = "All models had the same random effects (RE) structure. BF denotes the Bayes Factor in favor to the model with the highest WAIC weight."
  , escape = T
)
```

# General Discussion

```{r plots2}
pex2_1 <- ex2_data %>%
  group_by(condition,age_group,age_num, id) %>%
  summarise(correct = mean(correct))

pex2_2 <- pex2_1 %>%
  group_by(condition,age_group) %>%
  multi_boot_standard(col = "correct")

samples2 <- posterior_samples(ex2_m1, "^b")%>%
  mutate(sample = 1:length(b_age_num))

sample2 <- expand_grid(samples2,ex2_model_data$age_num)%>%
  filter(sample < 2000)%>%
  mutate(condition = ifelse(sample <1000, "high_input", "low_input"),
         y = ifelse(condition == "high_input", plogis(b_Intercept + b_age_num * `ex2_model_data$age_num`), plogis(b_Intercept + b_conditionlow_input + b_age_num * `ex2_model_data$age_num` + `b_age_num:conditionlow_input` * `ex2_model_data$age_num`)),
         age = `ex2_model_data$age_num` + mean(ex2_data$age_num))

map_model_2 <- tibble(
  age = rep(ex2_model_data$age_num, 2),
  condition = c(rep("high_input", length(ex2_model_data$age_num)),rep("low_input", length(ex2_model_data$age_num))),
  int = fixef(ex2_m1)[1,1],
  slope = fixef(ex2_m1)[2,1],
  speak = fixef(ex2_m1)[3,1],
  int_act = fixef(ex2_m1)[4,1]
)%>%
  mutate(y = ifelse(condition == "high_input", plogis(int + slope * age), plogis(int + speak + slope * age + int_act * age)),
         age = age + mean(ex2_data$age_num))

p2 <- ggplot() +
  geom_hline(yintercept = 1/3, lty=2, size = 1)+
  geom_jitter(data = pex2_1,aes(x = age_num, y= correct, col = condition), width = .00, height = .01, alpha = .5)+
  geom_line(data = sample2, aes(x = age, y = y, col = condition, group = sample), size = .025)+
  geom_line(data = map_model_2, aes(x = age, y = y, col = condition), size = 1)+
  #geom_smooth(data = ex2_data,aes(x = age_num, y= correct, col = condition), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5 )+
  #geom_pointrange(data = pex2_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)+
  scale_color_manual(name = "Input",
                   breaks = c("low_input", "high_input"),
                   labels = c("Low", "High"),
                   values = c("#CC6677", "#DDCC77"))+
  theme(legend.position = "bottom")

pex3_1 <- ex3_data %>%
  group_by(condition,age_group,age_num, id) %>%
  summarise(correct = mean(correct))

pex3_2 <- pex3_1 %>%
  group_by(condition,age_group) %>%
  multi_boot_standard(col = "correct")

samples3 <- posterior_samples(ex3_m1, "^b")%>%
  mutate(sample = 1:length(b_age_num))

sample3 <- expand_grid(samples3,ex3_model_data$age_num)%>%
  filter(sample < 2000)%>%
  mutate(condition = ifelse(sample <1000, "same_speaker", "different_speaker"),
         y = ifelse(condition == "different_speaker", plogis(b_Intercept + b_age_num * `ex3_model_data$age_num`), plogis(b_Intercept + b_conditionsame_speaker + b_age_num * `ex3_model_data$age_num` + `b_age_num:conditionsame_speaker` * `ex3_model_data$age_num`)),
         age = `ex3_model_data$age_num` + mean(ex3_data$age_num))

map_model_3 <- tibble(
  age = rep(ex3_model_data$age_num, 2),
  condition = c(rep("same_speaker", length(ex3_model_data$age_num)),rep("different_speaker", length(ex3_model_data$age_num))),
  int = fixef(ex3_m1)[1,1],
  slope = fixef(ex3_m1)[2,1],
  speak = fixef(ex3_m1)[3,1],
  int_act = fixef(ex3_m1)[4,1]
)%>%
  mutate(y = ifelse(condition == "different_speaker", plogis(int + slope * age), plogis(int + speak + slope * age + int_act * age)),
         age = age + mean(ex3_data$age_num))

p3 <- ggplot() +
  geom_hline(yintercept = 1/3, lty=2, size = 1)+
  geom_jitter(data = pex3_1,aes(x = age_num, y= correct, col = condition), width = .00, height = .01, alpha = .5)+
  geom_line(data = sample3, aes(x = age, y = y, col = condition, group = sample), size = .025)+
  geom_line(data = map_model_3, aes(x = age, y = y, col = condition), size = 1)+
  #geom_smooth(data = ex3_data,aes(x = age_num, y= correct, col = condition), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5)+
  #geom_pointrange(data = pex3_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)+
  scale_color_ptol(name = "Speaker",
                   breaks = c("different_speaker", "same_speaker"),
                   labels = c("Different", "Same"))+
  theme(legend.position = "bottom")

```

```{r plot2, fig.width=8, fig.height=4}
ggarrange(p2, p3, nrow = 1, labels = c("A","B"))
```

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2019-11-25 paper/manuscript.tex
update repo to check analysis

\documentclass[man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={What's she talking about? Category based discourse inferences in early childhood},
            pdfauthor={Manuel Bohn, Khuyen Nha Le, Benjamin Peloquin, Bahar Köymen, \& Michael C. Frank},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{What's she talking about? Category based discourse inferences in early
childhood}
    \author{Manuel Bohn\textsuperscript{1,2}, Khuyen Nha Le\textsuperscript{1},
Benjamin Peloquin\textsuperscript{1}, Bahar Köymen\textsuperscript{3},
\& Michael C. Frank\textsuperscript{1}}
    \date{}

\shorttitle{Discourse inferences in early childhood}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Stanford University\\\textsuperscript{2} Leipzig University\\\textsuperscript{3} University of Manchester}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\usepackage{lineno}

\linenumbers

\authornote{We thank Megan Merrick and Sabina Zacco for their
help with the data collection. MB received funding from the European
Union's Horizon 2020 research and innovation programme under the Marie
Sklodowska-Curie grant agreement no. 749229.

Correspondence concerning this article should be addressed to Manuel
Bohn, Jahnallee 59, 04109 Leipzig, Germany. E-mail:
\href{mailto:manuel.bohn@uni-leipzig.de}{\nolinkurl{manuel.bohn@uni-leipzig.de}}}

\abstract{
tbd\ldots{}

}

\begin{document}
\maketitle

\section{Experiment 1}\label{experiment-1}

All experimental procedures, sample sizes and statistical analysis were
pre-registered (see \url{https://osf.io/9ypxn} and
\url{https://osf.io/fyaxq}). The experimental procedure can be found in
the assoicated online repository at
\url{https://github.com/manuelbohn/disCon}.

\subsection{Participants}\label{participants}

We obtained valid data from 71 children, including 30 2-year-olds (mean
= 2.63, range = 2.00 - 2.98), 21 3-year-olds (mean = 3.56, range = 3.13
- 3.97) and 20 4-year-olds (mean = 4.50, range = 4.00 - 4.97). We tested
a larger sample of 2-year-olds because we expected a weaker effect in
this age group. In addition, 12 children were recruited but not tested
becasue their parents reported less than 75\% of English exposure at
home. Ten children started the experiment but did not finish it because
they became impatient (7) or the equipment broke (3). Three children
were tested but excluded becasue they were correct in less than 5/6
training trials (see below). All children were recruited from the floor
of a Children's museum in San José, California, USA. The population from
which this sample is drawn is characterised by diverse ethnic background
and high socioeconimic status. Parents gave informed consent and
provided demographic information. All experiments reported in this paper
were approved by the Stanford Institutional Review Board (protocol no.
357 19960).

\begin{figure}

{\centering \includegraphics[width=450px]{../figures/setup}

}

\caption{Left: Screenshot from the experimental setup. Right: Stimuli pictures for the four categories: fruits, vehicles, clothes and mammals.}\label{fig:fig1}
\end{figure}

\subsection{Method}\label{method}

Study materials were presented as a picture book on a tablet computer
(Frank, Sugarman, Horowitz, Lewis, \& Yurovsky, 2016). Children reponded
by touching objects on the screen. Responses were automatically saved.
The experimenter guided children through the procedure and read out
general instructions. The study was framed as visit to the house of the
little animals which would show the child the things they have at home.
Utterances made by the different animals were pre-recorded from native
English speakers, with one speaker per animal. On each trial, children
saw one animal in the middle of the screen with three objects above them
(Figure \ref{fig:fig1}, left). Each objects was from different category
(mammals, vehicles, clothes and fruits). For each category, we had
pictures of seven different category memebers (e.g.~for vehicles: car,
truck, train, bus, airplane, boat and motorbike, see Figure
\ref{fig:fig1}, right). The trial started with six training rounds, in
which the animal named one of the objects above them, asking the child
to touch it (e.g. \enquote{Look at that, can you touch the horse}). From
one round to the next, the pictures changed but the categories remained
the same. For example, children saw a skirt, a horse and a motorcylce on
the first training round and a jacket, a dog and a bus on the second.
During training, the speaker consitently named objects from the same
target category. After six training rounds, children received a test
round in which the speaker used a pronoun to refer to one of the objects
(\enquote{Look at that, can you touch \emph{it}}). Categories were
ranomdly selected at the beginning of each trial and so was the order of
pictures within each category. The position of each picture (left, right
mddle) was also randomly determined on each round. Children received
four trials, one with each category as the target.

\subsection{Results}\label{results}

\begin{figure}

{\centering \includegraphics{manuscript_files/figure-latex/fig2-1}

}

\caption{A: Posterior probability distribution for the mean for each age bin. Shaded regions indicate 95\% CIs. B: Correct  responses for age continously. Transparent dots show aggregated data from individual participants. Red line with grey shows the smoothed conditional mean of the data in each condition..}\label{fig:fig2}
\end{figure}

The dependent variable in all analysis was whether the touched object at
test was from the same category as the objects named throughout the
training rounds. All following analysis were computed in R (R Core Team,
2018). As a first step, we aggregated respones across trials for each
child and compared the proportion of correct responses to a level
expected by chance (33\% correct) within each age bin. We used the
function \texttt{ttestBF} from the R-package \texttt{BayesFactor} (Morey
\& Rouder, 2018) to compute a Bayes factor (BF) in favor of the
hypothesis that performance is above chance (see Figure
\ref{fig:fig2}A). We found little evidence that 2-year olds performed
above chance (mean proportion correct = 0.42, BF = 0.59) but found
subtantial evidence for 3-year-olds (mean proportion correct = 0.60, BF
= 90.77) and 4-year-olds (mean proportion correct = 0.55, BF = 10.39).

To analyse responses continously across age we used generalized linear
mixed models (GLMM) fit via the function \texttt{brm} from the R-package
\texttt{brms} (Bürkner, 2017). All models had default priors and
included random effects for participant id and speaker. Inference was
based on comparing models that differed in whether they included the key
predictor of interest, in this case age. Following McElreath (2016), we
compared models using WAIC (widely applicable information criterion)
scores and weights. WAIC is an indicator of the model's predictive
accuracy for out of sample data and model's with lower scores are
preferred. WAIC weights are an estimate of the probability that this
model (compared to all other models considered) will make the best
predictions on new data. We quantified the evidence in favor of the
model with the lowest WAIC score (highest WAIC weight) compared to
alternative models by computing Bayes factors via the funtion
\texttt{bayes\_factor} from the R-package \texttt{brms} (Bürkner, 2017).

The model comparison favored the model including age as a predictor
(Table \ref{tab:table1}). The model estiamte for age was positive
(\(\beta\) = 0.32, 95\% confidence interval (CI) = -0.08 - 0.75),
suggesting an increase in performance with age (see also Figure
\ref{fig:fig2}B). However, the evidence in support of this model was
modest, speaking against subtantial developmental gains across the age
range considered.

\subsection{Discussion}\label{discussion}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:table1}Model comparison for Experiment 1}
\begin{tabular}{lllll}
\toprule
Model & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{weight} & \multicolumn{1}{c}{BF}\\
\midrule
correct \textasciitilde{} age + RE & 387.20 & 7.67 & 0.56 & -\\
correct \textasciitilde{} 1 + RE & 387.69 & 7.11 & 0.44 & 1.77\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} All models had the same random effects (RE) structure. BF denotes the Bayes Factor in favor to the model with the highest WAIC weight.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\section{Experiment 2}\label{experiment-2}

Registration: \url{https://osf.io/x2k4p}

\subsection{Participants}\label{participants-1}

\subsection{Material and Procedure}\label{material-and-procedure}

\subsection{Results and Discussion}\label{results-and-discussion}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:table2}Model comparison for Experiment 2}
\begin{tabular}{lllll}
\toprule
Model & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{weight} & \multicolumn{1}{c}{BF}\\
\midrule
correct \textasciitilde{} age + RE & 176.48 & 9.28 & 0.43 & -\\
correct \textasciitilde{} age * condition + RE & 177.29 & 11.00 & 0.29 & 0.09\\
correct \textasciitilde{} age + condition + RE & 177.36 & 9.93 & 0.28 & 0.45\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} All models had the same random effects (RE) structure. BF denotes the Bayes Factor in favor to the model with the highest WAIC weight.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\section{Experiment 3}\label{experiment-3}

Registration: \url{https://osf.io/5e9pk}

\subsection{Participants}\label{participants-2}

\subsection{Material and Procedure}\label{material-and-procedure-1}

\subsection{Results and Discussion}\label{results-and-discussion-1}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:table3}Model comparison for Experiment 3}
\begin{tabular}{lllll}
\toprule
Model & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{weight} & \multicolumn{1}{c}{BF}\\
\midrule
correct \textasciitilde{} age * condition + RE & 325.21 & 10.50 & 0.58 & -\\
correct \textasciitilde{} age + condition + RE & 327.25 & 9.52 & 0.21 & 23.91\\
correct \textasciitilde{} age + RE & 327.30 & 8.96 & 0.21 & 23.88\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} All models had the same random effects (RE) structure. BF denotes the Bayes Factor in favor to the model with the highest WAIC weight.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\section{General Discussion}\label{general-discussion}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plot2-1.pdf}
\caption{}
\end{figure}

\newpage

\section{References}\label{references}

\begingroup
\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-R-brms_a}{}
Bürkner, P.-C. (2017). brms: An R package for Bayesian multilevel models
using Stan. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28.
doi:\href{https://doi.org/10.18637/jss.v080.i01}{10.18637/jss.v080.i01}

\hypertarget{ref-frank2016using}{}
Frank, M. C., Sugarman, E., Horowitz, A. C., Lewis, M. L., \& Yurovsky,
D. (2016). Using tablets to collect data from young children.
\emph{Journal of Cognition and Development}, \emph{17}(1), 1--17.

\hypertarget{ref-rethinking}{}
McElreath, R. (2016). \emph{Statistical rethinking: A bayesian course
with examples in R and Stan} (pp. xvii, 469). Boca Raton: CRC Press.

\hypertarget{ref-R-BayesFactor}{}
Morey, R. D., \& Rouder, J. N. (2018). \emph{BayesFactor: Computation of
bayes factors for common designs}. Retrieved from
\url{https://CRAN.R-project.org/package=BayesFactor}

\hypertarget{ref-R-base}{}
R Core Team. (2018). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.

\endgroup

\end{document}

### 2019-12-16 experiments/discon_look.js
clean repo

@@ -1,664 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
-}
-
[…]

### 2019-12-16 experiments/discon_look_600.js

@@ -1,664 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
-}
-
[…]

### 2019-12-16 experiments/discon_look_600_cat_name.js

@@ -1,695 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
-}
-
[…]

### 2019-12-16 experiments/discon_look_600_cat_vis.js

@@ -1,689 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
-}
-
[…]

### 2019-12-16 experiments/discon_look_600_mumble.js

@@ -1,693 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
-}
-
[…]

### 2019-12-16 experiments/discon_look_600_speakerchange.js

@@ -1,748 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
[…]

### 2019-12-16 experiments/discon_look_600_speakerchange_oppositeside.js

@@ -1,757 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
[…]

### 2019-12-16 experiments/discon_look_600_speakerchange_oppositeside_preference.js

@@ -1,749 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
[…]

### 2019-12-16 experiments/discon_look_kid_simple_4cat.js

@@ -1,772 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-//only preload relevant audios (no speaker change)
-var preloadAudios = ["hi", "lets", "intro", "thank", "it"];
-
-var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger", "Pig"])
-
-//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
-
-var audios = new Array();
-for (i = 0; i < posAgents.length; i++) {
-    for (j = 0; j < preloadAudios.length; j++) {
-        var audio = new Audio();
-        audio.src = "sounds/" + preloadAudios[j] + "_" + posAgents[i] + ".mp3"
-        audios.push(audio);
-    }
-    for (k = 0; k < preloadItems.length - 3; k++) {
-        var audio = new Audio();
-        audio.src = "sounds/" + preloadItems[k] + "_" + posAgents[i] + ".mp3"
-        audios.push(audio);
-    }
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
[…]

### 2019-12-16 experiments/discon_look_kid_simple_4cat_speakerchange.js

@@ -1,864 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-//only preload relevant audios (no speaker change)
-var preloadAudios = ["hi", "lets", "intro", "thank", "it", "needtogo", "imback"];
-
-var posAgents = shuffle(["Bear", "Cat", "Elephant", "Frog", "Sheep", "Tiger", "Mouse"])
-
-//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
-
-var audios = new Array();
-for (i = 0; i < posAgents.length; i++) {
-    for (j = 0; j < preloadAudios.length; j++) {
-        var audio = new Audio();
-        audio.src = "sounds/speakerchange/" + preloadAudios[j] + "_" + posAgents[i] + ".mp3"
-        audios.push(audio);
-    }
-    for (k = 0; k < preloadItems.length - 3; k++) {
-        var audio = new Audio();
-        audio.src = "sounds/speakerchange/" + preloadItems[k] + "_" + posAgents[i] + ".mp3"
-        audios.push(audio);
-    }
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
[…]

### 2019-12-16 experiments/discon_look_kid_simple_4cat_within.js

@@ -1,789 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-//only preload relevant audios (no speaker change)
-var preloadAudios = ["hi", "lets", "intro", "thank", "it"];
-
-var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger", "Pig"])
-
-//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
-
-var audios = new Array();
-for (i = 0; i < posAgents.length; i++) {
-    for (j = 0; j < preloadAudios.length; j++) {
-        var audio = new Audio();
-        audio.src = "sounds/" + preloadAudios[j] + "_" + posAgents[i] + ".mp3"
-        audios.push(audio);
-    }
-    for (k = 0; k < preloadItems.length - 3; k++) {
-        var audio = new Audio();
-        audio.src = "sounds/" + preloadItems[k] + "_" + posAgents[i] + ".mp3"
-        audios.push(audio);
-    }
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
[…]

### 2019-12-16 experiments/discon_look_relative.js

@@ -1,664 +1,0 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "bed", "chair", "table", "closet", "drawer", "sofa", "lamp", "stool", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "drum", "flute", "guitar", "piano", "trumpet", "violin", "xylophone", "bread", "tv", "pencil"];
-
-var images = new Array();
-for (i = 0; i < preloadItems.length; i++) {
-    images[i] = new Image();
-    images[i].src = "images/" + preloadItems[i] + ".png";
-}
-
-var backgroundImages = new Array();
-for (i = 1; i <= 12; i++) {
-    backgroundImages[i] = new Image();
-    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
-}
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-        showSlide("instructions");
-        alert("Please accept HIT to view");
-    } else {
-        showSlide('introAll')
-    }
-});
-
-function showSlide(id) {
-    // Hide all slides
-    $(".slide").hide();
-    // Show just the slide we want to show
-    $("#"+id).show();
-}
-
-function shuffle(array) {
-    for (var i = array.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = array[i];
-        array[i] = array[j];
-        array[j] = temp;
-    }
-    return array;
-}
-
-function showAgent(id, orient) {
-    $(".agent").hide();
-    $(".agent_transition").hide();
-    $("#"+id+"_"+orient).show();
-}
-
-function sourceRightItem(a) {
-    document.getElementById("item_r").src=a;
-}
-
-function showRightItem() {
-    document.getElementById('item_r').style.visibility='visible';
-}
-
-function hideRightItem() {
-    document.getElementById('item_r').style.visibility='hidden';
-}
-
-function sourceMiddleItem(a) {
-    document.getElementById("item_m").src=a;
-}
-
-function showMiddleItem() {
-    document.getElementById('item_m').style.visibility='visible';
-}
-
[…]

### 2019-12-16 experiments/mmturkey.js

@@ -1,263 +1,0 @@
-// Bundle in Crockford's JSON2.js
-var JSON;JSON||(JSON={});
-(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
-e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
-"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2019-12-16 experiments/mmturkey_kids_speaker_change.js

@@ -1,263 +1,0 @@
-// Bundle in Crockford's JSON2.js
-var JSON;JSON||(JSON={});
-(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
-e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
-"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2019-12-16 scripts/isignrank.test.R

@@ -1,420 +1,0 @@
-#isignrank.test Bayesian Wilcoxon signed rank test based on the Imprecise Dirichlet Process.
-#      This is the Bayesian improved version of iwilcox.test
-#
-#
-#   isignrank.test(x,y,"greater") performs a hypothesis test for P(Z>=-Z)>1/2 
-#   with Z=Y-X and posterior probability 0.95. It returns the result of the deicison.
-#   H=1 indicates that the hypothesis P(Z>=-Z)>1/2 is true with posterior
-#   probability greater than 0.95, i.e., Lower_Prob>0.95. H=0 indicates
-#   P(Z>=-Z)>1/2 is not true with posterior greater than 0.95, i.e.,
-#   Upper_Prob<0.95. Finally, H=2 indicates an indeterminate instance, i.e.,
-#   we cannot decide if  P(Z>=-Z)>1/2 is true with posterior probability
-#   greater than 0.95. This means that the posterior inferences are prior
-#   dependent, i.e., Lower_Prob<0.95 and  Upper_Prob>0.95.
-#
-#   isignrank.test(x,y,"greater") -- evaluates the hypothesis  P(Z>=-Z)>1/2. This is the
-#                Bayesian improved version of wilcox.test(x,y,"greater", paired=TRUE)  (default value).
-#   isignrank.test(x,y,"less") -- evaluates the hypothesis  P(Z <= -Z)>1/2. This is the
-#                Bayesian improved version of wilcox.test(x,y,"less", paired=TRUE) .
-#   isignrank.test(x,y,"two.sided") -- performs a two-sided Bayesian test, i.e., H=1 if 1/2 is
-#                not included in the 1-ALPHA lower and upper HPD credible
-#                intervals. H=0 if 1/2 is included in the 1-ALPHA lower and
-#                upper HPD credible. H=2 otherwise, indeterminate case.
-#                This is the Bayesian improved version of wilcox.test(x,y,'two.sided', paired=TRUE).
-#
-#   isignrank.test(...,alpha=value) returns the result of the hypothesis
-#   test with posterior probability gretaer than 1-value.
-#
-#   isignrank.test(...,s=value) sets the value of the prior strength of 
[…]

### 2019-12-16 scripts/signRankSampler.R

@@ -1,117 +1,0 @@
-
-signRankGibbsSampler <- function(xVals, yVals = NULL, testValue = 0, nSamples = 10000, progBar = FALSE, cauchyPriorParameter = 1/sqrt(2),
-                            nGibbsIterations = 5, varyTies = TRUE) {
-  
-  if (progBar) {
-    myBar <- txtProgressBar(min = 1, max = nSamples, initial = 1, char = "*",style=3,width=50)
-  }
-  
-  n <- length(xVals)
-  nDF <- n-1
-
-  if (!is.null(yVals)) { 
-    differenceScores <- xVals - yVals
-  } else {
-      differenceScores <- xVals - testValue
-  }
-  
-  differenceSigns <- (sign(differenceScores))
-  absDifferenceRanked <- rank(abs(differenceScores))
-  prodSignAbsRank <- differenceSigns * absDifferenceRanked
-  
-  initDiffSamples <- sort(abs(rnorm(n)))[absDifferenceRanked]
-  sampledDiffsAbs <- abs(initDiffSamples)
-  diffSamples <- numeric(n)
-  
-  deltaSamples <- gSamples <- numeric(nSamples)
-  diffSamplesMatrix <- matrix(nrow=nSamples,ncol=n)
-  
-  oldDeltaProp <- 0
-  
-  for (j in 1:nSamples) {
-    for (i in sample(n)) {
-      
-      currentRank <- absDifferenceRanked[i]
-      
-      currentBounds <- upperLowerTruncation(ranks=absDifferenceRanked, values=sampledDiffsAbs, currentRank=currentRank)
-      if (is.infinite(currentBounds[["under"]])) {currentBounds[["under"]] <- 0}
-      
-      sampledDiffsAbs[i] <- myTruncNormSim(currentBounds[["under"]], currentBounds[["upper"]], 
-                                           mu = abs(oldDeltaProp), sd=1)
-    }
-    
-    diffSamples <- sampledDiffsAbs * differenceSigns
-    
-    if (any(differenceSigns == 0) && varyTies) {
-      nullSamples <- sampledDiffsAbs[differenceSigns == 0] * sample(c(-1,1), size = sum(differenceSigns == 0), replace = T)
-      diffSamples[which(differenceSigns == 0)] <- nullSamples
-    }
-    
[…]

### 2019-12-16 paper/manuscript.Rmd
update clean repo

@@
 ---
-title             : "What’s she talking about? Category based discourse inferences in early childhood"
+title             : "What’s she talking about? Category based discourse inferences in young children"
 shorttitle        : "Discourse inferences in early childhood"
@@
 ex2_data <- read_csv(file="../data/data_ex2.csv")
-ex3_data <- read_csv(file="../data/data_ex3.csv")
 ```
@@
 All experimental procedures, sample sizes and statistical analysis were pre-registered (see https://osf.io/9ypxn and https://osf.io/fyaxq).
-The experimental procedure can be found in the assoicated online repository at https://github.com/manuelbohn/disCon.
+The study material can be found in the associated online repository at https://github.com/manuelbohn/disCon.
 
@@
 desc_ex1 <- ex1_data%>%
+  mutate(sex = ifelse(sex == "F",1,0))%>%
   group_by(age_group)%>%
@@
             min_age = min(age_num),
-            max_age = max(age_num))
+            max_age = max(age_num), 
+            sex = sum(sex, na.rm = T)/4)
 ```
 
-We obtained valid data from 71 children, including `r desc_ex1%>%filter(age_group == "2")%>%pull(n)` 2-year-olds (mean = `r desc_ex1%>%filter(age_group == "2")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "2")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "2")%>%pull(max_age)`), `r desc_ex1%>%filter(age_group == "3")%>%pull(n)` 3-year-olds (mean = `r desc_ex1%>%filter(age_group == "3")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "3")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "3")%>%pull(max_age)`) and `r desc_ex1%>%filter(age_group == "4")%>%pull(n)` 4-year-olds (mean = `r desc_ex1%>%filter(age_group == "4")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "4")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "4")%>%pull(max_age)`).
+We obtained valid data from 71 children, including `r desc_ex1%>%filter(age_group == "2")%>%pull(n)` 2-year-olds (mean = `r desc_ex1%>%filter(age_group == "2")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "2")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "2")%>%pull(max_age)`, `r desc_ex1%>%filter(age_group == "2")%>%pull(sex)` girls), `r desc_ex1%>%filter(age_group == "3")%>%pull(n)` 3-year-olds (mean = `r desc_ex1%>%filter(age_group == "3")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "3")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "3")%>%pull(max_age)`, `r desc_ex1%>%filter(age_group == "3")%>%pull(sex)` girls) and `r desc_ex1%>%filter(age_group == "4")%>%pull(n)` 4-year-olds (mean = `r desc_ex1%>%filter(age_group == "4")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "4")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "4")%>%pull(max_age)`, `r desc_ex1%>%filter(age_group == "4")%>%pull(sex)` girls).
 We tested a larger sample of 2-year-olds because we expected a weaker effect in this age group.
-In addition, 12 children were recruited but not tested becasue their parents reported less than 75% of English exposure at home.
+In addition, 12 children were recruited but not tested because their parents reported less than 75% of English exposure at home.
 Ten children started the experiment but did not finish it because they became impatient (7) or the equipment broke (3).
-Three children were tested but excluded becasue they were correct in less than 5/6 training trials (see below).
+Three children were tested but excluded because they were correct in less than 5/6 training trials (see below).
 All children were recruited from the floor of a Children's museum in San José, California, USA.
-The population from which this sample is drawn is characterised by diverse ethnic background and high socioeconimic status.
+The population from which this sample is drawn is characterized by diverse ethnic background (predominantly self identifying as White, Asian or of mixed ethnicity) and high levels of parental education and socioeconomic status.
 Parents gave informed consent and provided demographic information.
+Data was collected between January and September 2019.
 All experiments reported in this paper were approved by the Stanford Institutional Review Board (protocol no.
@@
 Study materials were presented as a picture book on a tablet computer [@frank2016using].
-Children reponded by touching objects on the screen.
+Children responded by touching objects on the screen.
 Responses were automatically saved.
 The experimenter guided children through the procedure and read out general instructions.
-The study was framed as visit to the house of the little animals which would show the child the things they have at home.
+The study was framed as visit to the house of the little animals during which the animals would show the child the things they have at home.
 Utterances made by the different animals were pre-recorded from native English speakers, with one speaker per animal.
 On each trial, children saw one animal in the middle of the screen with three objects above them (Figure \ref{fig:fig1}, left).
-Each objects was from different category (mammals, vehicles, clothes and fruits).
-For each category, we had pictures of seven different category memebers (e.g.
-for vehicles: car, truck, train, bus, airplane, boat and motorbike, see Figure \ref{fig:fig1}, right).
+Each objects came from a different category (mammals, vehicles, clothes and fruits).
+For each category, we selected pictures of seven different category members (e.g.
+for vehicles: car, truck, train, bus, airplane, boat and motorbike).
+The right panel of figure \ref{fig:fig1} shows all pictures used in the study grouped by category.
+
 The trial started with six training rounds, in which the animal named one of the objects above them, asking the child to touch it (e.g.
@@
 From one round to the next, the pictures changed but the categories remained the same.
-For example, children saw a skirt, a horse and a motorcylce on the first training round and a jacket, a dog and a bus on the second.
-During training, the speaker consitently named objects from the same target category.
-After six training rounds, children received a test round in which the speaker used a pronoun to refer to one of the objects ("Look at that, can you touch *it*").
-Categories were ranomdly selected at the beginning of each trial and so was the order of pictures within each category.
-The position of each picture (left, right mddle) was also randomly determined on each round.
+For example, children saw a skirt, a horse and a motorcycle on the first training round and a jacket, a dog and a bus on the second.
+During training, the speaker consistently named objects from the same target category.
+After six training rounds, children received a test round in which the speaker used an ambiguous pronoun to refer to one of the objects ("Look at that, can you touch *it*").
+Categories were randomly selected at the beginning of each trial and so was the order of pictures within each category.
+The position of each picture (left, right middle) was also randomly determined on each round.
 Children received four trials, one with each category as the target.
@@
 
-bf_t_overall <- ex1_data %>%
-  group_by(id) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  mutate(mean= mean(unlist(correct)),
-         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf)
+## comparison to chance
 
@@
 
+## mixed model to look at age continously
+
 ex1_model_data <- ex1_data%>%
@@
 
-prior_ex1_m1 <- c(set_prior("normal(0,10)", class = "b", coef = "age_num"))
-
-ex1_m1 <- brm(correct ~ age_num + (1|id) + (1|speaker),
-                    data = ex1_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          prior = prior_ex1_m1, 
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 50000)%>%
-  saveRDS(., "../saves/ex1_model1.rds")
+# ex1_m1 <- brm(correct ~ age_num + (1|id) + (1|speaker),
+#                     data = ex1_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = F,
+#           iter = 50000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/ex1_model1.rds")
+# 
+# ex1_m2 <- brm(correct ~ 1 + (1|id) + (1|speaker),
+#                     data = ex1_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = F,
+#           iter = 50000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/ex1_model2.rds")
 
@@
 
-ex1_m2 <- brm(correct ~ 1 + (1|id) + (1|speaker),
-                    data = ex1_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 50000)%>%
-  saveRDS(., "../saves/ex1_model2.rds")
-
 ex1_m2 <-readRDS("../saves/ex1_model2.rds")
 
-ex1_waic <- brms::waic(ex1_m1, ex1_m2, compare = F)
+#bf_ex1 <- bayes_factor(ex1_m1, ex1_m2, log = FALSE, maxiter = 5000)
 
-ex1_weights <- model_weights(ex1_m1, ex1_m2, weights = "waic")
-
-bf_ex1 <- bayes_factor(ex1_m1, ex1_m2, log = FALSE, maxiter = 5000)
-
-t1 <- tibble(
-  Model = c("correct ~ age + RE","correct ~ 1 + RE"),
-  WAIC = c(ex1_waic$loo$ex1_m1$estimates[3,1],ex1_waic$loo$ex1_m2$estimates[3,1]),
-  SE = c(ex1_waic$loo$ex1_m1$estimates[3,2],ex1_waic$loo$ex1_m2$estimates[3,2]),
-  weight = c(ex1_weights["ex1_m1"],ex1_weights["ex1_m2"]),
-  BF = c("-",round(bf_ex1$bf,2)))
+t1 <- loo_compare(ex1_m1, ex1_m2, criterion = "waic")%>%
+  as.data.frame() %>%
+  tibble::rownames_to_column("Predictors")%>%
+  mutate(
+    Predictors = recode(Predictors, ex1_m1 = "Age", 
+                   ex1_m2 = "Intercept only"),
+    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
+    weight = round(weight, 3),
+    WAIC = round(waic, 2),
+    #BF = c("-",round(bf_ex1$bf,2)),
+    SE = round(se_waic,2))%>%
+  select(Predictors, WAIC, SE, weight)
 ```
@@
   geom_hline(yintercept = 1/3, lty=2, size = 1)+
-  geom_jitter(data = pex1_1,aes(x = age_num, y= correct, col = experiment), width = .00, height = .01, alpha = .5)+
-  geom_line(data = samples, aes(x = age, y = y, group = sample), col = "#CC6677", size = .025)+
-  geom_line(data = map_model, aes(x = age, y = y), col = "#CC6677", size = 1)+
+  geom_jitter(data = pex1_1,aes(x = age_num, y= correct), width = .00, height = .01, alpha = .5)+
+  geom_line(data = samples, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
+  geom_line(data = map_model, aes(x = age, y = y), size = 1)+
+  geom_pointrange(data = pex1_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = experiment),size = .8, position = position_dodge(width = .2), pch = 4)+
   #geom_smooth(data = ex1_data,aes(x = age_num, y= correct, col = experiment), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5)+
@@
 # density plot
-
 plot_post <- ex1_data %>%
@@
   group_by(age_group) %>%
-  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 1000)[,"mu"])))%>%
+  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 2000)[,"mu"])))%>%
   select(-correct)
@@
 plot_dens <- tibble(
-  age = rep(c(2,3,4), each = 1000),
+  age = rep(c(2,3,4), each = 2000),
   posterior = c(unlist(plot_post%>%filter(age_group == "2") %>% pull(posterior)),unlist(plot_post%>%filter(age_group == "3") %>% pull(posterior)),unlist(plot_post%>%filter(age_group == "4") %>% pull(posterior)))
@@
   guides(alpha = F)+
-  scale_fill_ordinal(name = "Age")
+  scale_fill_colorblind(name = "Age")
 ```
 
-```{r fig2, include = T, fig.align = "center", fig.cap = "A: Posterior probability distribution for the mean for each age bin.
-Shaded regions indicate 95\\% CIs.
+```{r fig2, include = T, fig.align = "center", fig.cap = "A: Posterior probability distribution for the mean for each age bin based on one sample Bayesian t-test.
+Shaded regions indicate 95\\% credible intervals for each age bin.
 B: Correct responses for age continously.
-Transparent dots show aggregated data from individual participants.
-Red line with grey shows the smoothed conditional mean of the data in each condition..", fig.width=10, fig.height=4}
-
+Transparent dots show data aggregated for each individual participants.
+Red crosses show mean within age bin with 95\\% confidence intervals based on non-parametric bootstrap.
+Black line shows the mean of the posterior distribution of the model including age.
+Grey lines show 1000 random draws from the model posterior to depict uncertainty in the model.
+Dotted line indicates level of performance expected by chance.", fig.width=10, fig.height=4}
 ggarrange(post_plot,p1, nrow = 1, labels = c("A","B"))
@@
 The dependent variable in all analysis was whether the touched object at test was from the same category as the objects named throughout the training rounds.
-All following analysis were computed in R [@R-base].
-As a first step, we aggregated respones across trials for each child and compared the proportion of correct responses to a level expected by chance (33% correct) within each age bin.
-We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes factor (BF) in favor of the hypothesis that performance is above chance (see Figure \ref{fig:fig2}A).
-We found little evidence that 2-year olds performed above chance (mean proportion correct = `r bf_t_age%>%filter(age_group == "2")%>%pull(mean)`, BF = `r bf_t_age%>%filter(age_group == "2")%>%pull(bf)`) but found subtantial evidence for 3-year-olds (mean proportion correct = `r bf_t_age%>%filter(age_group == "3")%>%pull(mean)`, BF = `r bf_t_age%>%filter(age_group == "3")%>%pull(bf)`) and 4-year-olds (mean proportion correct = `r bf_t_age%>%filter(age_group == "4")%>%pull(mean)`, BF = `r bf_t_age%>%filter(age_group == "4")%>%pull(bf)`).
+All analysis were computed in R [@R-base].
+As a first step, we aggregated responses across trials for each child and compared the proportion of correct responses to a level expected by chance (33% correct) within each age bin.
+We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes factor (BF) in favor of the hypothesis that performance is above chance (0.33 correct).
+Figure \ref{fig:fig2}A shows the corresponding posterior distribution for each age bin.
+We found little evidence that 2-year olds performed above chance (mean proportion correct = `r bf_t_age%>%filter(age_group == "2")%>%pull(mean)`, BF~10~ = `r bf_t_age%>%filter(age_group == "2")%>%pull(bf)`) but found substantial evidence for 3-year-olds (mean proportion correct = `r bf_t_age%>%filter(age_group == "3")%>%pull(mean)`, BF~10 = `r bf_t_age%>%filter(age_group == "3")%>%pull(bf)`) and 4-year-olds (mean proportion correct = `r bf_t_age%>%filter(age_group == "4")%>%pull(mean)`, BF~10~ = `r bf_t_age%>%filter(age_group == "4")%>%pull(bf)`)\footnote{This result is robust to changes in the prior on the standardized effect size.
+Choosing a wider prior results in slightly smaller Bayes factors, see online repository for details}.
 
-To analyse responses continously across age we used generalized linear mixed models (GLMM) fit via the function `brm` from the R-package `brms` [@R-brms_a].
+To analyse responses continuously across age we used generalized linear mixed models (GLMM) fit via the function `brm` from the R-package `brms` [@R-brms_a].
 All models had default priors and included random effects for participant id and speaker.
@@
 Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights.
-WAIC is an indicator of the model's predictive accuracy for out of sample data and model's with lower scores are preferred.
+The WAIC score is an indicator of the model's predictive accuracy for out of sample data; model's with lower scores are preferred.
 WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data.
-We quantified the evidence in favor of the model with the lowest WAIC score (highest WAIC weight) compared to alternative models by computing Bayes factors via the funtion `bayes_factor` from the R-package `brms` [@R-brms_a].
+In addition, we inspected the posterior distribution for the key parameters in the model via it's mean and 95 % credible interval (CI).
 
-The model comparison favored the model including age as a predictor (Table \ref{tab:table1}).
-The model estiamte for age was positive ($\beta$ = `r fixef(ex1_m1)[2,1]`, 95% confidence interval (CI) = `r fixef(ex1_m1)[2,3]` - `r fixef(ex1_m1)[2,4]`), suggesting an increase in performance with age (see also Figure \ref{fig:fig2}B).
-However, the evidence in support of this model was modest, speaking against subtantial developmental gains across the age range considered.
-
-## Discussion
+For experiment 1, the model comparison favored the model including age as a predictor (Table \ref{tab:table1}).
+The mean model estimate for age was positive ($\beta$ = `r fixef(ex1_m1)[2,1]`, 95% CI = `r fixef(ex1_m1)[2,3]` - `r fixef(ex1_m1)[2,4]`), suggesting an increase in performance with age (see also Figure \ref{fig:fig2}B).
+However, the small difference in model weights and the fact that the 95% CI for the model estimate also overlapped with zero speak against substantial developmental gains in the age range considered.
 
@@
   , caption = "Model comparison for Experiment 1"
-  , note = "All models had the same random effects (RE) structure. BF denotes the Bayes Factor in favor to the model with the highest WAIC weight."
+  , note = "All models included random intercepts for participant and speaker."
   , escape = T
@@
 
+## Discussion
+This experiment presents evidence that children make inferences about conversational topics.
+Based on hearing a speaker consistently refer to objects from a certain category, children first inferred this category and then used it to interpret an ambiguous pronoun in a subsequent utterance.
+This suggests that children track common ground with a speaker not just in terms of remembering what has been talked about previously, but also in form of an overarching topic that guides the conversation and allows predictions about what will be talked about in the future.
+
+In a follow-up experiment we tested whether the number of training rounds affected children's ability to make the inference.
+WE contrasted one training round with six training rounds.
+The results suggest that fewer training rounds do not necessarily mean worse performance.
+However, the data is not conclusive and we therefore present the details of this experiment in the supplementary material.
+In the next experiment, we focus instead on whether this inference is conditional on the identity of a speaker.
+
 # Experiment 2
 
-Registration: https://osf.io/x2k4p
+Here we test whether children expect a conversational topic to be specific to a speaker.
+Because we only found limited evidence that 2-year-olds make category based discourse inferences in experiment 1, we only tested 3- and 4-year-olds in Experiment 2.
+The preregistration for this experiment can be found at https://osf.io/5e9pk and the study material are in the associated online repository.
 
 ## Participants
+```{r participants-ex2, include = F}
+desc_ex2 <- ex2_data%>%
+  mutate(sex = ifelse(sex == "F",1,0))%>%
+  group_by(age_group)%>%
+  summarise(n = length(unique(id)), 
+            age = mean(age_num), 
+            min_age = min(age_num),
+            max_age = max(age_num),
+            sex = sum(sex)/4)
+```
 
-## Material and Procedure
+We tested 60 children, including `r desc_ex2%>%filter(age_group == "3")%>%pull(n)` 3-year-olds (mean = `r desc_ex2%>%filter(age_group == "3")%>%pull(age)`, range = `r desc_ex2%>%filter(age_group == "3")%>%pull(min_age)` - `r desc_ex2%>%filter(age_group == "3")%>%pull(max_age)`, `r desc_ex2%>%filter(age_group == "3")%>%pull(sex)` girls) and `r desc_ex2%>%filter(age_group == "4")%>%pull(n)` 4-year-olds (mean = `r desc_ex2%>%filter(age_group == "4")%>%pull(age)`, range = `r desc_ex2%>%filter(age_group == "4")%>%pull(min_age)` - `r desc_ex2%>%filter(age_group == "4")%>%pull(max_age)`, `r desc_ex2%>%filter(age_group == "4")%>%pull(sex)` girls).
+Four additional children were recruited but not included because parents reported less than 75% English exposure at home.
+Another four children were tested but ended up not contributing data because the equipment failed (2) or because they did not finish the experiment (2).
+Data was collected in August and September of 2019.
+For details on population characteristics and ethical approval see experiment 1.
 
-## Results and Discussion
+## Method
+
+The general setup and procedure were the same as in experiment 1 except for the following changes.
+The animals were introduced as showing children their *favorite* things (experiment 1: things they have at home).
+We included this to focus children's attention on the individual speakers.
+Conversely, when making a request, speakers said: "I like that.
+Can you touch [object/it]".
+The speaker change manipulation was implemented in the following way: After the six training rounds, the speaker announced that they had to leave and left the scene by walking off the left edge of the screen.
+Then, either the same or a different animal returned to the scene and made a request using the ambiguous pronoun.
+If the same speaker returned, they entered from the same side as they left, if a new speaker appeared, they entered from the other side.
+This measure served to emphasize that the different speaker was new to the scene and therefore unfamiliar with the preceding discourse.
+We tested conditions within participant in a randomized order.
+Each child received four trials, two with the same and two with a different speaker returning.
+
+## Results
 
 ```{r experiment2, cache = T, include = F}
-
 ex2_model_data <- ex2_data%>%
@@
 
-prior_ex2_m1 <- c(set_prior("normal(0,10)", class = "b", coef = "age_num"),
-                  set_prior("normal(0,10)", class = "b", coef = "conditionlow_input"),
-                  set_prior("normal(0,10)", class = "b", coef = "age_num:conditionlow_input"))
-
-ex2_m1 <- brm(correct ~ age_num * condition + (condition|id) + (condition|speaker),
-                    data = ex2_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          prior = prior_ex2_m1,
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 50000)%>%
-  saveRDS(., "../saves/ex2_model1.rds")
+# ex2_m1 <- brm(correct ~ age_num * condition + (condition|id) + (condition|speaker),
+#                     data = ex2_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = F,
+#           iter = 50000)%>%
+#    add_criterion("waic")%>%
+#     saveRDS(., "../saves/ex2_model1.rds")
+# 
+# ex2_m2 <- brm(correct ~ age_num + condition + (condition|id) + (condition|speaker),
+#                     data = ex2_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = F,
+#           iter = 50000)%>%
+#    add_criterion("waic")%>%
+#     saveRDS(., "../saves/ex2_model2.rds")
+# 
+# ex2_m3 <- brm(correct ~ age_num + (condition|id) + (condition|speaker),
+#                     data = ex2_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = F,
+#           iter = 50000)%>%
+#    add_criterion("waic")%>%
+#     saveRDS(., "../saves/ex2_model3.rds")
 
@@
 
-prior_ex2_m2 <- c(set_prior("normal(0,10)", class = "b", coef = "age_num"),
-                  set_prior("normal(0,10)", class = "b", coef = "conditionlow_input"))
-
-ex2_m2 <- brm(correct ~ age_num + condition + (condition|id) + (condition|speaker),
-                    data = ex2_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          prior = prior_ex2_m2,
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 50000)%>%
-  saveRDS(., "../saves/ex2_model2.rds")
-
 ex2_m2 <-readRDS("../saves/ex2_model2.rds")
-
-prior_ex2_m3 <- c(set_prior("normal(0,10)", class = "b", coef = "age_num"))
-
-ex2_m3 <- brm(correct ~ age_num + (condition|id) + (condition|speaker),
-                    data = ex2_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          prior = prior_ex2_m3,
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 50000)%>%
-  saveRDS(., "../saves/ex2_model3.rds")
 
@@
 
-ex2_waic <- brms::waic(ex2_m1, ex2_m2,ex2_m3, compare = F)
-
-ex2_weights <- model_weights(ex2_m1, ex2_m2,ex2_m3, weights = "waic")
-
-bf_ex2_1 <- bayes_factor(ex2_m3, ex2_m1, log = FALSE)
-
-bf_ex2_2 <- bayes_factor(ex2_m3, ex2_m2, log = FALSE)
-
-t2 <- tibble(
-  Model = c("correct ~ age + RE","correct ~ age * condition + RE","correct ~ age + condition + RE"),
-  WAIC = c(ex2_waic$loo$ex2_m3$estimates[3,1],ex2_waic$loo$ex2_m1$estimates[3,1],ex2_waic$loo$ex2_m2$estimates[3,1]),
-  SE = c(ex2_waic$loo$ex2_m3$estimates[3,2],ex2_waic$loo$ex2_m1$estimates[3,2],ex2_waic$loo$ex2_m2$estimates[3,2]),
-  weight = c(ex2_weights[3],ex2_weights[1],ex2_weights[2]),
-  BF = c("-",round(bf_ex2_1$bf,2),round(bf_ex2_2$bf,2)))
+t2 <- loo_compare(ex2_m1, ex2_m2, ex2_m3, criterion = "waic")%>%
+  as.data.frame() %>%
+  tibble::rownames_to_column("Predictors")%>%
+  mutate(
+    Predictors = recode(Predictors, ex2_m1 = "Age * Condition", 
+                   ex2_m2 = "Age + Condition",
+                   ex2_m3 = "Age"),
+    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
+    weight = round(weight, 3),
+    WAIC = round(waic, 2),
+    SE = round(se_waic,2))%>%
+  select(Predictors, WAIC, SE, weight)
 ```
@@
   , caption = "Model comparison for Experiment 2"
-  , note = "All models had the same random effects (RE) structure. BF denotes the Bayes Factor in favor to the model with the highest WAIC weight."
+  , note = "All models included random intercepts for participant and speaker and random slopes for condition."
   , escape = T
@@
 ```
-
-# Experiment 3
-
-Registration: https://osf.io/5e9pk
-
-## Participants
-
-## Material and Procedure
-
-## Results and Discussion
-
-```{r experiment3, cache = T, include = F}
-
-ex3_model_data <- ex3_data%>%
-  mutate(age_num = age_num - mean(age_num))
-
-prior_ex3_m1 <- c(set_prior("normal(0,5)", class = "b", coef = "intercept"),
-                  set_prior("normal(0,5)", class = "b", coef = "age_num"),
-                  set_prior("normal(0,5)", class = "b", coef = "conditionsame_speaker"),
-                  set_prior("normal(0,5)", class = "b", coef = "age_num:conditionsame_speaker"))
-
-ex3_m1 <- brm(correct ~ age_num * condition + (condition|id) + (condition|speaker),
-                    data = ex3_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 10000)%>%
-   add_criterion("waic")%>%
-  saveRDS(., "../saves/ex3_model1.rds")
-
-hypothesis(ex3_m1, hypothesis = 'age_num:conditionsame_speaker = 0')
-
-ex3_m1 <-readRDS("../saves/ex3_model1.rds")
-
-ex3_m2 <- update(ex3_m1, 
-                 formula = ~ . -age_num:conditionsame_speaker, 
-                 newdata = ex3_model_data,
-                 chains = 4,
-                 cores = 4,
-                 save_all_pars = TRUE)%>%
-   add_criterion("waic")%>%
-  saveRDS(., "../saves/ex3_model2.rds")
-
-ex3_m2 <-readRDS("../saves/ex3_model2.rds")
-
-ex3_m3 <- update(ex3_m1, 
-                 formula = ~ . - age_num:conditionsame_speaker - conditionsame_speaker, 
-                 newdata = ex3_model_data,
-                 chains = 4,
-                 cores = 4,
-                 save_all_pars = TRUE)%>%
-   add_criterion("waic")%>%
-  saveRDS(., "../saves/ex3_model3.rds")
-
-ex3_m3 <-readRDS("../saves/ex3_model3.rds")
-
-bf_ex3_1 <- bayes_factor(ex3_m1, ex3_m2, log = FALSE)
-
-bf_ex3_2 <- bayes_factor(ex3_m1, ex3_m2, log = FALSE)
-
-t3 <- loo_compare(ex3_m1, ex3_m2, ex3_m3, criterion = "waic")%>%
-  as.data.frame() %>%
-  tibble::rownames_to_column("Model")%>%
-  mutate(
-    Model = recode(Model, ex3_m1 = "correct ~ age * condition + RE", 
-                   ex3_m2 = "correct ~ age + condition + RE",
-                   ex3_m3 = "correct ~ age + RE"),
-    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
-    weight = round(weight, 3),
-    WAIC = round(waic, 2),
-    SE = round(se_waic,2),
-    BF = c("-",round(bf_ex3_1$bf,2),round(bf_ex3_2$bf,2)))%>%
-  select(Model, WAIC, SE, BF)
-
-```
-
-```{r table3,results = "asis"}
-apa_table(
-  t3
-  , caption = "Model comparison for Experiment 3"
-  , note = "All models had the same random effects (RE) structure. BF denotes the Bayes Factor in favor to the model with the highest WAIC weight."
-  , escape = T
-)
-```
-
-# General Discussion
 
@@
   filter(sample < 2000)%>%
-  mutate(condition = ifelse(sample <1000, "high_input", "low_input"),
-         y = ifelse(condition == "high_input", plogis(b_Intercept + b_age_num * `ex2_model_data$age_num`), plogis(b_Intercept + b_conditionlow_input + b_age_num * `ex2_model_data$age_num` + `b_age_num:conditionlow_input` * `ex2_model_data$age_num`)),
+  mutate(condition = ifelse(sample <1000, "same_speaker", "different_speaker"),
+         y = ifelse(condition == "different_speaker", plogis(b_Intercept + b_age_num * `ex2_model_data$age_num`), plogis(b_Intercept + b_conditionsame_speaker + b_age_num * `ex2_model_data$age_num` + `b_age_num:conditionsame_speaker` * `ex2_model_data$age_num`)),
          age = `ex2_model_data$age_num` + mean(ex2_data$age_num))
@@
   age = rep(ex2_model_data$age_num, 2),
-  condition = c(rep("high_input", length(ex2_model_data$age_num)),rep("low_input", length(ex2_model_data$age_num))),
+  condition = c(rep("same_speaker", length(ex2_model_data$age_num)),rep("different_speaker", length(ex2_model_data$age_num))),
   int = fixef(ex2_m1)[1,1],
@@
 )%>%
-  mutate(y = ifelse(condition == "high_input", plogis(int + slope * age), plogis(int + speak + slope * age + int_act * age)),
+  mutate(y = ifelse(condition == "different_speaker", plogis(int + slope * age), plogis(int + speak + slope * age + int_act * age)),
          age = age + mean(ex2_data$age_num))
@@
   geom_line(data = map_model_2, aes(x = age, y = y, col = condition), size = 1)+
-  #geom_smooth(data = ex2_data,aes(x = age_num, y= correct, col = condition), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5 )+
-  #geom_pointrange(data = pex2_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
-  labs(x="Age",y="Proportion correct")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(3,5)+
-  guides(alpha = F)+
-  scale_color_manual(name = "Input",
-                   breaks = c("low_input", "high_input"),
-                   labels = c("Low", "High"),
-                   values = c("#CC6677", "#DDCC77"))+
-  theme(legend.position = "bottom")
-
-pex3_1 <- ex3_data %>%
-  group_by(condition,age_group,age_num, id) %>%
-  summarise(correct = mean(correct))
-
-pex3_2 <- pex3_1 %>%
-  group_by(condition,age_group) %>%
-  multi_boot_standard(col = "correct")
-
-samples3 <- posterior_samples(ex3_m1, "^b")%>%
-  mutate(sample = 1:length(b_age_num))
-
-sample3 <- expand_grid(samples3,ex3_model_data$age_num)%>%
-  filter(sample < 2000)%>%
-  mutate(condition = ifelse(sample <1000, "same_speaker", "different_speaker"),
-         y = ifelse(condition == "different_speaker", plogis(b_Intercept + b_age_num * `ex3_model_data$age_num`), plogis(b_Intercept + b_conditionsame_speaker + b_age_num * `ex3_model_data$age_num` + `b_age_num:conditionsame_speaker` * `ex3_model_data$age_num`)),
-         age = `ex3_model_data$age_num` + mean(ex3_data$age_num))
-
-map_model_3 <- tibble(
-  age = rep(ex3_model_data$age_num, 2),
-  condition = c(rep("same_speaker", length(ex3_model_data$age_num)),rep("different_speaker", length(ex3_model_data$age_num))),
-  int = fixef(ex3_m1)[1,1],
-  slope = fixef(ex3_m1)[2,1],
-  speak = fixef(ex3_m1)[3,1],
-  int_act = fixef(ex3_m1)[4,1]
-)%>%
-  mutate(y = ifelse(condition == "different_speaker", plogis(int + slope * age), plogis(int + speak + slope * age + int_act * age)),
-         age = age + mean(ex3_data$age_num))
-
-p3 <- ggplot() +
-  geom_hline(yintercept = 1/3, lty=2, size = 1)+
-  geom_jitter(data = pex3_1,aes(x = age_num, y= correct, col = condition), width = .00, height = .01, alpha = .5)+
-  geom_line(data = sample3, aes(x = age, y = y, col = condition, group = sample), size = .025)+
-  geom_line(data = map_model_3, aes(x = age, y = y, col = condition), size = 1)+
-  #geom_smooth(data = ex3_data,aes(x = age_num, y= correct, col = condition), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5)+
-  #geom_pointrange(data = pex3_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
+  #geom_smooth(data = ex2_data,aes(x = age_num, y= correct, col = condition), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5)+
+  geom_pointrange(data = pex2_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
   labs(x="Age",y="Proportion correct")+
@@
   theme(legend.position = "bottom")
-
 ```
 
-```{r plot2, fig.width=8, fig.height=4}
-ggarrange(p2, p3, nrow = 1, labels = c("A","B"))
+```{r fig3, include = T, fig.align = "center", fig.cap = "Correct responses in experiment 2 for age continously by age and condition.
+Transparent dots show aggregated data from individual participants.
+Blue and red crosses show mean within age bin based on aggregated data with 95\\% CI based on non-parametric bootstrap.
+Colored line shows the mean of the posterior distribution for each condition based on the interaction model.
+Lighter lines show 1000 random draws per condition from the model posterior to depict uncertainty.
+Dotted line indicates level of performance expected by chance.", out.width = '50%'}
+p2
 ```
+
+We tested the effect of speaker change on children's discourse inferences via a model comparison.
+We compared a base model including only age as a fixed effect to models also including condition, either as a main effect or in form of an interaction with age.
+Models were fitted and compared in the same way as in experiment 1.
+The model comparison clearly favored the interaction model (Table \ref{tab:table2}).
+The interaction term in the model itself was large and reliably different from zero ($\beta$ = `r fixef(ex2_m1)[4,1]`, 95% CI = `r fixef(ex2_m1)[4,3]` - `r fixef(ex2_m1)[4,4]`).
+Figure \ref{fig:fig3} visualizes the data and the model and shows that while younger children did not take into account speaker identity, older children (starting at around age 4) only interpreted the ambiguous pronoun in light of the previous discourse topic when the speaker remained the same.
+
+## Discussion
+
+In Experiment 2, we found evidence that children from four years onward assume that a conversational topic is specific to the identity of the speaker.
+When one speaker repeatedly referred to objects from the same category, they expected the same speaker, but not a different one, to continue communicating about the same category.
+Younger children did not take into account speaker identity.
+
+# General Discussion
 

### 2019-12-16 paper/supplementary_material.Rmd
update clean repo

---
title             : "Category based discourse inferences in early childhood  \nSupplementary material"
shorttitle        : " "

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2"
  - name          : "Khuyen Nha Le"
    affiliation   : "1"
  - name          : "Benjamin Peloquin"
    affiliation   : "1"
  - name          : "Bahar Köymen"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Stanford University"
  - id            : "2"
    institution   : "Leipzig University"
  - id            : "3"
    institution   : "University of Manchester"

bibliography      : ["r-references.bib"]

figsintext        : yes
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "doc"
output            : papaja::apa6_pdf
header-includes:
  \usepackage{caption}
  \usepackage{setspace}\doublespacing
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

```{r setup, include = FALSE}
library(papaja)
library(tidyverse)
library(ggplot2)
library(brms)
library(ggthemes)
library(langcog)
library(ggpubr)
library(BayesFactor)
library(broom)
library(coda)
library(reshape2)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

```{r analysis-preferences,include = F}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r load data,include = F}
ex1_data <- read_csv(file="../data/data_ex1.csv")
exs_data <- read_csv(file="../data/data_exs.csv")
ex2_data <- read_csv(file="../data/data_ex2.csv")
```

# Experiment 1

## Method

### Materials

The list below shows all words that were used to request objects during training rounds for each of the four categories. The corresponding pictures are shown in figure 1 in the main manuscript.

* fruit: strawberry, apple, banana, cherry, orange, melon, pineapple
* vehicles: car, truck, train, bus, airplane, boat, motorbike
* clothes: shoe, sock, hat, shirt, jacket, dress, skirt
* animals: dog, cat, horse, bear, cow, monkey, elephant

The object shown at test for each category was randomly selected from all objects of that category.

```{r experiment1, cache = T, include = F}
## check sensitivity to prior
bf_t_age_prior <- ex1_data %>%
  group_by(age_group, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(age_group)%>%
  mutate(mean= mean(unlist(correct)),
         default = round(extractBF(ttestBF(unlist(correct), mu = 1/3))$bf,2),
         wide = round(extractBF(ttestBF(unlist(correct), mu = 1/3, rscale = "wide"))$bf,2),
         ultrawide = round(extractBF(ttestBF(unlist(correct), mu = 1/3,rscale = "ultrawide"))$bf,2),
         Age = as.character(age_group))%>%
  ungroup()%>%
  select(Age, default, wide, ultrawide)
```

```{r tableS1,results = "asis"}
apa_table(
  bf_t_age_prior
  , caption = "Bayes factors based on Bayesian t-test with different priors on standardized effect size"
  , escape = T
)
```

### Analysis

We used `r cite_r("r-references.bib")` for all our analyses reported in the main manuscript and the supplementary material.

### Results

We conducted a sensitivity analysis for the Bayes factors that informed the comparison to chance in each age group. We re-ran the analysis using wider priors than the default priors from the package. Table \ref{tab:tableS1} reports the results. Results show that the conclusions - 3- and 4-year-olds, but not 2-year-olds, select the object from the same category above chance - are robust to changes in the prior width.

# Supplementary Experiment

In this study, we varied the number of training rounds before the test event. Procedures and analysis were pre-registered at https://osf.io/x2k4p. Our main focus was on condition differences and we therefore sampled a smaller number of children from each age group.

## Method

### Participants
```{r participants-exs, include = F}
desc_exs <- exs_data%>%
  mutate(sex = ifelse(sex == "F",1,0))%>%
  group_by(age_group)%>%
  summarise(n = length(unique(id)), 
            age = mean(age_num), 
            min_age = min(age_num),
            max_age = max(age_num),
            sex = sum(sex)/4)
```

We tested 33 children, including `r desc_exs%>%filter(age_group == "3")%>%pull(n)` 3-year-olds (mean = `r desc_exs%>%filter(age_group == "3")%>%pull(age)`, range = `r desc_exs%>%filter(age_group == "3")%>%pull(min_age)` - `r desc_exs%>%filter(age_group == "3")%>%pull(max_age)`, `r desc_exs%>%filter(age_group == "3")%>%pull(sex)` girls) and `r desc_exs%>%filter(age_group == "4")%>%pull(n)` 4-year-olds (mean = `r desc_exs%>%filter(age_group == "4")%>%pull(age)`, range = `r desc_exs%>%filter(age_group == "4")%>%pull(min_age)` - `r desc_exs%>%filter(age_group == "4")%>%pull(max_age)`, `r desc_exs%>%filter(age_group == "4")%>%pull(sex)` girls). For details on population characteristics and ethical approval see experiment 1.

### Materials and Procedure

Study material and procedure were identical to study 1 with the following change: we administered two types of trials that varied in the number of training rounds that preceded the test. *Low input* trials had one training round while *high input* trials had six training rounds. Participants received four trials, two in each condition. The order of conditions was randomized. Categories were randomly assigned to each condition and object positions were randomized in the same way as in study 1. Experimental procedures can be found in the associated online repository.

### Results

```{r experimentS, cache = T, include = F}

exs_model_data <- exs_data%>%
  mutate(age_num = age_num - mean(age_num))

# exs_m1 <- brm(correct ~ age_num * condition + (condition|id) + (condition|speaker),
#                     data = exs_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = F,
#           iter = 50000)%>%
#     add_criterion("waic")%>%
#   saveRDS(., "../saves/exs_model1.rds")
# 
# exs_m2 <- brm(correct ~ age_num + condition + (condition|id) + (condition|speaker),
#                     data = exs_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = F,
#           iter = 50000)%>%
#     add_criterion("waic")%>%
#   saveRDS(., "../saves/exs_model2.rds")
# 
# 
# 
# exs_m3 <- brm(correct ~ age_num + (condition|id) + (condition|speaker),
#                     data = exs_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = F,
#           iter = 50000)%>%
#     add_criterion("waic")%>%
#   saveRDS(., "../saves/exs_model3.rds")

exs_m1 <-readRDS("../saves/exs_model1.rds")

exs_m2 <-readRDS("../saves/exs_model2.rds")

exs_m3 <-readRDS("../saves/exs_model3.rds")

ts <- loo_compare(exs_m1, exs_m2, exs_m3, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Model")%>%
  mutate(
    Model = recode(Model, exs_m1 = "correct ~ age * condition + RE", 
                   exs_m2 = "correct ~ age + condition + RE",
                   exs_m3 = "correct ~ age + RE"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 3),
    WAIC = round(waic, 2),
    SE = round(se_waic,2))%>%
  select(Model, WAIC, SE, weight)
```

```{r plot1, include = F}
pexs_1 <- exs_data %>%
  group_by(condition,age_group,age_num, id) %>%
  summarise(correct = mean(correct))

pexs_2 <- pexs_1 %>%
  group_by(condition,age_group) %>%
  multi_boot_standard(col = "correct")

samples2 <- posterior_samples(exs_m1, "^b")%>%
  mutate(sample = 1:length(b_age_num))

sample2 <- expand_grid(samples2,exs_model_data$age_num)%>%
  filter(sample < 2000)%>%
  mutate(condition = ifelse(sample <1000, "high_input", "low_input"),
         y = ifelse(condition == "high_input", plogis(b_Intercept + b_age_num * `exs_model_data$age_num`), plogis(b_Intercept + b_conditionlow_input + b_age_num * `exs_model_data$age_num` + `b_age_num:conditionlow_input` * `exs_model_data$age_num`)),
         age = `exs_model_data$age_num` + mean(exs_data$age_num))

map_model_2 <- tibble(
  age = rep(exs_model_data$age_num, 2),
  condition = c(rep("high_input", length(exs_model_data$age_num)),rep("low_input", length(exs_model_data$age_num))),
  int = fixef(exs_m1)[1,1],
  slope = fixef(exs_m1)[2,1],
  speak = fixef(exs_m1)[3,1],
  int_act = fixef(exs_m1)[4,1]
)%>%
  mutate(y = ifelse(condition == "high_input", plogis(int + slope * age), plogis(int + speak + slope * age + int_act * age)),
         age = age + mean(exs_data$age_num))

p2 <- ggplot() +
  geom_hline(yintercept = 1/3, lty=2, size = 1)+
  geom_jitter(data = pexs_1,aes(x = age_num, y= correct, col = condition), width = .00, height = .01, alpha = .5)+
  geom_line(data = sample2, aes(x = age, y = y, col = condition, group = sample), size = .025)+
  geom_line(data = map_model_2, aes(x = age, y = y, col = condition), size = 1)+
  #geom_smooth(data = ex2_data,aes(x = age_num, y= correct, col = condition), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5 )+
  geom_pointrange(data = pexs_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)+
  scale_color_manual(name = "Input",
                   breaks = c("low_input", "high_input"),
                   labels = c("Low", "High"),
                   values = c("#CC6677", "#DDCC77"))+
  theme(legend.position = "right")
```

We used WAIC scores and weights to compare models including condition as a predictor to models lacking it. Table \ref{tab:tableS2} shows the results of the model comparison. The model without condition as a predictor (either as main effect or as an interaction with age) provided the best fit. In this model, the predictor for age was largely positive and different from zero ($\beta$ = `r fixef(exs_m3)[2,1]`, 95% CI = `r fixef(exs_m3)[2,3]` - `r fixef(exs_m3)[2,4]`) suggesting an increase in performance with age. Figure \ref{fig:plotS1} shows that, in contrast to study 1, 3-year-olds had difficulties with this version of the task.

```{r tableS2,results = "asis"}
apa_table(
  ts
  , caption = "Model comparison for Experiment 2"
  , note = "All models included random intercepts for particiapnt and speaker and random slopes for condition."
  , escape = T
)
```

```{r plotS1, include = T, fig.align = "center", fig.cap = "Correct responses in supplementary experiment by age and condition. Transparent dots show aggregated data from individual participants. Blue and red crosses show mean within age bin based on aggregated data with 95\\% CI based on non-parametric bootstrap. Colored lines show the mean of the posterior distribution for each condition based on the interaction model (note that the model comparison favored the model without condition). Lighter lines show 1000 random draws per condition from the model posterior to depict uncertainty. Dotted line indicates level of performance expected by chance.", out.width = '60%'}
p2
```

### Discussion

The results of this experiment suggest that hearing fewer examples of objects from the implied category does not automatically result in worse performance overall. However, this interpretation should be taken with caution. As it turns out, mixing low and high input trials substantially affected 3-year-olds' performance in the task. That is, in contrast to study 1 and 2, they struggled with the basic inference. This suggests that including low input trials made the task harder overall. The difference between conditions might be more prominent in a between subjects design. However, more data is needed to reach a conclusion and, as of now, we see these results as inconclusive at best.

# Exploratory analysis

This is an exploratory analysis that was not pre-registered. From all experiments we select the data with six training rounds and the same speaker. That is, we included all data from study 1, the high input condition from the supplementary experiment and the same speaker condition from study 2.

## Methods

### Participants

```{r}
con_data <- bind_rows(
  ex1_data, 
  exs_data%>%filter(condition == "high_input")%>%select(-condition),
  ex2_data%>%filter(condition == "same_speaker")%>%select(-condition)
) %>%
  mutate(target_category = ifelse(target_category == "mammals", "animals", target_category))
```

Data from all children (N = `r length(unique(con_data$id))`) who participated in one of the three experiments were included. For detailed information about age and population characteristics see individual experiments.

### Results

Figure \ref{fig:plotS2}A shows that performance differed widely across categories. This visual impression was corroborated in a model comparison. We compared a model with condition to a model without condition as a predictor in the same way as in previous experiments. Table \ref{tab:tableS3} shows that the model including category was clearly favored. For comparisons between categories we set clothes as the reference category. Figure \ref{fig:plotS2}B and \ref{fig:plotS3} show that children chose the object from the same category most often when fruits was the target category. Vehicles and animals (reference category) resulted in intermediate levels of performance while clothes was the most difficult.

## Discussion

This exploratory analysis suggests that children's ability to infer the topic of a conversation depends, in part, on the implied topic itself. Categories may differ in difficulty either because some category members might be less familiar to children and/or because children are less familiar with the category itself.

```{r suppanalysis, cache = T, include = F}
con_model_data <- con_data %>%
  mutate(age_num = age_num - mean(age_num))

# con_m1 <- brm(correct ~ age_num + target_category + (1|id) + (target_category|speaker),
#                     data = con_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = F,
#           iter = 50000)%>%
#     add_criterion("waic")%>%
#   saveRDS(., "../saves/con_model1.rds")
# #
# con_m2 <- brm(correct ~ age_num + (1|id) + (target_category|speaker),
#                     data = con_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           save_all_pars = F,
#           iter = 50000)%>%
#     add_criterion("waic")%>%
#   saveRDS(., "../saves/con_model2.rds")

con_m1 <-readRDS("../saves/con_model1.rds")

con_m2 <-readRDS("../saves/con_model2.rds")

#bf_exc <- bayes_factor(con_m1, con_m2, log = FALSE)

tcon <- loo_compare(con_m1, con_m2, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Model")%>%
  mutate(
    Model = recode(Model, con_m1 = "correct ~ age + category + RE", 
                  con_m2 = "correct ~ age + RE"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 3),
    WAIC = round(waic, 2),
    #BF = c(round(bf_exs_1$bf,2),round(bf_exs_2$bf,2) ,"-"),
    SE = round(se_waic,2))%>%
  select(Model, WAIC, SE, weight)
```

```{r plot2, include = F}
pc1 <- con_data%>%
  mutate(age_group = as.character(age_group))%>%
  group_by(experiment, target_category,age_group, id) %>%
  summarise(correct = mean(correct))

pc2 <- pc1 %>%
  group_by(target_category,age_group) %>%
  multi_boot_standard(col = "correct")

cp1 <- ggplot()+
  geom_hline(yintercept = 1/3, lty=2)+
  geom_jitter(data = pc1, aes(x = age_group, y = correct, col = target_category), position = position_jitterdodge(jitter.width = .1,jitter.height = .025, dodge.width = .75 ), alpha = .5)+
  geom_pointrange(data = pc2, aes(x = age_group, y = mean, ymin = ci_lower, ymax = ci_upper, col = target_category), position = position_dodge(width = .75), pch = 4)+
  #facet_grid(~experiment)+
  labs(x="Age",y="Proportion correct")+
  theme_few()+
  scale_color_colorblind(name = "Category")

samples_con <- posterior_samples(con_m1, "^b")%>%
  mutate(sample = 1:length(b_age_num))

con_sample <- expand_grid(samples_con,unique(con_model_data$age_num))%>%
  filter(sample < 4000)%>%
  mutate(y = ifelse(sample < 1000, plogis(b_Intercept + b_age_num * `unique(con_model_data$age_num)`),
                    ifelse( sample > 1000 & sample < 2000, plogis(b_Intercept + b_target_categoryfruits +  b_age_num * `unique(con_model_data$age_num)`),
                           ifelse(sample > 2000 & sample < 3000, plogis(b_Intercept + b_target_categoryclothes +  b_age_num * `unique(con_model_data$age_num)`),
                                  plogis(b_Intercept + b_target_categoryvehicles +  b_age_num * `unique(con_model_data$age_num)`)))),
         Category = ifelse(sample < 1000, "animals",
                    ifelse( sample > 1000 & sample < 2000, "fruits",
                           ifelse(sample > 2000 & sample < 3000, "clothes",
                                  "vehicles"))),
         age = `unique(con_model_data$age_num)` + mean(con_data$age_num))

map_con <- tibble(
  age = rep(con_model_data$age_num, 4),
  Category = c(rep("clothes", length(con_model_data$age_num)),rep("fruits", length(con_model_data$age_num)),rep("animals", length(con_model_data$age_num)),rep("vehicles", length(con_model_data$age_num))),
  int = fixef(con_m1)[1,1],
  slope = fixef(con_m1)[2,1],
  clothes = fixef(con_m1)[3,1],
  fruits = fixef(con_m1)[4,1],
  vehicles = fixef(con_m1)[5,1]
)%>%
  mutate(y = ifelse(
    Category == "animals", plogis(int + slope * age),
    ifelse(Category == "fruits", plogis(int + fruits + slope * age),
           ifelse(Category == "clothes", plogis(int + clothes + slope * age),
                  plogis(int + vehicles + slope * age)))),
         age = age + mean(con_data$age_num))

cp2 <- ggplot() +
  geom_hline(yintercept = 1/3, lty=2)+
  geom_line(data = con_sample, aes(x = age, y = y, col = Category, group = sample), size = .01)+
  geom_line(data = map_con, aes(x = age, y = y, col = Category), size = 1)+
  #geom_pointrange(data = pex3_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+
  scale_color_colorblind(name = "Category")+
  theme(legend.position = "right")

cp3 <- tidy(con_m1, prob = 0.95) %>%
  filter(term == "b_age_num" |
           term == "b_target_categoryfruits" |
           term == "b_target_categoryclothes" |
           term == "b_target_categoryvehicles")%>% 
  mutate(term = str_remove(term,"b_"),
         term = str_remove(term,"target_category"),
         term = str_remove(term,"_num"))%>%
  ggplot(aes(term, estimate, ymin = lower, ymax = upper)) + 
  geom_hline(yintercept=0, lty = 2)+
  geom_pointrange(position = position_dodge(width = .8))+
  coord_flip()+
  theme_few()

```

```{r tableS3,results = "asis"}
apa_table(
  tcon
  , caption = "Model comparison for exploratory analysis on category differences"
  , note = "All models included random intercepts for particiapnt and speaker and random slopes for category within speaker"
  , escape = T
)
```

```{r plotS2, include = T, fig.align = "center", fig.cap = "A: Data plotted by age bin and category. Transparent dots show data from individual participants. Colored crosses show mean within age bin and category with 95\\% confidence intervals based on non-parametric bootstrap. B: Correct responses for age continously. Colored lines show the mean of the posterior distribution of the model including category. Lighter lines show 1000 random draws from the model posterior to depict uncertainty in the model. Dotted line indicates level of performance expected by chance.", out.width = '100%', fig.asp = .5}
ggarrange(cp1, cp2, nrow = 1, labels = c("A","B"), common.legend = T, legend = "bottom")
```

```{r plotS3, include = T, fig.align = "center", fig.cap = "Model estimates for each category with clothes as the reference category. Dots show mean and error bars 95\\% credible intervals of the posterior distribution.", out.width = '60%', fig.asp = .5}
cp3
```

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2019-12-16 experiments/helper/mmturkey.js

@@ -1,0 +1,263 @@
+// Bundle in Crockford's JSON2.js
+var JSON;JSON||(JSON={});
+(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
+e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
+"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2019-12-16 experiments/js/study1.js

@@ -1,0 +1,772 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+//only preload relevant audios (no speaker change)
+var preloadAudios = ["hi", "lets", "intro", "thank", "it"];
+
+var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger", "Pig"])
+
+//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
+
+var audios = new Array();
+for (i = 0; i < posAgents.length; i++) {
+    for (j = 0; j < preloadAudios.length; j++) {
+        var audio = new Audio();
+        audio.src = "sounds/" + preloadAudios[j] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+    for (k = 0; k < preloadItems.length - 3; k++) {
+        var audio = new Audio();
+        audio.src = "sounds/" + preloadItems[k] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
[…]

### 2019-12-16 experiments/js/study2.js

@@ -1,0 +1,864 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+//only preload relevant audios (no speaker change)
+var preloadAudios = ["hi", "lets", "intro", "thank", "it", "needtogo", "imback"];
+
+var posAgents = shuffle(["Bear", "Cat", "Elephant", "Frog", "Sheep", "Tiger", "Mouse"])
+
+//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
+
+var audios = new Array();
+for (i = 0; i < posAgents.length; i++) {
+    for (j = 0; j < preloadAudios.length; j++) {
+        var audio = new Audio();
+        audio.src = "sounds/speakerchange/" + preloadAudios[j] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+    for (k = 0; k < preloadItems.length - 3; k++) {
+        var audio = new Audio();
+        audio.src = "sounds/speakerchange/" + preloadItems[k] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
[…]

### 2019-12-16 experiments/js/supplementary_experiment.js

@@ -1,0 +1,789 @@
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "bread", "tv", "pencil"];
+
+var images = new Array();
+for (i = 0; i < preloadItems.length; i++) {
+    images[i] = new Image();
+    images[i].src = "images/" + preloadItems[i] + ".png";
+}
+
+//only preload relevant audios (no speaker change)
+var preloadAudios = ["hi", "lets", "intro", "thank", "it"];
+
+var posAgents = shuffle(["Bunny", "Frog", "Mouse", "Beaver", "Sheep", "Tiger", "Pig"])
+
+//var posAgents = shuffle(["Bear", "Beaver", "Bunny", "Cat", "Dog", "Elephant", "Frog", "Monkey", "Mouse", "Pig", "Sheep", "Tiger"])
+
+var audios = new Array();
+for (i = 0; i < posAgents.length; i++) {
+    for (j = 0; j < preloadAudios.length; j++) {
+        var audio = new Audio();
+        audio.src = "sounds/" + preloadAudios[j] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+    for (k = 0; k < preloadItems.length - 3; k++) {
+        var audio = new Audio();
+        audio.src = "sounds/" + preloadItems[k] + "_" + posAgents[i] + ".mp3"
+        audios.push(audio);
+    }
+}
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#"+id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showAgent(id, orient) {
+    $(".agent").hide();
+    $(".agent_transition").hide();
[…]

### 2019-12-16 paper/supplementary_material.Rmd
update supplementary material

@@
 The difference between conditions might be more prominent in a between subjects design.
-However, more data is needed to reach a conclusion and, as of now, we see these results as inconclusive at best.
+However, more data is needed to reach a conclusion and, as of now, we see these results as inconclusive.
 
@@
 Figure \ref{fig:plotS2}B and \ref{fig:plotS3} show that children chose the object from the same category most often when fruits was the target category.
-Vehicles and animals (reference category) resulted in intermediate levels of performance while clothes was the most difficult.
+Vehicles and animals (reference category) resulted in intermediate levels of performance while clothes was the most difficult one.
 

### 2020-01-21 paper/supplementary_material.Rmd
update supplementary material

@@
 ---
-title             : "Category based discourse inferences in early childhood  \nSupplementary material"
+title             : "What’s she talking about? Social and topic based discourse inferences in young children  \nSupplementary material"
 shorttitle        : " "
@@
 library(reshape2)
+library(bayesplot)
 
@@
   mutate(mean= mean(unlist(correct)),
-         default = round(extractBF(ttestBF(unlist(correct), mu = 1/3))$bf,2),
-         wide = round(extractBF(ttestBF(unlist(correct), mu = 1/3, rscale = "wide"))$bf,2),
-         ultrawide = round(extractBF(ttestBF(unlist(correct), mu = 1/3,rscale = "ultrawide"))$bf,2),
+         `default prior` = round(extractBF(ttestBF(unlist(correct), mu = 1/3))$bf,2),
+         `wide prior` = round(extractBF(ttestBF(unlist(correct), mu = 1/3, rscale = "wide"))$bf,2),
+         `ultrawide prior` = round(extractBF(ttestBF(unlist(correct), mu = 1/3,rscale = "ultrawide"))$bf,2),
          Age = as.character(age_group))%>%
   ungroup()%>%
-  select(Age, default, wide, ultrawide)
+  select(Age, `default prior`, `wide prior`, `ultrawide prior`)
 ```
@@
 
+### Analysis
+
+We compared a model including category as a fixed effect to a model lacking this predictor.
+Models are compared in the same way as in previous experiments.
+Furthermore, to investigate the relative difficulty of each target category, we compare the posterior distributions of the parameter estimate for each category.
+
 ### Results
@@
 This visual impression was corroborated in a model comparison.
-We compared a model with condition to a model without condition as a predictor in the same way as in previous experiments.
 Table \ref{tab:tableS3} shows that the model including category was clearly favored.
-For comparisons between categories we set clothes as the reference category.
+For comparisons between categories we set animals as the reference category.
 Figure \ref{fig:plotS2}B and \ref{fig:plotS3} show that children chose the object from the same category most often when fruits was the target category.
-Vehicles and animals (reference category) resulted in intermediate levels of performance while clothes was the most difficult one.
+Vehicles and animals resulted in intermediate levels of performance while clothes was the most difficult one.
 
@@
 Categories may differ in difficulty either because some category members might be less familiar to children and/or because children are less familiar with the category itself.
+See general discussion section in the main manuscript for a discussion of how these results relate to the other studies.
 
@@
 
-cp3 <- tidy(con_m1, prob = 0.95) %>%
-  filter(term == "b_age_num" |
-           term == "b_target_categoryfruits" |
-           term == "b_target_categoryclothes" |
-           term == "b_target_categoryvehicles")%>% 
-  mutate(term = str_remove(term,"b_"),
-         term = str_remove(term,"target_category"),
-         term = str_remove(term,"_num"))%>%
-  ggplot(aes(term, estimate, ymin = lower, ymax = upper)) + 
-  geom_hline(yintercept=0, lty = 2)+
-  geom_pointrange(position = position_dodge(width = .8))+
-  coord_flip()+
+cp3 <-bayesplot::mcmc_areas(as.array(con_m1), 
+                      pars = c("b_target_categoryfruits", "b_target_categoryclothes", "b_target_categoryvehicles"), 
+                      prob = 0.95)+
+  geom_vline(xintercept = 0, lty = 2, col = "black")+
+  scale_y_discrete(breaks=c("b_target_categoryfruits","b_target_categoryclothes","b_target_categoryvehicles"),
+        labels=c("Fruits", "Clothes", "Vehicles"))+
   theme_few()
@@
 
-```{r plotS3, include = T, fig.align = "center", fig.cap = "Model estimates for each category with clothes as the reference category.
-Dots show mean and error bars 95\\% credible intervals of the posterior distribution.", out.width = '60%', fig.asp = .5}
+```{r plotS3, include = T, fig.align = "center", fig.cap = "Posterior distribution of model estimates for each category with animals as the reference category.
+Thick blue lines show mean and shaded regions show 95\\% credible intervals.", out.width = '60%', fig.asp = .5}
 cp3

### 2020-02-21 paper/manuscript.Rmd
update for submission

@@
 ---
-title             : "What’s she talking about? Category based discourse inferences in young children"
+title             : "Children’s interpretation of ambiguous pronouns based on prior discourse"
 shorttitle        : "Discourse inferences in early childhood"
@@
   - id            : "1"
-    institution   : "Stanford University"
+    institution   : "Department of Psychology, Stanford University"
   - id            : "2"
-    institution   : "Leipzig University"
+    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
   - id            : "3"
-    institution   : "University of Manchester"
+    institution   : "School of Health Sciences, University of Manchester"
 
 authornote: |
-  We thank Megan Merrick and Sabina Zacco for their help with the data collection.
-MB received funding from the European Union’s Horizon   2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
+  We thank Megan Merrick and Sabina Zacco for their help with the data collection and all families for participating.
+Manuel Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
 749229.
@@
 abstract: |
-  tbd...
+  In conversation, speech is almost always ambiguous, with this ambiguity resolved by context and discourse history (“common ground”).
+One important cue for disambiguation is the topic under discussion with a particular partner (e.g., “want to pick?” means something different in a conversation with a bluegrass musician vs.
+with a book club partner).
+Here, we investigated 2- to 5-year-old American English-speaking children’s (N = 131) reliance on conversational topics with specific partners to interpret ambiguous or novel words.
+Children heard a speaker consistently refer to objects from a category without mentioning the category itself.
+In Study 1, 3- and 4-year-olds interpreted the ambiguous pronoun it as referring to another member of the same category.
+In study 2, 4-year-olds only interpreted the pronoun as referring to the implied category when talking to the same speaker but not when talking to a new speaker.
+Thus, children’s conception of what constitutes common ground in discourse develops substantially between age 2 and 5.
 
-keywords          : "keywords"
-wordcount         : "X"
+keywords          : "Discourse, Pragmatics, Social cognition, Language development, Conceptual development"
 
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 library(reshape2)
+library(ggridges)
 
@@
 ```
+# Research highlights
 
-# Experiment 1
+* Conversational topics organize discourse with specific partners
+* Children make inferences about conversational topics from 3 years onwards
+* From 4 years onwards, children see conversational topics as speaker specific
+* Discourse structures communicative interactions and thereby helps children to resolve ambiguity and learn language
+
+# Introduction
+
+Language learning and use is a fundamentally social behavior -- when children hear ambiguous or novel words they can rely on social information to infer meaning [e.g.
+@bohn2019pervasive; @tomasello2008origins; @clark2009first].
+As discourse unfolds, interlocutors build up common ground - a set of shared knowledge and beliefs - that serves as a background against which new utterances are interpreted [@bohn2018common; @clark1996using].
+To use common ground in this way, children not only have to pay attention to what is said earlier but also with whom they have had this conversation and share this common ground.
+Children as young as 18 months old can use information from prior discourse to disambiguate words.
+Children typically interpret an ambiguous pronoun as referring to a previously mentioned object - even when it was absent from the scene [@ganea2007infants; @lidz2003infants].
+This behavior diversifies with age - 3 to 5-year olds use discourse context to interpret personal pronouns [@song2005s; @hartshorne2015development].
+
+Children can also rely on prior discourse to learn new words.
+For instance, when a speaker first states that they were hungry and then asks for a wug, 2-year-olds map the novel word onto an edible object [@sullivan2016discourse] Around age 3, children see the positioning of a novel word in discourse as a clue to its meaning [@horowitz2015young].
+And starting at age 4, children use discourse coherence - as expressed by connectives such as and or because - to interpret the meaning of a novel word [@sullivan2019discourse].
+Beyond nouns, children can also infer some aspects of verb meaning based on discourse context [@yuan2009really; @fisher2020developmental].
+
+In almost all of these studies, the loose construct of “discourse” or “common ground” is operationalized as including the specific objects that had been explicitly mentioned.
+In conversation, however, discourse is often organized in terms of an overarching topic rather than a specific object.
+Further, this topic is rarely stated explicitly; instead it is typically inferred based on the content of utterances [@clark1996using].
+For example, when a child reports from a school trip “I saw an elephant, a tiger, a giraffe, and another one that was really scary” the parent can infer that another one refers to yet another animal.
+One study comes closer to this conception of discourse topic.
+Akhtar [-@akhtar2002relevance] had children interact with an adult who repeatedly drew their attention to either the shape or the color of an object.
+When the adult later used a novel word to describe an object, children mapped the word on the property (color or shape) that was focused on during the preceding discourse.
+Children could solve this task by keeping track of which part of the objects they were jointly attending to (in the sense of looking at) with the speaker previously.
+Such visual anchoring, however, is not always possible because the topic may be absent and/or an abstract entity (such as “animals” in the example above).
+In this scenario the topic has to be inferred by reasoning about how the individual conversational bits relate to one another - how they are organized in conceptual terms.
+
+Another neglected aspect of discourse inference, at least in experimental work, is its social nature.
+Put differently, common ground built up during discourse is often partner-specific.
+Subsequent inferences therefore incorporate both the conversational topic(s), but crucially also social information - the participants engaging in the conversation.
+Children keep track of their conversational partners from a very young age [@bohn2018social].
+Saylor and Ganea [-@saylor2007infants] had 14 to 20 month old children play ball with two different experimenters.
+Depending on who later asked for “the ball”, children retrieved the object that featured in their previous play with that person.
+From 3 years onwards, children use partner specific referential expressions (referential pacts), both with adults and peers [@matthews2010s; @koymen2014young].
+Interestingly, speaker identity influences children’s interpretation of ambiguous utterances at an early point in language processing [@khu2019preschoolers; @san2015new].
+However, these social inferences based on the identity of the conversational partners have rarely been studied in conjunction with discourse inferences.
+Thus, it is unclear whether discourse inferences involve social reasoning at all.
+
+In the present set of studies, we investigated the impact of partner specific discourse topics on ambiguous pronoun resolution in 2- to 5-year-old children.
+First, we examine how children interpret ambiguous utterances in light of an overarching topic that guides conversation, but was never explicitly mentioned (and must be inferred in context).
+Second, we examine how their interpretation changes depending on the common ground shared with specific partners.
+In this way, we fill the gap between discourse and partner-specific reasoning.
+
+In Study 1, children interacted with a speaker who repeatedly mentioned objects from a particular category (e.g., horse and dog from the category animals).
+At a later time in the discourse the speaker used the ambiguous pronoun it in the context of three new objects - one object from the category mentioned earlier (e.g., a cat) and two other objects (e.g., a hat and a train).
+We found that children from age 3 onwards reliably interpret the ambiguous pronoun as referring to the object from the same category.
+
+In study 2 we tested whether these judgments were specific to particular speakers.
+Children heard one speaker talk about objects from a particular category.
+Then, either the same or a different speaker used the ambiguous pronoun.
+We found that children adjusted their inference to the identity of the speaker from age 4 onwards.
+
+# Study 1
 
 All experimental procedures, sample sizes and statistical analysis were pre-registered (see https://osf.io/9ypxn and https://osf.io/fyaxq).
-The study material can be found in the associated online repository at https://github.com/manuelbohn/disCon.
+All deviations from the pre-registration are explicitly mentioned.
+The experimental material can be found in the associated online repository at https://github.com/manuelbohn/disCon.
 
-## Participants
+## Methods
+
+### Participants
 ```{r participants-ex1, include = F}
@@
 
-We obtained valid data from 71 children, including `r desc_ex1%>%filter(age_group == "2")%>%pull(n)` 2-year-olds (mean = `r desc_ex1%>%filter(age_group == "2")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "2")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "2")%>%pull(max_age)`, `r desc_ex1%>%filter(age_group == "2")%>%pull(sex)` girls), `r desc_ex1%>%filter(age_group == "3")%>%pull(n)` 3-year-olds (mean = `r desc_ex1%>%filter(age_group == "3")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "3")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "3")%>%pull(max_age)`, `r desc_ex1%>%filter(age_group == "3")%>%pull(sex)` girls) and `r desc_ex1%>%filter(age_group == "4")%>%pull(n)` 4-year-olds (mean = `r desc_ex1%>%filter(age_group == "4")%>%pull(age)`, range = `r desc_ex1%>%filter(age_group == "4")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "4")%>%pull(max_age)`, `r desc_ex1%>%filter(age_group == "4")%>%pull(sex)` girls).
+Our final sample included data from 71 children, including `r desc_ex1%>%filter(age_group == "2")%>%pull(n)` 2-year-olds (*M* = `r desc_ex1%>%filter(age_group == "2")%>%pull(age)`, *range* = `r desc_ex1%>%filter(age_group == "2")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "2")%>%pull(max_age)`, `r desc_ex1%>%filter(age_group == "2")%>%pull(sex)` girls), `r desc_ex1%>%filter(age_group == "3")%>%pull(n)` 3-year-olds (*M* = `r desc_ex1%>%filter(age_group == "3")%>%pull(age)`, *range* = `r desc_ex1%>%filter(age_group == "3")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "3")%>%pull(max_age)`, `r desc_ex1%>%filter(age_group == "3")%>%pull(sex)` girls) and `r desc_ex1%>%filter(age_group == "4")%>%pull(n)` 4-year-olds (*M* = `r desc_ex1%>%filter(age_group == "4")%>%pull(age)`, *range* = `r desc_ex1%>%filter(age_group == "4")%>%pull(min_age)` - `r desc_ex1%>%filter(age_group == "4")%>%pull(max_age)`, `r desc_ex1%>%filter(age_group == "4")%>%pull(sex)` girls).
 We tested a larger sample of 2-year-olds because we expected a weaker effect in this age group.
-In addition, 12 children were recruited but not tested because their parents reported less than 75% of English exposure at home.
-Ten children started the experiment but did not finish it because they became impatient (7) or the equipment broke (3).
-Three children were tested but excluded because they were correct in less than 5/6 training trials (see below).
-All children were recruited from the floor of a Children's museum in San José, California, USA.
-The population from which this sample is drawn is characterized by diverse ethnic background (predominantly self identifying as White, Asian or of mixed ethnicity) and high levels of parental education and socioeconomic status.
-Parents gave informed consent and provided demographic information.
+In addition, 28 children were recruited but not included because they were reported to have less than 75% of English exposure at home (12 children); did not finish the task (10 children); were correct on less than 5/6 training rounds (3 children, see below), or equipment failed (3 children).
+All children were recruited from the floor of a Children’s museum in San José, California, USA.
+The population from which this sample is drawn is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status.
+Parents consented to their children’s participation and provided demographic information.
 Data was collected between January and September 2019.
-All experiments reported in this paper were approved by the Stanford Institutional Review Board (protocol no.
-357 19960).
+All experiments were approved by the Stanford Institutional Review Board (protocol no.
+19960).
 
@@
 Right: Stimuli pictures for the four categories: fruits, vehicles, clothes and mammals.", out.width="450px"}
-knitr::include_graphics("../figures/setup.png")
+knitr::include_graphics("../figures/Figure1.png")
 ```
 
-## Method
+### Materials
 
@@
 Responses were automatically saved.
-The experimenter guided children through the procedure and read out general instructions.
-The study was framed as visit to the house of the little animals during which the animals would show the child the things they have at home.
-Utterances made by the different animals were pre-recorded from native English speakers, with one speaker per animal.
-On each trial, children saw one animal in the middle of the screen with three objects above them (Figure \ref{fig:fig1}, left).
-Each objects came from a different category (mammals, vehicles, clothes and fruits).
-For each category, we selected pictures of seven different category members (e.g.
+We selected four categories of objects: animals, vehicles, clothes, and fruits.
+For each category, we chose pictures for seven different objects from that category (e.g.
 for vehicles: car, truck, train, bus, airplane, boat and motorbike).
-The right panel of figure \ref{fig:fig1} shows all pictures used in the study grouped by category.
+The right panel of figure 1 shows all pictures used in the study grouped by category (see supplementary material for a list of the corresponding words).
+All utterances made by the different speaker animals were pre-recorded from native English speakers, with one speaker per animal.
 
-The trial started with six training rounds, in which the animal named one of the objects above them, asking the child to touch it (e.g.
-"Look at that, can you touch the horse").
-From one round to the next, the pictures changed but the categories remained the same.
-For example, children saw a skirt, a horse and a motorcycle on the first training round and a jacket, a dog and a bus on the second.
-During training, the speaker consistently named objects from the same target category.
-After six training rounds, children received a test round in which the speaker used an ambiguous pronoun to refer to one of the objects ("Look at that, can you touch *it*").
-Categories were randomly selected at the beginning of each trial and so was the order of pictures within each category.
-The position of each picture (left, right middle) was also randomly determined on each round.
-Children received four trials, one with each category as the target.
+### Procedure
+
+The experimenter introduced the study as a visit to the house of the little animals, during which the animals would show the child the things they have at home.
+On each trial, children saw one animal (the speaker) in the middle of the screen with three objects above them (Figure 1, left).
+Each of the objects belonged to a different category.
+Trials started with six training rounds, in which the speaker named one of the three objects displayed above them and asked the child to touch it (“Look at that, can you touch the X?”).
+From one round to the next, the pictures changed but the three categories remained the same and the speaker consistently asked the child to touch the object from one category.
+For example, on the first training round, children saw a skirt, a horse, and a motorcycle and the speaker asked “Can you touch the motorcycle?” On the second training round, children saw a jacket, a dog, and a bus and the speaker asked “Can you touch the bus?”  After the six training rounds, children moved to the test and saw a new set of three (e.g.
+a hat, a cat and a train).
+However, instead of using a label, the speaker used an ambiguous pronoun to refer to one of the objects (“Look at that, can you touch it”).
+Children could identify the referent of the pronoun by assuming that the speaker continues to talk about objects from the same category as they did previously (vehicles in the example above).
+However, in order to do so, children had to infer the category by which all of the previous objects the speaker mentioned were grouped.
+
+Children received four sets of trials (six training trials and one test trial) with a different category as the target on each one.
+The categories, the order of the objects within each category and the position of the target object (left, right, middle) were randomized across children.
 
@@
 
-# ex1_m1 <- brm(correct ~ age_num + (1|id) + (1|speaker),
+# ex1_m1 <- brm(correct ~ age_num + (1|id) + (age_num|target_category),
 #                     data = ex1_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
+#           control = list(adapt_delta = 0.999, stepsize = 0.001, max_treedepth = 40),
 #           sample_prior = F,
@@
 #           save_all_pars = F,
-#           iter = 50000)%>%
+#           iter = 5000)%>%
 #   add_criterion("waic")%>%
@@
 # 
-# ex1_m2 <- brm(correct ~ 1 + (1|id) + (1|speaker),
+# ex1_m2 <- brm(correct ~ 1 + (1|id) + (age_num|target_category),
 #                     data = ex1_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
+#           control = list(adapt_delta = 0.999, stepsize = 0.001, max_treedepth = 40),
 #           sample_prior = F,
@@
 
-post_plot <- ggplot(plot_dens, aes(posterior, group = age)) +
-  geom_vline(xintercept = 1/3, lty=2, size = 1)+
-  geom_area(data = densities_df %>% filter(ci_shade == "ON"), aes(x = x, y = y, fill = age), alpha = .5) + 
-  geom_density(alpha = .5, size = 1)+
-  labs(y="Probability density", x="Proportion correct")+
-  theme_few() +
-  xlim(-0.05,1.05)+
-  guides(alpha = F)+
-  scale_fill_colorblind(name = "Age")
+# post_plot <- ggplot(plot_dens, aes(posterior, group = age)) +
+#   geom_vline(xintercept = 1/3, lty=2, size = 1)+
+#   geom_area(data = densities_df %>% filter(ci_shade == "ON"), aes(x = x, y = y, fill = age), alpha = .5) + 
+#   geom_density(alpha = .5, size = 1)+
+#   labs(y="Probability density", x="Proportion correct")+
+#   theme_few() +
+#   xlim(-0.05,1.05)+
+#   guides(alpha = F)+
+#   scale_fill_colorblind(name = "Age")
+
+post_plot <- ggplot(plot_dens, aes(y = factor(-age), x = posterior, fill = factor(stat(quantile))))+
+  stat_density_ridges(
+    geom = "density_ridges_gradient",
+    calc_ecdf = TRUE,
+    quantiles = c(0.025, 0.975)
+  ) +
+    labs(y="Age group", x="Proportion correct")+
+  geom_vline(xintercept = 1/3, col = "black", lty = 2)+
+  scale_fill_manual(values = c("#FF0000A0", "#A0A0A0A0", "#FF0000A0"))+
+  guides(fill = F)+
+  theme_few()+ 
+  scale_y_discrete(labels=c("-2" = "2", "-3" = "3",
+                              "-4" = "4"))
+
+p2 <- ggarrange(post_plot,p1, nrow = 1, labels = c("A","B"))
+
 ```
 
-```{r fig2, include = T, fig.align = "center", fig.cap = "A: Posterior probability distribution for the mean for each age bin based on one sample Bayesian t-test.
-Shaded regions indicate 95\\% credible intervals for each age bin.
-B: Correct responses for age continously.
-Transparent dots show data aggregated for each individual participants.
-Red crosses show mean within age bin with 95\\% confidence intervals based on non-parametric bootstrap.
+The dependent variable in all analyses was whether the object chosen at test was from the same category as the objects named throughout the training trials.
+All analyses were computed in R R [@R-base].
+As a first step, we aggregated responses across test trials for each child and compared the proportion of correct responses to a level expected by chance (33% correct) within each age bin.
+We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes factor (BF) in favor of the hypothesis that performance is above chance (0.33 correct).
+Figure \ref{fig:fig2}A shows the corresponding posterior distribution for each age bin.
+We found little evidence that 2-year olds performed above chance (mean proportion correct = `r bf_t_age%>%filter(age_group == "2")%>%pull(mean)`, BF~10~ = `r bf_t_age%>%filter(age_group == "2")%>%pull(bf)`) but found substantial evidence for 3-year-olds (mean proportion correct = `r bf_t_age%>%filter(age_group == "3")%>%pull(mean)`, BF~10~ = `r bf_t_age%>%filter(age_group == "3")%>%pull(bf)`) and 4-year-olds (mean proportion correct = `r bf_t_age%>%filter(age_group == "4")%>%pull(mean)`, BF~10~ = `r bf_t_age%>%filter(age_group == "4")%>%pull(bf)`).
+This result is robust to changes in the prior on the standardized effect size (see supplementary material for details).
+
+To analyze responses continuously across age we used logistic Bayesian generalized linear mixed models (GLMM) fit via the function `brm` from the R-package `brms` [@R-brms_a].
+All models had default priors and included random effects for participant and category\footnote{In the first preregistration (data collection with 3 and 4 year olds) we forgot to include random effects for category.
+All subsequent preregistration included it.}, with random slopes for age.
+Inference was based on comparing models that differed in whether they included the key predictor of interest, which was age in study 1.
+Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights.
+The WAIC score is an indicator of the model’s predictive accuracy for out of sample data; model’s with lower scores are preferred.
+WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data.
+In addition, we inspected the posterior distribution for the key parameters in the model via it’s mean and 95 % credible interval (CI).
+
+The model comparison favored the model including age as a predictor (Table \ref{tab:table1}).
+The mean model estimate for age was positive ($\beta$ = `r fixef(ex1_m1)[2,1]`, 95% CI = `r fixef(ex1_m1)[2,3]` - `r fixef(ex1_m1)[2,4]`), suggesting an increase of performance with age (see Figure \ref{fig:fig2}B).
+However, the small difference in model weights and the fact that the 95% CI for the model estimate also overlapped with zero speak against substantial developmental gains in the age range considered.
+
+```{r fig2, include = T, fig.align = "center", fig.cap = "(A) Posterior probability distribution for the mean for each age bin based on one sample Bayesian t-test.
+Grey regions indicate 95\\% credible intervals for each age group.
+(B) Correct responses for age continuously.
+Transparent dots show data aggregated for each individual participant.
+Red crosses show mean within age bin with 95\\% confidence intervals based on non-parametric bootstrap of the data.
 Black line shows the mean of the posterior distribution of the model including age.
 Grey lines show 1000 random draws from the model posterior to depict uncertainty in the model.
-Dotted line indicates level of performance expected by chance.", fig.width=10, fig.height=4}
-ggarrange(post_plot,p1, nrow = 1, labels = c("A","B"))
+Dotted line indicates a level of performance expected by chance.", fig.width=10, fig.height=4, fig.fullwidth = TRUE}
+p2
 ```
 
-The dependent variable in all analysis was whether the touched object at test was from the same category as the objects named throughout the training rounds.
-All analysis were computed in R [@R-base].
-As a first step, we aggregated responses across trials for each child and compared the proportion of correct responses to a level expected by chance (33% correct) within each age bin.
-We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes factor (BF) in favor of the hypothesis that performance is above chance (0.33 correct).
-Figure \ref{fig:fig2}A shows the corresponding posterior distribution for each age bin.
-We found little evidence that 2-year olds performed above chance (mean proportion correct = `r bf_t_age%>%filter(age_group == "2")%>%pull(mean)`, BF~10~ = `r bf_t_age%>%filter(age_group == "2")%>%pull(bf)`) but found substantial evidence for 3-year-olds (mean proportion correct = `r bf_t_age%>%filter(age_group == "3")%>%pull(mean)`, BF~10 = `r bf_t_age%>%filter(age_group == "3")%>%pull(bf)`) and 4-year-olds (mean proportion correct = `r bf_t_age%>%filter(age_group == "4")%>%pull(mean)`, BF~10~ = `r bf_t_age%>%filter(age_group == "4")%>%pull(bf)`)\footnote{This result is robust to changes in the prior on the standardized effect size.
-Choosing a wider prior results in slightly smaller Bayes factors, see online repository for details}.
-
-To analyse responses continuously across age we used generalized linear mixed models (GLMM) fit via the function `brm` from the R-package `brms` [@R-brms_a].
-All models had default priors and included random effects for participant id and speaker.
-Inference was based on comparing models that differed in whether they included the key predictor of interest, in this case age.
-Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights.
-The WAIC score is an indicator of the model's predictive accuracy for out of sample data; model's with lower scores are preferred.
-WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data.
-In addition, we inspected the posterior distribution for the key parameters in the model via it's mean and 95 % credible interval (CI).
-
-For experiment 1, the model comparison favored the model including age as a predictor (Table \ref{tab:table1}).
-The mean model estimate for age was positive ($\beta$ = `r fixef(ex1_m1)[2,1]`, 95% CI = `r fixef(ex1_m1)[2,3]` - `r fixef(ex1_m1)[2,4]`), suggesting an increase in performance with age (see also Figure \ref{fig:fig2}B).
-However, the small difference in model weights and the fact that the 95% CI for the model estimate also overlapped with zero speak against substantial developmental gains in the age range considered.
+```{r}
+#ggsave("../figures/Figure2.png", width = 8, height = 3, scale = 1.2)
+```
 
@@
   , caption = "Model comparison for Experiment 1"
-  , note = "All models included random intercepts for participant and speaker."
+  , note = "All models included random intercepts for participant and category and random slopes for age within category."
   , escape = T
@@
 ## Discussion
-This experiment presents evidence that children make inferences about conversational topics.
-Based on hearing a speaker consistently refer to objects from a certain category, children first inferred this category and then used it to interpret an ambiguous pronoun in a subsequent utterance.
-This suggests that children track common ground with a speaker not just in terms of remembering what has been talked about previously, but also in form of an overarching topic that guides the conversation and allows predictions about what will be talked about in the future.
+This study presents evidence consistent with the idea that starting around age 3, children make inferences about conversational topics.
+Based on hearing a speaker consistently refer to objects from a certain category, children interpreted the ambiguous pronoun it as referring to another object of the same category.
+This suggests that children track common ground with a speaker not just in terms of remembering what has been talked about previously, but also in the form of an overarching topic that guides the conversation and allows predictions about what will be talked about in the future.
 
-In a follow-up experiment we tested whether the number of training rounds affected children's ability to make the inference.
-WE contrasted one training round with six training rounds.
-The results suggest that fewer training rounds do not necessarily mean worse performance.
-However, the data is not conclusive and we therefore present the details of this experiment in the supplementary material.
-In the next experiment, we focus instead on whether this inference is conditional on the identity of a speaker.
+In a follow-up, we tested whether the number of training trials affected children’s ability to make the inference.
+We contrasted one training trial with six training trials.
+The results suggest that fewer training trials do not necessarily mean worse performance.
+However, the data were not conclusive and we therefore present the procedure and the analyses of this study in the supplementary material.
 
-# Experiment 2
+We also conducted an exploratory analysis (not pre-registered) to investigate whether the inference varied with the category that had to be inferred.
+Results point to differences between categories in that, for example, children were more likely to be correct when fruit is the target category compared to clothes.
+Details of this analysis are presented in the supplementary material.
+We return to this point in the general discussion.
+In the next study, we continued with the same number of training trials and categories and focused on whether the inference found in Study 1 is partner specific.
 
-Here we test whether children expect a conversational topic to be specific to a speaker.
-Because we only found limited evidence that 2-year-olds make category based discourse inferences in experiment 1, we only tested 3- and 4-year-olds in Experiment 2.
-The preregistration for this experiment can be found at https://osf.io/5e9pk and the study material are in the associated online repository.
+# Study 2
 
-## Participants
+Children carried out the same task as in Study 1.
+However, in half of the trials it was the same speaker who produced the ambiguous pronoun (“Can you touch it?”) as the speaker who presented the training trials and in the other half of the critical trials, it was a new speaker.
+Because we found limited evidence that 2-year-olds make category-based discourse inferences in study 1, we only tested 3- and 4-year-olds in study 2.
+The preregistration for this study can be found at https://osf.io/5e9pk and the study materials are in the associated online repository.
+
+## Methods
+
+### Participants
 ```{r participants-ex2, include = F}
@@
 
-We tested 60 children, including `r desc_ex2%>%filter(age_group == "3")%>%pull(n)` 3-year-olds (mean = `r desc_ex2%>%filter(age_group == "3")%>%pull(age)`, range = `r desc_ex2%>%filter(age_group == "3")%>%pull(min_age)` - `r desc_ex2%>%filter(age_group == "3")%>%pull(max_age)`, `r desc_ex2%>%filter(age_group == "3")%>%pull(sex)` girls) and `r desc_ex2%>%filter(age_group == "4")%>%pull(n)` 4-year-olds (mean = `r desc_ex2%>%filter(age_group == "4")%>%pull(age)`, range = `r desc_ex2%>%filter(age_group == "4")%>%pull(min_age)` - `r desc_ex2%>%filter(age_group == "4")%>%pull(max_age)`, `r desc_ex2%>%filter(age_group == "4")%>%pull(sex)` girls).
-Four additional children were recruited but not included because parents reported less than 75% English exposure at home.
-Another four children were tested but ended up not contributing data because the equipment failed (2) or because they did not finish the experiment (2).
+Sixty children, including `r desc_ex2%>%filter(age_group == "3")%>%pull(n)` 3-year-olds (*M* = `r desc_ex2%>%filter(age_group == "3")%>%pull(age)`, *range* = `r desc_ex2%>%filter(age_group == "3")%>%pull(min_age)` - `r desc_ex2%>%filter(age_group == "3")%>%pull(max_age)`, `r desc_ex2%>%filter(age_group == "3")%>%pull(sex)` girls) and `r desc_ex2%>%filter(age_group == "4")%>%pull(n)` 4-year-olds (*M* = `r desc_ex2%>%filter(age_group == "4")%>%pull(age)`, *range* = `r desc_ex2%>%filter(age_group == "4")%>%pull(min_age)` - `r desc_ex2%>%filter(age_group == "4")%>%pull(max_age)`, `r desc_ex2%>%filter(age_group == "4")%>%pull(sex)` girls) participated in this study.
+In addition, eight children were tested but not included because they had less than 75% English exposure at home (4 children); they did not finish the task (2 children), or the equipment failed (2 children).
 Data was collected in August and September of 2019.
-For details on population characteristics and ethical approval see experiment 1.
+For details on population characteristics and ethical approval see Study 1.
 
-## Method
+### Materials
 
-The general setup and procedure were the same as in experiment 1 except for the following changes.
-The animals were introduced as showing children their *favorite* things (experiment 1: things they have at home).
-We included this to focus children's attention on the individual speakers.
-Conversely, when making a request, speakers said: "I like that.
-Can you touch [object/it]".
-The speaker change manipulation was implemented in the following way: After the six training rounds, the speaker announced that they had to leave and left the scene by walking off the left edge of the screen.
-Then, either the same or a different animal returned to the scene and made a request using the ambiguous pronoun.
-If the same speaker returned, they entered from the same side as they left, if a new speaker appeared, they entered from the other side.
+Study materials were the same as in Study 1.
+
+## Procedure
+
+The general procedure was the same as in Study 1 except for the following changes.
+The speakers were introduced as showing children their *favorite* things (study 1: things they have at home).
+We included this to focus children’s attention on the individual speakers.
+Conversely, when making a request, speakers said: “I like that.
+Can you touch [object/it]”.
+The speaker change manipulation was implemented in the following way: After the six training trials, the speaker announced that they had to leave and left the scene by walking off the left edge of the screen.
+After a short pause, either the same or a different animal returned to the scene, positioned themselves in the middle, and made a request using the ambiguous pronoun.
+If the same speaker returned, they entered from the same side as they left; if a new speaker appeared, they entered from the other side.
 This measure served to emphasize that the different speaker was new to the scene and therefore unfamiliar with the preceding discourse.
-We tested conditions within participant in a randomized order.
-Each child received four trials, two with the same and two with a different speaker returning.
+If the speaker was the same as during the training trials, children could infer the referent of the pronoun in the same way as in Study 1.
+However, if the speaker changed, no such inference was licenced if children assumed that the discourse topic is specific to a speaker.
+
+Selection and positioning of objects and categories was randomized in the same way as in Study 1.
+Each child received four test trials, two with the same and two with a different speaker returning, in an order randomized for each child.
 
@@
 
-# ex2_m1 <- brm(correct ~ age_num * condition + (condition|id) + (condition|speaker),
+# ex2_m1 <- brm(correct ~ age_num * condition + (condition|id) + (age_num + condition|target_category),
 #                     data = ex2_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
+#           control = list(adapt_delta = 0.999, stepsize = 0.0001, max_treedepth = 50),
 #           sample_prior = F,
@@
 #           save_all_pars = F,
-#           iter = 50000)%>%
+#           iter = 5000)%>%
 #    add_criterion("waic")%>%
@@
 # 
-# ex2_m2 <- brm(correct ~ age_num + condition + (condition|id) + (condition|speaker),
+# ex2_m2 <- brm(correct ~ age_num + condition + (condition|id) + (age_num + condition|target_category),
 #                     data = ex2_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
+#           control = list(adapt_delta = 0.999, stepsize = 0.0001, max_treedepth = 50),
 #           sample_prior = F,
@@
 # 
-# ex2_m3 <- brm(correct ~ age_num + (condition|id) + (condition|speaker),
+# ex2_m3 <- brm(correct ~ age_num + (condition|id) + (age_num + condition|target_category),
 #                     data = ex2_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
+#           control = list(adapt_delta = 0.999, stepsize = 0.0001, max_treedepth = 50),
 #           sample_prior = F,
@@
     weight = exp(elpd_waic) / sum(exp(elpd_waic)),
-    weight = round(weight, 3),
+    weight = round(weight, 2),
     WAIC = round(waic, 2),
@@
   select(Predictors, WAIC, SE, weight)
+
 ```
@@
   , caption = "Model comparison for Experiment 2"
-  , note = "All models included random intercepts for participant and speaker and random slopes for condition."
+  , note = "All models included random intercepts for participant and speaker and random slopes for condition within participant and within condition and age within category."
   , escape = T
@@
 
-p2 <- ggplot() +
+p3 <- ggplot() +
   geom_hline(yintercept = 1/3, lty=2, size = 1)+
@@
                    breaks = c("different_speaker", "same_speaker"),
-                   labels = c("Different", "Same"))+
-  theme(legend.position = "bottom")
+                   labels = c("Different", "Same"))
 ```
 
-```{r fig3, include = T, fig.align = "center", fig.cap = "Correct responses in experiment 2 for age continously by age and condition.
+```{r fig3, include = T, fig.align = "center", fig.cap = "Correct responses in study 2 by age and condition.
 Transparent dots show aggregated data from individual participants.
-Blue and red crosses show mean within age bin based on aggregated data with 95\\% CI based on non-parametric bootstrap.
-Colored line shows the mean of the posterior distribution for each condition based on the interaction model.
+Blue and red crosses show data mean for by-year age bins with 95\\% confidence interval based on non-parametric bootstrap.
+Colored lines show the mean of the posterior distribution for each condition based on the interaction model.
 Lighter lines show 1000 random draws per condition from the model posterior to depict uncertainty.
-Dotted line indicates level of performance expected by chance.", out.width = '50%'}
-p2
+Dotted line indicates a level of performance expected by chance.", fig.width=6, fig.height=4, out.width = '60%'}
+p3
 ```
 
-We tested the effect of speaker change on children's discourse inferences via a model comparison.
-We compared a base model including only age as a fixed effect to models also including condition, either as a main effect or in form of an interaction with age.
-Models were fitted and compared in the same way as in experiment 1.
+```{r}
+ggsave("../figures/Figure3.png", width = 4, height = 3, scale = 1.5)
+```
+
+We tested the effect of speaker change on children’s discourse inferences via a model comparison.
+We compared a base model including only age as a fixed effect to models including speaker type, either as a main effect or as an interaction with age.
+Models were fitted and compared in the same way as in Study 1.
+Models now also included random slopes for condition.
 The model comparison clearly favored the interaction model (Table \ref{tab:table2}).
+The interaction model was three times more likely than the other models considered to make better predictions on new data.
 The interaction term in the model itself was large and reliably different from zero  ($\beta$ = `r fixef(ex2_m1)[4,1]`, 95% CI = `r fixef(ex2_m1)[4,3]` - `r fixef(ex2_m1)[4,4]`).
-Figure \ref{fig:fig3} visualizes the data and the model and shows that while younger children did not take into account speaker identity, older children (starting at around age 4) only interpreted the ambiguous pronoun in light of the previous discourse topic when the speaker remained the same.
+Figure \ref{fig:fig3} visualizes the data and the interaction model and shows that while younger children did not take into account speaker identity, older children (starting at around age 4) only interpreted the ambiguous pronoun in light of the previous discourse topic when the speaker remained the same.
 
@@
 
-In Experiment 2, we found evidence that children from four years onward assume that a conversational topic is specific to the identity of the speaker.
+In study 2, we found evidence that children from 4 years onward assume that a conversational topic is specific to the identity of the speaker.
 When one speaker repeatedly referred to objects from the same category, they expected the same speaker, but not a different one, to continue communicating about the same category.
-Younger children did not take into account speaker identity.
+3-year-olds, on the other hand, did not take into account speaker identity.
 
 # General Discussion
+
+We studied how children use conversational topics with specific partners to interpret ambiguous pronouns.
+Our results suggest that by age 3, children infer the topic of a conversation based on preceding discourse in order to identify the referent of an ambiguous pronoun.
+Moreover, starting at age 4, children also associated this inference with specific partners.
+These findings illustrate how children can leverage the structure of the social interactions in which conversations take place to disambiguate utterances.
+
+We did not find substantial evidence that children under the age of 3 are able to make the inference in Study 1.
+However, we suspect that this result is not due to younger children lacking the necessary inferential abilities but due to difficulties with processing the information the inference was based on.
+In an exploratory analysis we compared children’s performance in the different categories.
+We found that children across the age range were more likely to make the inference when fruit was the target category compared to when it was clothes.
+Animals and vehicles resulted in intermediate levels of performance (details for this analysis are reported in the supplementary material).
+On the one hand, younger children might not conceptualize e.g.
+clothes as a cohesive category.
+On the other hand, the individual objects in some categories might be less familiar to children and provide limited evidence for the category itself.
+From a developmental perspective, this pattern suggests that the main loci of change are children’s vocabulary and conceptual abilities.
+Of course, the exploratory nature of these results needs confirmation in future studies.
+
+Study 2 showed more pronounced developmental effects.
+While 3-year-olds tended to choose the object from the same category for both speakers (see Figure \ref{fig:fig3}), 4-year-olds only did so when the speaker was the same.
+The lack of sensitivity to speaker identity seems to conflict with earlier work which found speaker-specific communicative adjustment in younger children [@bohn2018social; @saylor2007infants].
+However, in these studies, speakers only communicated about objects that were communicated about before.
+Children could identify the referent by remembering which speaker had communicated about which object.
+In our study, the objects at test had never been communicated about before.
+The connection to the prior discourse only lay in the relation of the objects to the topic under discussion.
+Thus, children not only needed to track what objects had been talked about but also had to infer that talking about these objects is a product of the particular speaker intending to talk about a specific topic.
+
+Our setup provides an interesting and novel way to study the interplay between linguistic knowledge (necessary to make inferences about categories), conceptual knowledge (necessary to make inferences about additional category members) and social cognition (necessary to determine whether inferences are licensed).
+This interplay opens up questions about the processes involved in balancing and integrating these different information sources.
+Computational models provide a productive way to formalise theories of how information may be integrated.
+For example, Bohn and colleagues [-@bohn_tessler_merrick_frank_2019] used a Bayesian model of pragmatic reasoning [@frank2012predicting] to formalise and predict the process by which children integrate information from common ground with information that is provided by an utterance in the moment.
+
+An open question is how these results generalize outside the scope of the present context with data collected using tablet computers in a western, affluent study population.
+Regarding the first point, Frank and colleagues [-@frank2016using] found similar results when children were tested in a communication task either on a tablet or in a live interaction.
+Regarding the second point, there are relatively few cross-cultural developmental studies on pragmatic inference, with some finding similar [@zhao_ren_frank_zhou_2019] and others different [@fortier_kellier_flecha_frank_2018] trajectories compared to western, affluent settings.
+
+Taken together, the studies reported here illustrate the development of children’s ability to balance different layers of discourse.
+Thinking of discourse as organized by overarching topics allows listeners to predict what will be talked about next and, assuming that these predictions hold, increases the likelihood of successful comprehension.
+But discourse is also a form of social interaction and thus requires making inferences about the common ground shared between specific conversational partners.
+Here we show that children can use these processes to identify the referent of an ambiguous utterance.
+Because referent identification is a first step in language learning, we expect the same processes to also be recruited for language learning.
 

### 2020-02-21 paper/supplementary_material.Rmd
update for submission

@@
 ---
-title             : "What’s she talking about? Social and topic based discourse inferences in young children  \nSupplementary material"
+title             : "Supplementary material: Children’s interpretation of ambiguous pronouns based on prior discourse"
 shorttitle        : " "
@@
   - id            : "1"
-    institution   : "Stanford University"
+    institution   : "Department of Psychology, Stanford University"
   - id            : "2"
-    institution   : "Leipzig University"
+    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
   - id            : "3"
-    institution   : "University of Manchester"
+    institution   : "School of Health Sciences, University of Manchester"
 
@@
 
-The list below shows all words that were used to request objects during training rounds for each of the four categories. The corresponding pictures are shown in figure 1 in the main manuscript.
+The list below shows all words that were used to request objects during training trials for each of the four categories. The corresponding pictures are shown in figure 1 in the main manuscript.
 
@@
 
-In this study, we varied the number of training rounds before the test event.
-Procedures and analysis were pre-registered at https://osf.io/x2k4p.
+In this study, we varied the number of training trials before the test event.
+Procedures and analysis were pre-registered at https://osf.io/x2k4p/?view_only=d3440e61d88e42c892e3294a6072cc05.
 Our main focus was on condition differences and we therefore sampled a smaller number of children from each age group.
@@
 
-Study material and procedure were identical to study 1 with the following change: we administered two types of trials that varied in the number of training rounds that preceded the test.
-*Low input* trials had one training round while *high input* trials had six training rounds.
+Study material and procedure were identical to study 1 with the following change: we administered two types of trials that varied in the number of training trials that preceded the test.
+*Low input* trials had one training trial while *high input* trials had six training trials.
 Participants received four trials, two in each condition.
@@
 
-# exs_m1 <- brm(correct ~ age_num * condition + (condition|id) + (condition|speaker),
+# exs_m1 <- brm(correct ~ age_num * condition + (condition|id) + (age_num + condition|target_category),
 #                     data = exs_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
+#           control = list(adapt_delta = 0.999, stepsize = 0.0001, max_treedepth = 50),
 #           sample_prior = F,
@@
 #           save_all_pars = F,
-#           iter = 50000)%>%
+#           iter = 5000)%>%
 #     add_criterion("waic")%>%
@@
 # 
-# exs_m2 <- brm(correct ~ age_num + condition + (condition|id) + (condition|speaker),
+# exs_m2 <- brm(correct ~ age_num + condition + (condition|id) + (age_num + condition|target_category),
 #                     data = exs_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
+#           control = list(adapt_delta = 0.999, stepsize = 0.0001, max_treedepth = 50),
 #           sample_prior = F,
@@
 # 
-# exs_m3 <- brm(correct ~ age_num + (condition|id) + (condition|speaker),
+# exs_m3 <- brm(correct ~ age_num + (condition|id) + (age_num + condition|target_category),
 #                     data = exs_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
+#           control = list(adapt_delta = 0.999, stepsize = 0.0001, max_treedepth = 50),
 #           sample_prior = F,
@@
 This is an exploratory analysis that was not pre-registered.
-From all experiments we select the data with six training rounds and the same speaker.
+From all experiments we select the data with six training trials and the same speaker.
 That is, we included all data from study 1, the high input condition from the supplementary experiment and the same speaker condition from study 2.
@@
 
-We compared a model including category as a fixed effect to a model lacking this predictor.
-Models are compared in the same way as in previous experiments.
+We compared three models.
+The interaction model included an interaction between age and category, the main effects model included age and category as main effects and the baseline mode only included age as a predictor.
+Models were compared in the same way as in previous experiments.
 Furthermore, to investigate the relative difficulty of each target category, we compare the posterior distributions of the parameter estimate for each category.
@@
 Figure \ref{fig:plotS2}A shows that performance differed widely across categories.
-This visual impression was corroborated in a model comparison.
-Table \ref{tab:tableS3} shows that the model including category was clearly favored.
+This visual impression was corroborated in the model comparison.
+Table \ref{tab:tableS3} shows that the main effects model with category as a predictor was clearly favored.
 For comparisons between categories we set animals as the reference category.
 Figure \ref{fig:plotS2}B and \ref{fig:plotS3} show that children chose the object from the same category most often when fruits was the target category.
-Vehicles and animals resulted in intermediate levels of performance while clothes was the most difficult one.
+Vehicles and animals resulted in intermediate levels of performance while clothes was the most difficult category.
 
@@
 Categories may differ in difficulty either because some category members might be less familiar to children and/or because children are less familiar with the category itself.
-See general discussion section in the main manuscript for a discussion of how these results relate to the other studies.
+The general discussion section in the main manuscript offers a discussion of how these results relate to the other studies.
 
@@
 
-# con_m1 <- brm(correct ~ age_num + target_category + (1|id) + (target_category|speaker),
+# con_m1 <- brm(correct ~ age_num * target_category + (1|id),
 #                     data = con_model_data, family = bernoulli(),
@@
 #           save_all_pars = F,
-#           iter = 50000)%>%
+#           iter = 5000)%>%
 #     add_criterion("waic")%>%
 #   saveRDS(., "../saves/con_model1.rds")
-# #
-# con_m2 <- brm(correct ~ age_num + (1|id) + (target_category|speaker),
+# 
+# con_m2 <- brm(correct ~ age_num + target_category + (1|id),
 #                     data = con_model_data, family = bernoulli(),
@@
 #           save_all_pars = F,
-#           iter = 50000)%>%
+#           iter = 5000)%>%
 #     add_criterion("waic")%>%
 #   saveRDS(., "../saves/con_model2.rds")
+# 
+# con_m3 <- brm(correct ~ age_num + (1|id),
+#                     data = con_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = F,
+#           iter = 5000)%>%
+#     add_criterion("waic")%>%
+#   saveRDS(., "../saves/con_model3.rds")
 
@@
 
+con_m3 <-readRDS("../saves/con_model3.rds")
+
 #bf_exc <- bayes_factor(con_m1, con_m2, log = FALSE)
 
-tcon <- loo_compare(con_m1, con_m2, criterion = "waic")%>%
+tcon <- loo_compare(con_m1, con_m2, con_m3, criterion = "waic")%>%
   as.data.frame() %>%
@@
   mutate(
-    Model = recode(Model, con_m1 = "correct ~ age + category + RE", 
-                  con_m2 = "correct ~ age + RE"),
+    Model = recode(Model, 
+                   con_m1 = "correct ~ age * category + RE",
+                   con_m2 = "correct ~ age + category + RE", 
+                  con_m3 = "correct ~ age + RE"),
     weight = exp(elpd_waic) / sum(exp(elpd_waic)),
@@
   geom_hline(yintercept = 1/3, lty=2)+
-  geom_jitter(data = pc1, aes(x = age_group, y = correct, col = target_category), position = position_jitterdodge(jitter.width = .1,jitter.height = .025, dodge.width = .75 ), alpha = .5)+
+  geom_jitter(data = pc1, aes(x = age_group, y = correct, col = target_category), position = position_jitterdodge(jitter.width = .1,jitter.height = .025, dodge.width = .75 ), alpha = .3)+
   geom_pointrange(data = pc2, aes(x = age_group, y = mean, ymin = ci_lower, ymax = ci_upper, col = target_category), position = position_dodge(width = .75), pch = 4)+
@@
 
-samples_con <- posterior_samples(con_m1, "^b")%>%
+samples_con <- posterior_samples(con_m2, "^b")%>%
   mutate(sample = 1:length(b_age_num))
@@
   Category = c(rep("clothes", length(con_model_data$age_num)),rep("fruits", length(con_model_data$age_num)),rep("animals", length(con_model_data$age_num)),rep("vehicles", length(con_model_data$age_num))),
-  int = fixef(con_m1)[1,1],
-  slope = fixef(con_m1)[2,1],
-  clothes = fixef(con_m1)[3,1],
-  fruits = fixef(con_m1)[4,1],
-  vehicles = fixef(con_m1)[5,1]
+  int = fixef(con_m2)[1,1],
+  slope = fixef(con_m2)[2,1],
+  clothes = fixef(con_m2)[3,1],
+  fruits = fixef(con_m2)[4,1],
+  vehicles = fixef(con_m2)[5,1]
 )%>%
@@
   geom_hline(yintercept = 1/3, lty=2)+
-  geom_line(data = con_sample, aes(x = age, y = y, col = Category, group = sample), size = .01)+
+  geom_line(data = con_sample, aes(x = age, y = y, col = Category, group = sample), size = .01, alpha = .5)+
   geom_line(data = map_con, aes(x = age, y = y, col = Category), size = 1)+
@@
 
-cp3 <-bayesplot::mcmc_areas(as.array(con_m1), 
+cp3 <-bayesplot::mcmc_areas(as.array(con_m2), 
                       pars = c("b_target_categoryfruits", "b_target_categoryclothes", "b_target_categoryvehicles"), 
@@
 
-```{r plotS2, include = T, fig.align = "center", fig.cap = "A: Data plotted by age bin and category.
+```{r plotS2, include = T, fig.align = "center", fig.cap = "(A) Data plotted by age bin and category.
 Transparent dots show data from individual participants.
 Colored crosses show mean within age bin and category with 95\\% confidence intervals based on non-parametric bootstrap.
-B: Correct responses for age continously.
+(B) Correct responses for age continously.
 Colored lines show the mean of the posterior distribution of the model including category.

### 2020-02-21 paper/manuscript.Rmd
clean Rmd

@@
 
-#bf_ex1 <- bayes_factor(ex1_m1, ex1_m2, log = FALSE, maxiter = 5000)
-
 t1 <- loo_compare(ex1_m1, ex1_m2, criterion = "waic")%>%
@@
       ifelse( x <= plot_dens_ci%>%filter(age_group == "4")%>%pull(lci) | x >= plot_dens_ci%>%filter(age_group == "4")%>%pull(uci), "OFF", "ON"))))
-
-# post_plot <- ggplot(plot_dens, aes(posterior, group = age)) +
-#   geom_vline(xintercept = 1/3, lty=2, size = 1)+
-#   geom_area(data = densities_df %>% filter(ci_shade == "ON"), aes(x = x, y = y, fill = age), alpha = .5) + 
-#   geom_density(alpha = .5, size = 1)+
-#   labs(y="Probability density", x="Proportion correct")+
-#   theme_few() +
-#   xlim(-0.05,1.05)+
-#   guides(alpha = F)+
-#   scale_fill_colorblind(name = "Age")
 
@@
   geom_line(data = map_model_2, aes(x = age, y = y, col = condition), size = 1)+
-  #geom_smooth(data = ex2_data,aes(x = age_num, y= correct, col = condition), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5)+
   geom_pointrange(data = pex2_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+

### 2020-08-03 paper/manuscript.Rmd
update after revision

@@
 
-plot_dens_ci <- plot_post %>%
-  summarise(mode = estimate_mode(unlist(posterior)),
-            lci = hdi_lower(unlist(posterior)),
-            uci = hdi_upper(unlist(posterior)))
-
 plot_dens <- tibble(
@@
 )
-
-densities <- plot_dens %>%
-  group_by(age) %>%
-  do(., dens = density(.$posterior))
-
-densities_df <-
-  tibble(
-    age = c(rep('2', 512),
-            rep('3', 512),
-              rep('4', 512)),
-    x = c(densities$dens[[1]]$x, 
-          densities$dens[[2]]$x,
-          densities$dens[[3]]$x),
-    y = c(densities$dens[[1]]$y,
-          densities$dens[[2]]$y,
-          densities$dens[[3]]$y)
-  ) %>%
-  group_by(age)%>%
-  mutate (
-    ci_shade = ifelse( age == "3",
-                       ifelse( x <= plot_dens_ci%>%filter(age_group == "3")%>%pull(lci) | x >= plot_dens_ci%>%filter(age_group == "3")%>%pull(uci), "OFF", "ON"),
-                       ifelse(age == "2", ifelse( x <= plot_dens_ci%>%filter(age_group == "2")%>%pull(lci) | x >= plot_dens_ci%>%filter(age_group == "2")%>%pull(uci), "OFF", "ON"),
-      ifelse( x <= plot_dens_ci%>%filter(age_group == "4")%>%pull(lci) | x >= plot_dens_ci%>%filter(age_group == "4")%>%pull(uci), "OFF", "ON"))))
 

### 2020-08-03 paper/supplementary_material.Rmd
update after revision

@@
 library(bayesplot)
+library(ggridges)
 
@@
 ex2_data <- read_csv(file="../data/data_ex2.csv")
+
+ex1_adult_data <- read_csv(file="../data/adult_data_ex1.csv")
 ```
@@
 Results show that the conclusions - 3- and 4-year-olds, but not 2-year-olds, select the object from the same category above chance - are robust to changes in the prior width.
+
+# Experiment 1 - adults
+
+## Method
+
+We tested `r length(unique(ex1_adult_data$id))` adults recruited via Amazon Mechanical Turk (MTurk).
+Participants were restricted to have an US IP address and received payment equivalent to an hourly wage of ~ \$9.
+
+## Materials
+
+The setup and the procedure was the same as for children, with the following changes: Adults saw written instructions on top of the page instead of hearing pre-recorded audio files.
+The three objects were positioned at the bottom of the page (see Figure \ref{fig:adultsetup}).
+Furthermore, adults were tested in two additional categories with the following objects:
+
+* instruments: drum, flute, guitar, piano, trumpet, violin, xylophone
+* furniture: bed, chair, table, closet, drawer, sofa, lamp, stool
+
+As a consequence, each adult participant received a total number of six trials, one per category, in a randomized order.
+
+```{r adultsetup, include = T, fig.align = "center", fig.cap = "Left: Screenshot from the experimental setup for adults.", out.width="450px"}
+knitr::include_graphics("../figures/FigureS1.png")
+```
+
+## Results
+```{r, include = F}
+bf_t_adult <- ex1_adult_data %>%
+  group_by(id) %>%
+  summarise(correct = mean(correct)) %>%
+  summarise(correct = list(correct)) %>%
+  mutate(mean= mean(unlist(correct)),
+         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf)
+```
+
+```{r, include = F}
+# density plot
+plot_post <- ex1_data %>%
+  group_by(age_group,id) %>%
+  summarise(correct = mean(correct))%>%
+  summarise(correct = list(correct)) %>%
+  group_by(age_group) %>%
+  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 2000)[,"mu"])))%>%
+  select(-correct)
+
+plot_post_adult <- ex1_adult_data %>%
+  group_by(id) %>%
+  summarise(correct = mean(correct))%>%
+  summarise(correct = list(correct)) %>%
+  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 2000)[,"mu"])))%>%
+  select(-correct)
+
+plot_dens <- bind_rows(
+
+  tibble(
+  age = rep(c(2,3,4), each = 2000),
+  posterior = c(unlist(plot_post%>%filter(age_group == "2") %>% pull(posterior)),unlist(plot_post%>%filter(age_group == "3") %>% pull(posterior)),unlist(plot_post%>%filter(age_group == "4") %>% pull(posterior)))
+)%>%
+  mutate(age = as.character(age)),
+
+tibble(
+  age = "Adults",
+  posterior = c(unlist(plot_post_adult %>% pull(posterior)))
+)
+)%>%
+  mutate(age = factor(age, levels = c("Adults","4","3","2")))
+
+post_plot_adults <- ggplot(plot_dens, aes(y = age, x = posterior, fill = factor(stat(quantile))))+
+  stat_density_ridges(
+    geom = "density_ridges_gradient",
+    calc_ecdf = TRUE,
+    quantiles = c(0.025, 0.975)
+  ) +
+    labs(y="Age group", x="Proportion correct")+
+  geom_vline(xintercept = 1/3, col = "black", lty = 2)+
+  scale_fill_manual(values = c("#FF0000A0", "#A0A0A0A0", "#FF0000A0"))+
+  guides(fill = F)+
+  theme_few()+ 
+  scale_y_discrete()
+```
+
+To evaluate whether adults selected the object from the same category above chance (33% correct), we aggregated responses across test trials and ran one sample Bayesian t-tests.
+We found substantial evidence for this hypothesis (mean proportion correct = `r bf_t_adult%>%pull(mean)`, BF~10~ = `r bf_t_adult%>%pull(bf)`).
+Figure \ref{fig:figpost} shows the corresponding posterior distribution in comparison to the results with children reported in the main manuscript.
+Like children, adults tracked the topic guiding the interaction with the speaker and used it to make inferences about the referent of an ambiguous pronoun.
+
+```{r figpost, include = T, fig.align = "center", fig.cap = "Posterior probability distribution for the mean for each age group and for adults based on one sample Bayesian t-test.
+Grey regions indicate 95\\% credible intervals for each age group.", fig.width=6, fig.height=4, fig.fullwidth = TRUE}
+post_plot_adults
+```
 
@@
 The model without condition as a predictor (either as main effect or as an interaction with age) provided the best fit.
-In this model, the predictor for age was largely positive and different from zero ($\beta$ = `r fixef(exs_m3)[2,1]`, 95% CI = `r fixef(exs_m3)[2,3]` - `r fixef(exs_m3)[2,4]`) suggesting an increase in performance with age.
+In this model, the predictor for age was positive, but not reliably different from zero ($\beta$ = `r fixef(exs_m3)[2,1]`, 95% CI = `r fixef(exs_m3)[2,3]` - `r fixef(exs_m3)[2,4]`) suggesting a slight increase in performance with age.
 Figure \ref{fig:plotS1} shows that, in contrast to study 1, 3-year-olds had difficulties with this version of the task.

### 2020-08-12 paper/manuscript.Rmd
revision 1

@@
 abstract: |
-  In conversation, speech is almost always ambiguous, with this ambiguity resolved by context and discourse history (“common ground”).
-One important cue for disambiguation is the topic under discussion with a particular partner (e.g., “want to pick?” means something different in a conversation with a bluegrass musician vs.
+  In conversation, individual utterances are almost always ambiguous, with this ambiguity resolved by context and discourse history (common ground).
+One important cue for disambiguation is the topic under discussion with a particular partner (e.g., "want to pick?" means something different in a conversation with a bluegrass musician vs.
 with a book club partner).
-Here, we investigated 2- to 5-year-old American English-speaking children’s (N = 131) reliance on conversational topics with specific partners to interpret ambiguous or novel words.
-Children heard a speaker consistently refer to objects from a category without mentioning the category itself.
-In Study 1, 3- and 4-year-olds interpreted the ambiguous pronoun it as referring to another member of the same category.
-In study 2, 4-year-olds only interpreted the pronoun as referring to the implied category when talking to the same speaker but not when talking to a new speaker.
+Here, we investigated 2- to 5-year-old American English-speaking children’s (*N* = 131) reliance on conversational topics with specific partners to interpret ambiguous or novel words.
+In a tablet-based game, children heard a speaker consistently refer to objects from a category without mentioning the category itself.
+In study 1, 3- and 4-year-olds interpreted the ambiguous pronoun "it" as referring to another member of the same category.
+In study 2, only 4-year-olds interpreted the pronoun as referring to the implied category when talking to the same speaker but not when talking to a new speaker.
 Thus, children’s conception of what constitutes common ground in discourse develops substantially between age 2 and 5.
@@
 
-* Conversational topics organize discourse with specific partners
+* Conversational topics are used to organize discourse with specific partners
 * Children make inferences about conversational topics from 3 years onwards
 * From 4 years onwards, children see conversational topics as speaker specific
-* Discourse structures communicative interactions and thereby helps children to resolve ambiguity and learn language
+* Discourse can structure communicative interactions and thereby help children to resolve ambiguity and learn language
 
@@
 @bohn2019pervasive; @tomasello2008origins; @clark2009first].
-As discourse unfolds, interlocutors build up common ground - a set of shared knowledge and beliefs - that serves as a background against which new utterances are interpreted [@bohn2018common; @clark1996using].
-To use common ground in this way, children not only have to pay attention to what is said earlier but also with whom they have had this conversation and share this common ground.
-Children as young as 18 months old can use information from prior discourse to disambiguate words.
-Children typically interpret an ambiguous pronoun as referring to a previously mentioned object - even when it was absent from the scene [@ganea2007infants; @lidz2003infants].
-This behavior diversifies with age - 3 to 5-year olds use discourse context to interpret personal pronouns [@song2005s; @hartshorne2015development].
+One such information source is the social context of the utterance: as discourse unfolds, interlocutors build up common ground -- a set of shared knowledge and beliefs -- that serves as a background against which new utterances are interpreted [@bohn2018common; @clark1996using].
 
-Children can also rely on prior discourse to learn new words.
-For instance, when a speaker first states that they were hungry and then asks for a wug, 2-year-olds map the novel word onto an edible object [@sullivan2016discourse] Around age 3, children see the positioning of a novel word in discourse as a clue to its meaning [@horowitz2015young].
-And starting at age 4, children use discourse coherence - as expressed by connectives such as and or because - to interpret the meaning of a novel word [@sullivan2019discourse].
-Beyond nouns, children can also infer some aspects of verb meaning based on discourse context [@yuan2009really; @fisher2020developmental].
+Children’s interpretation of pronouns provides a good case to investigate their reliance on common ground because pronouns represent a referent that is mentioned or implied in the previous discourse.
+While children have difficulties with interpreting pronouns until about age 6 [@ambridge2011child; @matthews2009pronoun], recent evidence suggests that discourse structure helps children as young as 18 months to disambiguate pronouns.
+For example, children interpret the pronoun it as referring to a previously mentioned object -- even when it was absent from the scene [@ganea2007infants; @lidz2003infants].
+In a similar way, 3 to 5-year olds use discourse context to interpret personal pronouns [@hartshorne2015development; @song2005s].
+Beyond interpreting pronouns, children can also use discourse structure and common ground to learn the meaning of novel words[e.g.
+@horowitz2015young; @sullivan2016discourse; @yuan2009really].
 
-In almost all of these studies, the loose construct of “discourse” or “common ground” is operationalized as including the specific objects that had been explicitly mentioned.
-In conversation, however, discourse is often organized in terms of an overarching topic rather than a specific object.
-Further, this topic is rarely stated explicitly; instead it is typically inferred based on the content of utterances [@clark1996using].
-For example, when a child reports from a school trip “I saw an elephant, a tiger, a giraffe, and another one that was really scary” the parent can infer that another one refers to yet another animal.
+In most studies, the loose construct of "discourse" or "common ground" is operationalized as including the objects that have been explicitly mentioned.
+In conversation, however, discourse is often organized in terms of an overarching topic rather than a specific object referent.
+Further, this topic is not always stated explicitly but often has to be inferred based on the content of utterances [@clark1996using].
+For example, when a child reports from a school trip "I saw an elephant, a tiger, a giraffe, and another one that was really scary" the parent can infer that another one refers to yet another animal.
 One study comes closer to this conception of discourse topic.
 Akhtar [-@akhtar2002relevance] had children interact with an adult who repeatedly drew their attention to either the shape or the color of an object.
-When the adult later used a novel word to describe an object, children mapped the word on the property (color or shape) that was focused on during the preceding discourse.
-Children could solve this task by keeping track of which part of the objects they were jointly attending to (in the sense of looking at) with the speaker previously.
-Such visual anchoring, however, is not always possible because the topic may be absent and/or an abstract entity (such as “animals” in the example above).
-In this scenario the topic has to be inferred by reasoning about how the individual conversational bits relate to one another - how they are organized in conceptual terms.
+When the adult later used a novel word to describe an object, children seemed to infer that the word referred to the property (color or shape) that was emphasized during the preceding discourse.
+In that study, children could solve the task by keeping track of which part of the objects they were jointly attending to (in the sense of looking at) with the speaker previously.
+Such visual anchoring, however, is not always possible: the topic may be absent and/or an abstract entity (such as animals in the example above).
+In such cases, the topic has to be inferred by reasoning about how the individual conversational bits relate to one another -- how they are organized in conceptual terms.
 
 Another neglected aspect of discourse inference, at least in experimental work, is its social nature.
-Put differently, common ground built up during discourse is often partner-specific.
-Subsequent inferences therefore incorporate both the conversational topic(s), but crucially also social information - the participants engaging in the conversation.
-Children keep track of their conversational partners from a very young age [@bohn2018social].
-Saylor and Ganea [-@saylor2007infants] had 14 to 20 month old children play ball with two different experimenters.
-Depending on who later asked for “the ball”, children retrieved the object that featured in their previous play with that person.
-From 3 years onwards, children use partner specific referential expressions (referential pacts), both with adults and peers [@matthews2010s; @koymen2014young].
-Interestingly, speaker identity influences children’s interpretation of ambiguous utterances at an early point in language processing [@khu2019preschoolers; @san2015new].
+Common ground built up during discourse is often partner-specific, meaning that it is bound to this conversational partner and should not be assumed to be known by others.
+Common ground inferences therefore incorporate both conversational topic(s), but crucially also social information -- the participants engaging in the conversation.
+Children can keep track of their conversational partners from a very young age [@bohn2018social].
+In one relevant study, Saylor and Ganea [-@saylor2007infants] had 14 to 20 month old children play ball with two different experimenters.
+Depending on who later asked for "the ball", children retrieved the object that featured in their previous play with that person.
+From 3 years onwards, children use partner specific referential expressions (referential pacts), both with adults and peers [@koymen2014young; @matthews2010s].
+Interestingly, speaker identity influences children’s interpretation of ambiguous utterances at an early point in language processing [@khu2020preschoolers; @san2015new].
 However, these social inferences based on the identity of the conversational partners have rarely been studied in conjunction with discourse inferences.
-Thus, it is unclear whether discourse inferences involve social reasoning at all.
+Thus, it is unclear whether children’s discourse inferences involve social reasoning at all.
 
@@
 Second, we examine how their interpretation changes depending on the common ground shared with specific partners.
-In this way, we fill the gap between discourse and partner-specific reasoning.
+In this way, we fill the gap between discourse topic inferences and partner-specific reasoning.
 
-In Study 1, children interacted with a speaker who repeatedly mentioned objects from a particular category (e.g., horse and dog from the category animals).
-At a later time in the discourse the speaker used the ambiguous pronoun it in the context of three new objects - one object from the category mentioned earlier (e.g., a cat) and two other objects (e.g., a hat and a train).
+Our studies are presented as simple, storybook-like tablet games.
+In study 1, children interacted with a speaker who repeatedly mentioned objects from a particular category (e.g., horse and dog from the category animals).
+At a later time in the discourse, the speaker used the ambiguous pronoun it in the context of three new objects -- one object from the category mentioned earlier (e.g., a cat) and two other objects (e.g., a hat and a train).
+Thus, we operationalized the topic as the category label -- or the subordinate concept -- because children are aware of object categories starting from infancy [@bornstein2010development; @mareschal2003basic].
 We found that children from age 3 onwards reliably interpret the ambiguous pronoun as referring to the object from the same category.
@@
 All children were recruited from the floor of a Children’s museum in San José, California, USA.
-The population from which this sample is drawn is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status.
+The population from which this sample is drawn is characterized by diverse ethnic backgrounds (predominantly White, Asian, or mixed ethnicity) and relatively high levels of parental education and socioeconomic status.
 Parents consented to their children’s participation and provided demographic information.
@@
 for vehicles: car, truck, train, bus, airplane, boat and motorbike).
-The right panel of figure 1 shows all pictures used in the study grouped by category (see supplementary material for a list of the corresponding words).
+The right panel of Figure 1 shows all pictures used in the study grouped by category (see supplementary material for a list of the corresponding words).
 All utterances made by the different speaker animals were pre-recorded from native English speakers, with one speaker per animal.
@@
 Each of the objects belonged to a different category.
-Trials started with six training rounds, in which the speaker named one of the three objects displayed above them and asked the child to touch it (“Look at that, can you touch the X?”).
+Trials started with six training rounds, in which the speaker named one of the three objects displayed above them and asked the child to touch it ("Look at that, can you touch the X?").
 From one round to the next, the pictures changed but the three categories remained the same and the speaker consistently asked the child to touch the object from one category.
-For example, on the first training round, children saw a skirt, a horse, and a motorcycle and the speaker asked “Can you touch the motorcycle?” On the second training round, children saw a jacket, a dog, and a bus and the speaker asked “Can you touch the bus?”  After the six training rounds, children moved to the test and saw a new set of three (e.g.
+For example, on the first training round, children saw a skirt, a horse, and a motorcycle and the speaker asked "Can you touch the motorcycle?" On the second training round, children saw a jacket, a dog, and a bus and the speaker asked "Can you touch the bus?".
+After the six training rounds, children moved to the test and saw a new set of three (e.g.
 a hat, a cat and a train).
-However, instead of using a label, the speaker used an ambiguous pronoun to refer to one of the objects (“Look at that, can you touch it”).
+However, instead of using a label, the speaker used an ambiguous pronoun to refer to one of the objects ("Look at that, can you touch it").
 Children could identify the referent of the pronoun by assuming that the speaker continues to talk about objects from the same category as they did previously (vehicles in the example above).
@@
   geom_jitter(data = pex1_1,aes(x = age_num, y= correct), width = .00, height = .01, alpha = .5)+
-  geom_line(data = samples, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
+  geom_line(data = samples, aes(x = age, y = y, group = sample), alpha = .05, col = "grey")+
   geom_line(data = map_model, aes(x = age, y = y), size = 1)+
@@
 The dependent variable in all analyses was whether the object chosen at test was from the same category as the objects named throughout the training trials.
-All analyses were computed in R R [@R-base].
+All analyses were computed in *R* [@R-base].
 As a first step, we aggregated responses across test trials for each child and compared the proportion of correct responses to a level expected by chance (33% correct) within each age bin.
@@
 ## Discussion
-This study presents evidence consistent with the idea that starting around age 3, children make inferences about conversational topics.
-Based on hearing a speaker consistently refer to objects from a certain category, children interpreted the ambiguous pronoun it as referring to another object of the same category.
+This study presents evidence consistent with the idea that at least around age 3, children make inferences about conversational topics.
+Based on hearing a speaker consistently refer to objects from a certain category, children interpreted the ambiguous pronoun "it" as referring to an object of the same category.
 This suggests that children track common ground with a speaker not just in terms of remembering what has been talked about previously, but also in the form of an overarching topic that guides the conversation and allows predictions about what will be talked about in the future.
+In the supplementary material, we report an experiment that shows that adults make the same inference in a similar setup.
 
-In a follow-up, we tested whether the number of training trials affected children’s ability to make the inference.
+In a follow-up study, we tested whether the number of training trials affected children’s ability to make the inference.
 We contrasted one training trial with six training trials.
@@
 We also conducted an exploratory analysis (not pre-registered) to investigate whether the inference varied with the category that had to be inferred.
-Results point to differences between categories in that, for example, children were more likely to be correct when fruit is the target category compared to clothes.
+Results point to differences between categories in that, for example, children across the entire age range were more likely to be correct when fruit is the target category compared to clothes.
 Details of this analysis are presented in the supplementary material.
 We return to this point in the general discussion.
-In the next study, we continued with the same number of training trials and categories and focused on whether the inference found in Study 1 is partner specific.
+In the next study, we continued with the same number of training trials and categories and focused on whether the inference found in study 1 is partner specific.
 
@@
 
-Children carried out the same task as in Study 1.
-However, in half of the trials it was the same speaker who produced the ambiguous pronoun (“Can you touch it?”) as the speaker who presented the training trials and in the other half of the critical trials, it was a new speaker.
+Children carried out the same task as in study 1.
+However, in half of the trials it was the same speaker who produced the ambiguous pronoun ("Can you touch it?") as the speaker who presented the training trials and in the other half of the test trials, it was a new speaker.
 Because we found limited evidence that 2-year-olds make category-based discourse inferences in study 1, we only tested 3- and 4-year-olds in study 2.
-The preregistration for this study can be found at https://osf.io/5e9pk and the study materials are in the associated online repository.
+The preregistration for this study can be found at https://osf.io/5e9pk; study materials are in the associated online repository.
 
@@
 Data was collected in August and September of 2019.
-For details on population characteristics and ethical approval see Study 1.
+For details on population characteristics and ethical approval see study 1.
 
@@
 
-Study materials were the same as in Study 1.
+Study materials were the same as in study 1.
 
@@
 
-The general procedure was the same as in Study 1 except for the following changes.
-The speakers were introduced as showing children their *favorite* things (study 1: things they have at home).
+The general procedure was the same as in study 1 except for the following changes.
+The speakers were introduced as showing children their favorite things (in contrast to study 1, which used the category of things they have at home).
 We included this to focus children’s attention on the individual speakers.
-Conversely, when making a request, speakers said: “I like that.
-Can you touch [object/it]”.
+Conversely, when making a request, speakers said: "I like that.
+Can you touch [object/it]".
 The speaker change manipulation was implemented in the following way: After the six training trials, the speaker announced that they had to leave and left the scene by walking off the left edge of the screen.
@@
 This measure served to emphasize that the different speaker was new to the scene and therefore unfamiliar with the preceding discourse.
-If the speaker was the same as during the training trials, children could infer the referent of the pronoun in the same way as in Study 1.
+If the speaker was the same as during the training trials, children could infer the referent of the pronoun in the same way as in study 1.
 However, if the speaker changed, no such inference was licenced if children assumed that the discourse topic is specific to a speaker.
 
-Selection and positioning of objects and categories was randomized in the same way as in Study 1.
+Selection and positioning of objects and categories was randomized in the same way as in study 1.
 Each child received four test trials, two with the same and two with a different speaker returning, in an order randomized for each child.
@@
   geom_jitter(data = pex2_1,aes(x = age_num, y= correct, col = condition), width = .00, height = .01, alpha = .5)+
-  geom_line(data = sample2, aes(x = age, y = y, col = condition, group = sample), size = .025)+
+  geom_line(data = sample2, aes(x = age, y = y, col = condition, group = sample), alpha = .05)+
   geom_line(data = map_model_2, aes(x = age, y = y, col = condition), size = 1)+
@@
 We compared a base model including only age as a fixed effect to models including speaker type, either as a main effect or as an interaction with age.
-Models were fitted and compared in the same way as in Study 1.
+Models were fitted and compared in the same way as in study 1.
 Models now also included random slopes for condition.
@@
 We studied how children use conversational topics with specific partners to interpret ambiguous pronouns.
-Our results suggest that by age 3, children infer the topic of a conversation based on preceding discourse in order to identify the referent of an ambiguous pronoun.
-Moreover, starting at age 4, children also associated this inference with specific partners.
+Our results suggest that, by age 3, children can identify the referent of an ambiguous pronoun by inferring the topic of a conversation based on preceding discourse.
+Moreover, starting around age 4, children also associated this inference with specific partners.
 These findings illustrate how children can leverage the structure of the social interactions in which conversations take place to disambiguate utterances.
 
-We did not find substantial evidence that children under the age of 3 are able to make the inference in Study 1.
-However, we suspect that this result is not due to younger children lacking the necessary inferential abilities but due to difficulties with processing the information the inference was based on.
-In an exploratory analysis we compared children’s performance in the different categories.
-We found that children across the age range were more likely to make the inference when fruit was the target category compared to when it was clothes.
-Animals and vehicles resulted in intermediate levels of performance (details for this analysis are reported in the supplementary material).
+Our findings speak to preschoolers’ ability to reason about conversational topics.
+Around age 3, children highlight the relevance of their utterance to the prior discourse by adjusting the informativeness of their referring expressions.
+For example, in English, children use a pronoun instead of a noun phrase to mark the topic [@matthews2006effect; see also @chen2011tuning; @de2009experimental; @kurumada2009acquisition for cross-linguistic evidence].
+However, these studies do not necessarily show whether children consider partner-specificity aspect of topic-marking: topic-marking is necessary with the conversational partners who are familiar with the topic, but not with new conversational partners who do not share this common ground.
+In fact, it has been shown that when children interact with a new partner, who is unaware of the topic, their referring expressions oftentimes do not change [@bannard2017s].
+Thus, our findings expand these and suggest that young children not only track the topic of a conversation but also pay attention to with whom they share this common ground.
+
+We did not find substantial evidence in study 1 that children under the age of 3 are reliably able to infer the topic under discussion and use it to resolve ambiguity.
+However, we suspect that this result is not due to a lack of inferential abilities; instead, we suspect that it follows from difficulties with processing the information the inference was based on.
+In an exploratory analysis we compared children’s performance with the different categories (see supplementary materials).
+We found that children across the entire age range were more likely to make the inference when *fruit* was the target category compared to when it was *clothes.* *Animals* and *vehicles* resulted in intermediate levels of performance.
 On the one hand, younger children might not conceptualize e.g.
@@
 On the other hand, the individual objects in some categories might be less familiar to children and provide limited evidence for the category itself.
-From a developmental perspective, this pattern suggests that the main loci of change are children’s vocabulary and conceptual abilities.
+From a developmental perspective, this pattern suggests that the main loci of change might well be children’s vocabulary and their conceptual abilities, rather than their understanding of conversational topics.
 Of course, the exploratory nature of these results needs confirmation in future studies.
@@
 While 3-year-olds tended to choose the object from the same category for both speakers (see Figure \ref{fig:fig3}), 4-year-olds only did so when the speaker was the same.
-The lack of sensitivity to speaker identity seems to conflict with earlier work which found speaker-specific communicative adjustment in younger children [@bohn2018social; @saylor2007infants].
-However, in these studies, speakers only communicated about objects that were communicated about before.
+This lack of sensitivity to speaker identity seems to conflict with earlier work which has found speaker-specific communicative adjustment in younger children [@bohn2018social; @saylor2007infants].
+However, in these studies, speakers only communicated about specific objects that were communicated about before.
 Children could identify the referent by remembering which speaker had communicated about which object.
-In our study, the objects at test had never been communicated about before.
+In our study, the objects at test had never been mentioned before.
 The connection to the prior discourse only lay in the relation of the objects to the topic under discussion.
@@
 
-Our setup provides an interesting and novel way to study the interplay between linguistic knowledge (necessary to make inferences about categories), conceptual knowledge (necessary to make inferences about additional category members) and social cognition (necessary to determine whether inferences are licensed).
+Our setup provides a method to study the interplay between linguistic knowledge (necessary to make inferences about categories), conceptual knowledge (necessary to make inferences about additional category members) and social cognition (necessary to determine whether inferences are licensed).
 This interplay opens up questions about the processes involved in balancing and integrating these different information sources.
@@
 For example, Bohn and colleagues [-@bohn_tessler_merrick_frank_2019] used a Bayesian model of pragmatic reasoning [@frank2012predicting] to formalise and predict the process by which children integrate information from common ground with information that is provided by an utterance in the moment.
+Such integration mechanisms could in principle be extended to make use of discourse topics as well [@luong2013parsing; @rohde2014markers].
 
 An open question is how these results generalize outside the scope of the present context with data collected using tablet computers in a western, affluent study population.
-Regarding the first point, Frank and colleagues [-@frank2016using] found similar results when children were tested in a communication task either on a tablet or in a live interaction.
-Regarding the second point, there are relatively few cross-cultural developmental studies on pragmatic inference, with some finding similar [@zhao_ren_frank_zhou_2019] and others different [@fortier_kellier_flecha_frank_2018] trajectories compared to western, affluent settings.
+Regarding the first point, Frank and colleagues [-@frank2016using] found similar results when children were tested in word recognition and word learning  tasks either on a tablet or in a live interaction.
+Thus, we do not expect that the tablet format specifically should compromise the validity of the paradigm, but further work will be necessary to confirm that experimental findings apply to naturalistic conversational interactions.
+Regarding the second point, the cross-cultural generalizability of experimental pragmatics of the type we studied here is an open challenge for future research.
+While some semantic/pragmatic phenomena do appear to be general [@katsos2016cross], there are relatively few cross-cultural developmental studies on inference specifically, with some finding similar [@su2013scalar; @su2015interpretation; @zhao_ren_frank_zhou_2019] and others different [@fortier_kellier_flecha_frank_2018] trajectories compared to western settings.
 
@@
 Here we show that children can use these processes to identify the referent of an ambiguous utterance.
-Because referent identification is a first step in language learning, we expect the same processes to also be recruited for language learning.
+Because referent identification is a first step in language learning, we expect the same processes may also be recruited for language learning.
 

### 2020-08-12 paper/supplementary_material.Rmd
revision 1

@@
   geom_jitter(data = pexs_1,aes(x = age_num, y= correct, col = condition), width = .00, height = .01, alpha = .5)+
-  geom_line(data = sample2, aes(x = age, y = y, col = condition, group = sample), size = .025)+
+  geom_line(data = sample2, aes(x = age, y = y, col = condition, group = sample), alpha = .05)+
   geom_line(data = map_model_2, aes(x = age, y = y, col = condition), size = 1)+
@@
   geom_hline(yintercept = 1/3, lty=2)+
-  geom_line(data = con_sample, aes(x = age, y = y, col = Category, group = sample), size = .01, alpha = .5)+
+  geom_line(data = con_sample, aes(x = age, y = y, col = Category, group = sample), alpha = .01)+
   geom_line(data = map_con, aes(x = age, y = y, col = Category), size = 1)+
